### 2019-12-08 article_draft.tex
Initial Copy of paper

\documentclass{article}
\usepackage[margin = 0.5in]{geometry}
\usepackage[table]{xcolor}
\usepackage{amsmath,amsthm,amsfonts,dsfont,mathtools,float,setspace, booktabs, algorithm,tcolorbox,xparse,colortbl,longtable,array,multirow,wrapfig,float,pdflscape,tabu,threeparttable,threeparttablex,makecell,natbib}
\usepackage[normalem]{ulem}
\usepackage[english]{babel}
\bibliographystyle{plainnat}

\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
\newtheorem{theorem}{Theorem}
\newtheorem{refproof}{Proof}
\author{Adam Elder}
\newcommand{\bs}{\boldsymbol}
\newcommand{\sh}{\textcolor{red}}
\newcommand{\pr}{\text{Pr}}
\newcommand{\indep}{\raisebox{0.05em}{\rotatebox[origin=c]{90}{$\models$}}}
\usepackage[mathscr]{euscript}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\definecolor{Gray}{gray}{0.95}
\newcommand{\rvo}{X}
\newcommand{\norm}{f}
\newcommand{\rvoo}{x}
\newcommand{\disto}{P}
\newcommand{\rvv}{Y}
\newcommand{\distv}{Q}

\begin{document}
\section{Introduction}

\sh{It is often of interest if any of a large number of candiate measurements are useful in predicting some outcome}. In genetics many candidate snips and their association with some outcome is often of interest. Many studies take measurements on a large number of biomarkers to see if any can predict medical outcomes such as the presence  or progression of a disease. While interest in the existence of an association between two variables has existed for years, the vast number of potential predictors creates new statistical challenges.  In the univariate case, once a measure of association is selected, standard approaches exist to construct asymptotically valid (and sometimes optimal) tests \citep{neyman_jerzy_ix._1933}. In this setting, a test is considered optimal if it achieves the largest power for every alternative compared to every other test with the same type one error.  However, as mentioned above, scientists are often interested if any of a multitude of covariate are associated with the outcome of interest.  Even in the case with two covariates, a test with the above optimal property no longer exists.

To illustrate this, consider two tests with equal type one error rates. Both test the null that both of the two association measures $\psi_1$, $\psi_2$ are zero. The first test focuses only on the $\psi_1$ and the second test considers both $\psi_1$ and $\psi_2$.  When the $\psi_1$ is non-zero $\psi_2$ is zero the first test can outperform all other tests.  Conversely when only $\psi_2$ is non-zero the first test will be outperformed by the second test.  Additionally in this setting, the power of these tests will be tied to the covariance between the covariates (a problem that did not exist for a single covariate).  These two factors make it difficult to define a test that performs well across all possible alternatives.  
% Even coming up with optimal properties for tests becomes difficult since it must make assumptions about the true data-generating mechanism.

Work with \textcolor{red}{Simultaneous hypothesis testing}
%Tests capable of testing the union of multiple hypotheses simultaneously
began with Tukey in 1953 \citep{miller_simultaneous_1981}.  Previous work by Bonferroni was used by \citep{dunn_estimation_1959,dunn_multiple_1961} to come up with some of the first multiple hypothesis testing procedures.  Further improvements were proposed by \citep{hochberg_sharper_1988,holm_simple_1979,s._holland_improved_1988}.  Bonferroni-based correction procedures have the advantage of being easy to apply to already existing tests, while guaranteeing family-wise error control. However, these tests suffer from low power, especially in cases where the probability of rejecting each hypothesis is highly correlated.

Newer procedures \citep{donoho_higher_2004} and \sh{add other papers here} attain improved power compared to Bonferroni-based methods, but often rely on asymptotics to obtain these results, and don't account for the irregularity of the estimator on which their test is based.  Subsequent work \citep{mckeague_adaptive_2015, pan_powerful_2014, xu_adaptive_2016} addressed these concerns by accounting for the adaptive nature of the considered tests. Still, these newer tests are restricted to testing a particular hypothesis, 
% and test statistic used to test the hypothesis. 
must make assumptions about the data-generating mechanism to obtain theoretical guarantees.

In this article a test is proposed that works across a wide variety of data generating mechanisms and parameters of interest, but also achieves comparable power to tailor made procedures. Section \ref{sec:Working Examples} describes the data generating mechanisms that are considered to evaluate the performance of the test and the competing test made for the given data generating mechanism.  Section \ref{sec:prop_test_proc} proposes the testing procedure. \sh{Add other sections here}  
%This is done using a two step procedure.  In the first step, the limiting distribution of the entire vector of parameter estimates is estimated.  Next, an adaptive procedure selects a transformation of the vector of parameter estimates and distribution which is guessed provides the best power.  P-values are obtained using a permutation procedure.

\section{Working Examples}
\label{sec:Working Examples}
Let $\rvo_1, \dots, \rvo_n$ be independent identically distributed draws from some distribution $\disto$, and let $\boldsymbol{\rvo} = \{\rvo_1, \dots, \rvo_n\}$ . Let $\rvo_i = \left(Y_i, W_{1 i}, \dots, W_{d i}\right), i \in \{1, \dots n\}$ where $Y$ is the outcome of interest, and each $W$ is a covariate. Let $\psi_1 = \Psi_1(\disto), \dots, \psi_a = \Psi_a(\disto)$ be measures of association between $Y$ and some combination of the $W_j$'s.  While the results found in this article are valid for any integer $a$, for the remainder of this article assume $a = d$, the number of covariates. Also, let $\psi_j$ correspond to a measure of association between $Y$ and $W_j$.  The null hypothesis for our test will be the strong null:

\begin{align*}
H_0: \psi_1 = \psi_2 = \dots = \psi_a = 0 \hspace{0.1cm}\text{  versus  } \hspace{0.1cm} H_1: \psi_j \neq 0 \text{ for some } j \in \{1, \dots, a\}.
\end{align*}
Last, let $\mathscr{M}$ denote the set of all possible distributions.  Define $\mathscr{M}_0 = \left\{ \disto \in \mathscr{M} : H_0 \text{ holds}  \right\}$

\subsection{Correlation Parameter}
We will compare our method to both a simple bonferroni correction method, and the method described in \citep{zhang_comment_2015}.  The settings considered will be the same as the firs setting in \citep{mckeague_adaptive_2015}.  The parameter of interest, $\psi_j(P)$ will be the correlation between the outcome of interest and the $j$'th covariate.

The vector of covariates in this setting will be generated from a normal distribution with mean zero and a variance covariance of $\Sigma$ with $\Sigma_{ij}$ equal to $\rho$ when $i \neq j$ and equal to 1 when $i = j$, and .  Three different models are considered.  Three different models for the outcome of interest ($Y$) will be considered. Letting $\varepsilon \sim N(0, 1)$ and be independent of $X$, the first model let $Y = \varepsilon$, the second has $Y = X_1 / 4$, and third has $Y = \sum_{k = 1}^10 \beta_k X_k + \varepsilon$ where $\beta_k = 0.15$ for $k = \{1, \dots, 5\}$, and $\beta_k = -0.1$ for $k = \{6 \dots 10\}$.   in which Sample sizes of $100$ and $200$, dimensions of $10$, $50$, 100, 150, and 200, and $\rho$ of  $0, 0.5$, or $0.8$ will be considered,

\subsection{Missing Data Example}
In the second example, $Y$ is binary, $\Delta$ is a missingness indicator, and each $W_j$ is a covariate of interest.  When $\Delta = 0$ we don't observe $Y$.  The identifying assumption is $\Delta \indep Y | W$.  The parameter of interest is the risk ratio,
\begin{align*}
	\Psi_{j}\left(P^{\text{full}}\right) &= \frac{\text{Cov}\left(\log\left(Pr \left(Y = 1 |  W_j\right)\right), W_j\right)}{\text{Var}(W_j)}.\\
\end{align*}
Using the identifying assumption, the observed data parameter is:
\begin{align*}
	\tilde{\Psi}_{j}\left(P^{\text{obs}}\right)&= \frac{\text{Cov}\left(\log\left(E\left[Pr \left(\Delta  Y = 1 | \Delta = 1, W = W\right) |  W_j\right]\right), W_j\right)}{\text{Var}(W_j)}\\
\end{align*}

\textcolor{blue}{Right now, it seems that the time for a single test is quite a bit larger for this test than it is for the correlation test (which is reasonable), though it may speed up if Superlearner can be improved.  I am thinking of using similar simulation settings as was used before.}  There will be a single mechanism for the missingness, but it will be variable if the mechanism is known.  There will be three settings for between $W$ correlation.  All $W$ will be equally correlated, with $\rho = 0, 0.3$, or $0.7$.  Dimension will \textcolor{blue}{(depending on computation time)} be $10, 50, 100$ and possibly $200$.

There will be three settings for the $\beta$'s in the data generating model:
\begin{align*}
    \log(Pr(Y = 1 | W)) = \beta_0 + W^\top \beta
\end{align*}
In one setting $\beta = 0$.  In the second only one or two parts entries of $\beta$ will be non-zero.  In the last setting, many of the entries of $\beta$ will be non-zero (possibly $70$ or $80$ percent of the entries).

\subsection{Marginal Structural Model}
For this marginal structural model, we are interested in if the average treatment is modified by any covariates.  The marginal structural model for each $W_j$ is defined by
\begin{align*}
\text{logit}\left(Pr(Y^{(a)} = 1 | w)\right) = \beta_0 + \beta_1 a + \beta_2 w_j + \beta_3 w_j a
\end{align*}

\begin{align*}
(\beta_0^*, \beta_1^*, \beta_2^*, \beta_3^*) = \text{argmin}_{\beta_0, \beta_1, \beta_2, \beta_3}\int\left(\text{logit}\left(Pr(y^{(a)} = 1\right) - (\beta_0 + \beta_1 a + \beta_2w_j + \beta_3 w_j a) \right)^2 dP(y^{(a)}, w, a)
\end{align*}
The parameter of interest is $\beta_3^*$
\textcolor{blue}{The other $W_j$'s are included in the analysis and are marginalized over, but are not part of the defined model.} I am planning on using the same simulation settings as above, but also including non-changing effects for $a$, but am open to other ideas.
% \subsection{\sh{Something else possibly Tim's parameter (has something to do with survival)}}
% In this setting, the outcome is \sh{some measure of health}, and the covariates correspond to genetic measurements $W_{ij}$ that take value one for \sh{genes or snips which dont match the reference genome} and zero for those that do match. It is of interest if the measured outcome is associated with these genetic measurements.

\section{Proposed testing procedure}
\label{sec:prop_test_proc}
Denote the estimator of the $\boldsymbol{\psi}$ by $\hat{\boldsymbol{\Psi}}(\boldsymbol{\rvo})$, let $\hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$, and suppose that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to some distribution $\distv$ when $\disto \in \mathscr{M}_0$.  Any test of $\disto \in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0 \subset \mathbb{R}^d$. The region $\Theta_0$ can be chosen so the probability of rejection under the null will be controlled asymptotically:
\begin{align}
	Pr(\distv \in \Theta_0) = 1 - \alpha \text{ under } H_0. \label{eqn:alpha_rej}
\end{align}
Equation \eqref{eqn:alpha_rej} is satisfied by many different acceptance regions, but for now, consider an acceptance region that is a $\ell_2$ ball centered at the origin. To define the region, a radius such that \eqref{eqn:alpha_rej} is satisfied can be selected.

To find this radius, one could solve the following equation:
\begin{align*}
	r_\alpha = \min\left\{r : Pr(||\rvv||_2 \leq r) \geq 1 - \alpha \right\} \text{ where } \rvv \sim \distv 
\end{align*}
Above we have converted a problem of defining a region to a problem of defining a real value by using a norm.  This same idea can be used when defining a test:
\begin{align*}
	\text{reject } H_0 \text{ if } ||\sqrt{n} \hat{\boldsymbol{\psi}}||_2 \geq r_\alpha.
\end{align*}
Similarly, $Pr(||\rvv||_2 \geq ||\sqrt{n} \hat{\boldsymbol{\psi}}||_2)$ would provide a p-value. The quantity could also be used for a test, and since we know $Pr_Q(||\rvv||_2 \geq ||\sqrt{n} \hat{\boldsymbol{\Psi}}(\rvo)||_2)$ will be uniformly distributed on $(0, 1)$ asymptotically under the null, we can reject $H_0$ whenever this value is less than $\alpha$.

% As an example, a test is defined by a norm $p$ and level $\alpha$ which define the cutoff value;
% \begin{align*}
% 	c_{p, \alpha} = \min\left\{c : \frac{1}{B}\sum_{b = 1}^B I\left\{||\boldsymbol{Z}_b||_p \leq c\right\} \leq \alpha\right\},
% \end{align*}
% where $Z_1, \dots, Z_B$ are draws from $Q$. Reject the null if $||\sqrt{n}\hat{\boldsymbol{\psi}}||_p > c_{p, \alpha}$.

\begin{figure}
	\centering
	\includegraphics[width = \linewidth]{figure_code/pwr_cmp.jpeg}
	\caption{Plots of 100 observations from a limiting distribution of a hypothetical vector of parameter estimators in $\mathbb{R}^2$ (A) under the null, (B) under an alternative with $\psi_1 = 0, \psi_2 \neq 0$, and (C) under an alternative with $\psi_1, \psi_2 \neq 0$. The 95\% quantiles for the data based on the max (blue) and $\ell_2$ (red) norms under the null are given in all three panels. If a test statistic fell within the purple regions the test would fail to reject $H_0$ if the $\ell_\infty$ norm was used, but would reject $H_0$ if the $\ell_2$ norm was used.  The converse is true for the green regions.  Depending on the alternative, the $\ell_\infty$ norm (B) or the $\ell_2$ norm(C) will achieve higher power.}
	\label{fig:figure1}
\end{figure}

\subsection{Creating a rejection region using a function}
% Note that above while our test was defined by rejecting or accepting based on if $\sqrt{n}\hat{\psi} \in \Theta_0$, we can also think about defining our test decision based on if some function, say $\Gamma_P(x, ||\cdot||)$ that maps from a value and distribution in $\mathbb{R}^d$, and a norm $||\cdot||$ to a real value is greater than zero.
As alluded to above, any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x, ||\cdot||)$ that maps from a value and distribution in $\mathbb{R}^d$, and a norm $||\cdot||$ to a real value.  To obtain p-values and define the test, one compares $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\distv(\rvv, ||\cdot||)$ where $\rvv$ is a random variable with distribution $\distv$. Trivially, this function could be defined as: $\Gamma_\distv(x, ||\cdot||) = I\{x \in \Theta_0(\distv)\}$.  However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.

In the example above, $\Gamma_\distv(x, ||\cdot||) = Pr_\distv\left(||\rvv|| \geq ||x|| \right)$.  For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv, ||\cdot||)$ is uniformly distributed on $(0, 1)$.  However, for other $\Gamma$, this may not be the case. Consider 
\begin{align*}
	\Gamma_\distv(x, ||\cdot||) &= Pr_\distv(||\rvv^* + x|| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv|| < c) \geq 0.8 \} \text{ and } \rvv^* \overset{d}{=} \rvv.
\end{align*}
In this scenario, the test can be carried out by comparing $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\distv(\rvv, ||\cdot||).$

% This test statistic was then compared to the estimated limiting distribution of the test statistic under the null.  The key components of this test were to create a real valued summary of the observed test statistic, and compare this test statistic to draws of the test statistic under the null.  In the previous example, the test statistic was the quantile of the $\ell_2$ norm of our vector of parameter estimates.  We already know the distribution of this statistic is uniform from zero to one under the null, so calculating the p-value is trivial.

% However, we could consider other test statistics.  One example would be the estimated power of an observation is from the $80\%$ quantile of the limiting distribution under the null.  Here, while smaller values indicate more evidence against the null, the distribution of this test statistic is not as straightforward.  While more difficult, the distribution of this test statistic can be be estimated using a bootstrap.  We can take a single observation from our estimated limiting distribution of $\sqrt{n}\hat{\psi}$ and then find its multiplicative distance from the $80\%$ quantile under the $\ell_2$ norm.  This can be done many times to create a limiting distribution of our test statistic.  A p-value can then be obtained by comparing the test statistic to the bootstrapped test statistics.

While this way of defining a test allows for many different specifications, it does require that the user chooses a norm.  Figure \ref{fig:figure1} shows that the power a test achieves can depend on the norm chosen.  Consider the case when $d = 2$ and $100$ draws are taken from $Z$.  Cutoffs can be obtained by transforming these data (using the $l_p$ norm) and taking the 95\% quantile of this transformed data. The perimeter of the acceptance region when using the $\ell_2$ and $\ell_{\infty}$ norm are given in red and blue respectively. If $\sqrt{n}\hat{\boldsymbol{\psi}}$ falls within any of the purple regions, using the $\ell_\infty$ norm would result in failing to reject $H_0$ and using the $\ell_2$ norm would result in rejecting $H_0$.  The converse is true for the green regions.

\subsection{Adaptive selection of a norm}
In the previous section it was shown that a test can be defined by choosing a summarizing function and norm. However, the choice of norm influences the power of the test. In most scenarios it will not be clear a priori which norm will have maximal power for the true alternative. The procedure proposed in this section adaptively selects a norm and it will be shown that this procedure achieves greater power than a test with a fixed norm, while maintaining type 1 error control.

This is achieved by defining a $\Gamma$ similar to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.  For example, if we had $p$ different norms, $\norm_1, \dots, \norm_p$ and some summary function $\Gamma_\distv(x, ||\cdot||)$, we would define the adaptive version of $\Gamma$ as

\begin{align*}
	\Gamma^*_\distv(x) = \max\left\{\Gamma_\distv(x, \norm_1), \Gamma_\distv(x, \norm_2), \dots, \Gamma_\distv(x, \norm_p)\right\}.
\end{align*}
\textcolor{blue}{This will could be the min if smaller values indicate larger distances away from the norm (such as p-values).}

In many cases, it will be difficult to obtain the exact distribution of $\Gamma_\distv^*(\rvv)$. However, because this distribution is only a function of $\distv$, obtaining very good approximations of $\Gamma_\distv^*(\rvv)$ is possible by taking many draws from $\rvv$, both to estimate the function $\Gamma$ and to estimate $\Gamma^*_\distv(\rvv)$ .

% Let $g_1, \dots, g_k$ be a list candiate norms, and let $\boldsymbol{Z}_1, \dots, \boldsymbol{Z}_B$ and $\boldsymbol{V}_1, \dots, \boldsymbol{V}_B$ independent draws from $Q$.  For each of the possible norms, let a p-value be defined using the following quantity:

% \begin{align*}
% s_{p}\left(\sqrt{n}\hat{\boldsymbol{\psi}}, \boldsymbol{Z}_1, \dots, \boldsymbol{Z}_B\right) = \frac{1}{B}\sum_{i=1}^B I\left\{g_p\left(\sqrt{n}\hat{\boldsymbol{\psi}}\right)  \leq g_p(\boldsymbol{Z}_i)\right\}
% \end{align*}

% Using the $c_{p, \alpha}$ defined earlier, it is possible to obtain estimates of power for each norm for any assumed vector of parameters:
% \begin{align*}
% \hat{\omega}_{\alpha, p}(\boldsymbol{h}) = \frac{1}{B} \sum_{i=1}^B I\left\{g_p\left(\boldsymbol{h} + \boldsymbol{V}_i\right) \geq \hat{c}_{\alpha, p}\right\}
% \end{align*}
% The last quantity considered is the multiplicative distance the vector of parameter estimates is from a vector in the same direction which obtains a certain power:
% \begin{align*}
% \hat{r}_{\alpha, p}(a) = \min\left\{r : \hat{\omega}_{\alpha, p}(r \times \sqrt{n}\hat{\boldsymbol{\psi}}) > a\right\}
% \end{align*}
% As described above, there are a multitude of ways to evaluate the performance of the various norms.  Let $f_p(x_1, \dots, x_k)$ be the function that takes the observed data and a norm and returns a measure of the norm's estimated performance given the observed data. $f$ could be $s_p$, $\hat{\omega}_{\alpha, p}$, $\hat{s}_{\alpha, p}$, or some other function.  Let $p^*$ be the index of the ``optimal'' norm.  What is optimal depends on $f$.  If $f$ is the p-value measure $s_p$ then the optimal norm minimizes the $p-value$.  However if instead $f$ is estimated power, then the optimal norm maximizes estimated power.

% Define the test statistic $\hat{t}$ as 
% \begin{align*}
% \hat{t} = f_{p^*}(\boldsymbol{x}_1, \dots, \boldsymbol{x}_n)
% \end{align*}
% While it is not necessary to do this, the same $f$ used for norm selection will be used to define our test statistic.

\subsection{Obtaining the null distribution}
\label{ssec:obtaining_null}
The above procedure requires knowledge of the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ when $P \in \mathscr{M}_0$.  To obtain an estimate of this limiting distribution, assume the vector of parameter estimates $\hat{\boldsymbol{\psi}}$, converges to a normal distribution with an estimable variance covariance matrix when properly centered and normalized. Also assume each of the estimators $\hat{\boldsymbol{\psi}}_1, \dots, \hat{\boldsymbol{\psi}}_d$ of $\boldsymbol{\psi}_1, \dots, \boldsymbol{\psi}_d$ is asymptotically linear.  That is for each $j \in \{1, \dots, d\}$:
\begin{align*}
\hat{\psi}_j = \psi_j + \frac{1}{n}\sum_{i=1}^n D_j(\boldsymbol{x}_i) + o_p(1/\sqrt{n}) \text{ for some function } D_j
\end{align*}
When there is a fixed number of covariates, the Cramer-Wold device can be used to show that the vector of parameter estimates is asymptotically normal with mean zero, and variance covariance matrix given by $\Sigma = E_{\disto_0}\left[D(\rvo)^\top D(\rvo)\right]$:

\begin{align*}
    \sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right) \xrightarrow{d} Z \sim N\left(0, \Sigma\right)
\end{align*}
Under $H_0$, $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges to $Z$, and one can approximate $\Sigma$ with $\widehat{\Sigma} = \frac{1}{n}\sum_{i = 1}^n D(\boldsymbol{x}_i)^\top D(\boldsymbol{x}_i)$.  Thus, in practice we will use an estimate of $\distv$, $\hat{\distv}$ which is distributed $N(0, \widehat{\Sigma})$ in place of $\distv$, and the random variable $\hat{\rvv}$ with distribution $\hat{\distv}$ in place of $\rvv$.  Thus, the test statistic will be $\Gamma_{\hat{\distv}}(\sqrt{n} \hat{\boldsymbol{\psi}})$ and will be compared to $\Gamma_{\hat{\distv}}(\hat{\rvv})$.

\subsection{Using a permutation test for the test statistic}
While the above approach will work asymptotically, there can be issues for small sample sizes.  To avoid inflated type one error, a permutation based test can be used.  Here, $\hat{\distv}^\#$ is used to define $\Gamma$, and the test will compare $\Gamma_{\hat{\distv}}(\sqrt{n} \hat{\boldsymbol{\psi}})$ to $\Gamma_{\hat{\distv}}(\rvv^\#)$. To determine $\hat{\distv}^\#$, the $Y$'s from the observed data are permuted before calculating $\widehat \Sigma$.  Draws from $\rvv^\#$ are taken by permuting all of the $Y$'s of the observed data.  \textcolor{blue}{There are a few more complications here that need to be figured out.}

\sh{\subsection{Summary of how simulations are run}}

\section{Simulation Study}
\label{sec:sim_stdy}
\subsection{Correlation}
% A wide variety of simulation settings are considered in this section to show the breath of settings in which the adaptive test can be used.  The first setting considers independent draws from a random vector with mean zero and variance-covariance matrix $\Sigma$.  The measure of association between $Y$ and each covariate will be $\text{Cov}(Y, W_{j})/\text{Var}(W_j)$.  The dimension of the vector, denoted $d$ takes values $10, 50$, and $200$.  The number of correlated covariates will be zero, one, or $0.1, 0.2$, or $0.6$ of all the correlated covariates.  The correlation between each of the covariates will be either $0$ or $0.5$.  The sample sizes considered are $100$ and $500$.

\sh{
\begin{enumerate}
	\item Two-Phase sampling Scheme of correlation
	\item Marginal structural model example.
\end{enumerate}
All three examples will come with simulation results in the form of figures.  Not sure how many figures to use or what sample size(s) to use.
}

\section{Data Application}

\sh{\begin{enumerate}
	\item Data from Peter Gilbert
\end{enumerate}
}

\section{Discussion}

\section{Appendix}

\subsection{Test Consistency}
\label{sec:test_cnsty}

\begin{theorem}
\label{thm:cnst}
Assume the performance metric of choice is $\hat{r}_{\alpha, p}(a)$, and each the norms $g_a$ considered have the following properties: 
\begin{align}
& \text{for } x \in \mathbb{R}^d, \text{ and } s, l > 0, s \cdot \max({\boldsymbol{x}}) \leq g_a(\boldsymbol{x}) \leq l \cdot d \cdot \max({\boldsymbol{x}}) \label{eqn:nrm_bounds}\\
& \text{for } s \leq 1, l \geq 1, g_a(s \cdot \boldsymbol{x}) \leq g_a(\boldsymbol{x}) \leq g_a(l \cdot \boldsymbol{x}) \label{eqn:linegrowth}
\end{align}
Then for all $P \not \in \mathscr{M}_0$ 
\begin{align*}
	Pr \left(\frac{1}{B}\sum_{k = 1}^B I\left\{\hat{T} \leq \hat{T}_k^{\#}\right\} < 0.05\right) \xrightarrow{p} 1 \text{ as } n \to \infty
\end{align*}
or Equivalently

\begin{align*}
Pr\left(\hat{T} \leq F^{-1}_{\hat{T}^\#}(0.05)\right) \xrightarrow{p} 1 \text{ as } n \to \infty
\end{align*}
\end{theorem}

\begin{proof}
This proof will consist of three parts.  We will first show that as $n \to \infty, \hat{T}_a^\#$ becomes bounded away from $0$ for any valid norm.  Next we will show $\hat{T}_a$ converges to $0$ in probability for any valid norm.  Last we will show the two previous findings imply theorem \ref{thm:cnst}.

Let $P^\#_{\rvo}$ denote the distribution of the randomly permuted observations.  \sh{Because $Pr(Y^{\#}_i \indep \boldsymbol{W}^\#_{i}) \to 0$, $\boldsymbol{\Psi}(P^\#_{\rvo}) = \boldsymbol{0}$.  Additionally, $\sqrt{n}\left(\hat{\boldsymbol{\psi}}^\# -\boldsymbol{\psi}^\# \right) \xrightarrow{d} Z^\# \sim N\left(\boldsymbol{0}, \Sigma_{\text{perm}}\right)$}.
Define $\hat{T}_a^\# = \min_s\{s : g_a(s \cdot \sqrt{n}\hat{\boldsymbol{\psi}}^\#) \geq C_{0.95, a}^\# \}$ and $C^\#_{0.95, a}$ is $F^{-1}_{Z^\#}(0.95)$.  Since we know that $\psi^\# = \boldsymbol{0}$, it follows that $\sqrt{n}\hat{\boldsymbol{\psi}}^\# \overset{d}{\approx} Z^\#$.

Now, consider:
\begin{align*}
	\pr\left(\hat{T}^\#_a  > \epsilon\right) &= \pr\left(g_a\left(\epsilon \cdot \sqrt{n}\hat{\boldsymbol{\psi}}^\#\right) \leq C_{0.95, a}\right)\\
	& \geq \pr\left(\epsilon \cdot d \cdot  \max\left(\sqrt{n} \hat{\boldsymbol{\psi}}^\# \right)\leq C_{0.95, a}\right)\\
	& = \pr\left( \max\left(\sqrt{n} \hat{\boldsymbol{\psi}}^\# \right)\leq C_{0.95, a}/(\epsilon \cdot d)\right)
\end{align*}
Because $\max\left(\left|\sqrt{n} \hat{\boldsymbol{\psi}}^\#\right|\right)$ converges to a well defined, positive distribution as a result of the continuous mapping theorem, for each constant $c < 1$, we know there exists an $\epsilon_c$ such that $\pr\left(\hat{T}^\#_a  > \epsilon_c\right) \geq c$.

%From the definition of $C_{0.95, a}^\#$ it follows that $Pr(g_a(\sqrt{n}\hat{\boldsymbol{\psi}}^\#) \leq C^\#_{0.95, a}) \to 0.95$.  For realizations in which $g_a(\sqrt{n}\hat{\boldsymbol{\psi}}^\#) \leq C^\#_{0.95, a}$ it must also be true that $\hat{t}^\# > 1$  from \eqref{eqn:linegrowth}. From the above logic it follows that $Pr(\hat{T}_a^\# > 1) \geq 0.95$ and thus $F^{-1}_{\hat{T}_a^\#}(0.05) \geq 1$ with a probability approaching 1.

Now, shifting our focus to $\hat{T}_a$, under alternatives, $\boldsymbol{\psi} \neq \boldsymbol{0}$. Define $\psi_{\max} = \max(\psi_1, \dots, \psi_d)$.  Using this knowledge, and \eqref{eqn:nrm_bounds}, note that 
\begin{align}
\pr\left(\hat{T}_a < \epsilon\right) &= \pr\left(g_a\left(\epsilon \cdot \sqrt{n} \hat{\boldsymbol{\psi}}\right) \geq C_{0.95, a}\right) \nonumber\\
&\geq \pr\left(\epsilon \cdot \sqrt{n}\max(\hat{\psi}_1, \dots, \hat{\psi}_d) \geq C_{0.95, a}\right) \nonumber \\
&= \pr\left(\max(\hat{\psi}_1, \dots, \hat{\psi}_d) \geq C_{0.95, a}/\left(\epsilon \cdot \sqrt{n}\right)\right) \nonumber \\
&\geq \pr\left(\max(\hat{\psi}_1, \dots, \hat{\psi}_d) \geq \psi_{\max}/2\right) \pr\left(\psi_{\max}/2\geq C_{0.95, a}/\left(\epsilon \cdot \sqrt{n}\right)\right) \label{eqn:prod_tlte} 
\end{align}
The first factor of the product in \eqref{eqn:prod_tlte} will converge to 1 as $n \to \infty$ from the consistency of $\hat{\boldsymbol{\psi}}$.  The second quantity will be equal to 1 for sufficiently large $n$.   Thus $\hat{T}_a \xrightarrow{p} 0$ under any alternative.

It was shown that for each $a$ that $\hat{T}_a \xrightarrow{p} 0$.  This means that our adaptive estimator $\hat{T} \xrightarrow{p} 0$ as well.  Now, let $c = 0.05/k$ and $\epsilon_c$ be small enough that $\pr\left(\hat{T}^\#_a  > \epsilon_c\right) \geq 1 - (0.05/k)$.  The permutation version of the adaptive estimator $\hat{T}^\#$ has the property that
\begin{align*}
	\pr\left(\hat{T}^\# < \epsilon_c\right) \leq \pr(\hat{T}^\#_1 < \epsilon_c) + \dots + \pr(\hat{T}^\#_k < \epsilon_c) \leq 0.05,
\end{align*}
and the theorem's conclusion follows.
\end{proof}

\sh{\subsection{Unbiasedness at local alternatives}
Show that the test will reject the null with a probability greater than $\alpha$ for an $\alpha$ level test }
\sh{Proof Outline: \\
\begin{itemize}
	\item Under local alternatives, $\sqrt{n}\hat{\boldsymbol{\psi}} \xrightarrow{d} N(\boldsymbol{c}, \Sigma)$
	\item The permutation test statistic will converge in distribution to a standard normal.  This paper should help: \citep{omelka_testing_2012}
	\item For each norm selected, \citep{gupta_inequalitites_1972} states that the power will be non-decreasing as long as the rejection region is convex (This should be true most of our rejection regions), and the probability density is decreasing away from the mean (which is true of a normal distribution).  
	\item Show that for $n$ large, the norm is selected to give the best power.  Thus since each norm obtains local power, the adaptive test will also obtain local power for $n$ large.
\end{itemize}}

\sh{\subsection{Consistency of norm selection} 
This proof would likely be difficult and require some slower than $\sqrt{n}$ covergence rates of the local alternative considered.  Under fixed alternatives, all norms perform equally perfectly}

\sh{\subsection{Type 1 error control}
Proof is so short, I am not sure if it is worth including
Under the null, $Y \indep \rvo$.  Thus the test statistic will be taken from the same distribution as all of the permutation based test statistics used to estimate the distirbution of the test statistic under the null.  Therefore, as $B$ grows, $Pr(T_n \geq F_{T^\#_{k,n}|\rvo_n}(0.95)) \Rightarrow 0.05$
}

%However, determining which observations should be considered more extreme is not straightforward.  
%One way to solve this problem is by using a norm to transform all of your data to $\mathbb{R}$ instead of $\mathbb{R}^d$.  After taking the norm of your vector of parameter estimates and your estimated limiting distribution you can create a cutoff for your test.
% People are interested in discovering if their data about $\rvo$ could be predictive of some outcome $Y$.  While many there have been many procedures that have come before this one, the procedure outlined in this article has a few distinct advantages that are valuable to scientists.

% For each covariate of interest, we can specify a measure of association between the covariate of interest and the outcome which is defined as a parameter of the data generating mechanism.  This measure of association can be estimated for each covariate of interest giving us a parameter for each covariate of interest. The null hypothesis which we will be testing is whether or not all of these parameters are equal to zero (or some other value which indicates no association exists).

% As with most test, our test will calculate a test statistic, and then estimate the limiting distribution of this test statistic under the null. Obtaining the test statistic is a three step procedure.  The first step is to obtain the limiting distribution of the vector of parameter estimates under the null.  This first step is made possible through the use of influence functions and a multiplier bootstrap.  This technique is applicable for a wide range of parameters that measure association.  Next, a norm is selected from a range of possible norms based on the norms' approximated performance under various alternatives.  After this, the selected norm is applied to the vector of parameter estimates and transformed by a function (which could be dependent on the norm) to give us our test statistic.

% There are two options for obtaining the limiting distribution of this test statistic under the null.  The first is to use a parametric bootstrap.  We can take a single draw from the limiting distribution of our vector of parameter estimates under the null and treat this draw as if it were our vector of parameter estimates.  Using the same three step procedure described above we can obtain a single draw from the limiting distribution of our test statistic under the null.  This procedure can be repeated many times over to obtain the limiting distribution of our test statistic under the null.  The other option is to randomly permute our outcome variable and use this data to estimate the vector of parameter estimates.  Passing this vector through the three step procedure, we obtain a draw from the limiting distribution under the null.  Many draws can be obtained by taking many draws coming from different permutations of the outcome variable.

% The permutation technique is less prone to inflated type 1 error rates, but comes at the cost of larger computational burden.

% The procedure is fast because estimation of the limiting distribution is done using a multiplier bootstrap.  The procedure's use of influence functions allows scientists to define the parameter of association that is best suited to answering their scientific question.  Adaptive selection of the norm used improves the testing procedure's ability to detect an association when one exists for a wide variety of data generating mechanisms.  Simulating the test-statistic generating procedure under the null using a permutation guarantees family-wise error control. 
\bibliography{paper_bib}

\end{document}

### 2019-12-08 figure_code/paper_scripts.R

@@ -1,0 +1,161 @@
+
+
+set.seed(103)
+my_data <- MASS::mvrnorm(n = 100, mu = rep(0, 2), Sigma = diag(2))
+
+plot(my_data[, 1], my_data[, 2], axes = FALSE, asp = 1, 
+     bty = 'n', panel.first = grid(), pch = 16)
+axis(1, (-4):4, pos = 0, cex.axis = 0.8)
+axis(2, (-4):4, pos = 0, cex.axis = 0.8, las = 2)
+
+l_2_cutoff <- quantile(apply(my_data, 1, function(x) sqrt(sum(x ** 2))), 0.95)
+l_h_cutoff <- quantile(apply(my_data, 1, function(x) sum(sqrt(abs(x))) ** 2), 0.95)
+max_cutoff <- quantile(apply(my_data, 1, function(x) max(abs(x))), 0.95)
+max_line <- cbind(c(-max_cutoff, max_cutoff, max_cutoff,-max_cutoff, -max_cutoff),
+                 c(-max_cutoff, -max_cutoff, max_cutoff, max_cutoff, -max_cutoff))
+half_line_x <- seq(from = -l_h_cutoff, to = l_h_cutoff, length.out = 1000)
+half_line_y <- (l_h_cutoff ** (1/2) - half_line_x ** (1/2)) ** 2
+half_line_df <- cbind(c(half_line_x, rev(half_line_x), -half_line_x, -rev(half_line_x)), 
+                      c(half_line_y, -rev(half_line_y), -half_line_y, rev(half_line_y)))
+thetas <- seq(from = 0, to = 2 * pi, length.out = 1000)
+l_2_line <- l_2_cutoff * cbind(sin(thetas), cos(thetas))
+lines(max_line[, 1], max_line[, 2], col = "blue", lwd = 4)
+lines(l_2_line[, 1], l_2_line[, 2], col = "red", lwd = 4)
+lines(half_line_df[, 1], half_line_df[, 2], col = "purple", lwd = 4)
+points(my_data[, 1], my_data[, 2], pch = 16)
+
+
+make_plot <- function(seed){
+  set.seed(seed)
+  my_data <- MASS::mvrnorm(n = 100, mu = rep(0, 2), Sigma = diag(2))
+  
+  plot(my_data[, 1], my_data[, 2], axes = FALSE, asp = 1, 
[…]

### 2019-12-09 article_draft.tex
Add first of Alex and my corrections

@@
 \newcommand{\disto}{P}
-\newcommand{\rvv}{Y}
+\newcommand{\rvv}{Z}
 \newcommand{\distv}{Q}
@@
 In one setting $\beta = 0$.
-In the second only one or two parts entries of $\beta$ will be non-zero.
+In the second only one or two entries of $\beta$ will be non-zero.
 In the last setting, many of the entries of $\beta$ will be non-zero (possibly $70$ or $80$ percent of the entries).
@@
 \label{sec:prop_test_proc}
-Denote the estimator of the $\boldsymbol{\psi}$ by $\hat{\boldsymbol{\Psi}}(\boldsymbol{\rvo})$, let $\hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$, and suppose that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to some distribution $\distv$ when $\disto \in \mathscr{M}_0$.
-Any test of $\disto \in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0 \subset \mathbb{R}^d$.
+Denote the estimator of the $\boldsymbol{\psi}$ by $\hat{\boldsymbol{\Psi}}(\boldsymbol{\rvo})$, let $\hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$, and suppose that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to some distribution $\distv(P)$ when $\disto \in \mathscr{M}_0$.
+Any test of $\disto \in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$.
 The region $\Theta_0$ can be chosen so the probability of rejection under the null will be controlled asymptotically:
 \begin{align}
-	Pr(\distv \in \Theta_0) = 1 - \alpha \text{ under } H_0. \label{eqn:alpha_rej}
+  Pr(\rvv \in \Theta_0(P)) = 1 - \alpha \text{ for every } P \in M_0. \label{eqn:alpha_rej}
 \end{align}
-Equation \eqref{eqn:alpha_rej} is satisfied by many different acceptance regions, but for now, consider an acceptance region that is a $\ell_2$ ball centered at the origin.
-To define the region, a radius such that \eqref{eqn:alpha_rej} is satisfied can be selected.
+There are infinitely many regions satisfying \eqref{eqn:alpha_rej}.
+We focus on a class of regions defined using $\ell_p$ norms.
+First consider the $\ell_2$ norm.
+This creates an acceptance region that is a $\ell_2$ ball centered at the origin.
+For this region to satisfy \eqref{eqn:alpha_rej}, let the radius of our ball $r_\alpha$ satisfy:
 
-To find this radius, one could solve the following equation:
 \begin{align*}
-	r_\alpha = \min\left\{r : Pr(||\rvv||_2 \leq r) \geq 1 - \alpha \right\} \text{ where } \rvv \sim \distv 
+	r_\alpha = \min\left\{r : Pr(||\rvv||_2 \leq r) \geq 1 - \alpha \right\} \text{ where } \rvv \sim \distv.
 \end{align*}
@@
 Similarly, $Pr(||\rvv||_2 \geq ||\sqrt{n} \hat{\boldsymbol{\psi}}||_2)$ would provide a p-value.
-The quantity could also be used for a test, and since we know $Pr_Q(||\rvv||_2 \geq ||\sqrt{n} \hat{\boldsymbol{\Psi}}(\rvo)||_2)$ will be uniformly distributed on $(0, 1)$ asymptotically under the null, we can reject $H_0$ whenever this value is less than $\alpha$.
+%The quantity could also be used for a test, and since we know $Pr_Q(||\rvv||_2 \geq ||\sqrt{n} \hat{\boldsymbol{\Psi}}(\rvo)||_2)$ will be uniformly distributed on $(0, 1)$ asymptotically under the null, we can reject $H_0$ whenever this value is less than $\alpha$.
 
@@
 
-\subsection{Creating a rejection region using a function}
+\subsection{\textcolor{blue}{Creating a rejection region using a function}}
 % Note that above while our test was defined by rejecting or accepting based on if $\sqrt{n}\hat{\psi} \in \Theta_0$, we can also think about defining our test decision based on if some function, say $\Gamma_P(x, ||\cdot||)$ that maps from a value and distribution in $\mathbb{R}^d$, and a norm $||\cdot||$ to a real value is greater than zero.
-As alluded to above, any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x, ||\cdot||)$ that maps from a value and distribution in $\mathbb{R}^d$, and a norm $||\cdot||$ to a real value.
-To obtain p-values and define the test, one compares $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\distv(\rvv, ||\cdot||)$ where $\rvv$ is a random variable with distribution $\distv$.
-Trivially, this function could be defined as: $\Gamma_\distv(x, ||\cdot||) = I\{x \in \Theta_0(\distv)\}$.
+
+As alluded to above, any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$, and a norm $||\cdot||$ to a real value.
+To obtain p-values and define the test, compare $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to $\Gamma_\distv(\rvv)$ where $\rvv$ is a random variable with distribution $\distv$.
+Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.
 However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.
 
-In the example above, $\Gamma_\distv(x, ||\cdot||) = Pr_\distv\left(||\rvv|| \geq ||x|| \right)$.
-For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv, ||\cdot||)$ is uniformly distributed on $(0, 1)$.
+In the example above, $\Gamma_\distv(x) = Pr_\distv\left(||\rvv|| \geq ||x|| \right)$.
+For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.
 However, for other $\Gamma$, this may not be the case.
@@
 \begin{align*}
-	\Gamma_\distv(x, ||\cdot||) &= Pr_\distv(||\rvv^* + x|| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv|| < c) \geq 0.8 \} \text{ and } \rvv^* \overset{d}{=} \rvv.
+	\Gamma_\distv(x) &= Pr_\distv(||\rvv^* + x|| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv|| < c) \geq 0.8 \} \text{ and } \rvv^* \overset{d}{=} \rvv.
 \end{align*}
-In this scenario, the test can be carried out by comparing $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\distv(\rvv, ||\cdot||).$
+In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\distv(\rvv, ||\cdot||).$
 
@@
 \end{align*}
-Under $H_0$, $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges to $Z$, and one can approximate $\Sigma$ with $\widehat{\Sigma} = \frac{1}{n}\sum_{i = 1}^n D(\boldsymbol{x}_i)^\top D(\boldsymbol{x}_i)$.
+Under $H_0$, $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges to $Z$, and $\Sigma$ can be approximates with $\widehat{\Sigma} = \frac{1}{n}\sum_{i = 1}^n D(\boldsymbol{x}_i)^\top D(\boldsymbol{x}_i)$.
 Thus, in practice we will use an estimate of $\distv$, $\hat{\distv}$ which is distributed $N(0, \widehat{\Sigma})$ in place of $\distv$, and the random variable $\hat{\rvv}$ with distribution $\hat{\distv}$ in place of $\rvv$.

### 2019-12-09 article_draft.tex
other small edits

@@
 
-As alluded to above, any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$, and a norm $||\cdot||$ to a real value.
+As alluded to above, any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.
+While it is not always required, most $\Gamma$ we consider use some norm $||\cdot||$.
 To obtain p-values and define the test, compare $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to $\Gamma_\distv(\rvv)$ where $\rvv$ is a random variable with distribution $\distv$.

### 2019-12-12 article_draft.tex
Made changes to intro

@@
 
-\sh{It is often of interest if any of a large number of candiate measurements are useful in predicting some outcome}.
-In genetics many candidate snips and their association with some outcome is often of interest.
-Many studies take measurements on a large number of biomarkers to see if any can predict medical outcomes such as the presence  or progression of a disease.
-While interest in the existence of an association between two variables has existed for years, the vast number of potential predictors creates new statistical challenges.
+\sh{In nearly all areas of high-dimensional statistics distinguishing between the important and unimportant predictors is of intrest}.
+In genetics many candidate snips and their association with some outcome is of interest.
+Many studies take measurements on a large number of biomarkers to predict medical outcomes such as the presence or progression of a disease.
+While there has been much focus on finding important predictors, there has been less interest in knowing if any predictors are actually important.
+The vast number of potential predictors creates new statistical challenges to answering this less obvious question.
+
 In the univariate case, once a measure of association is selected, standard approaches exist to construct asymptotically valid (and sometimes optimal) tests \citep{neyman_jerzy_ix._1933}.
 In this setting, a test is considered optimal if it achieves the largest power for every alternative compared to every other test with the same type one error.
-However, as mentioned above, scientists are often interested if any of a multitude of covariate are associated with the outcome of interest.
-Even in the case with two covariates, a test with the above optimal property no longer exists.
+However, scientists are often interested if any of a multitude of covariate are associated with the outcome of interest.
+Even in the case with two covariates, a test with the above optimal property no longer exists and the alternative plays a larger role in which tests are more or less powerful.
 
 To illustrate this, consider two tests with equal type one error rates.
-Both test the null that both of the two association measures $\psi_1$, $\psi_2$ are zero.
+Both test the null that both of two association measures $\psi_1$, $\psi_2$ are zero.
 The first test focuses only on the $\psi_1$ and the second test considers both $\psi_1$ and $\psi_2$.

### 2019-12-13 article_draft.tex
Another modification of Section 3

@@
 \label{sec:prop_test_proc}
-Denote the estimator of the $\boldsymbol{\psi}$ by $\hat{\boldsymbol{\Psi}}(\boldsymbol{\rvo})$, let $\hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$, and suppose that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to some distribution $\distv(P)$ when $\disto \in \mathscr{M}_0$.
+Denote the estimator of the $\boldsymbol{\psi}$ by $\hat{\boldsymbol{\Psi}}(\boldsymbol{\rvo})$ and let $\hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$.
+Suppose that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to some distribution $\distv(P)$ when $\disto \in \mathscr{M}_0$.
 Any test of $\disto \in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$.
-The region $\Theta_0$ can be chosen so the probability of rejection under the null will be controlled asymptotically:
+The region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
 \begin{align}
-  Pr(\rvv \in \Theta_0(P)) = 1 - \alpha \text{ for every } P \in M_0. \label{eqn:alpha_rej}
+  Pr(\rvv \in \Theta_0(P)) = 1 - \alpha \text{ for every } P \in M_0 \text{ where } \rvv \sim \distv(\disto).\label{eqn:alpha_rej}
 \end{align}
-There are infinitely many regions satisfying \eqref{eqn:alpha_rej}.
-We focus on a class of regions defined using $\ell_p$ norms.
-First consider the $\ell_2$ norm.
-This creates an acceptance region that is a $\ell_2$ ball centered at the origin.
-For this region to satisfy \eqref{eqn:alpha_rej}, let the radius of our ball $r_\alpha$ satisfy:
-
+While there are infinitely many regions satisfying \eqref{eqn:alpha_rej},  we focus on a class of regions defined using $\ell_p$ norms.
+For simplicity, first consider regions defined using an $\ell_2$ norm:
 \begin{align*}
-	r_\alpha = \min\left\{r : Pr(||\rvv||_2 \leq r) \geq 1 - \alpha \right\} \text{ where } \rvv \sim \distv.
+	\Theta_0(r) = \left\{\omega : ||\omega||_2 \leq r\right\}
 \end{align*}
-Above we have converted a problem of defining a region to a problem of defining a real value by using a norm.  This same idea can be used when defining a test:
+A region satisfying \eqref{eqn:alpha_rej} has a radius: 
+\begin{align*}
+	r_\alpha(\disto) = \min\left\{r : Pr_{\distv(\disto)}(||\rvv||_2 \leq r) \geq 1 - \alpha \right\}.
+\end{align*}
+By constraining the possible regions we consider, we can now define our test in a simple algebraic form:
 \begin{align*}
@@
 \end{align*}
-Similarly, $Pr(||\rvv||_2 \geq ||\sqrt{n} \hat{\boldsymbol{\psi}}||_2)$ would provide a p-value.
+Similarly, p-values can now be simply defined as $Pr(||\rvv||_2 \geq ||\sqrt{n} \hat{\boldsymbol{\psi}}||_2)$.
 %The quantity could also be used for a test, and since we know $Pr_Q(||\rvv||_2 \geq ||\sqrt{n} \hat{\boldsymbol{\Psi}}(\rvo)||_2)$ will be uniformly distributed on $(0, 1)$ asymptotically under the null, we can reject $H_0$ whenever this value is less than $\alpha$.
@@
 
-\subsection{\textcolor{blue}{Creating a rejection region using a function}}
+% \subsection{\textcolor{blue}{Creating a rejection region using a function}}
 % Note that above while our test was defined by rejecting or accepting based on if $\sqrt{n}\hat{\psi} \in \Theta_0$, we can also think about defining our test decision based on if some function, say $\Gamma_P(x, ||\cdot||)$ that maps from a value and distribution in $\mathbb{R}^d$, and a norm $||\cdot||$ to a real value is greater than zero.
 
-As alluded to above, any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.
-While it is not always required, most $\Gamma$ we consider use some norm $||\cdot||$.
-To obtain p-values and define the test, compare $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to $\Gamma_\distv(\rvv)$ where $\rvv$ is a random variable with distribution $\distv$.
+Above we used a norm to constrain the considered rejection regions and allow for a test based on the value of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under the norm and the distribution of $\distv$ under the norm.
+However, this approach will also work with more complicated functions.
+Consider instead of norm, some function $\Gamma_{\distv}(x)$ that maps from a value and distribution in $\mathbb{R}^d$ to $\mathbb{R}$.
+The distribution of $\Gamma_\distv(\rvv)$ can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test.
+Consider, for example:
+% any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.
 Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.
 However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.
-
-In the example above, $\Gamma_\distv(x) = Pr_\distv\left(||\rvv|| \geq ||x|| \right)$.
+% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(||\rvv|| \geq ||x|| \right)$.
 For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.
@@
 
-While this way of defining a test allows for many different specifications, it does require that the user chooses a norm.
+While this method for defining tests allows for many different specifications, it often requires users chooses a norm as part of their definition of $\Gamma$.
 Figure \ref{fig:figure1} shows that the power a test achieves can depend on the norm chosen.
@@
 
-This is achieved by defining a $\Gamma$ similar to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.
+To achieve this, first define $\Gamma_{1, \distv}(x), \dots, \Gamma_{p, \distv}(x)$ as collection of functions in which the functions only differ by the norm used in their definition. Next, define
+% by defining a $\Gamma$ to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.
 For example, if we had $p$ different norms, $\norm_1, \dots, \norm_p$ and some summary function $\Gamma_\distv(x, ||\cdot||)$, we would define the adaptive version of $\Gamma$ as
-
 \begin{align*}
-	\Gamma^*_\distv(x) = \max\left\{\Gamma_\distv(x, \norm_1), \Gamma_\distv(x, \norm_2), \dots, \Gamma_\distv(x, \norm_p)\right\}.
+	\Gamma^*_\distv(x) = \max\left\{\Gamma_{1, \distv}(x), \Gamma_{2, \distv}(x), \dots, \Gamma_{p, \distv}(x)\right\}.
 \end{align*}
@@
 
-In many cases, it will be difficult to obtain the exact distribution of $\Gamma_\distv^*(\rvv)$.
-However, because this distribution is only a function of $\distv$, obtaining very good approximations of $\Gamma_\distv^*(\rvv)$ is possible by taking many draws from $\rvv$, both to estimate the function $\Gamma$ and to estimate $\Gamma^*_\distv(\rvv)$ .
+While it may be difficult to obtain the exact distribution of $\Gamma_\distv^*(\rvv)$ in practice, the distribution is a function of $\distv$, so obtaining very good approximations of $\Gamma_\distv^*(\rvv)$ is possible by taking many draws from $\rvv$.
+This technique can be used both to estimate the function $\Gamma$ and to estimate $\Gamma^*_\distv(\rvv)$ .
 

### 2019-12-13 article_draft.tex
More changes.

@@
 \end{align*}
-A region satisfying \eqref{eqn:alpha_rej} has a radius: 
+A region satisfying \eqref{eqn:alpha_rej} has a radius defined by: 
 \begin{align*}
@@
 Above we used a norm to constrain the considered rejection regions and allow for a test based on the value of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under the norm and the distribution of $\distv$ under the norm.
-However, this approach will also work with more complicated functions.
-Consider instead of norm, some function $\Gamma_{\distv}(x)$ that maps from a value and distribution in $\mathbb{R}^d$ to $\mathbb{R}$.
+However, this approach also works with more complicated functions.
+Let $\Gamma_{\distv}(x)$ be a function that maps from a value and distribution in $\mathbb{R}^d$ to $\mathbb{R}$.
 The distribution of $\Gamma_\distv(\rvv)$ can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test.
-Consider, for example:
+An example of $\Gamma$ is given below:
 % any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.
@@
 \end{align*}
-In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\distv(\rvv, ||\cdot||).$
+% In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\distv(\rvv, ||\cdot||).$
 
@@
 
-While this method for defining tests allows for many different specifications, it often requires users chooses a norm as part of their definition of $\Gamma$.
+While this method for defining tests allows for many different specifications, it often requires choosing a norm as part of the definition of $\Gamma$.
 Figure \ref{fig:figure1} shows that the power a test achieves can depend on the norm chosen.
@@
 \end{align*}
-\textcolor{blue}{This will could be the min if smaller values indicate larger distances away from the norm (such as p-values).}
+\textcolor{blue}{This could be the min if smaller values indicate larger distances away from the norm (such as p-values).}
 
-While it may be difficult to obtain the exact distribution of $\Gamma_\distv^*(\rvv)$ in practice, the distribution is a function of $\distv$, so obtaining very good approximations of $\Gamma_\distv^*(\rvv)$ is possible by taking many draws from $\rvv$.
+While this function is more complicated than before,  $\Gamma^*_{\distv}(\rvv))$ can still be compared to $\Gamma^*_{\distv}(\sqrt{n}\hat{\psi})$ to obtain a p-value.
+Also, while it may be difficult to obtain the exact distribution of $\Gamma_\distv^*(\rvv)$, the distribution is a function of $\distv$, so obtaining very good approximations of $\Gamma_\distv^*(\rvv)$ is possible by taking many draws from $\rvv$.
 This technique can be used both to estimate the function $\Gamma$ and to estimate $\Gamma^*_\distv(\rvv)$ .
@@
 \subsection{Using a permutation test for the test statistic}
-While the above approach will work asymptotically, there can be issues for small sample sizes.
+While the above approach works asymptotically, there can be issues for small sample sizes.
 To avoid inflated type one error, a permutation based test can be used.

### 2019-12-16 article_draft.tex
Updates from Overleaf

@@
 \label{sec:prop_test_proc}
-Denote the estimator of the $\boldsymbol{\psi}$ by $\hat{\boldsymbol{\Psi}}(\boldsymbol{\rvo})$ and let $\hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$.
+Denote the estimator of $\boldsymbol{\psi}$ by $\hat{\boldsymbol{\Psi}}(\boldsymbol{\rvo})$ and let $\hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$.
 Suppose that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to some distribution $\distv(P)$ when $\disto \in \mathscr{M}_0$.
-Any test of $\disto \in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$.
+Any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$.
 The region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
 \begin{align}
-  Pr(\rvv \in \Theta_0(P)) = 1 - \alpha \text{ for every } P \in M_0 \text{ where } \rvv \sim \distv(\disto).\label{eqn:alpha_rej}
+  Pr_{\distv(\disto)}\{\rvv \not \in \Theta_0(P)\} = 1 - \alpha \text{ for every } P \in \mathscr{M}_0.\label{eqn:alpha_rej}
 \end{align}
-While there are infinitely many regions satisfying \eqref{eqn:alpha_rej},  we focus on a class of regions defined using $\ell_p$ norms.
+While there are infinitely many regions satisfying \eqref{eqn:alpha_rej},  we focus on a particular class of regions defined using $\ell_p$ norms.
 For simplicity, first consider regions defined using an $\ell_2$ norm:
 \begin{align*}
-	\Theta_0(r) = \left\{\omega : ||\omega||_2 \leq r\right\}
+	\Theta_0(r) = \left\{\omega : ||\omega||_2 \leq r\right\}.
 \end{align*}
-A region satisfying \eqref{eqn:alpha_rej} has a radius defined by: 
+A region satisfying \eqref{eqn:alpha_rej} has a radius defined by: \textcolor{blue}{be consistent on indexing ``$Pr$'' -- if you're going to write as $Pr_{Q(P)}$, do this throughout!}
 \begin{align*}
@@
 
-Above we used a norm to constrain the considered rejection regions and allow for a test based on the value of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under the norm and the distribution of $\distv$ under the norm.
+Above we used a norm to constrain the considered rejection regions and allow for a test based on the value of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under the norm and the distribution of $\distv$ under the norm \textcolor{blue}{I don't understand the end of this sentence}.
 However, this approach also works with more complicated functions.
 Let $\Gamma_{\distv}(x)$ be a function that maps from a value and distribution in $\mathbb{R}^d$ to $\mathbb{R}$.
-The distribution of $\Gamma_\distv(\rvv)$ can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test.
+\textcolor{blue}{I see $\Gamma_{\distv}$ being an $\mathbb{R}^d$ to $\mathbb{R}$ function.
+I don't see $\Gamma_Q(x)$ being a function?
+I also don't understand how this maps ``from a ...
+distribution'' to anywhere?
+Do you mean: ``For any distribution $Q$ with support contained in $\mathbb{R}^d$, let $\Gamma_Q$ be a function mapping from $\mathbb{R}^d$ to $\mathbb{R}$''?}  The distribution of $\Gamma_\distv(\rvv)$ \textcolor{blue}{(when $Z$ is sampled from what?)} can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test.
 An example of $\Gamma$ is given below:
@@
 \end{align*}
+\textcolor{blue}{What is $\rvv^* \overset{d}{=} \rvv$ telling us?
+Don't we already know that the probabilities over both of these quantities are indexed by $Q$?
+Also, why use different notation at all?
+Why not just $\rvv^*$ for both?}
 % In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\distv(\rvv, ||\cdot||).$
@@
 Consider the case when $d = 2$ and $100$ draws are taken from $Z$.
-Cutoffs can be obtained by transforming these data (using the $l_p$ norm) and taking the 95\% quantile of this transformed data.
+Cutoffs can be obtained by transforming these data (using the $\ell_p$ norm) and taking the 95\% quantile of this transformed data.
 The perimeter of the acceptance region when using the $\ell_2$ and $\ell_{\infty}$ norm are given in red and blue respectively.
@@
 \end{align*}
-When there is a fixed number of covariates, the Cramer-Wold device can be used to show that the vector of parameter estimates is asymptotically normal with mean zero, and variance covariance matrix given by $\Sigma = E_{\disto_0}\left[D(\rvo)^\top D(\rvo)\right]$:
+When there is a fixed number of covariates, the Cramer-Wold device can be used to show that the vector of parameter estimates is asymptotically normal with mean zero, and variance covariance matrix given by $\Sigma = E_{\disto_0}\left[D(\rvo)^\top D(\rvo)\right]$: \textcolor{blue}{Note from Alex: do you mean $D(\rvo) D(\rvo)^\top$?
+This is what you would want if $D(\rvo)$ were a column vector, which would be more standard (similar comment in other places where `$\top$' is used)}
 

### 2019-12-19 article_draft.tex
Updates from Overleaf

@@
 \end{align*}
-Similarly, p-values can now be simply defined as $Pr(||\rvv||_2 \geq ||\sqrt{n} \hat{\boldsymbol{\psi}}||_2)$.
+Similarly, p-values can now be simply defined as $Pr_Q(||\rvv||_2 \geq ||\sqrt{n} \hat{\boldsymbol{\psi}}||_2)$.
 %The quantity could also be used for a test, and since we know $Pr_Q(||\rvv||_2 \geq ||\sqrt{n} \hat{\boldsymbol{\Psi}}(\rvo)||_2)$ will be uniformly distributed on $(0, 1)$ asymptotically under the null, we can reject $H_0$ whenever this value is less than $\alpha$.
@@
 Do you mean: ``For any distribution $Q$ with support contained in $\mathbb{R}^d$, let $\Gamma_Q$ be a function mapping from $\mathbb{R}^d$ to $\mathbb{R}$''?}  The distribution of $\Gamma_\distv(\rvv)$ \textcolor{blue}{(when $Z$ is sampled from what?)} can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test.
-An example of $\Gamma$ is given below:
+An example of $\Gamma_\distv$ is given below:
 % any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.
@@
 \end{align*}
-When there is a fixed number of covariates, the Cramer-Wold device can be used to show that the vector of parameter estimates is asymptotically normal with mean zero, and variance covariance matrix given by $\Sigma = E_{\disto_0}\left[D(\rvo)^\top D(\rvo)\right]$: \textcolor{blue}{Note from Alex: do you mean $D(\rvo) D(\rvo)^\top$?
+When there is a fixed number of covariates, the Cramer-Wold device can be used to show that the vector of parameter estimates is asymptotically normal with mean zero, and variance covariance matrix given by $\Sigma = E_{\disto_0}\left[D(\rvo) D(\rvo)^\top \right]$: \textcolor{blue}{Note from Alex: do you mean $D(\rvo) D(\rvo)^\top$?
 This is what you would want if $D(\rvo)$ were a column vector, which would be more standard (similar comment in other places where `$\top$' is used)}
@@
 \end{align*}
-Under $H_0$, $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges to $Z$, and $\Sigma$ can be approximates with $\widehat{\Sigma} = \frac{1}{n}\sum_{i = 1}^n D(\boldsymbol{x}_i)^\top D(\boldsymbol{x}_i)$.
+Under $H_0$, $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges to $Z$, and $\Sigma$ can be approximates with $\widehat{\Sigma} = \frac{1}{n}\sum_{i = 1}^n D(\boldsymbol{x}_i) D(\boldsymbol{x}_i)^\top$.
 Thus, in practice we will use an estimate of $\distv$, $\hat{\distv}$ which is distributed $N(0, \widehat{\Sigma})$ in place of $\distv$, and the random variable $\hat{\rvv}$ with distribution $\hat{\distv}$ in place of $\rvv$.

### 2019-12-20 article_draft.tex
Address some of Alex's comments

@@
 \begin{align*}
-(\beta_0^*, \beta_1^*, \beta_2^*, \beta_3^*) = \text{argmin}_{\beta_0, \beta_1, \beta_2, \beta_3}\int\left(\text{logit}\left(Pr(y^{(a)} = 1\right) - (\beta_0 + \beta_1 a + \beta_2w_j + \beta_3 w_j a) \right)^2 dP(y^{(a)}, w, a)
+(\beta_0^*, \beta_1^*, \beta_2^*, \beta_3^*) = \text{argmin}_{\beta_0, \beta_1, \beta_2, \beta_3}\int\left(\text{logit}\left(Pr(Y^{(a)} = 1 | w\right) - (\beta_0 + \beta_1 a + \beta_2w_j + \beta_3 w_j a) \right)^2 dP(w, a)
 \end{align*}
@@
 
-Above we used a norm to constrain the considered rejection regions and allow for a test based on the value of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under the norm and the distribution of $\distv$ under the norm \textcolor{blue}{I don't understand the end of this sentence}.
+Above we used a norm to constrain the considered rejection regions and allow for a test based on the value of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under the norm the distribution of $\rvv$ under the norm, both of which reside in $\mathbb{R}$.
+Above, we have used a single norm to transform both the distribution of $\rvv$ and $\sqrt{n}\hat{\boldsymbol{\psi}}$ into $\mathbb{R}$ which allows for creating tests and calculating p-values similar to the univariate case.
+% \textcolor{blue}{I don't understand the end of this sentence}.
 However, this approach also works with more complicated functions.
-Let $\Gamma_{\distv}(x)$ be a function that maps from a value and distribution in $\mathbb{R}^d$ to $\mathbb{R}$.
-\textcolor{blue}{I see $\Gamma_{\distv}$ being an $\mathbb{R}^d$ to $\mathbb{R}$ function.
+For every distribution $\distv$ with support conntained in $\mathbb{R}^d$, let $\Gamma_{\distv}$ be a function mapping from  $\mathbb{R}^d$ to $\mathbb{R}$.
+% \textcolor{blue}{I see $\Gamma_{\distv}$ being an $\mathbb{R}^d$ to $\mathbb{R}$ function.
 I don't see $\Gamma_Q(x)$ being a function?
@@
 distribution'' to anywhere?
-Do you mean: ``For any distribution $Q$ with support contained in $\mathbb{R}^d$, let $\Gamma_Q$ be a function mapping from $\mathbb{R}^d$ to $\mathbb{R}$''?}  The distribution of $\Gamma_\distv(\rvv)$ \textcolor{blue}{(when $Z$ is sampled from what?)} can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test.
+Do you mean: ``For any distribution $Q$ with support contained in $\mathbb{R}^d$, let $\Gamma_Q$ be a function mapping from $\mathbb{R}^d$ to $\mathbb{R}$''?}
+The distribution of $\Gamma_\distv(\rvv)$ \textcolor{blue}{(when $Z$ is sampled from what?)} can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test.
 An example of $\Gamma_\distv$ is given below:
@@
 \end{align*}
-When there is a fixed number of covariates, the Cramer-Wold device can be used to show that the vector of parameter estimates is asymptotically normal with mean zero, and variance covariance matrix given by $\Sigma = E_{\disto_0}\left[D(\rvo) D(\rvo)^\top \right]$: \textcolor{blue}{Note from Alex: do you mean $D(\rvo) D(\rvo)^\top$?
+When there is a fixed number of covariates, the Cramer-Wold device can be used to show that the vector of parameter estimates is asymptotically normal with mean zero, and variance covariance matrix given by $\Sigma = E_{\disto_0}\left[D(\rvo) D(\rvo)^\top \right]$:
+%  \textcolor{blue}{Note from Alex: do you mean $D(\rvo) D(\rvo)^\top$?
 This is what you would want if $D(\rvo)$ were a column vector, which would be more standard (similar comment in other places where `$\top$' is used)}

### 2019-12-20 article_draft.tex
Adding back Alex's comment to make sure I addressed comments

@@
 Any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$.
-The region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
+Letting $\rvv$ be distributed $\distv(\disto)$, the region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
 \begin{align}
@@
 
-Above we used a norm to constrain the considered rejection regions and allow for a test based on the value of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under the norm the distribution of $\rvv$ under the norm, both of which reside in $\mathbb{R}$.
-Above, we have used a single norm to transform both the distribution of $\rvv$ and $\sqrt{n}\hat{\boldsymbol{\psi}}$ into $\mathbb{R}$ which allows for creating tests and calculating p-values similar to the univariate case.
-% \textcolor{blue}{I don't understand the end of this sentence}.
+% Above we used a norm to constrain the considered rejection regions and allow for a test based on the value of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under the norm the distribution of $\rvv$ under the norm, both of which reside in $\mathbb{R}$.
+Above, we have used a norm to transform both the distribution of $\rvv$ and $\sqrt{n}\hat{\boldsymbol{\psi}}$ into $\mathbb{R}$.
+This allows for creating tests and calculating p-values in a similar manner to the univariate case.
+\textcolor{blue}{I don't understand the end of this sentence}.
 However, this approach also works with more complicated functions.
 For every distribution $\distv$ with support conntained in $\mathbb{R}^d$, let $\Gamma_{\distv}$ be a function mapping from  $\mathbb{R}^d$ to $\mathbb{R}$.
-% \textcolor{blue}{I see $\Gamma_{\distv}$ being an $\mathbb{R}^d$ to $\mathbb{R}$ function.
+\textcolor{blue}{I see $\Gamma_{\distv}$ being an $\mathbb{R}^d$ to $\mathbb{R}$ function.
 I don't see $\Gamma_Q(x)$ being a function?
@@
 Do you mean: ``For any distribution $Q$ with support contained in $\mathbb{R}^d$, let $\Gamma_Q$ be a function mapping from $\mathbb{R}^d$ to $\mathbb{R}$''?}
-The distribution of $\Gamma_\distv(\rvv)$ \textcolor{blue}{(when $Z$ is sampled from what?)} can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test.
-An example of $\Gamma_\distv$ is given below:
+The distribution of $\Gamma_\distv(\rvv)$
+\textcolor{blue}{(when $Z$ is sampled from what?)}
+can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test. An example of $\Gamma_\distv$ is given below:
 % any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.
@@
 When there is a fixed number of covariates, the Cramer-Wold device can be used to show that the vector of parameter estimates is asymptotically normal with mean zero, and variance covariance matrix given by $\Sigma = E_{\disto_0}\left[D(\rvo) D(\rvo)^\top \right]$:
-%  \textcolor{blue}{Note from Alex: do you mean $D(\rvo) D(\rvo)^\top$?
+ \textcolor{blue}{Note from Alex: do you mean $D(\rvo) D(\rvo)^\top$?
 This is what you would want if $D(\rvo)$ were a column vector, which would be more standard (similar comment in other places where `$\top$' is used)}

### 2019-12-21 article_draft.tex

@@
 Also, why use different notation at all?
-Why not just $\rvv^*$ for both?}
+Why not just $\rvv^*$ for both?
+Here because $c_{0.8}$ is not random so this is distinction does not need to be made.}
 % In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\distv(\rvv, ||\cdot||).$
@@
 	\item Under local alternatives, $\sqrt{n}\hat{\boldsymbol{\psi}} \xrightarrow{d} N(\boldsymbol{c}, \Sigma)$
+    \item \textcolor{blue}{Think of Gamma as a funciton indexed by $\Sigma$ to allow it to be similar.
+Also make some assumptions about how smooth $\Gamma$ is with respect to this parameters.
+For any given value of the input ($t$) think about }
 	\item The permutation test statistic will converge in distribution to a standard normal.  This paper should help: \citep{omelka_testing_2012}

### 2020-01-06 article_draft.tex
Updates from Overleaf

@@
 \sh{\subsection{Unbiasedness at local alternatives}
+Consider a local alternative in which the true value of $\phi$ is shrinking towards zero at a root $n$ rate: $\phi = \underline{h}/\sqrt{n}$
 Show that the test will reject the null with a probability greater than $\alpha$ for an $\alpha$ level test }
@@
 For any given value of the input ($t$) think about }
-	\item The permutation test statistic will converge in distribution to a standard normal.  This paper should help: \citep{omelka_testing_2012}
+	\item \textcolor{blue}{Right now we have given up on proving things for the permutation test, but we may try to do it again at some point.} The permutation test statistic will converge in distribution to a standard normal.
+This paper should help: \citep{omelka_testing_2012}
 	\item For each norm selected, \citep{gupta_inequalitites_1972} states that the power will be non-decreasing as long as the rejection region is convex (This should be true most of our rejection regions), and the probability density is decreasing away from the mean (which is true of a normal distribution).

### 2020-01-10 article_draft.tex
Added changes, and started proof of local consistancy

@@
 \newtheorem{theorem}{Theorem}
+\newtheorem{lemma}[theorem]{Lemma}
 \newtheorem{refproof}{Proof}
@@
 \begin{align}
-  Pr_{\distv(\disto)}\{\rvv \not \in \Theta_0(P)\} = 1 - \alpha \text{ for every } P \in \mathscr{M}_0.\label{eqn:alpha_rej}
+  Pr_{\distv}\{\rvv \not \in \Theta_0(P)\} = 1 - \alpha \text{ for every } P \in \mathscr{M}_0.\label{eqn:alpha_rej}
 \end{align}
@@
 \end{align*}
-A region satisfying \eqref{eqn:alpha_rej} has a radius defined by: \textcolor{blue}{be consistent on indexing ``$Pr$'' -- if you're going to write as $Pr_{Q(P)}$, do this throughout!}
+A region satisfying \eqref{eqn:alpha_rej} has a radius defined by: 
+% \textcolor{blue}{be consistent on indexing ``$Pr$'' -- if you're going to write as $Pr_{Q(P)}$, do this throughout!}
 \begin{align*}
-	r_\alpha(\disto) = \min\left\{r : Pr_{\distv(\disto)}(||\rvv||_2 \leq r) \geq 1 - \alpha \right\}.
+	r_\alpha(\disto) = \min\left\{r : Pr_{\distv}(||\rvv||_2 \leq r) \geq 1 - \alpha \right\}.
 \end{align*}
@@
 This allows for creating tests and calculating p-values in a similar manner to the univariate case.
-\textcolor{blue}{I don't understand the end of this sentence}.
+% \textcolor{blue}{I don't understand the end of this sentence}.
 However, this approach also works with more complicated functions.
 For every distribution $\distv$ with support conntained in $\mathbb{R}^d$, let $\Gamma_{\distv}$ be a function mapping from  $\mathbb{R}^d$ to $\mathbb{R}$.
-\textcolor{blue}{I see $\Gamma_{\distv}$ being an $\mathbb{R}^d$ to $\mathbb{R}$ function.
+% \textcolor{blue}{I see $\Gamma_{\distv}$ being an $\mathbb{R}^d$ to $\mathbb{R}$ function.
 I don't see $\Gamma_Q(x)$ being a function?
@@
 Do you mean: ``For any distribution $Q$ with support contained in $\mathbb{R}^d$, let $\Gamma_Q$ be a function mapping from $\mathbb{R}^d$ to $\mathbb{R}$''?}
-The distribution of $\Gamma_\distv(\rvv)$
-\textcolor{blue}{(when $Z$ is sampled from what?)}
+The distribution of $\Gamma_\distv(\rvv)$ (where $\rvv \sim \distv$)
+% \textcolor{blue}{(when $Z$ is sampled from what?)}
 can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test. An example of $\Gamma_\distv$ is given below:
@@
 \begin{align*}
-	\Gamma_\distv(x) &= Pr_\distv(||\rvv^* + x|| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv|| < c) \geq 0.8 \} \text{ and } \rvv^* \overset{d}{=} \rvv.
+	\Gamma_\distv(x) &= Pr_\distv(||\rvv^* + x|| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv^*|| < c) \geq 0.8 \} \text{ and } \rvv^* \overset{d}{=} \rvv.
 \end{align*}
-\textcolor{blue}{What is $\rvv^* \overset{d}{=} \rvv$ telling us?
+% \textcolor{blue}{What is $\rvv^* \overset{d}{=} \rvv$ telling us?
 Don't we already know that the probabilities over both of these quantities are indexed by $Q$?
@@
 When there is a fixed number of covariates, the Cramer-Wold device can be used to show that the vector of parameter estimates is asymptotically normal with mean zero, and variance covariance matrix given by $\Sigma = E_{\disto_0}\left[D(\rvo) D(\rvo)^\top \right]$:
- \textcolor{blue}{Note from Alex: do you mean $D(\rvo) D(\rvo)^\top$?
+% \textcolor{blue}{Note from Alex: do you mean $D(\rvo) D(\rvo)^\top$?
 This is what you would want if $D(\rvo)$ were a column vector, which would be more standard (similar comment in other places where `$\top$' is used)}
@@
 \sh{\subsection{Unbiasedness at local alternatives}
-Consider a local alternative in which the true value of $\phi$ is shrinking towards zero at a root $n$ rate: $\phi = \underline{h}/\sqrt{n}$
-Show that the test will reject the null with a probability greater than $\alpha$ for an $\alpha$ level test }
+Consider a local alternative in which the true value of $\psi$ is shrinking towards zero at a root $n$ rate: $\psi = \underline{h}/\sqrt{n}$.
+For each potential norm, we assume the norm is convex.
+This assumption can be relaxed to what was described by Eaton and Perlman (1991) (Concentration inequalitites for multivariate distributions: mv normal).
+Under this local alternative, we will have $\sqrt{n} \hat{\psi} \xrightarrow{d} N(\underline{h}, \Sigma)$.
+Show that the test will reject the null with a probability greater than $\alpha$ for an $\alpha$ level test}
+
+\begin{theorem}
+
+Under local alternatives described above, 
+\begin{align*}
+	Pr_{\disto}\left(\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}}) \leq F^{-1}_{\Gamma^*_{\hat{\distv}}(\hat{\distv})}(\alpha)\right) \geq \alpha
+\end{align*}
+Here (unlike other parts of the paper) small values of $\Gamma$ provide evidence against the null.  Values of $\Gamma$ can be thought of as similar to $p$-valuesx
+
+\begin{lemma}
+	\begin{align*}
+	\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}})	\xrightarrow{d}\Gamma^*_{\distv}(\distv) \text{ and } F^{-1}_{\Gamma^*_{\hat{\distv}}(\hat{\distv})}(\alpha) \rightarrow  F^{-1}_{\Gamma^*_{\distv}(\distv)}(\alpha)
+	\end{align*}
+\end{lemma}
+\textcolor{blue}{
+	The proofs of these will be similar, but I am not sure quite how to do it.  While the following expansion is useful for me, I am not sure how to deal with each part:
+	\begin{align*}
+		Pr_{\disto}(\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}}) > t) - Pr_{\disto}(\Gamma^*_{\distv}(\distv) > t) & = Pr_{\disto}(\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}}) > t) - Pr_{\disto}(\Gamma^*_{\hat{\distv}}(\distv) > t) - \left( Pr_{\disto}(\Gamma^*_{\distv}(\distv) > t) - Pr_{\disto}(\Gamma^*_{\hat{\distv}}(\distv) > t) \right)
+	\end{align*}
+	We can make arguments that the second two terms will cancel because of an assumed continuity of our function $\Gamma^*$ with respect to $Q$.
+We can also think of $\Gamma^*$ as being indexed by $Q$'s covariance matrix instead of its entire distribution to make more simple continuity arguments.\\
+	However, I am not exactly sure how to argue that the first two terms cancel.
+Initially I want to use the continuous mapping theorem.
+Because the function itself changes with $n$ and is random, I am not sure what to do.
+If we again use the continuity of $\Gamma$ could we argue that the values of the random functions will be close to the values of the non-random funcitons (where $\hat\distv$ is replaced by $\distv$)\\
+	My other idea was to assume that the function class of $\Gamma*$ is $P$-Donsker, but I think this may be overly complicated, and not necessary.
+}
+
+A result of \citep{anderson_integral_1955} is that for two centrally symmetric, unimodal functions, $f_1(x)$ and  $f_2(x)$, the convolution,  
+\begin{align*}
+	g(\theta) = \int f_1(\theta) f_2(x - \theta)
+\end{align*}
+is centrally symmetric and ray decreasing.
+A function $f(x)$ on $\mathbb{R}^p$ is centrally symmetric if $f(-x) = f(x)$ for every $x$.
+A function is unimodal if for every $k$, the set $\{x : f(x) \geq k\}$ is convex.
+A function $f(x)$ on $\mathbb{R}^p$ is ray decreasing if for every $x$ in $\mathbb{R}^p$, the function $g(\beta) = f(\beta x), \beta \in \mathbb{R}$ is a decreasing function of $\beta$.
+
+For now, we will assume that each of our $\Gamma_Q(x)$ is a unimodal, centrally symmetric function.
+In certain cases, $\Gamma_Q(x)$ is increasing $x$ moves away from the origin.
+In these cases, for the purposes of this proof, instead use $\Gamma^{-1}_Q(x) = \left(\Gamma_Q(x)\right)^{-1}$.
+
+\begin{lemma}
+	\label{lemma:min_cent_sym_unm}
+	Let $\Gamma_1(x), \dots, \Gamma_d(x)$ all be centrally symmetric, unimodal functions.
+Then $\Gamma^*(x) = \min\left\{\Gamma_1(x), \dots, \Gamma_d(x)\right\}$ is also centrally symmetric and unimodal.
+
+	Centrally symmetric:
+	\begin{align*}
+	\Gamma^*(x) = \min\left\{\Gamma_1(x), \dots, \Gamma_d(x)\right\} = \min\left\{\Gamma_1(-x), \dots, \Gamma_d(-x)\right\} = \Gamma^*(-x)
+	\end{align*}
+
+	Unimodal:
+	\begin{align*}
+		\left\{x : \Gamma^*(x) \geq k\right\} = \left\{x : \Gamma_1(x) \geq k, \dots, \Gamma_d(x) \geq k\right\} = \bigcap_{i = 1}^d \left\{x : \Gamma_i(x) \geq k \right\}
+	\end{align*}
+	The intersection of multiple convex sets is also convex, so $\Gamma^*(x)$ is unimodal.
+\end{lemma}
+
+\begin{lemma}
+	\label{lemma:indct_cent_sym_unm}
+	Let $f(x)$ be a centrally symmetric, unimodal function.  Then $g(x) = I\left\{f(x) \geq c\right\}$ where $c \in \mathbb{R}$ is also centrally symmetric and unimodal.
+
+	Centrally symmetric:
+	\begin{align*}
+	g(x) = I\left\{f(x) \geq c\right\} = I\left\{f(-x) \geq c\right\} = g(-x)
+	\end{align*}
+
+	Unimodal:
+	If $k < 0$ or $k > 1$, then $\left\{x : g(x) \geq k\right\}$ will be the empty set or all of $\mathbb{R}^d$ respectively, and both sets are convex.  Otherwise, 
+	\begin{align*}
+		\left\{x : g(x) \geq k\right\} = \left\{x : I\left\{f(x) \geq c\right\} \geq k\right\} = \left\{x : f(x) \geq c\right\}
+	\end{align*}
+	which is convex by definition.
+\end{lemma}
+A consequence of lemmas \ref{lemma:min_cent_sym_unm} and \ref{lemma:indct_cent_sym_unm}, the function $I\left\{\Gamma^*_Q(x) \geq c_{0.95}\right\}$ is centrally symmetric and unimodal.
+
+\begin{align*}
+	\int I\left\{\Gamma^*_Q(x) \leq c_{0.95}\right\} \phi(x - \mu) dx &= \int \left(1 - I\left\{\Gamma^*_Q(x) \geq c_{0.95}\right\}\right)\phi(x - \mu) dx
+	\\
+	&= 1 - \int I\left\{\Gamma^*_Q(x) \geq c_{0.95}\right\} \phi(x - \mu) dx
+\end{align*}
+Since the subtracted quantity is decreasing by \citep{anderson_integral_1955}, the quantity as a whole will be increasing.  Thus local power is obtained.
+
+\end{theorem}
+
 \sh{Proof Outline: \\
@@
 	\item Under local alternatives, $\sqrt{n}\hat{\boldsymbol{\psi}} \xrightarrow{d} N(\boldsymbol{c}, \Sigma)$
+	\item With a large enough sample size, and enough MC draws, we have that for each norm: 
     \item \textcolor{blue}{Think of Gamma as a funciton indexed by $\Sigma$ to allow it to be similar.
@@
 \end{itemize}} 
+\begin{align*}
+	\mathcal{L}\left(\Gamma_{\hat{\distv}}\left(\sqrt{n} \hat{\boldsymbol{\Psi}}(\boldsymbol{X})\right), \Gamma_{\distv}\left(\sqrt{n} \hat{\boldsymbol{\Psi}}(\boldsymbol{X})\right)\right) \rightarrow 0
+\end{align*}
 

### 2020-01-15 article_draft.tex
Updates from Overleaf

@@
 \end{align*}
+\textcolor{blue}{Change * so that they are not suppersetting both the rv and functions}
 \textcolor{blue}{This could be the min if smaller values indicate larger distances away from the norm (such as p-values).}
@@
 Consider a local alternative in which the true value of $\psi$ is shrinking towards zero at a root $n$ rate: $\psi = \underline{h}/\sqrt{n}$.
-For each potential norm, we assume the norm is convex.
+We assume that each potential norm is convex.
 This assumption can be relaxed to what was described by Eaton and Perlman (1991) (Concentration inequalitites for multivariate distributions: mv normal).
@@
 
-\begin{lemma}
+\begin{lemma} \textcolor{red}{plus $h$?}
 	\begin{align*}
-	\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}})	\xrightarrow{d}\Gamma^*_{\distv}(\distv) \text{ and } F^{-1}_{\Gamma^*_{\hat{\distv}}(\hat{\distv})}(\alpha) \rightarrow  F^{-1}_{\Gamma^*_{\distv}(\distv)}(\alpha)
+	\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}})	\xrightarrow{d}\Gamma^*_{\distv}(\rvv) \text{ and } F^{-1}_{\Gamma^*_{\hat{\distv}}(\hat{\distv})}(\alpha) \rightarrow  F^{-1}_{\Gamma^*_{\distv}(\rvv) }(\alpha)
 	\end{align*}
@@
 
-For now, we will assume that each of our $\Gamma_Q(x)$ is a unimodal, centrally symmetric function.
-In certain cases, $\Gamma_Q(x)$ is increasing $x$ moves away from the origin.
+For now, we will assume that each of our $\Gamma_Q$ is a unimodal, centrally symmetric function.
+In certain cases, $\Gamma_Q$ is increasing $x$ moves away from the origin.
 In these cases, for the purposes of this proof, instead use $\Gamma^{-1}_Q(x) = \left(\Gamma_Q(x)\right)^{-1}$.
@@
 	\label{lemma:min_cent_sym_unm}
-	Let $\Gamma_1(x), \dots, \Gamma_d(x)$ all be centrally symmetric, unimodal functions.
-Then $\Gamma^*(x) = \min\left\{\Gamma_1(x), \dots, \Gamma_d(x)\right\}$ is also centrally symmetric and unimodal.
+	Let $\Gamma_1, \dots, \Gamma_d$ all be centrally symmetric, unimodal functions.  Then $\Gamma^* = \min\left\{\Gamma_1, \dots, \Gamma_d\right\}$ is also centrally symmetric and unimodal.
 

### 2020-01-15 article_draft.tex
More changes to the proof

@@
 Consider
-\begin{align*}
-	\Gamma_\distv(x) &= Pr_\distv(||\rvv^* + x|| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv^*|| < c) \geq 0.8 \} \text{ and } \rvv^* \overset{d}{=} \rvv.
-\end{align*}
+\begin{align}
+	\Gamma_\distv(x) &= Pr_\distv(||\rvv^* + x|| > c_{0.8})  \text{ where }  c_{\distv, 0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv^*|| < c) \geq 0.8 \} \text{ and } \rvv^* \overset{d}{=} \rvv.
+\label{gamma:pow}
+\end{align}
 % \textcolor{blue}{What is $\rvv^* \overset{d}{=} \rvv$ telling us?
@@
 
-% Let $g_1, \dots, g_k$ be a list candiate norms, and let $\boldsymbol{Z}_1, \dots, \boldsymbol{Z}_B$ and $\boldsymbol{V}_1, \dots, \boldsymbol{V}_B$ independent draws from $Q$.
+% Let $g_1, \dots, g_k$ be a list candidate norms, and let $\boldsymbol{Z}_1, \dots, \boldsymbol{Z}_B$ and $\boldsymbol{V}_1, \dots, \boldsymbol{V}_B$ independent draws from $Q$.
 For each of the possible norms, let a p-value be defined using the following quantity:
@@
 \subsection{Correlation}
+\includegraphics[width = \linewidth]{uncor.jpg}
+\includegraphics[width = \linewidth]{some_core.jpg}
+\includegraphics[width = \linewidth]{lots_cor.jpg}
 % A wide variety of simulation settings are considered in this section to show the breath of settings in which the adaptive test can be used.
@@
 \begin{align*}
-	Pr_{\disto}\left(\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}}) \leq F^{-1}_{\Gamma^*_{\hat{\distv}}(\hat{\distv})}(\alpha)\right) \geq \alpha
+	Pr_{\disto}\left(\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}}) \leq F^{-1}_{\Gamma^*_{\hat{\distv}}(\hat{\rvv})}(\alpha)\right) \geq \alpha,
 \end{align*}
-Here (unlike other parts of the paper) small values of $\Gamma$ provide evidence against the null.  Values of $\Gamma$ can be thought of as similar to $p$-valuesx
+Where $\hat{\rvv} \sim \hat{\distv}$ and $\rvv \sim \distv$.
+Here (unlike other parts of the paper) small values of $\Gamma$ provide evidence against the null.
+Values of $\Gamma$ can be thought of as similar to $p$-values.
 
@@
 	\begin{align*}
-	\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}})	\xrightarrow{d}\Gamma^*_{\distv}(\rvv) \text{ and } F^{-1}_{\Gamma^*_{\hat{\distv}}(\hat{\distv})}(\alpha) \rightarrow  F^{-1}_{\Gamma^*_{\distv}(\rvv) }(\alpha)
+	\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}})	\xrightarrow{d}\Gamma^*_{\distv}(\rvv + \underline{h}) \text{ and } F^{-1}_{\Gamma^*_{\hat{\distv}}(\hat{\rvv})}(\alpha) \rightarrow  F^{-1}_{\Gamma^*_{\distv}(\rvv) }(\alpha)
 	\end{align*}
@@
 }
+
+For fixed every $t$,  
+\begin{align*}
+\Gamma^*_{\hat{\distv}}(t) \rightarrow \Gamma^*_{\distv}(t)	\text{ if } \Gamma_{i, \hat{\distv}}(t) \rightarrow \Gamma^*_{i, \distv}(t) \text{ for every } i \in \{1, 2, \dots, d\}
+\end{align*}
+
+The function defined in \eqref{gamma:pow} satisfy this condition
+
+\begin{lemma}
+	Let $t$ be fixed.
+By the consistency of our variance estimator, we know that $\hat{Z} \xrightarrow{d} Z$, and by continuous mapping theorem $||\hat{Z}|| \xrightarrow{d} ||Z||$.
+Thus it can be shown that $C_{\hat{\distv}, 0.8} \rightarrow C_{\distv, 0.8}$ because the distribution functions for both $\hat{\rvv}$ and $\rvv$ are continuous.
+
+	The above findings and Slutsky's theorem imply that $||\hat{Z} + \underline{t}|| - C_{\hat{\distv}, 0.8} \xrightarrow{d} ||Z - \underline{t}|| + C_{\distv, 0.8}$ so: 
+\begin{align*}
+	&\Gamma_{i, \hat{Q}}(t) = Pr_{\hat{\distv}}||\left(\hat{Z} + \underline{t}|| > C_{\hat{\distv}, 0.8}\right) = Pr_{\hat{\distv}}\left(||\hat{Z} + \underline{t}|| - C_{\hat{\distv}, 0.8} > 0\right) \rightarrow\\
+	& Pr_{\distv}\left(||Z + \underline{t}|| - C_{\distv, 0.8} > 0\right) = Pr_{\distv}\left(||Z + \underline{t}|| > C_{\distv, 0.8}\right) =\Gamma_{i, Q}(t) 
+\end{align*}
+% \begin{align*}
+% 	Pr(||\hat{\rvv}|| > c^-_{0.8}) \rightarrow Pr(||\rvv|| > c^-_{0.8}) < 0.8.
+% \end{align*}
+\end{lemma}
 

### 2020-01-22 article_draft.tex
Updates from Overleaf
added more edits

--- 2020-01-15 article_draft.tex
@@
 \newcommand{\pr}{\text{Pr}}
+\newcommand{\vmat}{\Sigma}
 \newcommand{\indep}{\raisebox{0.05em}{\rotatebox[origin=c]{90}{$\models$}}}
@@
 \newcommand{\distv}{Q}
+\newcommand{\pf}{\Phi}
+\newcommand{\gi}{\Upsilon}
 
@@
 Three different models for the outcome of interest ($Y$) will be considered.
-Letting $\varepsilon \sim N(0, 1)$ and be independent of $X$, the first model let $Y = \varepsilon$, the second has $Y = X_1 / 4$, and third has $Y = \sum_{k = 1}^10 \beta_k X_k + \varepsilon$ where $\beta_k = 0.15$ for $k = \{1, \dots, 5\}$, and $\beta_k = -0.1$ for $k = \{6 \dots 10\}$.
+Letting $\varepsilon \sim N(0, 1)$ and be independent of $X$, the first model let $Y = \varepsilon$, the second has $Y = X_1 / 4$, and third has $Y = \sum_{k = 1}^{10} \beta_k X_k + \varepsilon$ where $\beta_k = 0.15$ for $k = \{1, \dots, 5\}$, and $\beta_k = -0.1$ for $k = \{6 \dots 10\}$.
 in which Sample sizes of $100$ and $200$, dimensions of $10$, $50$, 100, 150, and 200, and $\rho$ of  $0, 0.5$, or $0.8$ will be considered,
@@
 % \textcolor{blue}{(when $Z$ is sampled from what?)}
-can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test. An example of $\Gamma_\distv$ is given below:
+can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test.
+The $\distv$ used to define $\Gamma_\distv$ will always be an estimated limiting distribution and the estimators considered for this method are all asymptotically linear.
+Thus, $\distv$ will always be a centered multivariate normal distribution so we can index our functions through $\vmat$, the variance covariance matrix of $\distv$, instead of $\distv$ itself.
+An example of $\Gamma_\vmat$ is given below:
 % any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.
@@
 Consider
-\begin{align*}
-	\Gamma_\distv(x) &= Pr_\distv(||\rvv^* + x|| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv^*|| < c) \geq 0.8 \} \text{ and } \rvv^* \overset{d}{=} \rvv.
-\end{align*}
+\begin{align}
+	\Gamma_\vmat(x) &= Pr_\distv(||\rvv^* + x|| > c_{0.8})  \text{ where }  c_{\vmat, 0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv^*|| < c) \geq 0.8 \} \text{ and } \rvv^* \overset{d}{=} \rvv.
+\label{gamma:pow}
+\end{align}
 % \textcolor{blue}{What is $\rvv^* \overset{d}{=} \rvv$ telling us?
@@
 Here because $c_{0.8}$ is not random so this is distinction does not need to be made.}
-% In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\distv(\rvv, ||\cdot||).$
+% In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\vmat(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\vmat(\rvv, ||\cdot||).$
 
@@
 
-To achieve this, first define $\Gamma_{1, \distv}(x), \dots, \Gamma_{p, \distv}(x)$ as collection of functions in which the functions only differ by the norm used in their definition. Next, define
+To achieve this, first define $\Gamma_{1, \vmat}(x), \dots, \Gamma_{p, \vmat}(x)$ as collection of functions in which the functions only differ by the norm used in their definition. Next, define
 % by defining a $\Gamma$ to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.
-For example, if we had $p$ different norms, $\norm_1, \dots, \norm_p$ and some summary function $\Gamma_\distv(x, ||\cdot||)$, we would define the adaptive version of $\Gamma$ as
+For example, if we had $p$ different norms, $\norm_1, \dots, \norm_p$ and some summary function $\Gamma_\vmat(x, ||\cdot||)$, we would define the adaptive version of $\Gamma$ as
 \begin{align*}
-	\Gamma^*_\distv(x) = \max\left\{\Gamma_{1, \distv}(x), \Gamma_{2, \distv}(x), \dots, \Gamma_{p, \distv}(x)\right\}.
+	\Gamma^*_\vmat(x) = \max\left\{\Gamma_{1, \vmat}(x), \Gamma_{2, \vmat}(x), \dots, \Gamma_{p, \vmat}(x)\right\}.
 \end{align*}
@@
 
-While this function is more complicated than before,  $\Gamma^*_{\distv}(\rvv))$ can still be compared to $\Gamma^*_{\distv}(\sqrt{n}\hat{\psi})$ to obtain a p-value.
-Also, while it may be difficult to obtain the exact distribution of $\Gamma_\distv^*(\rvv)$, the distribution is a function of $\distv$, so obtaining very good approximations of $\Gamma_\distv^*(\rvv)$ is possible by taking many draws from $\rvv$.
-This technique can be used both to estimate the function $\Gamma$ and to estimate $\Gamma^*_\distv(\rvv)$ .
+While this function is more complicated than before,  $\Gamma^*_{\vmat}(\rvv))$ can still be compared to $\Gamma^*_{\vmat}(\sqrt{n}\hat{\psi})$ to obtain a p-value.
+Also, while it may be difficult to obtain the exact distribution of $\Gamma_\vmat^*(\rvv)$, the distribution is a function of $\distv$, so obtaining very good approximations of $\Gamma_\vmat^*(\rvv)$ is possible by taking many draws from $\rvv$.
+This technique can be used both to estimate the function $\Gamma$ and to estimate $\Gamma^*_\vmat(\rvv)$ .
 
-% Let $g_1, \dots, g_k$ be a list candiate norms, and let $\boldsymbol{Z}_1, \dots, \boldsymbol{Z}_B$ and $\boldsymbol{V}_1, \dots, \boldsymbol{V}_B$ independent draws from $Q$.
+% Let $g_1, \dots, g_k$ be a list candidate norms, and let $\boldsymbol{Z}_1, \dots, \boldsymbol{Z}_B$ and $\boldsymbol{V}_1, \dots, \boldsymbol{V}_B$ independent draws from $Q$.
 For each of the possible norms, let a p-value be defined using the following quantity:
@@
 \end{align*}
-Under $H_0$, $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges to $Z$, and $\Sigma$ can be approximates with $\widehat{\Sigma} = \frac{1}{n}\sum_{i = 1}^n D(\boldsymbol{x}_i) D(\boldsymbol{x}_i)^\top$.
-Thus, in practice we will use an estimate of $\distv$, $\hat{\distv}$ which is distributed $N(0, \widehat{\Sigma})$ in place of $\distv$, and the random variable $\hat{\rvv}$ with distribution $\hat{\distv}$ in place of $\rvv$.
-Thus, the test statistic will be $\Gamma_{\hat{\distv}}(\sqrt{n} \hat{\boldsymbol{\psi}})$ and will be compared to $\Gamma_{\hat{\distv}}(\hat{\rvv})$.
+Under $H_0$, $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges to $Z$, and $\Sigma$ can be approximated with $\widehat{\Sigma} = \frac{1}{n}\sum_{i = 1}^n D(\boldsymbol{x}_i) D(\boldsymbol{x}_i)^\top$.
+In practice, a consistent estimator of $\vmat$, $\hat{\vmat}$ will be used in place of $\vmat$.
+Similarly, the random variable $\hat{\rvv}$ with distribution $\hat{\distv}$ will be used in place of $\rvv$.
+Thus, the test statistic will be $\Gamma_{\hat{\vmat}}(\sqrt{n} \hat{\boldsymbol{\psi}})$ and will be compared to $\Gamma_{\hat{\vmat}}(\hat{\rvv})$.
 
@@
 \begin{align*}
-	Pr_{\disto}\left(\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}}) \leq F^{-1}_{\Gamma^*_{\hat{\distv}}(\hat{\distv})}(\alpha)\right) \geq \alpha
+	Pr_{\disto}\left(\Gamma^*_{\hat{\vmat}}(\sqrt{n}\hat{\boldsymbol{\psi}}) \leq F^{-1}_{\Gamma^*_{\hat{\vmat}}(\hat{\rvv})}(\alpha)\right) > \alpha,
 \end{align*}
-Here (unlike other parts of the paper) small values of $\Gamma$ provide evidence against the null.  Values of $\Gamma$ can be thought of as similar to $p$-valuesx
 
-\begin{lemma} \textcolor{red}{plus $h$?}
+Where $\hat{\rvv} \sim \hat{\distv}$ and $\rvv \sim \distv$.
+Here (unlike other parts of the paper) small values of $\Gamma$ provide evidence against the null.
+Values of $\Gamma$ can be thought of as similar to $p$-values.
+\end{theorem}
+
+\begin{lemma}
+	\label{lemma:cont_of_gam}
+	The function:
 	\begin{align*}
-	\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}})	\xrightarrow{d}\Gamma^*_{\distv}(\rvv) \text{ and } F^{-1}_{\Gamma^*_{\hat{\distv}}(\hat{\distv})}(\alpha) \rightarrow  F^{-1}_{\Gamma^*_{\distv}(\rvv) }(\alpha)
+		\Gamma_{\Sigma}(t) = Pr_\distv(||\rvv^* + t|| > c_{0.8})  \text{ where }  c_{\vmat, 0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv^*|| < c) \geq 0.8 \} \text{ and } \rvv^* \sim N(0, \Sigma)
+	\end{align*}
+	is continuous with respect to $\Sigma$ and $t$.  
+\end{lemma}
+
+This lemma will follow because $\Gamma$ is the integral of a composition of bounded, continuous functions.
+
+\begin{proof}
+	The multivariate normal probability density function
+\begin{align*}
+	\phi(x, \mu, \Sigma) = \left(2\pi\right)^{-k} \text{det}\left({\Sigma}\right)^{- \frac{1}{2}} \exp\left(-\frac{1}{2} (x - \mu)^\top \Sigma^{-1}(x - \mu)\right) 
+\end{align*}	
+is continuous with respect to both $\Sigma$ and $t$.
+
+Since the exponential function, determinate, matrix inverses, and linear operators are all differentiable, they are also all continuous.
+Because the multivariate normal pdf is the composition of continuous functions, it is also continuous.
+
+It follows that if $\mu_n \rightarrow \mu$, and $\Sigma_n \rightarrow \Sigma$, then for each $x$, $\psi(x, \mu_n, \Sigma_n) \rightarrow \psi(x, \mu, \Sigma)$.
+This result and the dominated convergence theorem imply the corresponding CDF's are also continuous ($\phi(x, \hat{\mu}, \hat{\Sigma}) + \phi(x, \mu, \Sigma)$ can be used as the dominating measure):
+
+\begin{align*}
+	\pf_{\hat{\Sigma}, \hat{\mu}}\left(t \right) = \int_{||x|| < t} \phi(x, \hat{\mu}, \hat{\Sigma})dx \rightarrow \int_{||x|| < t} \phi(x, \mu, \Sigma)dx = \Phi_{\Sigma, \mu}(t).
+\end{align*}
+
+Because the normal cdf is continuous, we know the normal quantile function will be continuous as well.
+Also, because $\Phi_{\Sigma, \mu}(t)$ has a bounded derivative, it is uniformly continuous.
+These findings imply the following:
+
+\begin{align*}
+	\Gamma_{\hat{\Sigma}}(x) - \Gamma_{\Sigma}(x) &= Pr_{\hat{\distv}}(||\rvv^* + x|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) - Pr_{\distv}(||\rvv^* + x|| > \Phi^{-1}_{\Sigma, 0}(0.8))\\
+	&\leq \int_{\mathbb{R}^d} |\phi(t, x, \hat{\Sigma}) I\{||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \} - \phi(t, x, \Sigma) I\{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8) \}|dt \\ 
+	& = \int_{||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8), \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
+	& \hspace{5em} \int_{\Phi^{-1}_{\Sigma, 0}(0.8) \geq ||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8)} |\phi(t, x, \hat{\Sigma})|dt + \int_{\Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \geq ||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} | \phi(t, x, \Sigma)|dt \\
+	& \leq \int_{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
+	& \hspace{5em} \int_{\Phi^{-1}_{\Sigma, 0}(0.8) \geq ||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8)} \phi(t, x, \hat{\Sigma})dt + \int_{\Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \geq ||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} \phi(t, x, \Sigma)dt \\
+	& = \int_{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
+	& \hspace{5em} \Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) + \Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) \\
+	& = \int_{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
+	& \hspace{5em} \Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) - \left(\Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8))\right)+\\
+	& \hspace{5em} \left(\Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8))\right) +  \Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) \\
+	& = \int_{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
+	& \hspace{5em} \left(\Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) \right) - \left(\Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) -  \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8))\right)+\\
+	& \hspace{5em} \left(\Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8))\right) +  \Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) \\
+\end{align*}
+
+Taking the limit as $n \to \infty$ of the quantity above, we find that the first term is zero by dominated convergence theorem.
+The other four terms are also zero because of the uniform continuity of $\Phi_{\Sigma, x}$ and continuity of $\Phi^{-1}_{\Sigma, x}$
+\end{proof}
+
+\begin{lemma}
+Under local alternatives, 
+	\begin{align*}
+		\Gamma^*_{\hat{\Sigma}}(\sqrt{n} \hat{\boldsymbol{\psi}}) \xrightarrow{d} \Gamma^*_{\Sigma}(Z + \underline{h}) 
 	\end{align*}
 \end{lemma}
-\textcolor{blue}{
-	The proofs of these will be similar, but I am not sure quite how to do it.  While the following expansion is useful for me, I am not sure how to deal with each part:
+
+\begin{proof}
+	It was shown in Lemma \ref{lemma:cont_of_gam} that for each norm $||\cdot||$, $\Gamma_{\Sigma}(x)$ is continuous with respect to $\Sigma$ and $x$.
+This finding, the continuity of the max function, and because a composition of continuous functions is also continuous it follows that
+
 	\begin{align*}
-		Pr_{\disto}(\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}}) > t) - Pr_{\disto}(\Gamma^*_{\distv}(\distv) > t) & = Pr_{\disto}(\Gamma^*_{\hat{\distv}}(\sqrt{n}\hat{\boldsymbol{\psi}}) > t) - Pr_{\disto}(\Gamma^*_{\hat{\distv}}(\distv) > t) - \left( Pr_{\disto}(\Gamma^*_{\distv}(\distv) > t) - Pr_{\disto}(\Gamma^*_{\hat{\distv}}(\distv) > t) \right)
+		\Gamma^*_{\Sigma} \equiv \max\left\{\Gamma_{1, \Sigma}, \dots, \Gamma_{d, \Sigma}\right\}
 	\end{align*}
-	We can make arguments that the second two terms will cancel because of an assumed continuity of our function $\Gamma^*$ with respect to $Q$.
-We can also think of $\Gamma^*$ as being indexed by $Q$'s covariance matrix instead of its entire distribution to make more simple continuity arguments.\\
-	However, I am not exactly sure how to argue that the first two terms cancel.
-Initially I want to use the continuous mapping theorem.
-Because the function itself changes with $n$ and is random, I am not sure what to do.
-If we again use the continuity of $\Gamma$ could we argue that the values of the random functions will be close to the values of the non-random funcitons (where $\hat\distv$ is replaced by $\distv$)\\
-	My other idea was to assume that the function class of $\Gamma*$ is $P$-Donsker, but I think this may be overly complicated, and not necessary.
-}
+	is also continuos with respect to $\Sigma$ and $x$.
+Under local alternatives, $\sqrt{n} \hat{\boldsymbol{\psi}} \xrightarrow{d} Z + \underline{h}$ and $\hat{\Sigma} \xrightarrow{p} \Sigma$.
+It follows from the continuous mapping theorem that $\Gamma^*_{\hat{\Sigma}}(\sqrt{n} \hat{\boldsymbol{\psi}}) \xrightarrow{d} \Gamma^*_{\Sigma}(Z + \underline{h}) $
+\end{proof}
+
+It has now been establish that under local alternatives the distribution of our estimate converges to $\Gamma^*_{\Sigma}(Z + \underline{h})$.
+Denote the CDF of $\Gamma^*_{\Sigma}(Z + t)$ this distribution by $F_{\Sigma, t}$ and the corresponding quantile function of the distribution by $F^{-1}_{\Sigma, t}$.
+
+To prove unbiasedness at local alternatives, we show 
+\begin{align*}
+	F_{\Sigma, t}(F^{-1}_{\Sigma, 0}(1 - \alpha)) \geq F_{\Sigma, 0}(F^{-1}_{\Sigma, 0}(1 - \alpha)) = \alpha
+\end{align*}
+using results from the \citep{anderson_integral_1955} manuscript.
+% \textcolor{blue}{What is $\rvv^* \overset{d}{=} \rvv$ telling us?
+Don't we already know that the probabilities over both of these quantities are indexed by $Q$?
+Also, why use different notation at all?
+Why not just $\rvv^*$ for both?
+Here because $c_{0.8}$ is not random so this is distinction does not need to be made.}
+% In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\vmat(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\vmat(\rvv, ||\cdot||).$
 
@@
 \begin{align*}
-	g(\theta) = \int f_1(\theta) f_2(x - \theta)
+	g(\theta) = \int f_1(x) f_2(x - \theta)
 \end{align*}
@@
 
-For now, we will assume that each of our $\Gamma_Q$ is a unimodal, centrally symmetric function.
-In certain cases, $\Gamma_Q$ is increasing $x$ moves away from the origin.
-In these cases, for the purposes of this proof, instead use $\Gamma^{-1}_Q(x) = \left(\Gamma_Q(x)\right)^{-1}$.
+For now, we will assume that.
+We assume that our tests will always be define our tests in such a way that we reject the null when $\Gamma^*_{\hat{\vmat}}(\sqrt{n} \hat{\boldsymbol{\psi}}) > c$ for some $c$.
+It is expected that $\Gamma^*_{\vmat}(x)$  increases as $x$ moves away from the origin.
+For the purposes of this proof it will be useful to define new functions
+
+\begin{align*}
+	\gi_{i, \Sigma} \equiv \left(\gi_{i, \Sigma}\right)^{-1} \text{ and } \gi_{\Sigma}^* = \min\left\{\gi_{1, \Sigma}, \dots, \gi_{d, \Sigma}\right\}
+\end{align*}
+
+that decrease as $x$ moves away from the origin.
 
@@
 	\label{lemma:min_cent_sym_unm}
-	Let $\Gamma_1, \dots, \Gamma_d$ all be centrally symmetric, unimodal functions.  Then $\Gamma^* = \min\left\{\Gamma_1, \dots, \Gamma_d\right\}$ is also centrally symmetric and unimodal.
-
-	Centrally symmetric:
+	Let $\gi_1, \dots, \gi_d$ all be centrally symmetric, unimodal functions.  Then $\gi^* = \min\left\{\gi_1, \dots, \gi_d\right\}$ is also centrally symmetric and unimodal.
+\end{lemma}
+\begin{proof}
+Because each $\gi_i$ is a centrally symmetric and $\gi^*$ is a function of $x$ only through the $\gi_i$'s, $\gi^*$ is also centrally symmetric:
 	\begin{align*}
-	\Gamma^*(x) = \min\left\{\Gamma_1(x), \dots, \Gamma_d(x)\right\} = \min\left\{\Gamma_1(-x), \dots, \Gamma_d(-x)\right\} = \Gamma^*(-x)
+	\gi^*(x) = \min\left\{\gi_1(x), \dots, \gi_d(x)\right\} = \min\left\{\gi_1(-x), \dots, \gi_d(-x)\right\} = \gi^*(-x)
 	\end{align*}
-
-	Unimodal:
-	\begin{align*}
-		\left\{x : \Gamma^*(x) \geq k\right\} = \left\{x : \Gamma_1(x) \geq k, \dots, \Gamma_d(x) \geq k\right\} = \bigcap_{i = 1}^d \left\{x : \Gamma_i(x) \geq k \right\}
-	\end{align*}
-	The intersection of multiple convex sets is also convex, so $\Gamma^*(x)$ is unimodal.
-\end{lemma}
+The set $M^* \equiv \{x : \gi^*(x) \geq k\}$ contains all of the $x$ for which $\gi_i(x) \geq k$ for all $i \in \{1, \dots, d\}$.
+Thus $M^*$ is the intersection of all sets $M_i \equiv \{x : \gi_i(x) \geq k\}$.
+Each $M_i$ is convex because each $\gi_i$ is unimodal, and the intersection of a countable number of convex sets is convex.
+Thus $M^*$ is convex and $\gi^*$ is unimodal.
+	% \begin{align*}
+	% 	\left\{x : \gi^*(x) \geq k\right\} = \left\{x : \gi_1(x) \geq k, \dots, \gi_d(x) \geq k\right\} = \bigcap_{i = 1}^d \left\{x : \gi_i(x) \geq k \right\}
+	% \end{align*}
+\end{proof}
 
@@
 	Let $f(x)$ be a centrally symmetric, unimodal function.  Then $g(x) = I\left\{f(x) \geq c\right\}$ where $c \in \mathbb{R}$ is also centrally symmetric and unimodal. 
-
-	Centrally symmetric:
+\end{lemma}
+\begin{proof}
+Because $f$ is centrally symmetric and $g$ is a function of $x$ only through $g$, $g$ is also centrally symmetric:
 	\begin{align*}
@@
 
-	Unimodal:
-	If $k < 0$ or $k > 1$, then $\left\{x : g(x) \geq k\right\}$ will be the empty set or all of $\mathbb{R}^d$ respectively, and both sets are convex.  Otherwise, 
-	\begin{align*}
-		\left\{x : g(x) \geq k\right\} = \left\{x : I\left\{f(x) \geq c\right\} \geq k\right\} = \left\{x : f(x) \geq c\right\}
-	\end{align*}
-	which is convex by definition.
-\end{lemma}
-A consequence of lemmas \ref{lemma:min_cent_sym_unm} and \ref{lemma:indct_cent_sym_unm}, the function $I\left\{\Gamma^*_Q(x) \geq c_{0.95}\right\}$ is centrally symmetric and unimodal.
+	If $k < 0$ or $k > 1$, then $\left\{x : g(x) \geq k\right\}$ will be the empty set or all of $\mathbb{R}^d$ respectively, and both sets are convex.
+
+	Otherwise, the set $\left\{x : g(x) \geq k\right\} = \left\{x : I\left\{f(x) \geq c\right\} \geq k\right\}$.
+The indicator function will be greater than or equal to $k$ whenever $f(x) \geq c$, so $\left\{x : g(x) \geq k\right\} =\left\{x : f(x) \geq c\right\}$
+	which is convex because $f$ is unimodal.
+
+	Thus $g$ is unimodal.
+\end{proof}
+
+Because each $\gi_{\Sigma, i}$ is unimodal and centrally symmetric, lemma \ref{lemma:min_cent_sym_unm} implies $\gi^*_{\Sigma, i}$ is also unimodal and centrally symmetric.
+It follows from lemma \ref{lemma:indct_cent_sym_unm} and the previous finding that $I\left\{\gi^*_Q(x) \geq c_{0.95}\right\}$ is centrally symmetric and unimodal.
 
 \begin{align*}
-	\int I\left\{\Gamma^*_Q(x) \leq c_{0.95}\right\} \phi(x - \mu) dx &= \int \left(1 - I\left\{\Gamma^*_Q(x) \geq c_{0.95}\right\}\right)\phi(x - \mu) dx
+	\int I\left\{\Gamma^*_Q(x) > c_{0.95}\right\} \phi(x - \mu) dx &= \int I\left\{\gi^*_Q(x) < c_{0.95}^{-1}\right\} \phi(x - \mu) dx\\
+	& = \int \left(1 - I\left\{\gi^*_Q(x) \geq c^{-1}_{0.95}\right\}\right)\phi(x - \mu) dx
 	\\
-	&= 1 - \int I\left\{\Gamma^*_Q(x) \geq c_{0.95}\right\} \phi(x - \mu) dx
+	&= 1 - \int I\left\{\gi^*_Q(x) \geq c^{-1}_{0.95}\right\} \phi(x - \mu) dx
 \end{align*}
 Since the subtracted quantity is decreasing by \citep{anderson_integral_1955}, the quantity as a whole will be increasing.  Thus local power is obtained.
-
-\end{theorem}
 
@@
     \item \textcolor{blue}{Think of Gamma as a funciton indexed by $\Sigma$ to allow it to be similar.
-Also make some assumptions about how smooth $\Gamma$ is with respect to this parameters.
+Also make some assumptions about how smooth $\gi$ is with respect to this parameters.
 For any given value of the input ($t$) think about }
@@
 \begin{align*}
-	\mathcal{L}\left(\Gamma_{\hat{\distv}}\left(\sqrt{n} \hat{\boldsymbol{\Psi}}(\boldsymbol{X})\right), \Gamma_{\distv}\left(\sqrt{n} \hat{\boldsymbol{\Psi}}(\boldsymbol{X})\right)\right) \rightarrow 0
+	\mathcal{L}\left(\Gamma_{\hat{\vmat}}\left(\sqrt{n} \hat{\boldsymbol{\Psi}}(\boldsymbol{X})\right), \Gamma_{\vmat}\left(\sqrt{n} \hat{\boldsymbol{\Psi}}(\boldsymbol{X})\right)\right) \rightarrow 0
 \end{align*}
@@
 \end{document}
+
+% \begin{lemma} \textcolor{red}{plus $h$?}
+% 	\begin{align*}
+% 	\Gamma^*_{\hat{\vmat}}(\sqrt{n}\hat{\boldsymbol{\psi}})	\xrightarrow{d}\Gamma^*_{\vmat}(\rvv + \underline{h}) \text{ and } F^{-1}_{\Gamma^*_{\hat{\vmat}}(\hat{\rvv})}(\alpha) \rightarrow  F^{-1}_{\Gamma^*_{\vmat}(\rvv) }(\alpha)
+% 	\end{align*}
+% \end{lemma}
+% \textcolor{blue}{
+% 	The proofs of these will be similar, but I am not sure quite how to do it.  While the following expansion is useful for me, I am not sure how to deal with each part:
+% 	\begin{align*}
+% 		Pr_{\disto}(\Gamma^*_{\hat{\vmat}}(\sqrt{n}\hat{\boldsymbol{\psi}}) > t) - Pr_{\disto}(\Gamma^*_{\vmat}(\vmat) > t) & = Pr_{\disto}(\Gamma^*_{\hat{\vmat}}(\sqrt{n}\hat{\boldsymbol{\psi}}) > t) - Pr_{\disto}(\Gamma^*_{\hat{\vmat}}(\vmat) > t) - \left( Pr_{\disto}(\Gamma^*_{\vmat}(\vmat) > t) - Pr_{\disto}(\Gamma^*_{\hat{\vmat}}(\vmat) > t) \right)
+% 	\end{align*}
+% 	We can make arguments that the second two terms will cancel because of an assumed continuity of our function $\Gamma^*$ with respect to $Q$.
+We can also think of $\Gamma^*$ as being indexed by $Q$'s covariance matrix instead of its entire distribution to make more simple continuity arguments.\\
+% 	However, I am not exactly sure how to argue that the first two terms cancel.
+Initially I want to use the continuous mapping theorem.
+Because the function itself changes with $n$ and is random, I am not sure what to do.
+If we again use the continuity of $\Gamma$ could we argue that the values of the random functions will be close to the values of the non-random funcitons (where $\hat\distv$ is replaced by $\distv$)\\
+% 	My other idea was to assume that the function class of $\Gamma*$ is $P$-Donsker, but I think this may be overly complicated, and not necessary.
+% }
+
+% For fixed every $t$,  
+% \begin{align*}
+% \Gamma^*_{\hat{\vmat}}(t) \rightarrow \Gamma^*_{\vmat}(t)	\text{ if } \Gamma_{i, \hat{\vmat}}(t) \rightarrow \Gamma_{i, \vmat}(t) \text{ for every } i \in \{1, 2, \dots, d\}
+% \end{align*}
+
+% The function defined in \eqref{gamma:pow} satisfy this condition
+
+% \begin{lemma}
+% 	Let $t$ be fixed.
+By the consistency of our variance estimator, we know that $\hat{Z} \xrightarrow{d} Z$, and by continuous mapping theorem $||\hat{Z}|| \xrightarrow{d} ||Z||$.
+Thus it can be shown that $C_{\hat{\vmat}, 0.8} \rightarrow C_{\vmat, 0.8}$ because the distribution functions for both $\hat{\rvv}$ and $\rvv$ are continuous.
+
+% 	The above findings and Slutsky's theorem imply that $||\hat{Z} + \underline{t}|| - C_{\hat{\vmat}, 0.8} \xrightarrow{d} ||Z - \underline{t}|| + C_{\vmat, 0.8}$ so: 
+% \begin{align*}
+% 	&\Gamma_{i, \hat{Q}}(t) = Pr_{\hat{\distv}}||\left(\hat{Z} + \underline{t}|| > C_{\hat{\distv}, 0.8}\right) = Pr_{\hat{\distv}}\left(||\hat{Z} + \underline{t}|| - C_{\hat{\distv}, 0.8} > 0\right) \rightarrow\\
+% 	& Pr_{\distv}\left(||Z + \underline{t}|| - C_{\distv, 0.8} > 0\right) = Pr_{\distv}\left(||Z + \underline{t}|| > C_{\distv, 0.8}\right) =\Gamma_{i, Q}(t) 
+% \end{align*}
+% % \begin{align*}
+% % 	Pr(||\hat{\rvv}|| > c^-_{0.8}) \rightarrow Pr(||\rvv|| > c^-_{0.8}) < 0.8.
+% % \end{align*}
+% \end{lemma}

### 2020-01-22 article_draft.tex
Updates from Overleaf

@@
 
-It follows that if $\mu_n \rightarrow \mu$, and $\Sigma_n \rightarrow \Sigma$, then for each $x$, $\psi(x, \mu_n, \Sigma_n) \rightarrow \psi(x, \mu, \Sigma)$.
-This result and the dominated convergence theorem imply the corresponding CDF's are also continuous ($\phi(x, \hat{\mu}, \hat{\Sigma}) + \phi(x, \mu, \Sigma)$ can be used as the dominating measure):
+It follows that if $\mu_n \rightarrow \mu$, and $\Sigma_n \rightarrow \Sigma$, then for each $x$, $\phi(x, \mu_n, \Sigma_n) \rightarrow \phi(x, \mu, \Sigma)$.
+This result and the dominated convergence theorem imply the corresponding CDF's are also continuous ($\phi(x, \hat{\mu}, \hat{\Sigma}) + \phi(x, \mu, \Sigma)$ can be used as the dominating measure): \textcolor{blue}{(dominating function shouldn't depend on $n$)}
 
@@
 \end{align*}
+
+\textcolor{blue}{Show (or find reference showing that) $\Phi_{\Sigma_n,0}^{-1}(0.8)\rightarrow \Phi_{\Sigma,0}^{-1}(0.8)$ when $\Sigma_n\rightarrow \Sigma$.
+E.g., implicit function theorem will do this}
 
@@
 \begin{align*}
-	\Gamma_{\hat{\Sigma}}(x) - \Gamma_{\Sigma}(x) &= Pr_{\hat{\distv}}(||\rvv^* + x|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) - Pr_{\distv}(||\rvv^* + x|| > \Phi^{-1}_{\Sigma, 0}(0.8))\\
+	\left|\Gamma_{\hat{\Sigma}}(x) - \Gamma_{\Sigma}(x)\right| &= \left|Pr_{\hat{\distv}}(||\rvv^* + x|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) - Pr_{\distv}(||\rvv^* + x|| > \Phi^{-1}_{\Sigma, 0}(0.8))\right|\\
+	&= \left|\int_{\mathbb{R}^d} \phi(t, 0, \hat{\Sigma}) I\{||t+x|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \} - \phi(t, 0, \Sigma) I\{||t+x|| > \Phi^{-1}_{\Sigma, 0}(0.8) \}dt \right| \\ 
+	&= \left|\int_{\mathbb{R}^d} \phi(t, x, \hat{\Sigma}) I\{||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \} - \phi(t, x, \Sigma) I\{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8) \}dt \right| \\ 
 	&\leq \int_{\mathbb{R}^d} |\phi(t, x, \hat{\Sigma}) I\{||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \} - \phi(t, x, \Sigma) I\{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8) \}|dt \\ 
@@
 \end{align*}
+\textcolor{blue}{LHS should be $|\Gamma_{\Sigma_n}(x_n) - \Gamma_{\Sigma}(x)|$}
 
@@
 
-To prove unbiasedness at local alternatives, we show 
+To prove unbiasedness at local alternatives, we show \textcolor{blue}{$>$?}
 \begin{align*}
@@
 is centrally symmetric and ray decreasing.
-A function $f(x)$ on $\mathbb{R}^p$ is centrally symmetric if $f(-x) = f(x)$ for every $x$.
+A function $f :\mathbb{R}^p\rightarrow\mathbb{R}$ is centrally symmetric if $f(-x) = f(x)$ for every $x$.
 A function is unimodal if for every $k$, the set $\{x : f(x) \geq k\}$ is convex.
-A function $f(x)$ on $\mathbb{R}^p$ is ray decreasing if for every $x$ in $\mathbb{R}^p$, the function $g(\beta) = f(\beta x), \beta \in \mathbb{R}$ is a decreasing function of $\beta$.
+A function $f$ on $\mathbb{R}^p$ is ray decreasing if for every $x$ in $\mathbb{R}^p$, the function $g(\beta) = f(\beta x), \beta \in \mathbb{R}$ is a decreasing function of $\beta$.
 

### 2020-01-29 article_draft.tex
More Changes

@@
 
-\begin{document}
-\section{Introduction}
+\begin{document} \section{Introduction}
 
@@
 
-Work with \textcolor{red}{Simultaneous hypothesis testing}
+Work with \textcolor{red}{simultaneous hypothesis testing}
 %Tests capable of testing the union of multiple hypotheses simultaneously
@@
 \label{sec:prop_test_proc}
-Denote the estimator of $\boldsymbol{\psi}$ by $\hat{\boldsymbol{\Psi}}(\boldsymbol{\rvo})$ and let $\hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$.
-Suppose that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to some distribution $\distv(P)$ when $\disto \in \mathscr{M}_0$.
+Let $\hat{\boldsymbol{\Psi}}(\boldsymbol{\rvo})$ be an estimator of $\boldsymbol{\psi}$, and let $\hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$.
+Suppose for now that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to a normal distribution $\distv(P)$ in a model space $\mathcal{M}_0$.
 Any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$.
@@
 \begin{align*}
-	\Theta_0(r) = \left\{\omega : ||\omega||_2 \leq r\right\}.
+	\Theta_0(r) = \left\{\omega : \|\omega\|_2 \leq r\right\}.
 \end{align*}
@@
 \begin{align*}
-	r_\alpha(\disto) = \min\left\{r : Pr_{\distv}(||\rvv||_2 \leq r) \geq 1 - \alpha \right\}.
+	r_\alpha(\disto) = \min\left\{r : Pr_{\distv}(\|\rvv\|_2 \leq r) \geq 1 - \alpha \right\}.
 \end{align*}
-By constraining the possible regions we consider, we can now define our test in a simple algebraic form:
+By constraining the possible regions we consider, we can now define our test by:
 \begin{align*}
-	\text{reject } H_0 \text{ if } ||\sqrt{n} \hat{\boldsymbol{\psi}}||_2 \geq r_\alpha.
+	\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha.
 \end{align*}
-Similarly, p-values can now be simply defined as $Pr_Q(||\rvv||_2 \geq ||\sqrt{n} \hat{\boldsymbol{\psi}}||_2)$.
-%The quantity could also be used for a test, and since we know $Pr_Q(||\rvv||_2 \geq ||\sqrt{n} \hat{\boldsymbol{\Psi}}(\rvo)||_2)$ will be uniformly distributed on $(0, 1)$ asymptotically under the null, we can reject $H_0$ whenever this value is less than $\alpha$.
-
+Similarly, p-values can now be defined as $Pr_Q(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2)$.
+%The quantity could also be used for a test, and since we know $Pr_Q(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\Psi}}(\rvo)\|_2)$ will be uniformly distributed on $(0, 1)$ asymptotically under the null, we can reject $H_0$ whenever this value is less than $\alpha$.
 % As an example, a test is defined by a norm $p$ and level $\alpha$ which define the cutoff value;
 % \begin{align*}
-% 	c_{p, \alpha} = \min\left\{c : \frac{1}{B}\sum_{b = 1}^B I\left\{||\boldsymbol{Z}_b||_p \leq c\right\} \leq \alpha\right\},
+% 	c_{p, \alpha} = \min\left\{c : \frac{1}{B}\sum_{b = 1}^B I\left\{\|\boldsymbol{Z}_b\|_p \leq c\right\} \leq \alpha\right\},
 % \end{align*}
-% where $Z_1, \dots, Z_B$ are draws from $Q$. Reject the null if $||\sqrt{n}\hat{\boldsymbol{\psi}}||_p > c_{p, \alpha}$.
+% where $Z_1, \dots, Z_B$ are draws from $Q$. Reject the null if $\|\sqrt{n}\hat{\boldsymbol{\psi}}\|_p > c_{p, \alpha}$.
 
@@
 % \subsection{\textcolor{blue}{Creating a rejection region using a function}}
-% Note that above while our test was defined by rejecting or accepting based on if $\sqrt{n}\hat{\psi} \in \Theta_0$, we can also think about defining our test decision based on if some function, say $\Gamma_P(x, ||\cdot||)$ that maps from a value and distribution in $\mathbb{R}^d$, and a norm $||\cdot||$ to a real value is greater than zero.
-
-% Above we used a norm to constrain the considered rejection regions and allow for a test based on the value of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under the norm the distribution of $\rvv$ under the norm, both of which reside in $\mathbb{R}$.
-Above, we have used a norm to transform both the distribution of $\rvv$ and $\sqrt{n}\hat{\boldsymbol{\psi}}$ into $\mathbb{R}$.
-This allows for creating tests and calculating p-values in a similar manner to the univariate case.
+Above, a norm mapped the distribution of $\rvv$ and value  of $\sqrt{n}\hat{\boldsymbol{\psi}}$ into $\mathbb{R}$.  This distribution and value in $\mathbb{R}$ can be used to  calculate a p-value. 
 % \textcolor{blue}{I don't understand the end of this sentence}. 
-However, this approach also works with more complicated functions.
-For every distribution $\distv$ with support conntained in $\mathbb{R}^d$, let $\Gamma_{\distv}$ be a function mapping from  $\mathbb{R}^d$ to $\mathbb{R}$.
+This method for finding $p$-values can be used with more complicated functions.
+We can think of the above test as a function of the test statistic, $\sqrt{n}\hat{\boldsymbol{\psi}}$ and $\sqrt{n}\hat{\boldsymbol{\psi}}$'s limiting distribution.
+For the purposes of a test, the distribution used to define any function will be the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ which is distributed according to a multivariate normal with a mean of zero.
+Because the variance covariance matrix of this multivariate normal (denoted $\Sigma$) \textcolor{blue}{is one-to-one with the possible distributions}, we will index our functions $\Gamma$ by $\Sigma$.
+% For every distribution $\distv$ with support contained in $\mathbb{R}^d$, let $\Gamma_{\distv}$ be a function mapping from  $\mathbb{R}^d$ to $\mathbb{R}$.
+The distribution of $\Gamma_\distv(\rvv)$ (where $\rvv \sim \distv$) can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test.
 % \textcolor{blue}{I see $\Gamma_{\distv}$ being an $\mathbb{R}^d$ to $\mathbb{R}$ function.
@@
 Do you mean: ``For any distribution $Q$ with support contained in $\mathbb{R}^d$, let $\Gamma_Q$ be a function mapping from $\mathbb{R}^d$ to $\mathbb{R}$''?}
-The distribution of $\Gamma_\distv(\rvv)$ (where $\rvv \sim \distv$)
-% \textcolor{blue}{(when $Z$ is sampled from what?)}
-can be compared to $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to obtain p-values and define a test.
-The $\distv$ used to define $\Gamma_\distv$ will always be an estimated limiting distribution and the estimators considered for this method are all asymptotically linear.
-Thus, $\distv$ will always be a centered multivariate normal distribution so we can index our functions through $\vmat$, the variance covariance matrix of $\distv$, instead of $\distv$ itself.
-An example of $\Gamma_\vmat$ is given below:
+An example of a more complicated function $\Gamma_\vmat$ is given below:
 % any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.
@@
 However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.
-% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(||\rvv|| \geq ||x|| \right)$.
+% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(\|\rvv\| \geq \|x\| \right)$.
 For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.
@@
 Consider
+
 \begin{align}
-	\Gamma_\vmat(x) &= Pr_\distv(||\rvv^* + x|| > c_{0.8})  \text{ where }  c_{\vmat, 0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv^*|| < c) \geq 0.8 \} \text{ and } \rvv^* \overset{d}{=} \rvv.
+	\Gamma_\vmat(x) &= Pr_\distv(\|\tilde\rvv + x\| > c_{0.8})  \text{ where }  c_{\vmat, 0.8} \equiv \min_{c}\{c : Pr_\distv(\|\tilde\rvv\| < c) \geq 0.8 \} \text{ and } \tilde\rvv \overset{d}{=} \rvv.
 \label{gamma:pow}
 \end{align}
-% \textcolor{blue}{What is $\rvv^* \overset{d}{=} \rvv$ telling us?
+% \textcolor{blue}{What is $\tilde\rvv \overset{d}{=} \rvv$ telling us?
 Don't we already know that the probabilities over both of these quantities are indexed by $Q$?
@@
 Here because $c_{0.8}$ is not random so this is distinction does not need to be made.}
-% In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\vmat(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\vmat(\rvv, ||\cdot||).$
+% In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\vmat(\sqrt{n}\hat{\boldsymbol{\psi}}, \|\cdot\|)$ to $\Gamma_\vmat(\rvv, \|\cdot\|).$
 
@@
 % by defining a $\Gamma$ to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.
-For example, if we had $p$ different norms, $\norm_1, \dots, \norm_p$ and some summary function $\Gamma_\vmat(x, ||\cdot||)$, we would define the adaptive version of $\Gamma$ as
+For example, if we had $p$ different norms, $\norm_1, \dots, \norm_p$ and some summary function $\Gamma_\vmat(x, \|\cdot\|)$, we would define the adaptive version of $\Gamma$ as
 \begin{align*}
@@
 \end{align*}
-\textcolor{blue}{Change * so that they are not suppersetting both the rv and functions}
+\textcolor{blue}{Change * so that they are not suppersetting both the rv and functions.}
 \textcolor{blue}{This could be the min if smaller values indicate larger distances away from the norm (such as p-values).}
@@
 
-\sh{\subsection{Summary of how simulations are run}}
-
 \section{Simulation Study}
 \label{sec:sim_stdy}
+
 \subsection{Correlation}
+
+In the first set of experiments, we compare our method to both a Bonferroni based method and a tailor made method.
+The Bonferroni based method computes a p-value for each covariate using a marginal linear regression.
+If any p-value is smaller than the Bonferroni adjusted cutoff value, the null hypothesis is rejected.
+The method outlined by \citep{zhang_comment_2015} is similar to our method, but uses a parametric estimate of the correlation instead of using an influence function based estimator.
+Four versions of our test are displayed in these plots.
+Our test that uses the $\ell_2$ norm, our test that uses the $\ell_\infty$ or max norm, and our test that selects over five possible $\ell_p$ norms.
+The last version of our test selecs over many different versions of the following norm : $\|x\|_k = \sum_{i = 1}^k x_{(i)}^2$ where $x^2_{(i)}$ are the ordered statistics of $x^2$.
+
+In each setting, each test is run 1000 times.  The proportion of tests that reject the null is plotted for each simulation setting and for each test.
+
+\begin{figure}[]
+	\centering
 \includegraphics[width = \linewidth]{uncor.jpg}
+	\caption{Display of simulations for vector of covariates in this setting will be generated from a normal distribution with mean zero and a variance covariance of $\Sigma$ with $\Sigma_{ij}$ equal to $0$ when $i \neq j$ and equal to 1 when $i = j$.
+Three different models for the outcome of interest ($Y$) will are considered.
+Letting $\varepsilon \sim N(0, 1)$ and be independent of $X$, in the first model $Y = \varepsilon$, in the second $Y = X_1 / 4$, and in the third $Y = \sum_{k = 1}^{10} \beta_k X_k + \varepsilon$ where $\beta_k = 0.15$ for $k = \{1, \dots, 5\}$, and $\beta_k = -0.1$ for $k = \{6 \dots 10\}$.
+Sample sizes of $100$ and $200$, dimensions of $10$, $50$, $100$, $150$, and $200$ are considered.}
+	\label{fig:uncor}
+\end{figure}
+
+\begin{figure}[]
+	\centering
 \includegraphics[width = \linewidth]{some_core.jpg}
+	\caption{The same simulation settings as those used in Figure \ref{fig:uncor}, but $\Sigma_{ij} = 0.5$ for $i \neq j$.}
+	\label{fig:somecor}
+\end{figure}
+
+\begin{figure}[]
+	\centering
 \includegraphics[width = \linewidth]{lots_cor.jpg}
+	\caption{The same simulation settings as those used in Figure \ref{fig:uncor}, but $\Sigma_{ij} = 0.8$ for $i \neq j$.}
+	\label{fig:lotscor}
+\end{figure}
+
+We find that our procedure uses obtains relatively good power across a variety of settings.
+While in certain settings our test is beaten by that of Zhang and Laber, this is to be expected because their procedure is tailor made for the setting in which there is normal data that follows a linear model.
+We also find that the adaptive version o the test consitently outperforms the Bonferroni based method in all settings except those in which there is no between-covariate correlation.
+
 % A wide variety of simulation settings are considered in this section to show the breath of settings in which the adaptive test can be used.
@@
 	\begin{align*}
-		\Gamma_{\Sigma}(t) = Pr_\distv(||\rvv^* + t|| > c_{0.8})  \text{ where }  c_{\vmat, 0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv^*|| < c) \geq 0.8 \} \text{ and } \rvv^* \sim N(0, \Sigma)
+		\Gamma_{\Sigma}(t) = Pr_\distv(\|\tilde\rvv + t\| > c_{0.8})  \text{ where }  c_{\vmat, 0.8} \equiv \min_{c}\{c : Pr_\distv(\|\tilde\rvv\| < c) \geq 0.8 \} \text{ and } \tilde\rvv \sim N(0, \Sigma)
 	\end{align*}
@@
 \begin{align*}
-	\phi(x, \mu, \Sigma) = \left(2\pi\right)^{-k} \text{det}\left({\Sigma}\right)^{- \frac{1}{2}} \exp\left(-\frac{1}{2} (x - \mu)^\top \Sigma^{-1}(x - \mu)\right) 
+	\phi(x, \mu, \Sigma) = \left(2\pi\right)^{-k} \text{det}\left({\Sigma}\right)^{- \frac{1}{2}} \exp\left(-\frac{1}{2} (x - \mu)^\top \Sigma^{-1}(x - \mu)i\right) 
 \end{align*}	
@@
 It follows that if $\mu_n \rightarrow \mu$, and $\Sigma_n \rightarrow \Sigma$, then for each $x$, $\phi(x, \mu_n, \Sigma_n) \rightarrow \phi(x, \mu, \Sigma)$.
-This result and the dominated convergence theorem imply the corresponding CDF's are also continuous ($\phi(x, \hat{\mu}, \hat{\Sigma}) + \phi(x, \mu, \Sigma)$ can be used as the dominating measure): \textcolor{blue}{(dominating function shouldn't depend on $n$)}
+This result and the dominated convergence theorem imply the corresponding CDF's are also continuous \textcolor{blue}{($\phi(x, \hat{\mu}, \hat{\Sigma}) + \phi(x, \mu, \Sigma)$ can be used as the dominating measure): (dominating function shouldn't depend on $n$)}  To find a dominating measure, assume that $\vmat_n^{-1}$ is close enough to $\vmat^{-1}$ so the smallest eigenvalue is within $\varepsilon$ then bound the pdf using this fact and that $(x - \mu)^\top \Sigma^{-1}(x - \mu) = (x - \mu)^\top ADA^{-1}(x - \mu) \leq \|(x - \mu)\|^2 c$ where $c$ is the largest eigen value (can be done to provide oposite direction as well).
 
 \begin{align*}
-	\pf_{\hat{\Sigma}, \hat{\mu}}\left(t \right) = \int_{||x|| < t} \phi(x, \hat{\mu}, \hat{\Sigma})dx \rightarrow \int_{||x|| < t} \phi(x, \mu, \Sigma)dx = \Phi_{\Sigma, \mu}(t).
+	\pf_{\hat{\Sigma}, \hat{\mu}}\left(t \right) = \int_{\|x\| < t} \phi(x, \hat{\mu}, \hat{\Sigma})dx \rightarrow \int_{\|x\| < t} \phi(x, \mu, \Sigma)dx = \Phi_{\Sigma, \mu}(t).
 \end{align*}
@@
 Because the normal cdf is continuous, we know the normal quantile function will be continuous as well.
-Also, because $\Phi_{\Sigma, \mu}(t)$ has a bounded derivative, it is uniformly continuous.
+Potentially we can prove the existence of the inverse using the fact the CDF has a bounded derivative on all of $\mathbb{R}$.
+Let $\Sigma_n \rightarrow \Sigma$ and $h_n \rightarrow h$.
+Also, let $Q_n$ be a normal distribution with mean zero and variance-covaraince $\Sigma_n$.
 These findings imply the following:
@@
 \begin{align*}
-	\left|\Gamma_{\hat{\Sigma}}(x) - \Gamma_{\Sigma}(x)\right| &= \left|Pr_{\hat{\distv}}(||\rvv^* + x|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) - Pr_{\distv}(||\rvv^* + x|| > \Phi^{-1}_{\Sigma, 0}(0.8))\right|\\
-	&= \left|\int_{\mathbb{R}^d} \phi(t, 0, \hat{\Sigma}) I\{||t+x|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \} - \phi(t, 0, \Sigma) I\{||t+x|| > \Phi^{-1}_{\Sigma, 0}(0.8) \}dt \right| \\ 
-	&= \left|\int_{\mathbb{R}^d} \phi(t, x, \hat{\Sigma}) I\{||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \} - \phi(t, x, \Sigma) I\{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8) \}dt \right| \\ 
-	&\leq \int_{\mathbb{R}^d} |\phi(t, x, \hat{\Sigma}) I\{||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \} - \phi(t, x, \Sigma) I\{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8) \}|dt \\ 
-	& = \int_{||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8), \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
-	& \hspace{5em} \int_{\Phi^{-1}_{\Sigma, 0}(0.8) \geq ||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8)} |\phi(t, x, \hat{\Sigma})|dt + \int_{\Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \geq ||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} | \phi(t, x, \Sigma)|dt \\
-	& \leq \int_{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
-	& \hspace{5em} \int_{\Phi^{-1}_{\Sigma, 0}(0.8) \geq ||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8)} \phi(t, x, \hat{\Sigma})dt + \int_{\Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \geq ||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} \phi(t, x, \Sigma)dt \\
-	& = \int_{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
-	& \hspace{5em} \Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) + \Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) \\
-	& = \int_{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
-	& \hspace{5em} \Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) - \left(\Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8))\right)+\\
-	& \hspace{5em} \left(\Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8))\right) +  \Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) \\
-	& = \int_{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
-	& \hspace{5em} \left(\Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) \right) - \left(\Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) -  \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8))\right)+\\
-	& \hspace{5em} \left(\Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8))\right) +  \Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) \\
+	\left|\Gamma_{\Sigma_n}(h) - \Gamma_{\Sigma}(h)\right| &= \left|Pr_{\distv_n}(\|\tilde\rvv + h\| > \Phi^{-1}_{\Sigma_n, 0}(0.8)) - Pr_{\distv}(\|\tilde\rvv + h\| > \Phi^{-1}_{\Sigma, 0}(0.8))\right|\\
+	&= \left|\int_{\mathbb{R}^d} \phi(t, 0, \Sigma_n) I\{\|t+h\| > \Phi^{-1}_{\Sigma_n, 0}(0.8) \} - \phi(t, 0, \Sigma) I\{\|t+h\| > \Phi^{-1}_{\Sigma, 0}(0.8) \}dt \right| \\ 
+	&= \left|\int_{\mathbb{R}^d \setminus \left\{t : ||t|| =  \Phi^{-1}_{\Sigma, 0}(0.8) \right\}} \phi(t, h, \Sigma_n) I\{\|t\| > \Phi^{-1}_{\Sigma_n, 0}(0.8) \} - \phi(t, h, \Sigma) I\{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8) \}dt \right| \\
+	&\leq \int_{\mathbb{R}^d \setminus \left\{t : ||t|| =  \Phi^{-1}_{\Sigma, 0}(0.8) \right\}} |\phi(t, h, \Sigma_n) I\{\|t\| > \Phi^{-1}_{\Sigma_n, 0}(0.8) \} - \phi(t, h, \Sigma) I\{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8) \}|dt \\
 \end{align*}
-\textcolor{blue}{LHS should be $|\Gamma_{\Sigma_n}(x_n) - \Gamma_{\Sigma}(x)|$}
+The above quantity converges to zero by the dominated convergence theorem.
+
+\begin{align*}
+	& = \int_{\|t\| > \Phi^{-1}_{\Sigma_n, 0}(0.8), \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, h, \Sigma_n) - \phi(t, h, \Sigma)|dt + \\
+	& \hspace{5em} \int_{\Phi^{-1}_{\Sigma, 0}(0.8) \geq \|t\| > \Phi^{-1}_{\Sigma_n, 0}(0.8)} |\phi(t, h, \Sigma_n)|dt + \int_{\Phi^{-1}_{\Sigma_n, 0}(0.8) \geq \|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} | \phi(t, h, \Sigma)|dt \\
+	& \leq \int_{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, h, \Sigma_n) - \phi(t, h, \Sigma)|dt + \\
+	& \hspace{5em} \int_{\Phi^{-1}_{\Sigma, 0}(0.8) \geq \|t\| > \Phi^{-1}_{\Sigma_n, 0}(0.8)} \phi(t, h, \Sigma_n)dt + \int_{\Phi^{-1}_{\Sigma_n, 0}(0.8) \geq \|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} \phi(t, h, \Sigma)dt \\
+	& = \int_{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, h, \Sigma_n) - \phi(t, h, \Sigma)|dt + \\
+	& \hspace{5em} \Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) + \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) \\
+	& = \int_{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, h, \Sigma_n) - \phi(t, h, \Sigma)|dt + \\
+	& \hspace{5em} \Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) - \left(\Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8))\right)+\\
+	& \hspace{5em} \left(\Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8))\right) +  \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) \\
+	& = \int_{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, h, \Sigma_n) - \phi(t, h, \Sigma)|dt + \\
+	& \hspace{5em} \left(\Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) \right) - \left(\Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) -  \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8))\right)+\\
+% Also, because $\Phi_{\Sigma, \mu}(t)$ has a bounded derivative, it is uniformly continuous.
+	& \hspace{5em} \left(\Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8))\right) +  \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) \\
+\end{align*}
+% \textcolor{blue}{LHS should be $|\Gamma_{\Sigma_n}(x_n) - \Gamma_{\Sigma}(x)|$}
 
@@
 \begin{proof}
-	It was shown in Lemma \ref{lemma:cont_of_gam} that for each norm $||\cdot||$, $\Gamma_{\Sigma}(x)$ is continuous with respect to $\Sigma$ and $x$.
+	It was shown in Lemma \ref{lemma:cont_of_gam} that for each norm $\|\cdot\|$, $\Gamma_{\Sigma}(x)$ is continuous with respect to $\Sigma$ and $x$.
 This finding, the continuity of the max function, and because a composition of continuous functions is also continuous it follows that
@@
 % 	Let $t$ be fixed.
-By the consistency of our variance estimator, we know that $\hat{Z} \xrightarrow{d} Z$, and by continuous mapping theorem $||\hat{Z}|| \xrightarrow{d} ||Z||$.
+By the consistency of our variance estimator, we know that $\hat{Z} \xrightarrow{d} Z$, and by continuous mapping theorem $\|\hat{Z}\| \xrightarrow{d} \|Z\|$.
 Thus it can be shown that $C_{\hat{\vmat}, 0.8} \rightarrow C_{\vmat, 0.8}$ because the distribution functions for both $\hat{\rvv}$ and $\rvv$ are continuous.
 
-% 	The above findings and Slutsky's theorem imply that $||\hat{Z} + \underline{t}|| - C_{\hat{\vmat}, 0.8} \xrightarrow{d} ||Z - \underline{t}|| + C_{\vmat, 0.8}$ so: 
+% 	The above findings and Slutsky's theorem imply that $\|\hat{Z} + \underline{t}\| - C_{\hat{\vmat}, 0.8} \xrightarrow{d} \|Z - \underline{t}\| + C_{\vmat, 0.8}$ so: 
 % \begin{align*}
-% 	&\Gamma_{i, \hat{Q}}(t) = Pr_{\hat{\distv}}||\left(\hat{Z} + \underline{t}|| > C_{\hat{\distv}, 0.8}\right) = Pr_{\hat{\distv}}\left(||\hat{Z} + \underline{t}|| - C_{\hat{\distv}, 0.8} > 0\right) \rightarrow\\
-% 	& Pr_{\distv}\left(||Z + \underline{t}|| - C_{\distv, 0.8} > 0\right) = Pr_{\distv}\left(||Z + \underline{t}|| > C_{\distv, 0.8}\right) =\Gamma_{i, Q}(t) 
+% 	&\Gamma_{i, \hat{Q}}(t) = Pr_{\hat{\distv}}\|\left(\hat{Z} + \underline{t}\| > C_{\hat{\distv}, 0.8}\right) = Pr_{\hat{\distv}}\left(\|\hat{Z} + \underline{t}\| - C_{\hat{\distv}, 0.8} > 0\right) \rightarrow\\
+% 	& Pr_{\distv}\left(\|Z + \underline{t}\| - C_{\distv, 0.8} > 0\right) = Pr_{\distv}\left(\|Z + \underline{t}\| > C_{\distv, 0.8}\right) =\Gamma_{i, Q}(t) 
 % \end{align*}
 % % \begin{align*}
-% % 	Pr(||\hat{\rvv}|| > c^-_{0.8}) \rightarrow Pr(||\rvv|| > c^-_{0.8}) < 0.8.
+% % 	Pr(\|\hat{\rvv}\| > c^-_{0.8}) \rightarrow Pr(\|\rvv\| > c^-_{0.8}) < 0.8.
 % % \end{align*}
 % \end{lemma}
+
+% Note that above while our test was defined by rejecting or accepting based on if $\sqrt{n}\hat{\psi} \in \Theta_0$, we can also think about defining our test decision based on if some function, say $\Gamma_P(x, \|\cdot\|)$ that maps from a value and distribution in $\mathbb{R}^d$, and a norm $\|\cdot\|$ to a real value is greater than zero.
+
+% Above we used a norm to constrain the considered rejection regions and allow for a test based on the value of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under the norm the distribution of $\rvv$ under the norm, both of which reside in $\mathbb{R}$.

### 2020-02-12 article_draft.tex
Changes before moving sigma to estimator

@@
 
-\section{Proposed testing procedure}
+\section{proposed testing procedure}
 \label{sec:prop_test_proc}
-Let $\hat{\boldsymbol{\Psi}}(\boldsymbol{\rvo})$ be an estimator of $\boldsymbol{\psi}$, and let $\hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$.
-Suppose for now that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to a normal distribution $\distv(P)$ in a model space $\mathcal{M}_0$.
+% We want to define a test
+% All tests in high dimensions can be defined using acceptance / rejection regions.
+% First we consider a simple example. 
+As with all tests, our test will be defined by an acceptance region 
 Any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$.
-Letting $\rvv$ be distributed $\distv(\disto)$, the region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
+This region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
 \begin{align}
-  Pr_{\distv}\{\rvv \not \in \Theta_0(P)\} = 1 - \alpha \text{ for every } P \in \mathscr{M}_0.\label{eqn:alpha_rej}
+  PR_{\distv}\{\rvv \not \in \Theta_0(p)\} = 1 - \alpha \text{ for every } P \in \mathscr{M}_0 \text{ where } \rvv \sim \distv(\disto).\label{eqn:alpha_rej}
 \end{align}
-While there are infinitely many regions satisfying \eqref{eqn:alpha_rej},  we focus on a particular class of regions defined using $\ell_p$ norms.
+While there are infinitely many regions satisfying \eqref{eqn:alpha_rej},  we focus for now on a particular class of regions defined using $\ell_p$ norms which will naturally lead to a straightforward testing procedure.
 For simplicity, first consider regions defined using an $\ell_2$ norm:
+\begin{align}
+	\Theta_0(r) = \left\{\omega : \|\omega\|_2 \leq r\right\}. \label{eqn:region}
+\end{align}
+a region satisfying \eqref{eqn:alpha_rej} and \eqref{eqn:region} has a radius defined by: 
+% \textcolor{blue}{be consistent on indexing ``$pr$'' -- if you're going to write as $pr_{q(p)}$, do this throughout!}
 \begin{align*}
-	\Theta_0(r) = \left\{\omega : \|\omega\|_2 \leq r\right\}.
+	r_\alpha(\disto) = \min\left\{r : PR_{\distv}(\|\rvv\|_2 \leq r) \geq 1 - \alpha \right\}.
 \end{align*}
-A region satisfying \eqref{eqn:alpha_rej} has a radius defined by: 
-% \textcolor{blue}{be consistent on indexing ``$Pr$'' -- if you're going to write as $Pr_{Q(P)}$, do this throughout!}
-\begin{align*}
-	r_\alpha(\disto) = \min\left\{r : Pr_{\distv}(\|\rvv\|_2 \leq r) \geq 1 - \alpha \right\}.
-\end{align*}
-By constraining the possible regions we consider, we can now define our test by:
-\begin{align*}
-	\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha.
-\end{align*}
-Similarly, p-values can now be defined as $Pr_Q(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2)$.
-%The quantity could also be used for a test, and since we know $Pr_Q(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\Psi}}(\rvo)\|_2)$ will be uniformly distributed on $(0, 1)$ asymptotically under the null, we can reject $H_0$ whenever this value is less than $\alpha$.
-% As an example, a test is defined by a norm $p$ and level $\alpha$ which define the cutoff value;
-% \begin{align*}
-% 	c_{p, \alpha} = \min\left\{c : \frac{1}{B}\sum_{b = 1}^B I\left\{\|\boldsymbol{Z}_b\|_p \leq c\right\} \leq \alpha\right\},
-% \end{align*}
-% where $Z_1, \dots, Z_B$ are draws from $Q$. Reject the null if $\|\sqrt{n}\hat{\boldsymbol{\psi}}\|_p > c_{p, \alpha}$.
+By constraining the possible regions we consider, we can now define our test.
+Let $\hat{\boldsymbol{\Psi}} : \mathbb{R}^d \to \mathbb{R}$ be an estimator of $\boldsymbol{\psi}$, and let $\Hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$.
+Suppose for now that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to a normal distribution $\distv(p)$ when $p$ is contained in the model space  $\mathcal{M}_0$.
+Our test can be defined by
+\begin{align}
+\label{eqn:simp_test}
+	\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha,
+\end{align} and 
+ p-values can now be defined by $\text{Pr}_\distv(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2)$.
+This example illustrates how functions mapping into $\mathbb{R}$ (the $\ell_2$ norm in this case) allow us to define a test and p-value for $H_0$.
+Next consider this procedure in more generality.
+
+% \subsection{\textcolor{blue}{Creating a rejection region using a function}}
+Consider a function $\Gamma$, of a vector in $\mathbb{R}^d$ (corresponding to $\sqrt{n}\hat{\boldsymbol{\psi}}$) and a $d$ dimensional distribution function (corresponding to $\sqrt{n}\hat{\boldsymbol{\psi}}$'s limiting distribution).
+%For the example of the $\ell_2$ norm, the p-value calculation was a function of the limiting distribution $Z$ and the test statistic $\sqrt{n}\hat{\boldsymbol{\psi}}$
+Because the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under $H_0$ is always a mean zero multivariate normal, we will index our general functions $\Gamma$ by the $d$ by $d$ variance covariance matrix instead of the infinite dimensional distribution function.
+%   Under $H_0$, the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ will be a mean zero multivariate normal distribution. 
+An example of a more complicated function $\Gamma_\vmat$ is given below:
+% any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.
+Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.
+However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.
+% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(\|\rvv\| \geq \|x\| \right)$.
+For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.
+However, for other $\Gamma$, this may not be the case.
+Consider
+\begin{align}
+	\Gamma_\vmat(x) &= Pr_\distv(\|\tilde\rvv + x\| > c_{0.8})  \text{ where }  c_{\vmat, 0.8} \equiv \min_{c}\{c : Pr_\distv(\|\tilde\rvv\| < c) \geq 0.8 \} \text{ and } \tilde\rvv \sim N(0, \Sigma).
+\label{gamma:pow}
+\end{align}
+
+% \textcolor{blue}{I don't understand the end of this sentence}. 
+% While the the above test has nice properties (type one error control, consistency), it is not clear how this test will perform compared to other tests with similar properties.
 
@@
 
-% \subsection{\textcolor{blue}{Creating a rejection region using a function}}
-Above, a norm mapped the distribution of $\rvv$ and value  of $\sqrt{n}\hat{\boldsymbol{\psi}}$ into $\mathbb{R}$.  This distribution and value in $\mathbb{R}$ can be used to  calculate a p-value. 
-% \textcolor{blue}{I don't understand the end of this sentence}. 
-This method for finding $p$-values can be used with more complicated functions.
-We can think of the above test as a function of the test statistic, $\sqrt{n}\hat{\boldsymbol{\psi}}$ and $\sqrt{n}\hat{\boldsymbol{\psi}}$'s limiting distribution.
-For the purposes of a test, the distribution used to define any function will be the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ which is distributed according to a multivariate normal with a mean of zero.
-Because the variance covariance matrix of this multivariate normal (denoted $\Sigma$) \textcolor{blue}{is one-to-one with the possible distributions}, we will index our functions $\Gamma$ by $\Sigma$.
+While we have outlined a way of defining different tests of $H_0$, the natural next question is which test will perform the best.
+To explore this question, consider a simple example comparing the test described in equation \eqref{eqn:simp_test} with a test that is identical except it uses the maximum absolute value instead of $\ell_2$ norm.
+Figure \ref{fig:figure1}, panel (A) illustrates these two tests in $\mathbb{R}^2$.
+One hundred draws are taken from a bivariate normal distribution with mean zero and identity covariance matrix.
+All observations in panel (A) except the five with the largest $\ell_2$ norm are contained within the red circle.
+The blue squares in each panel contains all observations except the five with the largest $\ell_\infty$ norm.
+\textcolor{blue}{The circle and square represent the cutoffs of tests using empirical estimates of the $95^{\text{th}}$ percentile of $\ell_2(Z)$ and $\ell_\infty(Z)$ respectively.}
+Observations that fall within the purple region would result in a rejected null hypothesis if the $\ell_2$ norm was used to define the test, but not if the $\ell_\infty$ norm was used.
+The converse is true of the green region.
+Panels B shows draws from an alternative in which $\psi_2 \ne 0$ and $\psi_1 = 0$ and the $\ell_\infty$ norm performs better (achieves higher power).
+Panel C shows draws from an alternative in which $\psi_1$ and $\psi_2 \neq 0$ and the $\ell_2$ norm performs better.
+
+While both acceptance regions are created so to achieve type $1$ error control, depending on the alternative one test will outperform the other.
+Panel $B$ shows an alternative in which only $\psi_2$ is non-zero.
+Because the max norm only considers the largest coordinate, shifting each observations in only a single direction will have larger impact on the max norm of the observations compared to the $\ell_2$ norm.
+This trend is shown by the numerous green observations outside of the blue box (equivalent to rejecting $H_0$) and inside the red circle (equivalent to failing to reject $H_0$).
+In contrast, there is only a single observation that is outside the red circle, and inside the blue box.
+The converse trend is shown in panel $C$.
+Here, the $\ell_2$ norm performs better, because it takes into account both coordinates of the shift whereas the $\ell_\infty$ norm can only take into account one of these coordinate shift.
+
+The efficiency that can be gained from using the correct norm can be quite larger, especially when dimension grows.
+Work done by \citep{pinelis_schur2-concavity_2014} states that even for dimensions as small as $3$ the gains in asymptotic efficiency can become arbitrarily large between two potential norms.
+
 % For every distribution $\distv$ with support contained in $\mathbb{R}^d$, let $\Gamma_{\distv}$ be a function mapping from  $\mathbb{R}^d$ to $\mathbb{R}$.
@@
 Do you mean: ``For any distribution $Q$ with support contained in $\mathbb{R}^d$, let $\Gamma_Q$ be a function mapping from $\mathbb{R}^d$ to $\mathbb{R}$''?}
-An example of a more complicated function $\Gamma_\vmat$ is given below:
-% any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.
-Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.
-However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.
-% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(\|\rvv\| \geq \|x\| \right)$.
-For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.
-However, for other $\Gamma$, this may not be the case.
-Consider
-
-\begin{align}
-	\Gamma_\vmat(x) &= Pr_\distv(\|\tilde\rvv + x\| > c_{0.8})  \text{ where }  c_{\vmat, 0.8} \equiv \min_{c}\{c : Pr_\distv(\|\tilde\rvv\| < c) \geq 0.8 \} \text{ and } \tilde\rvv \overset{d}{=} \rvv.
-\label{gamma:pow}
-\end{align}
 % \textcolor{blue}{What is $\tilde\rvv \overset{d}{=} \rvv$ telling us?
@@
 
-While this method for defining tests allows for many different specifications, it often requires choosing a norm as part of the definition of $\Gamma$.
-Figure \ref{fig:figure1} shows that the power a test achieves can depend on the norm chosen.
-Consider the case when $d = 2$ and $100$ draws are taken from $Z$.
-Cutoffs can be obtained by transforming these data (using the $\ell_p$ norm) and taking the 95\% quantile of this transformed data.
-The perimeter of the acceptance region when using the $\ell_2$ and $\ell_{\infty}$ norm are given in red and blue respectively.
-If $\sqrt{n}\hat{\boldsymbol{\psi}}$ falls within any of the purple regions, using the $\ell_\infty$ norm would result in failing to reject $H_0$ and using the $\ell_2$ norm would result in rejecting $H_0$.
-The converse is true for the green regions.
-
 \subsection{Adaptive selection of a norm}
-In the previous section it was shown that a test can be defined by choosing a summarizing function and norm.
-However, the choice of norm influences the power of the test.
-In most scenarios it will not be clear a priori which norm will have maximal power for the true alternative.
+In the previous section we showed that a test can be defined with a summarizing function and norm.
+However, the choice of norm can influence the power of the test.
+In most scenarios it will not be clear a priori which test will have maximal power for the true alternative.
 The procedure proposed in this section adaptively selects a norm and it will be shown that this procedure achieves greater power than a test with a fixed norm, while maintaining type 1 error control.
@@
 \end{align*}
-\textcolor{blue}{Change * so that they are not suppersetting both the rv and functions.}
 \textcolor{blue}{This could be the min if smaller values indicate larger distances away from the norm (such as p-values).}
@@
 While this function is more complicated than before,  $\Gamma^*_{\vmat}(\rvv))$ can still be compared to $\Gamma^*_{\vmat}(\sqrt{n}\hat{\psi})$ to obtain a p-value.
-Also, while it may be difficult to obtain the exact distribution of $\Gamma_\vmat^*(\rvv)$, the distribution is a function of $\distv$, so obtaining very good approximations of $\Gamma_\vmat^*(\rvv)$ is possible by taking many draws from $\rvv$.
-This technique can be used both to estimate the function $\Gamma$ and to estimate $\Gamma^*_\vmat(\rvv)$ .
+Also, while it may be difficult to obtain the exact distribution of $\Gamma_\vmat^*(\rvv)$, the distribution is a function of $\vmat$, so obtaining good approximations of $\Gamma_\vmat^*(\rvv)$ is possible by taking many draws from $\rvv$.
 
@@
 \section{Discussion}
+\begin{itemize}
+	\item The most generalizable methods for hypothesis testing suffer from poor power, and ignore correlation between covariates.
+	\item Tests with high power are often difficult to generalize, working only for a single parameter, or relying on parametric assumptions.
+	\item We find a happy medium in this article.
+	\item Our method has comparable power to tailor made methods, without require modeling assumptions or parameters of interest.
+	\item We showed the methods flexibility through the use of three different data examples that include missing data and a causual model.
+	\item This method can also be expanded by using different $\Gamma$ functions, potentially optimizing of entire classes of $\Gamma$ functions with machine learning algorithms.
+	\item Also look at multiplying $\sqrt{n}\hat{\boldsymbol{\psi}}$ by inverse of influence function. 
+	\item There are issues with using parametric bootstrap, which can be avoided in certain cases by using a permutation test.
+\end{itemize}
+
+\section{Conclusion}
 
@@
 % Above we used a norm to constrain the considered rejection regions and allow for a test based on the value of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under the norm the distribution of $\rvv$ under the norm, both of which reside in $\mathbb{R}$.
+%the quantity could also be used for a test, and since we know $pr_q(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}(\rvo)\|_2)$ will be uniformly distributed on $(0, 1)$ asymptotically under the null, we can reject $h_0$ whenever this value is less than $\alpha$.
+% as an example, a test is defined by a norm $p$ and level $\alpha$ which define the cutoff value;
+% \begin{align*}
+% 	c_{p, \alpha} = \min\left\{c : \frac{1}{b}\sum_{b = 1}^b i\left\{\|\boldsymbol{z}_b\|_p \leq c\right\} \leq \alpha\right\},
+% \end{align*}
+% where $z_1, \dots, z_b$ are draws from $q$. reject the null if $\|\sqrt{n}\hat{\boldsymbol{\psi}}\|_p > c_{p, \alpha}$. 
+%the quantity could also be used for a test, and since we know $pr_q(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}(\rvo)\|_2)$ will be uniformly distributed on $(0, 1)$ asymptotically under the null, we can reject $h_0$ whenever this value is less than $\alpha$.
+% as an example, a test is defined by a norm $p$ and level $\alpha$ which define the cutoff value;
+% \begin{align*}
+% 	c_{p, \alpha} = \min\left\{c : \frac{1}{b}\sum_{b = 1}^b i\left\{\|\boldsymbol{z}_b\|_p \leq c\right\} \leq \alpha\right\},
+% \end{align*}
+% where $z_1, \dots, z_b$ are draws from $q$. reject the null if $\|\sqrt{n}\hat{\boldsymbol{\psi}}\|_p > c_{p, \alpha}$.

### 2020-02-12 article_draft.tex
Post adding sigma changes

@@
 \newcommand{\disto}{P}
+\newcommand{\tst}{\hat{\boldsymbol{t}}}
+\newcommand{\rvt}{Y}
 \newcommand{\rvv}{Z}
@@
 \label{sec:prop_test_proc}
-% We want to define a test
-% All tests in high dimensions can be defined using acceptance / rejection regions.
-% First we consider a simple example. 
-As with all tests, our test will be defined by an acceptance region 
-Any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$.
+For some test statistic $\tst$, any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$.
 This region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
 \begin{align}
-  PR_{\distv}\{\rvv \not \in \Theta_0(p)\} = 1 - \alpha \text{ for every } P \in \mathscr{M}_0 \text{ where } \rvv \sim \distv(\disto).\label{eqn:alpha_rej}
+  PR_{\distv}\{\rvv \not \in \Theta_0(p)\} = 1 - \alpha \text{ for every } P_0 \in \mathscr{M}_0 \text{ where } \tst \xrightarrow{P_0} \rvv \sim \distv(\disto).\label{eqn:alpha_rej}
 \end{align}
@@
 \begin{align*}
-	r_\alpha(\disto) = \min\left\{r : PR_{\distv}(\|\rvv\|_2 \leq r) \geq 1 - \alpha \right\}.
+	r_\alpha(\disto) = \min\left\{r : Pr_{\distv}(\|\rvv\|_2 \leq r) \geq 1 - \alpha \right\}.
 \end{align*}
@@
 Let $\hat{\boldsymbol{\Psi}} : \mathbb{R}^d \to \mathbb{R}$ be an estimator of $\boldsymbol{\psi}$, and let $\Hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$.
-Suppose for now that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to a normal distribution $\distv(p)$ when $p$ is contained in the model space  $\mathcal{M}_0$.
+Suppose for now that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to a normal distribution $\distv(P)$ when $P$ is contained in the model space  $\mathcal{M}_0$.
 Our test can be defined by
@@
 	\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha,
-\end{align} and 
- p-values can now be defined by $\text{Pr}_\distv(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2)$.
-This example illustrates how functions mapping into $\mathbb{R}$ (the $\ell_2$ norm in this case) allow us to define a test and p-value for $H_0$.
+\end{align} and p-values can now be defined by 
+\begin{align}
+	\text{Pr}_\distv(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2)
+\end{align}.
+
+% This example illustrates how functions mapping into $\mathbb{R}$ (the $\ell_2$ norm in this case) allow us to define a test and p-value for $H_0$.
+
+The test defined in \eqref{eqn:simp_test} is a function of three objects.
+The first was the chosen.
+The second was $\sqrt{n}\hat{\boldsymbol{\psi}}$.
+The third was the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$.
+To simplify this test, replace  $\sqrt{n}\hat{\boldsymbol{\psi}}$ with $ \tst \equiv \sqrt{n}\Sigma^{-1/2}\hat{\boldsymbol{\psi}}$.
+Because $\tst$ will always converge to a standard multivariate normal regardless of which $P \in \mathscr{M}_0$ is true \textcolor{blue}{(point to proof)}, for the test defined using $\tst$:
+
+\begin{align}
+\label{eqn:simp_test_simp}
+		\text{reject } H_0 \text{ if } \|\sqrt{n}\Sigma^{-1/2} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha \text{ where } r_\alpha = \min\left\{r : Pr(\|\rvt\|_2 \leq r) \geq 1 - \alpha \right\} \text{ where } \rvt \sim N(\boldsymbol{0}, I).
+\end{align}
+has the property that $r_\alpha$ will not vary between null distributions.
+Using this simplification, the result of this test is determined by the norm chosen and the value of the test statistic.
 Next consider this procedure in more generality.
-
 % \subsection{\textcolor{blue}{Creating a rejection region using a function}}
-Consider a function $\Gamma$, of a vector in $\mathbb{R}^d$ (corresponding to $\sqrt{n}\hat{\boldsymbol{\psi}}$) and a $d$ dimensional distribution function (corresponding to $\sqrt{n}\hat{\boldsymbol{\psi}}$'s limiting distribution).
+Consider a function $\Gamma$, of a vector in $\mathbb{R}^d$ (corresponding to $\tst$). While $\Gamma(x)$ should get larger as $x$ moves away from the null, $\Gamma$ can quite general.
 %For the example of the $\ell_2$ norm, the p-value calculation was a function of the limiting distribution $Z$ and the test statistic $\sqrt{n}\hat{\boldsymbol{\psi}}$
-Because the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under $H_0$ is always a mean zero multivariate normal, we will index our general functions $\Gamma$ by the $d$ by $d$ variance covariance matrix instead of the infinite dimensional distribution function.
+% Because the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under $H_0$ is always a mean zero multivariate normal, we will index our general functions $\Gamma$ by the $d$ by $d$ variance covariance matrix instead of the infinite dimensional distribution function.
 %   Under $H_0$, the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ will be a mean zero multivariate normal distribution. 
-An example of a more complicated function $\Gamma_\vmat$ is given below:
+An example of a more complicated $\Gamma$ is given below:
 % any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.
@@
 \begin{align}
-	\Gamma_\vmat(x) &= Pr_\distv(\|\tilde\rvv + x\| > c_{0.8})  \text{ where }  c_{\vmat, 0.8} \equiv \min_{c}\{c : Pr_\distv(\|\tilde\rvv\| < c) \geq 0.8 \} \text{ and } \tilde\rvv \sim N(0, \Sigma).
-\label{gamma:pow}
+	\Gamma(x) &= Pr_\distv(\|\rvt + x\| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr(\|\rvt\| < c) \geq 0.8 \} \text{ and } \rvt \sim N(0, I). \label{gamma:pow}
 \end{align}
-
+Define the test using $\Gamma$ as 
+\begin{align*}
+	\text{reject } H_0 \text{ if } \Gamma(\tst) > c_{1 - \alpha} \text { where } c_{1 - \alpha} = \min_{c}\{c : \text{Pr}(\Gamma(Y) \geq c) < \alpha\} \text{ where } Y \sim N(\boldsymbol{0}, I)
+\end{align*}
 % \textcolor{blue}{I don't understand the end of this sentence}. 
@@
 The blue squares in each panel contains all observations except the five with the largest $\ell_\infty$ norm.
-\textcolor{blue}{The circle and square represent the cutoffs of tests using empirical estimates of the $95^{\text{th}}$ percentile of $\ell_2(Z)$ and $\ell_\infty(Z)$ respectively.}
+\textcolor{blue}{The circle and square represent the cutoffs of tests using empirical estimates of the $95^{\text{th}}$ percentile of $\ell_2(\rvt)$ and $\ell_\infty(\rvt)$ respectively.}
 Observations that fall within the purple region would result in a rejected null hypothesis if the $\ell_2$ norm was used to define the test, but not if the $\ell_\infty$ norm was used.
@@
 
-To achieve this, first define $\Gamma_{1, \vmat}(x), \dots, \Gamma_{p, \vmat}(x)$ as collection of functions in which the functions only differ by the norm used in their definition. Next, define
+To achieve this, first define $\Gamma_{1}(x), \dots, \Gamma_{p}(x)$ as collection of functions in which the functions only differ by the norm used in their definition. Next, define
 % by defining a $\Gamma$ to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.
@@
 \begin{align*}
-	\Gamma^*_\vmat(x) = \max\left\{\Gamma_{1, \vmat}(x), \Gamma_{2, \vmat}(x), \dots, \Gamma_{p, \vmat}(x)\right\}.
+	\Gamma^*(x) = \max\left\{\Gamma_{1}(x), \Gamma_{2}(x), \dots, \Gamma_{p}(x)\right\}.
 \end{align*}
@@
 
-While this function is more complicated than before,  $\Gamma^*_{\vmat}(\rvv))$ can still be compared to $\Gamma^*_{\vmat}(\sqrt{n}\hat{\psi})$ to obtain a p-value.
-Also, while it may be difficult to obtain the exact distribution of $\Gamma_\vmat^*(\rvv)$, the distribution is a function of $\vmat$, so obtaining good approximations of $\Gamma_\vmat^*(\rvv)$ is possible by taking many draws from $\rvv$.
+While this function is more complicated than before,  $\Gamma^*(\rvt)$ can still be compared to $\Gamma^*(\tst)$ to obtain a p-value.
+Also, while it may be difficult to obtain the exact distribution of $\Gamma^*(\rvt)$, the distribution is a function of $\vmat$, so obtaining good approximations of $\Gamma^*(\rvt)$ is possible by taking many draws from $\rvt$.
 
@@
 The above procedure requires knowledge of the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ when $P \in \mathscr{M}_0$.
-To obtain an estimate of this limiting distribution, assume the vector of parameter estimates $\hat{\boldsymbol{\psi}}$, converges to a normal distribution with an estimable variance covariance matrix when properly centered and normalized.
+To obtain an estimate of this limiting distribution, assume $\sqrt{n}\hat{\boldsymbol{\psi}}$, converges to a normal distribution with an estimable variance covariance matrix when properly centered and normalized.
 Also assume each of the estimators $\hat{\boldsymbol{\psi}}_1, \dots, \hat{\boldsymbol{\psi}}_d$ of $\boldsymbol{\psi}_1, \dots, \boldsymbol{\psi}_d$ is asymptotically linear.
@@
 \begin{align*}
-    \sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right) \xrightarrow{d} Z \sim N\left(0, \Sigma\right)
+    \sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right) \xrightarrow{d} \rvv \sim N\left(0, \Sigma\right)
 \end{align*}
 Under $H_0$, $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges to $Z$, and $\Sigma$ can be approximated with $\widehat{\Sigma} = \frac{1}{n}\sum_{i = 1}^n D(\boldsymbol{x}_i) D(\boldsymbol{x}_i)^\top$.
-In practice, a consistent estimator of $\vmat$, $\hat{\vmat}$ will be used in place of $\vmat$.
-Similarly, the random variable $\hat{\rvv}$ with distribution $\hat{\distv}$ will be used in place of $\rvv$.
-Thus, the test statistic will be $\Gamma_{\hat{\vmat}}(\sqrt{n} \hat{\boldsymbol{\psi}})$ and will be compared to $\Gamma_{\hat{\vmat}}(\hat{\rvv})$.
+In practice, a consistent estimator of $\vmat$, $\hat{\vmat}$ will be used in place of $\vmat$ for the calculation of $\tst$.
+Thus, the test statistic will be $\Gamma(\tst)$ will be compared to $\Gamma(\rvt)$.
 

### 2020-03-11 article_draft.tex
More edits

@@
 \usepackage[table]{xcolor}
-\usepackage{amsmath,amsthm,amsfonts,dsfont,mathtools,float,setspace, booktabs, algorithm,tcolorbox,xparse,colortbl,longtable,array,multirow,wrapfig,float,pdflscape,tabu,threeparttable,threeparttablex,makecell,natbib}
+\usepackage{amsmath,amsthm,amsfonts,dsfont,mathtools,float,setspace, booktabs, algorithm,tcolorbox,xparse,colortbl,longtable,array,multirow,wrapfig,float,pdflscape,tabu, setspace, threeparttable,threeparttablex,makecell,natbib, pdfpages}
 \usepackage[normalem]{ulem}
@@
 \newcommand{\distv}{Q}
+\newcommand{\Gammaf}{\Gamma_{\Sigma}}
+\newcommand{\Gammafe}{\Gamma_{\hat{\Sigma}}}
 \newcommand{\pf}{\Phi}
@@
 \begin{document} \section{Introduction}
+\doublespacing
 
-\sh{In nearly all areas of high-dimensional statistics distinguishing between the important and unimportant predictors is of intrest}.
+It is common across scientific disciplines to be interested in predicting an outcome using some (potentially large) number of covariates.
+A first step to constructing accurate predictions is to find out if any covariate is associated with the outcome.
+Testing for the existence of an association can be done with a variety of existing methods, but frequently a trade off must be made between generalizability (ability to use the test for different parameters of interest and data generating mechanisms) and power (ability to detect an association when one exists).
+We propose an approach testing for the existence of an association between an outcome and any number of covariates that can be carried out for most parameters of interest that performs nearly as well as tests designed for a specific parameter and data generating mechanism.
+We compare our method with other modern methods in a simple simulated data setting.
+We then study the tests performance in a setting with a complex sampling scheme, and a setting with a complex parameter of interest.
+
+Back in the day, people used to think about which data to collect.
+However, as it became cheaper, more and more data are collected without knowing if any of it can be predictive of the outcome of interest.
+We gather many covariates rather than a single one, and whether any of them are predictive is an important first step to using them to do predictions.
+It used to be assumed that the covariates we collected were in some way predictive of the outcome.
+However, with data collection being so cheep, this is now a question that needs to be answered.
+
+% Multiple hypotheses testing has been an area of interest since at least [].  However finding an elegant
+
+% \sh{In nearly all areas of high-dimensional statistics distinguishing between the important and unimportant predictors is of intrest}.
 In genetics many candidate snips and their association with some outcome is of interest.
@@
 
-In the univariate case, once a measure of association is selected, standard approaches exist to construct asymptotically valid (and sometimes optimal) tests \citep{neyman_jerzy_ix._1933}.
+% In the univariate case, once a measure of association is selected, standard approaches exist to construct asymptotically valid (and sometimes optimal) tests \citep{neyman_jerzy_ix._1933}.
 In this setting, a test is considered optimal if it achieves the largest power for every alternative compared to every other test with the same type one error.
@@
 
-To illustrate this, consider two tests with equal type one error rates.
+% To illustrate this, consider two tests with equal type one error rates.
 Both test the null that both of two association measures $\psi_1$, $\psi_2$ are zero.
@@
 Bonferroni-based correction procedures have the advantage of being easy to apply to already existing tests, while guaranteeing family-wise error control.
-However, these tests suffer from low power, especially in cases where the probability of rejecting each hypothesis is highly correlated.
+However because these tests ignore the joint distribution of the test statistics, they suffer from low power, especially in cases where the probability of rejecting each hypothesis is highly correlated.
 
@@
 \end{align*}
-Last, let $\mathscr{M}$ denote the set of all possible distributions.  Define $\mathscr{M}_0 = \left\{ \disto \in \mathscr{M} : H_0 \text{ holds}  \right\}$
+
+Last, let $\mathscr{M}$ denote the set of all possible distributions, and let $\mathscr{M}_0  \subset \mathscr{M}$ be the subset of distributions in $\mathscr{M}$ satisfying $H_0$.
+
+We consider three different simulated data settings to study the test's performance.
 
 \subsection{Correlation Parameter}
-We will compare our method to both a simple bonferroni correction method, and the method described in \citep{zhang_comment_2015}.
+We will compare our method to a Bonferroni correct marginal testing method and the method described in \citep{zhang_comment_2015}.
 The settings considered will be the same as the firs setting in \citep{mckeague_adaptive_2015}.
@@
 
-The vector of covariates in this setting will be generated from a normal distribution with mean zero and a variance covariance of $\Sigma$ with $\Sigma_{ij}$ equal to $\rho$ when $i \neq j$ and equal to 1 when $i = j$, and .
-Three different models are considered.
+The vector of covariates in this setting will be generated from a normal distribution with mean zero and a variance covariance of $\Sigma$ with $\Sigma_{ij}$ equal to $\rho$ when $i \neq j$ and equal to 1 when $i = j$.
 Three different models for the outcome of interest ($Y$) will be considered.
-Letting $\varepsilon \sim N(0, 1)$ and be independent of $X$, the first model let $Y = \varepsilon$, the second has $Y = X_1 / 4$, and third has $Y = \sum_{k = 1}^{10} \beta_k X_k + \varepsilon$ where $\beta_k = 0.15$ for $k = \{1, \dots, 5\}$, and $\beta_k = -0.1$ for $k = \{6 \dots 10\}$.
-in which Sample sizes of $100$ and $200$, dimensions of $10$, $50$, 100, 150, and 200, and $\rho$ of  $0, 0.5$, or $0.8$ will be considered,
+For all considered settings, $\varepsilon \sim N(0, 1)$ and is independent of all $X$.
+In the first model $Y = \varepsilon$, in the second model $Y = X_1 / 4 + \varepsilon$, and in the third model $Y = \sum_{k = 1}^{10} \beta_k X_k + \varepsilon$ where $\beta_k = 0.15$ for $k = \{1, \dots, 5\}$, and $\beta_k = -0.1$ for $k = \{6 \dots 10\}$.
+Sample sizes of $100$ and $200$, dimensions of $10$, $50$, $100$, $150$, and $200$, and $\rho$ of  $0, 0.5$, and $0.8$ are considered.
+All combinations of model, sample size, dimension and $\rho$ are considered, and every test's performance is measured for all considered settings.
 
@@
 When $\Delta = 0$ we don't observe $Y$.
-The identifying assumption is $\Delta \indep Y | W$.
-The parameter of interest is the risk ratio,
+The identifying assumption is $\Delta \indep Y | W$, and the parameter of interest is the risk ratio under a poission working model for the probability that $Y = 1$.
+
 \begin{align*}
@@
 \end{align*}
+
 Using the identifying assumption, the observed data parameter is:
+
 \begin{align*}
@@
 
-\textcolor{blue}{Right now, it seems that the time for a single test is quite a bit larger for this test than it is for the correlation test (which is reasonable), though it may speed up if Superlearner can be improved.
-I am thinking of using similar simulation settings as was used before.}  There will be a single mechanism for the missingness, but it will be variable if the mechanism is known.
-There will be three settings for between $W$ correlation.
-All $W$ will be equally correlated, with $\rho = 0, 0.3$, or $0.7$.
-Dimension will \textcolor{blue}{(depending on computation time)} be $10, 50, 100$ and possibly $200$.
+The data are drawn from a binomial model:
 
-There will be three settings for the $\beta$'s in the data generating model:
 \begin{align*}
-    \log(Pr(Y = 1 | W)) = \beta_0 + W^\top \beta
+    \log(Pr(Y = 1 | W)) = \beta_0 + W^\top \beta.
 \end{align*}
-In one setting $\beta = 0$.
-In the second only one or two entries of $\beta$ will be non-zero.
-In the last setting, many of the entries of $\beta$ will be non-zero (possibly $70$ or $80$ percent of the entries).
+
+There will be three settings considered which determine  the values of the $\beta$'s in the data generating model:
+
+In all simulation settings the working model is used to take draws from $y$.
+In each setting, the vector $\boldsymbol{W}$ is draw from a multivariate normal with mean zero and covariance matrix $\Sigma_{DE2}$ where $\Sigma_{DE2, i, j} = 1$ for $i = j$ and $0.6$ for $i \neq j$.
+$A$ is drawn from a binomial distribution independent from $W$.
+For all three settings
+
+\begin{align*}
+	\text{logit}\left(Pr(Y = 1 | w, a)\right) = \sum_{i = 1}^{d} \beta_{i} w_i
+\end{align*}
+
+In the first setting $\beta_1 \dots \beta_d = 0$.
+In the second setting $\beta_1 = 3$ and $\beta_2, \dots \beta_d = 0$.
+In the last setting, $\beta_1 \dots \beta_5 = 1$, $\beta_6 \dots \beta_{10} = -1$ and $\beta_{11} \dots \beta_d = 0$.
+Data are generated from all three models with every possible combination of sample size ($n = 100$, or $200$), and dimension ($d = 10, 50, 100, 150$, or $200$).
 
 \subsection{Marginal Structural Model}
-For this marginal structural model, we are interested in if the average treatment is modified by any covariates.  The marginal structural model for each $W_j$ is defined by
+The third data example is a marginal structural model in which we test if the average treatment effect of a binary treatment $A$ is modified by any covariates $W_j$.
+The marginal structural model for each $W_j$ is defined by the working model:
+
 \begin{align*}
@@
 
+in which our parameter of interest is:
+
 \begin{align*}
@@
 \end{align*}
-The parameter of interest is $\beta_3^*$
-\textcolor{blue}{The other $W_j$'s are included in the analysis and are marginalized over, but are not part of the defined model.} I am planning on using the same simulation settings as above, but also including non-changing effects for $a$, but am open to other ideas.
+
+The parameter of interest is $\beta_3^*$, but is worth noting that parameter is different from a usual logistic regression parameter because we are marginalizing over all $w_i$, not just $w_j$.
+
+In all simulation settings the working model is used to take draws from $y$.
+In each setting, the vector $\boldsymbol{W}$ is draw from a multivariate normal with mean zero and covariance matrix $\Sigma_{DE3}$ where $\Sigma_{DE3, i, j} = 1$ for $i = j$ and $0.6$ for $i \neq j$.
+$A$ is drawn from a binomial distribution independent from $W$.
+For all three settings
+
+\begin{align*}
+	\text{logit}\left(Pr(Y = 1 | w, a)\right) = \beta_1 a + \sum_{i = 1}^{d} \beta_{i + 1} w_i + \sum_{j = 1}^d \gamma_{j} w_j a
+\end{align*}
+
+In every setting, $\beta_1 = 0.2$, $\beta_2, \dots \beta_{d/2 + 1} = 2/\sqrt{d}$, and $\beta_{d/2 + 1} \dots \beta_{d + 1} = 0$.
+In the first (null) setting, $\gamma_{1} \dots \gamma{d} = 0$.
+In the second setting, $\gamma_{1} = 3$ and $\gamma_{2} \dots \gamma_{d} = 0$.
+In the final setting $\gamma_{1} \dots \beta_{5} = 1, \gamma_{6} \dots \beta_{10} = -1$, and $\gamma_{11} \dots \gamma_{d} = 0$.
+Data are generated from all three models with every possible combination of sample size ($n = 100$, or $200$), and dimension ($d = 10, 50, 100, 150$, or $200$).
+
 % \subsection{\sh{Something else possibly Tim's parameter (has something to do with survival)}}
@@
 The test defined in \eqref{eqn:simp_test} is a function of three objects.
-The first was the chosen.
+The first was the chosen norm.
 The second was $\sqrt{n}\hat{\boldsymbol{\psi}}$.
-The third was the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$.
-To simplify this test, replace  $\sqrt{n}\hat{\boldsymbol{\psi}}$ with $ \tst \equiv \sqrt{n}\Sigma^{-1/2}\hat{\boldsymbol{\psi}}$.
+The third was the limiting distribution of $\hat{t} = \sqrt{n}\hat{\boldsymbol{\psi}}$.
+Note that the limiting distribution of $\hat{t}$ under the null will always be a multivariate normal with mean zero with some covariance $\Sigma$.
+Thus potential tests can be defined using the finite dimensional $\Sigma$ matrix rather than the infinite dimension distribution $Q(P)$.
+Choosing the $\ell_2$ norm, we can define our test by:
+
+% To simplify this test, replace  $\sqrt{n}\hat{\boldsymbol{\psi}}$ with $ \tst \equiv \sqrt{n}\Sigma^{-1/2}\hat{\boldsymbol{\psi}}$.
 Because $\tst$ will always converge to a standard multivariate normal regardless of which $P \in \mathscr{M}_0$ is true \textcolor{blue}{(point to proof)}, for the test defined using $\tst$:
 
-\begin{align}
-\label{eqn:simp_test_simp}
-		\text{reject } H_0 \text{ if } \|\sqrt{n}\Sigma^{-1/2} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha \text{ where } r_\alpha = \min\left\{r : Pr(\|\rvt\|_2 \leq r) \geq 1 - \alpha \right\} \text{ where } \rvt \sim N(\boldsymbol{0}, I).
-\end{align}
-has the property that $r_\alpha$ will not vary between null distributions.
-Using this simplification, the result of this test is determined by the norm chosen and the value of the test statistic.
+% \begin{align}
+% \label{eqn:simp_test_simp}
+% 		\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha \text{ where } r_\alpha = \min\left\{r : Pr(\|\rvt\|_2 \leq r) \geq 1 - \alpha \right\} \text{ where } \rvt \sim N(\boldsymbol{0}, \Sigma).
+% \end{align}
+
+% has the property that $r_\alpha$ will not vary between null distributions. Using this simplification, the result of this test is determined by the norm chosen and the value of the test statistic.
+
 Next consider this procedure in more generality. 
 % \subsection{\textcolor{blue}{Creating a rejection region using a function}}
-Consider a function $\Gamma$, of a vector in $\mathbb{R}^d$ (corresponding to $\tst$). While $\Gamma(x)$ should get larger as $x$ moves away from the null, $\Gamma$ can quite general.
+Consider a function $\Gammaf$, of a vector in $\mathbb{R}^d$ (corresponding to $\tst$). While $\Gammaf(x)$ should get larger as $x$ moves away from the null, $\Gammaf$ can be quite general.
 %For the example of the $\ell_2$ norm, the p-value calculation was a function of the limiting distribution $Z$ and the test statistic $\sqrt{n}\hat{\boldsymbol{\psi}}$
@@
 %   Under $H_0$, the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ will be a mean zero multivariate normal distribution. 
-An example of a more complicated $\Gamma$ is given below:
+An example of a more complicated $\Gammaf$ is given below:
 % any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.
@@
 \begin{align}
-	\Gamma(x) &= Pr_\distv(\|\rvt + x\| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr(\|\rvt\| < c) \geq 0.8 \} \text{ and } \rvt \sim N(0, I). \label{gamma:pow}
+	\Gammaf(x) &= Pr_\distv(\|\rvt + x\| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr(\|\rvt\| < c) \geq 0.8 \} \text{ and } \rvt \sim N(0, \Sigma). \label{gamma:pow}
 \end{align}
-Define the test using $\Gamma$ as 
+Define the test using $\Gammaf$ as 
 \begin{align*}
-	\text{reject } H_0 \text{ if } \Gamma(\tst) > c_{1 - \alpha} \text { where } c_{1 - \alpha} = \min_{c}\{c : \text{Pr}(\Gamma(Y) \geq c) < \alpha\} \text{ where } Y \sim N(\boldsymbol{0}, I)
+	\text{reject } H_0 \text{ if } \Gammaf(\tst) > c_{1 - \alpha} \text { where } c_{1 - \alpha} = \min_{c}\{c : \text{Pr}(\Gammaf(Y) \geq c) < \alpha\} \text{ where } Y \sim N(\boldsymbol{0}, \Sigma)
 \end{align*}
@@
 
-To achieve this, first define $\Gamma_{1}(x), \dots, \Gamma_{p}(x)$ as collection of functions in which the functions only differ by the norm used in their definition. Next, define
+To achieve this, first define $\Gamma_{\Sigma, 1}(x), \dots, \Gamma_{\Sigma, p}(x)$ as collection of functions in which the functions only differ by the norm used in their definition. Next, define
 % by defining a $\Gamma$ to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.
@@
 \begin{align*}
-	\Gamma^*(x) = \max\left\{\Gamma_{1}(x), \Gamma_{2}(x), \dots, \Gamma_{p}(x)\right\}.
+	\Gammaf^*(x) = \max\left\{\Gamma_{\Sigma, 1}(x), \Gamma_{\Sigma, 2}(x), \dots, \Gamma_{\Sigma, p}(x)\right\}.
 \end{align*}
@@
 
-While this function is more complicated than before,  $\Gamma^*(\rvt)$ can still be compared to $\Gamma^*(\tst)$ to obtain a p-value.
-Also, while it may be difficult to obtain the exact distribution of $\Gamma^*(\rvt)$, the distribution is a function of $\vmat$, so obtaining good approximations of $\Gamma^*(\rvt)$ is possible by taking many draws from $\rvt$.
+While this function is more complicated than before,  $\Gammaf^*(\rvt)$ can still be compared to $\Gammaf^*(\tst)$ to obtain a p-value.
+Also, while it may be difficult to obtain the exact distribution of $\Gammaf^*(\rvt)$, the distribution is a function of $\vmat$, so obtaining good approximations of $\Gammaf^*(\rvt)$ is possible by taking many draws from $\rvt$.
 
@@
 In practice, a consistent estimator of $\vmat$, $\hat{\vmat}$ will be used in place of $\vmat$ for the calculation of $\tst$.
-Thus, the test statistic will be $\Gamma(\tst)$ will be compared to $\Gamma(\rvt)$.
+Thus, the test statistic will be $\Gammaf(\tst)$ will be compared to $\Gammaf(\rvt)$.
 
@@
 To avoid inflated type one error, a permutation based test can be used.
-Here, $\hat{\distv}^\#$ is used to define $\Gamma$, and the test will compare $\Gamma_{\hat{\distv}}(\sqrt{n} \hat{\boldsymbol{\psi}})$ to $\Gamma_{\hat{\distv}}(\rvv^\#)$.
+Here, $\hat{\distv}^\#$ is used to define $\Gammaf$, and the test will compare $\Gamma_{\hat{\distv}}(\sqrt{n} \hat{\boldsymbol{\psi}})$ to $\Gamma_{\hat{\distv}}(\rvv^\#)$.
 To determine $\hat{\distv}^\#$, the $Y$'s from the observed data are permuted before calculating $\widehat \Sigma$.
@@
 
-In the first set of experiments, we compare our method to both a Bonferroni based method and a tailor made method.
+% In the first set of experiments, we compare our method to both a Bonferroni based method and a tailor made method.
 The Bonferroni based method computes a p-value for each covariate using a marginal linear regression.
@@
 
-In each setting, each test is run 1000 times.  The proportion of tests that reject the null is plotted for each simulation setting and for each test.
+% In each setting, each test is run 1000 times.  The proportion of tests that reject the null is plotted for each simulation setting and for each test.
 
@@
 
-We find that our procedure uses obtains relatively good power across a variety of settings.
+% We find that our procedure uses obtains relatively good power across a variety of settings.
 While in certain settings our test is beaten by that of Zhang and Laber, this is to be expected because their procedure is tailor made for the setting in which there is normal data that follows a linear model.
 We also find that the adaptive version o the test consitently outperforms the Bonferroni based method in all settings except those in which there is no between-covariate correlation.
+
+In the above figure, the rejection rates of six different tests are shown for a wide variety of settings.
+Data are generated from three different potential models.
+In the first model no covariates are directly associated with the outcome ($H_0$ holds), in the second model a single covariate is strongly directly associated with the outcome ($H_0$ does not hold), and in the third model ten covariates are directly associated with the outcome ($H_0$ does not hold).
+In all models the covariates are generated from a mean zero multivariate normal distribution $\Sigma$, where $\Sigma_{ij} = 0.8$ for $i \neq j$ and 1 for $i = j$.
+Each color of dots represents a different type of test.
+The red dots indicate a bonferroni adjusted marginal test for each covariates estimated correlation with the outcome.
+The light blue dots indicate performance of the test proposed by [Zhang and Laber].
+The other colors correspond to different variants of our test.
+Dark green and yellow dots indicate the performance of our test using only the $\ell_2$ or maximum absolute value norm respectively.
+The light green dots indicate the performance of our test when it adaptively select one of the $\ell_p$ norms.
+Brown dots indicate our tests performance when the test adaptively selects over various sum of squares norms.
+The dotted red line in each plot indicates the $0.05$ rejection rate that should be observed when $H_0$ holds.
+
+Because $H_0$ is true for model one, we expect the rejection rates for this model to be $0.05$.
+Figures \ref{fig:uncor}, \ref{fig:somecor}, and \ref{fig:lotscor} show these rates are achieved by every testing procedure except the bonferroni based test which is somewhat conservative.
+For the other two models, $H_0$ does not hold so these plots compare the powers between the different testing procedures.
+The bonferroni based test has the lowest power in all of the considered settings and for larger numbers of covariates this differences is larger.
+All other tests have similar power in most settings, with the test proposed by [Zhang and Laber] performing slightly better in most settings where a difference exists.
+All tests perform better for larger sample sizes, but tend to perform similarly for varying dimension and generating model.
+
+One setting in which the adaptive test performs poorly is in settings in which a single covariate is correlated with the outcome of interest and no covariates are correlated as seen for model 2 in figure \ref{fig:uncor}.
+This behavior could be due to the parameter estimates inability to be sparse even in settings when sparsity occurs.
+The many small errors in the parameter estimate across many covariates leads to a preference for the $\ell_2$ norm that obtains an overly optimistic estimate of power due to the accumulation of many small effects across all the covariates.
 
@@
 The sample sizes considered are $100$ and $500$.
+
+\subsection*{Two Phase Sampling Risk Ratio}
+
+\begin{figure}[]
+	\centering
+\includegraphics[width = \linewidth]{magnitude.pdf}
+	\caption{Rejection rates across three different data generating mechanisms.}
+	\label{fig:magnitude}
+\end{figure}
+
+\begin{figure}[]
+	\centering
+\includegraphics[width = \linewidth]{power.pdf}
+	\caption{Rejection rates across three different data generating mechanisms.}
+	\label{fig:magnitude}
+\end{figure}
+
+Here, we would expect that the $\ell_2$ norm would perform poorly in the model 2 setting while performing well in the model 3 setting, and that the max norm would perform poorly in the model three setting while performing well in the model two setting.
+However, we see the opposite behavior.
+Additionally, we find that our adaptive test performs well consistently across all alternatives.
+
+\begin{itemize}
+	\item The simulations we considered in this setting are $X$.  
+	\item We conducted the tests on each simulated dataset using our $R$ package.  
+	\item The test performs as we would expect, having \textcolor{blue}{This Power} in settings in which the alternative is large and there are many observations, and having \textcolor{blue}{This rejection rate} in settings where the null hypothesis holds.
+	\item The reasons for the test struggling to obtain power in \textcolor{blue}{THESE SETTINGS} could be due to a variety of factors.
+	\item This simulation shows that our method can be successfully applied to a setting in which there is a complex sampling scheme.
+\end{itemize}
 
@@
 \section{Discussion}
+In this paper, we have discussed the difficulties of creating multivariate test of no correlated coefficients.
+General methods are have wide applicability, but are often underpowered.
+More powerful methods are frequently difficult to understand, and will only work properly in narrow settings for a single parameter of interest.
+
+We described a test that addresses these issues, by achieving comparable performance to taylor made methods, while being applicable in a wide variety of settings.
+We have demonstrated the methods ability to compete with existing methods in section \ref{sec:sim_stdy}, and shown novel settings in which the method can also be performed.
+Data example 2 was an example of testing a relatively simple parameter (a risk ratio) in a setting with a non-standard sampling scheme.
+Data example 3 was an example of testing a more complex parameter (a parameter inside of a marginal structural model) for a straightforward sampling scheme.
+
+While our procedure does rely on asymptotic results to function properly for many parameters, in certain cases, a our test can be carried out using permutations of the data to obtain better finite sample properties.
+This is done by repeating our estimation procedure many times after randomly permuting the outcome variable.
+The method is used in our first data example, and could be used for our third data example.
+However, in certain settings with more complicated sampling schemes, the permutation based test is more difficult to implement because many of the outcomes are not even observed.
+
+While we have outlined some of the ways in which our method can be used, there are many other ways in which it can be extended improved.
+
+While we focused on the studying the limiting distribution of $\sqrt{n}\hat{\psi}$ once can also consider the limiting distribution of $\sqrt{n}\hat{\Sigma}^{-1/2}\hat{\psi}$.
+This estimator will always have a multivariate normal limiting distribution with an identity covariance matrix, which simplifies notation by always having a single limiting distribution.
+It also simplifies proofs, and potentially could allow for analytical solutions for which norm (or weighted average of norms) would provide the best power.
+However, this estimator runs into issues when $p > n$ and $\hat{\Sigma}^{-1/2}$ becomes impossible to estimate because of the rank deficiency of the variance estimator.
+While this problem still technically exist when indexing our $\Gamma$'s by $\hat{\Sigma}$, using a multiplier bootstrap to take draws from $N(0, \Sigma)$ avoids the computation issues of having a degenerate estimate of the limiting distributions variance matrix.
+
+While changing the test statistic as described above has major hurdles to overcome to be implemented in $p > n$ settings, there are other extensions or generalizations of our procedure that are possible without much change.
+While we considered one set of $\Gammaf$ funcitons in this article, any set of reasonable $\Gammaf$ functions could be used.
+These $\Gammaf$ functions could even be picked by machine learning methods used for classification.
+The classifier would provide a probability that any observation was generated from the null distribution.
+Doing this provides a more rich set of $\Gammaf$ over which to select, and has the potential to provide large increases in test performance.
+One would expect that a classifier would perform better better when data are generated at an alternative versus at the null.
+Thus one could reject when the classification performance is especially large.
+
+While our procedure currently only selects a single norm to calculate the test statistic, it is possible to also consider an estimator that is a weighted average of the many different norms.
+The weights would be estimates of the probability that each norm was optimal.
+These probabilities could be estimated by taking many draws from a normal with mean $\sqrt{n}\hat{\boldsymbol{\psi}}$ and variance $\hat{\Sigma}$ and finding the optimal norm for each of these draws.
+This method while being more computationally costly, could potentially be shown to be optimal in the sense that it would maximize the average power of all tests based on the specified family of norms for each local alternative.
+
+While $\ell_p$ norms were used throughout this paper, one issue observed with our test is that it selects the $\ell_2$ norm more frequently than it should, likely because of the many small estimates for parameters that are not associated with the outcome.
+One could consider a slightly modified norm that sets to zero all component values of the vector that are less than some value (say $2 \times \text{var}(X)\sqrt{n}$).
+This would hopefully solve issues of small values close to zero causing incorrect selection of norms that perform well when there are many small effects.
+
 \begin{itemize}
-	\item The most generalizable methods for hypothesis testing suffer from poor power, and ignore correlation between covariates.
-	\item Tests with high power are often difficult to generalize, working only for a single parameter, or relying on parametric assumptions.
-	\item We find a happy medium in this article.
-	\item Our method has comparable power to tailor made methods, without require modeling assumptions or parameters of interest.
-	\item We showed the methods flexibility through the use of three different data examples that include missing data and a causual model.
-	\item This method can also be expanded by using different $\Gamma$ functions, potentially optimizing of entire classes of $\Gamma$ functions with machine learning algorithms.
+	\item Problems with Multiple hypothesis testing
+\begin{itemize}
+		\item The problem of multiple hypothesis testing offers many possibilities, but no great way to choose between them. 
+		\item The most generalizable methods for hypothesis testing (Bonferroni) suffer from poor power, and ignore correlation between covariates.
+		\item Specialized tests often attain high power, but come with certain drawbacks.
+\end{itemize}
+\item Specialized tests often attain high power, but come with certain drawbacks.
+\begin{itemize}
+	\item Only work for a single parameter
+	\item require parametric assumptions about the data generating mechanism.
+	\item unknown by individuals who would could potentially use the test.
+	\item Only work for simple data generating mechanisms
+\end{itemize}
+\item We have shown where our method finds a happy medium because it works well in many settings
+\begin{itemize}
+	\item We show our method is competitive with tailor made methods, and can outperform bonferroni
+	\item Our method is generalizable to many different parameters.
+	\item Our method can be used for complex sampling schemes as shown in data example 2 and it attains reasonable power in these settings.
+	\item Our method can be used for complex parameters (shown in data example 3) 
+\end{itemize}
+\item Potential extensions of the method
+\begin{itemize}
+	\item This method can also be expanded by using different $\Gammaf$ functions, potentially optimizing of entire classes of $\Gammaf$ functions with machine learning algorithms.
 	\item Also look at multiplying $\sqrt{n}\hat{\boldsymbol{\psi}}$ by inverse of influence function. 
 	\item There are issues with using parametric bootstrap, which can be avoided in certain cases by using a permutation test.
+\end{itemize}
 \end{itemize}
@@
 
+While each set of performance measures will require a proof that they are centrally symmetric and unimodal, we will show that the estimate power performance measure is centrally symmetric and unimodal.
+Consider the power function.
+
+\begin{align*}
+	\Gammaf(\mu) & = \int I\left\{\|x\|_p > c\right\} \phi_{\Sigma}(x - \mu)
+\end{align*}
+
+Consider two values $\mu_1$, $\mu_2$ such that $ \Gammaf(\mu_1), \Gammaf(\mu_2) \geq k$.  Now, consider $\Gammaf\left(t\mu_1 + (1 - t)\mu_2\right)$
+
+\begin{align*}
+	\Gammaf\left(t\mu_1 + (1 - t)\mu_2\right) & = \int I\left\{\|x\|_p > c\right\} \phi_{\Sigma}(x - t\mu_1 + (1 - t)\mu_2)dx \\
+	& =  \int I\left\{\|x\|_p > c\right\} \phi_{\Sigma}(t(x - \mu_1) + (1 - t)(x - \mu_2))dx\\
+	& \geq  \int I\left\{\|x\|_p > c\right\} \left[t\phi_{\Sigma}(x - \mu_1)) + (1 - t)\phi_{\Sigma}(x - \mu_2)\right]dx \\
+	& = t \int I\left\{\|x\|_p > c\right\} \phi_{\Sigma}(x - \mu_1))dx + (1 - t) \int I\left\{\|x\|_p > c\right\} \phi_{\Sigma}(x - \mu_2)dx \\
+	& = t \Gammaf(\mu_1) + (1 - t) \Gammaf(\mu_2) \geq k	
+\end{align*}
+The inequality on the third line comes from the fact that multivariate normal pdf is concave.
+
 \sh{Proof Outline: \\

### 2020-03-11 article_draft.tex
Updates from Overleaf

--- 2020-02-12 article_draft.tex
@@
 
-\sh{In nearly all areas of high-dimensional statistics distinguishing between the important and unimportant predictors is of intrest}.
+\sh{In nearly all areas of high-dimensional statistics, distinguishing between the important and unimportant predictors is of interest}.
 In genetics many candidate snips and their association with some outcome is of interest.
@@
 
-\section{proposed testing procedure}
+\section{Proposed Testing Procedure}
 \label{sec:prop_test_proc}
 For some test statistic $\tst$, any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$.
+\textcolor{blue}{Let $ \tst \xrightarrow{P_0} \rvv \sim \distv(\disto)$}.
 This region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
 \begin{align}
-  PR_{\distv}\{\rvv \not \in \Theta_0(p)\} = 1 - \alpha \text{ for every } P_0 \in \mathscr{M}_0 \text{ where } \tst \xrightarrow{P_0} \rvv \sim \distv(\disto).\label{eqn:alpha_rej}
+  Pr_{\distv}\{\rvv \not \in \Theta_0(p)\} = 1 - \alpha \text{ for every } P_0 \in \mathscr{M}_0.\label{eqn:alpha_rej}
 \end{align}
-While there are infinitely many regions satisfying \eqref{eqn:alpha_rej},  we focus for now on a particular class of regions defined using $\ell_p$ norms which will naturally lead to a straightforward testing procedure.
-For simplicity, first consider regions defined using an $\ell_2$ norm:
+While there are many regions satisfying \eqref{eqn:alpha_rej},  we focus for now on a particular class of regions defined using $\ell_p$ norms which will naturally lead to a straightforward testing procedure.
+For simplicity, \textcolor{blue}{we} first consider regions defined using an $\ell_2$ norm:
 \begin{align}
@@
 \end{align}
-a region satisfying \eqref{eqn:alpha_rej} and \eqref{eqn:region} has a radius defined by: 
+A region satisfying \eqref{eqn:alpha_rej} and \eqref{eqn:region} has a radius defined by: 
 % \textcolor{blue}{be consistent on indexing ``$pr$'' -- if you're going to write as $pr_{q(p)}$, do this throughout!}
@@
 \end{align*}
-By constraining the possible regions we consider, we can now define our test.
+We now construct a test using the region defined above.
 Let $\hat{\boldsymbol{\Psi}} : \mathbb{R}^d \to \mathbb{R}$ be an estimator of $\boldsymbol{\psi}$, and let $\Hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$.
@@
 	\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha,
-\end{align} and p-values can now be defined by 
-\begin{align}
-	\text{Pr}_\distv(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2)
-\end{align}.
+\end{align} and the corresponding p-values are defined by $
+	\text{Pr}_\distv(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2)$.
 
 % This example illustrates how functions mapping into $\mathbb{R}$ (the $\ell_2$ norm in this case) allow us to define a test and p-value for $H_0$.
-
-The test defined in \eqref{eqn:simp_test} is a function of three objects.
-The first was the chosen.
+We can vary any of these three things to give us another test=
+The test defined in \eqref{eqn:simp_test} depends on three objects.
+The first was the chosen norm.
 The second was $\sqrt{n}\hat{\boldsymbol{\psi}}$.

### 2020-03-11 article_draft.tex

--- 2020-03-11 article_draft.tex
@@
 	\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha,
-\end{align} and p-values can now be defined by 
-\begin{align}
-	\text{Pr}_\distv(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2)
-\end{align}.
+\end{align} and the corresponding p-values are defined by $
+	\text{Pr}_\distv(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2)$.
 
@@
 
-The test defined in \eqref{eqn:simp_test} is a function of three objects.
+We can vary any of these three things to give us another test=
+The test defined in \eqref{eqn:simp_test} depends on three objects.
 The first was the chosen norm.
 The second was $\sqrt{n}\hat{\boldsymbol{\psi}}$.
-The third was the limiting distribution of $\hat{t} = \sqrt{n}\hat{\boldsymbol{\psi}}$.
-Note that the limiting distribution of $\hat{t}$ under the null will always be a multivariate normal with mean zero with some covariance $\Sigma$.
-Thus potential tests can be defined using the finite dimensional $\Sigma$ matrix rather than the infinite dimension distribution $Q(P)$.
-Choosing the $\ell_2$ norm, we can define our test by:
+The third was the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$.
+To simplify this test, replace  $\sqrt{n}\hat{\boldsymbol{\psi}}$ with $ \tst \equiv \sqrt{n}\Sigma^{-1/2}\hat{\boldsymbol{\psi}}$.
+Because $\tst$ will always converge to a standard multivariate normal regardless of which $P \in \mathscr{M}_0$ is true \textcolor{blue}{(point to proof)}, for the test defined using $\tst$:
 

### 2020-03-15 figure_code/paper_scripts.R
more changes

@@ -2,6 +2,8 @@
 
 set.seed(103)
 my_data <- MASS::mvrnorm(n = 100, mu = rep(0, 2), Sigma = diag(2))
+cols <- wesanderson::wes_palettes$Darjeeling1
+cols[c(2, 4)] <- cols[c(4, 2)]
 
 plot(my_data[, 1], my_data[, 2], axes = FALSE, asp = 1, 
      bty = 'n', panel.first = grid(), pch = 16)
@@ -19,9 +21,9 @@ half_line_df <- cbind(c(half_line_x, rev(half_line_x), -half_line_x, -rev(half_l
                       c(half_line_y, -rev(half_line_y), -half_line_y, rev(half_line_y)))
 thetas <- seq(from = 0, to = 2 * pi, length.out = 1000)
 l_2_line <- l_2_cutoff * cbind(sin(thetas), cos(thetas))
-lines(max_line[, 1], max_line[, 2], col = "blue", lwd = 4)
-lines(l_2_line[, 1], l_2_line[, 2], col = "red", lwd = 4)
-lines(half_line_df[, 1], half_line_df[, 2], col = "purple", lwd = 4)
+lines(max_line[, 1], max_line[, 2], col = cols[1], lwd = 4)
+lines(l_2_line[, 1], l_2_line[, 2], col = cols[5], lwd = 4)
+lines(half_line_df[, 1], half_line_df[, 2], col = cols[2], lwd = 4)
 points(my_data[, 1], my_data[, 2], pch = 16)
 
 
@@ -50,16 +52,16 @@ make_plot <- function(seed){
   l_2_rej_2 <- cbind(c(l_2_cutoff * sin(seq_3), max_cutoff, max_cutoff), 
                      c(l_2_cutoff * cos(seq_3), max_cutoff, l_2_cutoff * cos(seq_3[1])))
   
-  polygon(max_rej[, 1], max_rej[, 2], col = "green")
-  polygon(- 1 * max_rej[, 1], max_rej[, 2], col = "green")
-  polygon(max_rej_2[, 1], max_rej_2[, 2], col = "green")
-  polygon(max_rej_2[, 1], -1 * max_rej_2[, 2], col = "green")
-  polygon(l_2_rej_2[, 1], l_2_rej_2[, 2], col = "purple")
[…]

### 2020-03-16 article_draft.tex
more changes

@@
 \documentclass{article}
-\usepackage[margin = 0.5in]{geometry}
+\usepackage[margin = 1in]{geometry}
 \usepackage[table]{xcolor}
@@
 
-\begin{document} \section{Introduction}
+\begin{document} 
 \doublespacing
 
+\begin{abstract}
 It is common across scientific disciplines to be interested in predicting an outcome using some (potentially large) number of covariates.
-A first step to constructing accurate predictions is to find out if any covariate is associated with the outcome.
-Testing for the existence of an association can be done with a variety of existing methods, but frequently a trade off must be made between generalizability (ability to use the test for different parameters of interest and data generating mechanisms) and power (ability to detect an association when one exists).
+A first step to constructing accurate predictions is to decide if any covariate is associated with the outcome.
+Testing for the existence of an association can be done with a variety of existing methods, but frequently a trade off is made between generalizability (ability to use the test for different parameters of interest and data generating mechanisms) and power (ability to detect an association when one exists).
 We propose an approach testing for the existence of an association between an outcome and any number of covariates that can be carried out for most parameters of interest that performs nearly as well as tests designed for a specific parameter and data generating mechanism.
@@
 We then study the tests performance in a setting with a complex sampling scheme, and a setting with a complex parameter of interest.
+\end{abstract}
 
-Back in the day, people used to think about which data to collect.
-However, as it became cheaper, more and more data are collected without knowing if any of it can be predictive of the outcome of interest.
-We gather many covariates rather than a single one, and whether any of them are predictive is an important first step to using them to do predictions.
-It used to be assumed that the covariates we collected were in some way predictive of the outcome.
-However, with data collection being so cheep, this is now a question that needs to be answered.
+\section{Introduction}
 
-% Multiple hypotheses testing has been an area of interest since at least [].  However finding an elegant
+One of the central goals of science is to be able to predict some outcome, often with the help of other related information.
+This goal is often attained using the construction of mathematical and statistical models in which many covariates are used to predict the outcome of interest.
+Because the accuracy of the models is dependent on the presence of an association between the outcome of interest and some number of the covariates it is important to know if any associations exist before attempting to create a model.
+While this first step is always important, it has become more important as it becomes more common for large numbers of covariates to be collected, often without an explicit outcome of interest in mind.
 
-% \sh{In nearly all areas of high-dimensional statistics distinguishing between the important and unimportant predictors is of intrest}.
-In genetics many candidate snips and their association with some outcome is of interest.
-Many studies take measurements on a large number of biomarkers to predict medical outcomes such as the presence or progression of a disease.
-While there has been much focus on finding important predictors, there has been less interest in knowing if any predictors are actually important.
-The vast number of potential predictors creates new statistical challenges to answering this less obvious question.
-
-% In the univariate case, once a measure of association is selected, standard approaches exist to construct asymptotically valid (and sometimes optimal) tests \citep{neyman_jerzy_ix._1933}.
-In this setting, a test is considered optimal if it achieves the largest power for every alternative compared to every other test with the same type one error.
-However, scientists are often interested if any of a multitude of covariate are associated with the outcome of interest.
-Even in the case with two covariates, a test with the above optimal property no longer exists and the alternative plays a larger role in which tests are more or less powerful.
-
-% To illustrate this, consider two tests with equal type one error rates.
-Both test the null that both of two association measures $\psi_1$, $\psi_2$ are zero.
-The first test focuses only on the $\psi_1$ and the second test considers both $\psi_1$ and $\psi_2$.
-When the $\psi_1$ is non-zero $\psi_2$ is zero the first test can outperform all other tests.
-Conversely when only $\psi_2$ is non-zero the first test will be outperformed by the second test.
-Additionally in this setting, the power of these tests will be tied to the covariance between the covariates (a problem that did not exist for a single covariate).
-These two factors make it difficult to define a test that performs well across all possible alternatives.
-% Even coming up with optimal properties for tests becomes difficult since it must make assumptions about the true data-generating mechanism.
+To test if any covariate is associated with the outcome, a standard approach is to test each covariates association with the outcome.
+It is desirable for the testing procedure to account for the potentially large number of hypotheses that are simultaneously being tested when using this approach.
 
 Work with \textcolor{red}{simultaneous hypothesis testing}
-%Tests capable of testing the union of multiple hypotheses simultaneously
 began with Tukey in 1953 \citep{miller_simultaneous_1981}.
@@
 Further improvements were proposed by \citep{hochberg_sharper_1988,holm_simple_1979,s._holland_improved_1988}.
-Bonferroni-based correction procedures have the advantage of being easy to apply to already existing tests, while guaranteeing family-wise error control.
+Bonferroni-based correction procedures are easy to apply to already existing tests, while guaranteeing family-wise error control.
 However because these tests ignore the joint distribution of the test statistics, they suffer from low power, especially in cases where the probability of rejecting each hypothesis is highly correlated.
@@
 Subsequent work \citep{mckeague_adaptive_2015, pan_powerful_2014, xu_adaptive_2016} addressed these concerns by accounting for the adaptive nature of the considered tests.
-Still, these newer tests are restricted to testing a particular hypothesis,
-% and test statistic used to test the hypothesis. 
-must make assumptions about the data-generating mechanism to obtain theoretical guarantees.
+While these tests obtain higher power while maintaining type one error control, they were constructed using assumptions about the data generating mechanism, and for only a single measure of association between the outcome of interest and each covariate.
+As a result, investigators may still choose to use bonferroni correction based tests if they are interested in a different measure of association or are unsure of how deviations from the assumed data generating mechanism could effect the properties of the testing procedure.
 
-In this article a test is proposed that works across a wide variety of data generating mechanisms and parameters of interest, but also achieves comparable power to tailor made procedures.
+In this article a testing procedure is proposed that can be used for a wide variety of data generating mechanisms and parameters of interest, but also achieves comparable power to tailor made procedures.
 Section \ref{sec:Working Examples} describes the data generating mechanisms that are considered to evaluate the performance of the test and the competing test made for the given data generating mechanism.
 Section \ref{sec:prop_test_proc} proposes the testing procedure.
-\sh{Add other sections here}
+Section \ref{sec:sim_stdy} shows the performance of our testing procedure in the three considered simulation settings.
+Section \ref{sec:data_app} shows the application of our method to real world data.
+Section \ref{sec:discuss} summarizes the findings of this article and notes potential weaknesses and extensions of our procedure.
 %This is done using a two step procedure.
@@
 For some test statistic $\tst$, any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$.
-\textcolor{blue}{Let $ \tst \xrightarrow{P_0} \rvv \sim \distv(\disto)$}.
-This region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
+Letting $ \tst \xrightarrow{P_0} \rvv \sim \distv(\disto)$ for any $P_0 \in \mathscr{M}_0$, the region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
 \begin{align}
-  Pr_{\distv}\{\rvv \not \in \Theta_0(p)\} = 1 - \alpha \text{ for every } P_0 \in \mathscr{M}_0.\label{eqn:alpha_rej}
+  Pr_{\distv}\{\rvv \not \in \Theta_0(P)\} = 1 - \alpha \text{ for every } P_0 \in \mathscr{M}_0.\label{eqn:alpha_rej}
 \end{align}
 While there are many regions satisfying \eqref{eqn:alpha_rej},  we focus for now on a particular class of regions defined using $\ell_p$ norms which will naturally lead to a straightforward testing procedure.
-For simplicity, \textcolor{blue}{we} first consider regions defined using an $\ell_2$ norm:
+For simplicity, first consider regions defined using an $\ell_2$ norm:
 \begin{align}
@@
 % \textcolor{blue}{be consistent on indexing ``$pr$'' -- if you're going to write as $pr_{q(p)}$, do this throughout!}
-\begin{align*}
-	r_\alpha(\disto) = \min\left\{r : Pr_{\distv}(\|\rvv\|_2 \leq r) \geq 1 - \alpha \right\}.
-\end{align*}
-We now construct a test using the region defined above.
-Let $\hat{\boldsymbol{\Psi}} : \mathbb{R}^d \to \mathbb{R}$ be an estimator of $\boldsymbol{\psi}$, and let $\Hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$.
+\begin{align}
+	r_\alpha(\disto) = \min\left\{r : Pr_{\distv}(\|\rvv\|_2 \leq r) \geq 1 - \alpha \right\}. \label{eqn:ra}
+\end{align}
+To construct a test using the region defined above, let $\hat{\boldsymbol{\Psi}} : \mathbb{R}^d \to \mathbb{R}$ be an estimator of $\boldsymbol{\psi}$, and let $\Hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$.
 Suppose for now that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to a normal distribution $\distv(P)$ when $P$ is contained in the model space  $\mathcal{M}_0$.
-Our test can be defined by
+The test can be defined by
 \begin{align}
 \label{eqn:simp_test}
-	\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha,
-\end{align} and the corresponding p-values are defined by $
+	\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha(P_0),
+\end{align} 
+and the corresponding p-values are defined by $
 	\text{Pr}_\distv(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2)$.
@@
 
-We can vary any of these three things to give us another test=
-The test defined in \eqref{eqn:simp_test} depends on three objects.
-The first was the chosen norm.
-The second was $\sqrt{n}\hat{\boldsymbol{\psi}}$.
-The third was the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$.
-To simplify this test, replace  $\sqrt{n}\hat{\boldsymbol{\psi}}$ with $ \tst \equiv \sqrt{n}\Sigma^{-1/2}\hat{\boldsymbol{\psi}}$.
-Because $\tst$ will always converge to a standard multivariate normal regardless of which $P \in \mathscr{M}_0$ is true \textcolor{blue}{(point to proof)}, for the test defined using $\tst$:
-
-% To simplify this test, replace  $\sqrt{n}\hat{\boldsymbol{\psi}}$ with $ \tst \equiv \sqrt{n}\Sigma^{-1/2}\hat{\boldsymbol{\psi}}$.
-Because $\tst$ will always converge to a standard multivariate normal regardless of which $P \in \mathscr{M}_0$ is true \textcolor{blue}{(point to proof)}, for the test defined using $\tst$:
-
-% \begin{align}
-% \label{eqn:simp_test_simp}
-% 		\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha \text{ where } r_\alpha = \min\left\{r : Pr(\|\rvt\|_2 \leq r) \geq 1 - \alpha \right\} \text{ where } \rvt \sim N(\boldsymbol{0}, \Sigma).
-% \end{align}
-
-% has the property that $r_\alpha$ will not vary between null distributions. Using this simplification, the result of this test is determined by the norm chosen and the value of the test statistic.
-
-Next consider this procedure in more generality. 
-% \subsection{\textcolor{blue}{Creating a rejection region using a function}}
-Consider a function $\Gammaf$, of a vector in $\mathbb{R}^d$ (corresponding to $\tst$). While $\Gammaf(x)$ should get larger as $x$ moves away from the null, $\Gammaf$ can be quite general.
-%For the example of the $\ell_2$ norm, the p-value calculation was a function of the limiting distribution $Z$ and the test statistic $\sqrt{n}\hat{\boldsymbol{\psi}}$
-% Because the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under $H_0$ is always a mean zero multivariate normal, we will index our general functions $\Gamma$ by the $d$ by $d$ variance covariance matrix instead of the infinite dimensional distribution function.
-%   Under $H_0$, the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ will be a mean zero multivariate normal distribution. 
-An example of a more complicated $\Gammaf$ is given below:
-% any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.
-Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.
-However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.
-% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(\|\rvv\| \geq \|x\| \right)$.
-For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.
-However, for other $\Gamma$, this may not be the case.
-Consider
-\begin{align}
-	\Gammaf(x) &= Pr_\distv(\|\rvt + x\| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr(\|\rvt\| < c) \geq 0.8 \} \text{ and } \rvt \sim N(0, \Sigma). \label{gamma:pow}
-\end{align}
-Define the test using $\Gammaf$ as 
-\begin{align*}
-	\text{reject } H_0 \text{ if } \Gammaf(\tst) > c_{1 - \alpha} \text { where } c_{1 - \alpha} = \min_{c}\{c : \text{Pr}(\Gammaf(Y) \geq c) < \alpha\} \text{ where } Y \sim N(\boldsymbol{0}, \Sigma)
-\end{align*}
-% \textcolor{blue}{I don't understand the end of this sentence}. 
-% While the the above test has nice properties (type one error control, consistency), it is not clear how this test will perform compared to other tests with similar properties.
-
 \begin{figure}
 	\centering
-	\includegraphics[width = \linewidth]{figure_code/pwr_cmp.jpeg}
+	\includegraphics[width = \linewidth]{figure_code/new_pwr_cmpr.jpeg}
 	\caption{Plots of 100 observations from a limiting distribution of a hypothetical vector of parameter estimators in $\mathbb{R}^2$ (A) under the null, (B) under an alternative with $\psi_1 = 0, \psi_2 \neq 0$, and (C) under an alternative with $\psi_1, \psi_2 \neq 0$.
 The 95\% quantiles for the data based on the max (blue) and $\ell_2$ (red) norms under the null are given in all three panels.
-If a test statistic fell within the purple regions the test would fail to reject $H_0$ if the $\ell_\infty$ norm was used, but would reject $H_0$ if the $\ell_2$ norm was used.
-The converse is true for the green regions.
+If a test statistic fell within the blue regions the test would fail to reject $H_0$ if the $\ell_\infty$ norm was used, but would reject $H_0$ if the $\ell_2$ norm was used.
+The converse is true for the red regions.
 Depending on the alternative, the $\ell_\infty$ norm (B) or the $\ell_2$ norm(C) will achieve higher power.}
@@
 
-While we have outlined a way of defining different tests of $H_0$, the natural next question is which test will perform the best.
-To explore this question, consider a simple example comparing the test described in equation \eqref{eqn:simp_test} with a test that is identical except it uses the maximum absolute value instead of $\ell_2$ norm.
+So far, we have outlined a method of constructing a test of $H_0$, but it is easy to imagine other tests defined using different norms.
+The natural next question is which test will perform the best, and does the choice of norm make a difference.
+To explore this question, consider a simple example comparing the test described in equation \eqref{eqn:simp_test} with a test that is identical except it uses the $\ell_\infty$ norm (maximum absolute value) instead of the $\ell_2$ norm.
 Figure \ref{fig:figure1}, panel (A) illustrates these two tests in $\mathbb{R}^2$.
-One hundred draws are taken from a bivariate normal distribution with mean zero and identity covariance matrix.
+One hundred draws are taken from $Y$, a bivariate normal distribution with mean zero and identity covariance matrix.
 All observations in panel (A) except the five with the largest $\ell_2$ norm are contained within the red circle.
-The blue squares in each panel contains all observations except the five with the largest $\ell_\infty$ norm.
-\textcolor{blue}{The circle and square represent the cutoffs of tests using empirical estimates of the $95^{\text{th}}$ percentile of $\ell_2(\rvt)$ and $\ell_\infty(\rvt)$ respectively.}
-Observations that fall within the purple region would result in a rejected null hypothesis if the $\ell_2$ norm was used to define the test, but not if the $\ell_\infty$ norm was used.
-The converse is true of the green region.
+The blue square contains all observations in panel (A) except the five with the largest $\ell_\infty$ norm.
+The circle and square represent the acceptance regions of tests using empirical estimates of the $95^{\text{th}}$ percentile of $\ell_2(\rvt)$ and $\ell_\infty(\rvt)$ respectively corresponding to $r_\alpha(P)$ from \eqref{eqn:ra}.
+The same square and circle are redrawn in panels (B) and (C) to illustrate the test's performance under two alternatives.
+Observations that fall within the blue shaded region would result in a rejected null hypothesis if the $\ell_2$ norm was used to define the test, but not if the $\ell_\infty$ norm was used.
+The converse is true of the red shaded region.
 Panels B shows draws from an alternative in which $\psi_2 \ne 0$ and $\psi_1 = 0$ and the $\ell_\infty$ norm performs better (achieves higher power).
@@
 
-While both acceptance regions are created so to achieve type $1$ error control, depending on the alternative one test will outperform the other.
+While both acceptance regions are created to achieve asymptotic type $1$ error control, depending on the alternative one test will outperform the other.
 Panel $B$ shows an alternative in which only $\psi_2$ is non-zero.
-Because the max norm only considers the largest coordinate, shifting each observations in only a single direction will have larger impact on the max norm of the observations compared to the $\ell_2$ norm.
-This trend is shown by the numerous green observations outside of the blue box (equivalent to rejecting $H_0$) and inside the red circle (equivalent to failing to reject $H_0$).
+Because the max norm only considers the largest coordinate, shifting each observation in only a single direction will have larger impact on the max norm of the observations compared to the $\ell_2$ norm.
+This trend is shown by the numerous red observations outside of the blue box (equivalent to rejecting $H_0$) and inside the red circle (equivalent to failing to reject $H_0$).
 In contrast, there is only a single observation that is outside the red circle, and inside the blue box.
@@
 
-The efficiency that can be gained from using the correct norm can be quite larger, especially when dimension grows.
-Work done by \citep{pinelis_schur2-concavity_2014} states that even for dimensions as small as $3$ the gains in asymptotic efficiency can become arbitrarily large between two potential norms.
+The efficiency that can be gained from using the correct norm can be quite large, especially in high dimension settings.
+Work done by \citep{pinelis_schur2-concavity_2014} states that even for dimensions as small as $3$ the gains in asymptotic efficiency for selecting the correct norm can become arbitrarily large between two potential norms \textcolor{blue}{Review this}.
 
@@
 However, the choice of norm can influence the power of the test.
-In most scenarios it will not be clear a priori which test will have maximal power for the true alternative.
+In many scenarios it will not be clear a priori which test will have maximal power for the true alternative.
 The procedure proposed in this section adaptively selects a norm and it will be shown that this procedure achieves greater power than a test with a fixed norm, while maintaining type 1 error control.
 
-To achieve this, first define $\Gamma_{\Sigma, 1}(x), \dots, \Gamma_{\Sigma, p}(x)$ as collection of functions in which the functions only differ by the norm used in their definition. Next, define
+The test defined in \eqref{eqn:simp_test} is a function of three objects; the chosen norm, $\sqrt{n}\hat{\boldsymbol{\psi}}$, and the limiting distribution of  $\hat{t} = \sqrt{n}\hat{\boldsymbol{\psi}}$.
+Note that the limiting distribution of $\hat{t}$ under the null will always be a multivariate normal with mean zero with some covariance $\Sigma$.
+Thus potential tests can be defined using the finite dimensional $\Sigma$ matrix rather than the infinite dimension distribution $Q(P)$.
+
+In order to choose between tests (or norms) it will be important to measures the tests performance in a way that is consistent across norms.
+While all tests will reject as the test statistic becomes larger, if the measure of performance was the norm $\hat{t}$ then the optimal norm would always be the $\ell_1$ norm.
+To achive this goal, we will consider other mappings from $\mathbb{R}$ into $\mathbb{R}$ that are comparable across norms.
+Consider a general function $\Gammaf$, of a vector in $\mathbb{R}^d$ (corresponding to $\tst$).
+While $\Gammaf(x)$ should get larger as $x$ moves away from the null, $\Gammaf$ can be quite general.
+An example of a more complicated $\Gammaf$ is given below:
+\begin{align}
+	\Gammaf(x) &= Pr_\distv(\|\rvt + x\| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr(\|\rvt\| < c) \geq 0.8 \} \text{ and } \rvt \sim N(0, \Sigma). \label{gamma:pow}
+\end{align}
+% To simplify this test, replace  $\sqrt{n}\hat{\boldsymbol{\psi}}$ with $ \tst \equiv \sqrt{n}\Sigma^{-1/2}\hat{\boldsymbol{\psi}}$.
+Because $\tst$ will always converge to a standard multivariate normal regardless of which $P \in \mathscr{M}_0$ is true \textcolor{blue}{(point to proof)}, for the test defined using $\tst$:
+
+% \begin{align}
+% \label{eqn:simp_test_simp}
+% 		\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha \text{ where } r_\alpha = \min\left\{r : Pr(\|\rvt\|_2 \leq r) \geq 1 - \alpha \right\} \text{ where } \rvt \sim N(\boldsymbol{0}, \Sigma).
+% \end{align}
+
+% has the property that $r_\alpha$ will not vary between null distributions. Using this simplification, the result of this test is determined by the norm chosen and the value of the test statistic.
+% \subsection{\textcolor{blue}{Creating a rejection region using a function}}
+
+%For the example of the $\ell_2$ norm, the p-value calculation was a function of the limiting distribution $Z$ and the test statistic $\sqrt{n}\hat{\boldsymbol{\psi}}$
+% Because the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under $H_0$ is always a mean zero multivariate normal, we will index our general functions $\Gamma$ by the $d$ by $d$ variance covariance matrix instead of the infinite dimensional distribution function.
+%   Under $H_0$, the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ will be a mean zero multivariate normal distribution. 
+% any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.
+Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.
+However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.
+% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(\|\rvv\| \geq \|x\| \right)$.
+For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.
+However, for other $\Gamma$, this may not be the case.
+Consider
+
+We can define the test using $\Gammaf$ as 
+\begin{align*}
+	\text{reject } H_0 \text{ if } \Gammaf(\tst) > c_{1 - \alpha} \text { where } c_{1 - \alpha} = \min_{c}\{c : \text{Pr}(\Gammaf(Y) \geq c) < \alpha\} \text{ where } Y \sim N(\boldsymbol{0}, \Sigma)
+\end{align*}
+% \textcolor{blue}{I don't understand the end of this sentence}. 
+% While the the above test has nice properties (type one error control, consistency), it is not clear how this test will perform compared to other tests with similar properties.
+
+Considering the $\Gammaf$ for which it is possible to compare across norms, we can now define a new, adaptive $\Gammaf^*$ which is the pointwise maximum of all of the considered $\Gammaf$'s.
+First define $\Gamma_{\Sigma, 1}(x), \dots, \Gamma_{\Sigma, p}(x)$ as collection of functions in which the functions only differ by the norm used in their definition.
+Next, define
 % by defining a $\Gamma$ to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.
@@
 
-While this function is more complicated than before,  $\Gammaf^*(\rvt)$ can still be compared to $\Gammaf^*(\tst)$ to obtain a p-value.
+While this function is more complicated than before, distribution of $\Gammaf^*(\rvt)$ can still be compared to $\Gammaf^*(\tst)$ to obtain a p-value.
 Also, while it may be difficult to obtain the exact distribution of $\Gammaf^*(\rvt)$, the distribution is a function of $\vmat$, so obtaining good approximations of $\Gammaf^*(\rvt)$ is possible by taking many draws from $\rvt$.
@@
 \label{ssec:obtaining_null}
-The above procedure requires knowledge of the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ when $P \in \mathscr{M}_0$.
-To obtain an estimate of this limiting distribution, assume $\sqrt{n}\hat{\boldsymbol{\psi}}$, converges to a normal distribution with an estimable variance covariance matrix when properly centered and normalized.
-Also assume each of the estimators $\hat{\boldsymbol{\psi}}_1, \dots, \hat{\boldsymbol{\psi}}_d$ of $\boldsymbol{\psi}_1, \dots, \boldsymbol{\psi}_d$ is asymptotically linear.
+The described procedure requires knowledge of the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ when $P \in \mathscr{M}_0$.
+To obtain an estimate of this limiting distribution, we require that each of the estimators $\hat{\boldsymbol{\psi}}_1, \dots, \hat{\boldsymbol{\psi}}_d$ of $\boldsymbol{\psi}_1, \dots, \boldsymbol{\psi}_d$ is asymptotically linear.
 That is for each $j \in \{1, \dots, d\}$:
@@
 \end{align*}
+
+Where the $D_j$ function will be referred to as an influence function.
+While this requirement may seem rigid, most standard measures of association are asymptotically linear, and there exists a rich and growing body of literature that describes asymptotically linear estimators and their corresponding functions \textcolor{blue}{Need citations here}.
+
+% $\sqrt{n}\hat{\boldsymbol{\psi}}$, converges to a normal distribution with an estimable variance covariance matrix when properly centered and normalized.
+
 When there is a fixed number of covariates, the Cramer-Wold device can be used to show that the vector of parameter estimates is asymptotically normal with mean zero, and variance covariance matrix given by $\Sigma = E_{\disto_0}\left[D(\rvo) D(\rvo)^\top \right]$:
@@
 \end{align*}
+
 Under $H_0$, $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges to $Z$, and $\Sigma$ can be approximated with $\widehat{\Sigma} = \frac{1}{n}\sum_{i = 1}^n D(\boldsymbol{x}_i) D(\boldsymbol{x}_i)^\top$.
 In practice, a consistent estimator of $\vmat$, $\hat{\vmat}$ will be used in place of $\vmat$ for the calculation of $\tst$.
-Thus, the test statistic will be $\Gammaf(\tst)$ will be compared to $\Gammaf(\rvt)$.
+Thus, the test statistic will be $\Gammafe(\tst)$ will be compared to $\Gammafe(\rvt)$.
 
@@
 \subsection*{Two Phase Sampling Risk Ratio}
-
-\begin{figure}[]
-	\centering
-\includegraphics[width = \linewidth]{magnitude.pdf}
-	\caption{Rejection rates across three different data generating mechanisms.}
-	\label{fig:magnitude}
-\end{figure}
-
-\begin{figure}[]
-	\centering
-\includegraphics[width = \linewidth]{power.pdf}
-	\caption{Rejection rates across three different data generating mechanisms.}
-	\label{fig:magnitude}
-\end{figure}
-
 Here, we would expect that the $\ell_2$ norm would perform poorly in the model 2 setting while performing well in the model 3 setting, and that the max norm would perform poorly in the model three setting while performing well in the model two setting.
@@
 
-\begin{itemize}
-	\item The simulations we considered in this setting are $X$.  
-	\item We conducted the tests on each simulated dataset using our $R$ package.  
-	\item The test performs as we would expect, having \textcolor{blue}{This Power} in settings in which the alternative is large and there are many observations, and having \textcolor{blue}{This rejection rate} in settings where the null hypothesis holds.
-	\item The reasons for the test struggling to obtain power in \textcolor{blue}{THESE SETTINGS} could be due to a variety of factors.
-	\item This simulation shows that our method can be successfully applied to a setting in which there is a complex sampling scheme.
-\end{itemize}
+\textcolor{blue}{I will eventually just chose one of these figures because performance will be very similar between the two measures.
+I just want to see how similar they are once I get a complete set of simulation results.}
 
-\sh{
-\begin{enumerate}
-	\item Two-Phase sampling Scheme of correlation
-	\item Marginal structural model example.
-\end{enumerate}
-All three examples will come with simulation results in the form of figures.  Not sure how many figures to use or what sample size(s) to use.
-}
+\begin{figure}[H]
+	\centering
+\includegraphics[width = 0.7 \linewidth]{magnitude.pdf}
+	\caption{Rejection rates across three different data generating mechanisms.
+Here we are using the the multiplicative distance our test statistic is from obtaining 80\% power as our measure of performance.}
+	\label{fig:magnitude}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+\includegraphics[width = 0.7 \linewidth]{power.pdf}
+	\caption{Rejection rates across three different data generating mechanisms. Here we are using estimated power as the measure of performance.}
+	\label{fig:magnitude}
+\end{figure}
 
 \section{Data Application}
+\label{sec:data_app}
 
@@
 
+\subsection*{Marginal Structural Model}
+
 \section{Discussion}
+\label{sec:discuss}
+
 In this paper, we have discussed the difficulties of creating multivariate test of no correlated coefficients.
@@
 
-\begin{itemize}
-	\item Problems with Multiple hypothesis testing
-\begin{itemize}
-		\item The problem of multiple hypothesis testing offers many possibilities, but no great way to choose between them. 
-		\item The most generalizable methods for hypothesis testing (Bonferroni) suffer from poor power, and ignore correlation between covariates.
-		\item Specialized tests often attain high power, but come with certain drawbacks.
-\end{itemize}
-\item Specialized tests often attain high power, but come with certain drawbacks.
-\begin{itemize}
-	\item Only work for a single parameter
-	\item require parametric assumptions about the data generating mechanism.
-	\item unknown by individuals who would could potentially use the test.
-	\item Only work for simple data generating mechanisms
-\end{itemize}
-\item We have shown where our method finds a happy medium because it works well in many settings
-\begin{itemize}
-	\item We show our method is competitive with tailor made methods, and can outperform bonferroni
-	\item Our method is generalizable to many different parameters.
-	\item Our method can be used for complex sampling schemes as shown in data example 2 and it attains reasonable power in these settings.
-	\item Our method can be used for complex parameters (shown in data example 3) 
-\end{itemize}
-\item Potential extensions of the method
-\begin{itemize}
-	\item This method can also be expanded by using different $\Gammaf$ functions, potentially optimizing of entire classes of $\Gammaf$ functions with machine learning algorithms.
-	\item Also look at multiplying $\sqrt{n}\hat{\boldsymbol{\psi}}$ by inverse of influence function. 
-	\item There are issues with using parametric bootstrap, which can be avoided in certain cases by using a permutation test.
-\end{itemize}
-\end{itemize}
+\textcolor{blue}{add notes about limitation of our method (need to fin influence function)}
+
+\textcolor{blue}{Multiple measures of association for each covariate.)}
 
@@
 % where $z_1, \dots, z_b$ are draws from $q$. reject the null if $\|\sqrt{n}\hat{\boldsymbol{\psi}}\|_p > c_{p, \alpha}$.
+
+% In the univariate case, once a measure of association is selected, standard approaches exist to construct asymptotically valid (and sometimes optimal) tests \citep{neyman_jerzy_ix._1933}.
+In this setting, a test is considered optimal if it achieves the largest power for every alternative compared to every other test with the same type one error.
+However, scientists are often interested if any of a multitude of covariate are associated with the outcome of interest.
+Even in the case with two covariates, a test with the above optimal property no longer exists and the alternative plays a larger role in which tests are more or less powerful.
+
+% To illustrate this, consider two tests with equal type one error rates.
+Both test the null that both of two association measures $\psi_1$, $\psi_2$ are zero.
+The first test focuses only on the $\psi_1$ and the second test considers both $\psi_1$ and $\psi_2$.
+When the $\psi_1$ is non-zero $\psi_2$ is zero the first test can outperform all other tests.
+Conversely when only $\psi_2$ is non-zero the first test will be outperformed by the second test.
+Additionally in this setting, the power of these tests will be tied to the covariance between the covariates (a problem that did not exist for a single covariate).
+These two factors make it difficult to define a test that performs well across all possible alternatives.
+% Even coming up with optimal properties for tests becomes difficult since it must make assumptions about the true data-generating mechanism.

### 2020-03-16 figure_code/paper_scripts.R

@@ -161,6 +161,6 @@ make_three_plot <- function(seed){
 }
 
 cols <- pal_freiburg_info <- c("#2a6ebb", "#a7c1e3", "#739600",
-                               "#7b2927", "#de3831",  "#92d400")
+                               "#f52c2c", "#a10500",  "#92d400")
 
 make_three_plot(201)

### 2020-05-14 article_draft.tex
More edits

@@
 \usepackage[table]{xcolor}
-\usepackage{amsmath,amsthm,amsfonts,dsfont,mathtools,float,setspace, booktabs, algorithm,tcolorbox,xparse,colortbl,longtable,array,multirow,wrapfig,float,pdflscape,tabu, setspace, threeparttable,threeparttablex,makecell,natbib, pdfpages}
+\usepackage{amsmath,amsthm,amsfonts,dsfont,mathtools,float,setspace, booktabs, algorithm,tcolorbox,xparse,colortbl,longtable,array,multirow,wrapfig,float,pdflscape,tabu, setspace, threeparttable,threeparttablex,makecell,natbib, pdfpages, url}
+\usepackage{lineno}[displaymath, mathlines]
 \usepackage[normalem]{ulem}
@@
 \newcommand{\rvv}{Z}
+\newcommand{\nrvs}{Y_\Sigma}
+\newcommand{\nrvi}{Y_I}
 \newcommand{\distv}{Q}
@@
 \newcommand{\pf}{\Phi}
-\newcommand{\gi}{\Upsilon}
+\newcommand{\gi}{\Gamma}
+\newcommand{\gamestz}{\Gamma(\hat{\rvv}, \hat{\Sigma})}
+\newcommand{\gamestp}{\Gamma(\sqrt{n}\hat{\boldsymbol{\psi}}, \hat{\Sigma})}
+\newcommand{\rnp}{\sqrt{n} \hat{\boldsymbol{\psi}}}
+\newcommand{\gamp}{\Gamma(\sqrt{n}\boldsymbol{\psi}, \Sigma)}
+\newcommand{\gamz}{\Gamma(\rvv, \Sigma)}
+\newcounter{conditions}
 
 \begin{document}
+\linenumbers
 \doublespacing
@@
 \begin{abstract}
-It is common across scientific disciplines to be interested in predicting an outcome using some (potentially large) number of covariates.
-A first step to constructing accurate predictions is to decide if any covariate is associated with the outcome.
-Testing for the existence of an association can be done with a variety of existing methods, but frequently a trade off is made between generalizability (ability to use the test for different parameters of interest and data generating mechanisms) and power (ability to detect an association when one exists).
-We propose an approach testing for the existence of an association between an outcome and any number of covariates that can be carried out for most parameters of interest that performs nearly as well as tests designed for a specific parameter and data generating mechanism.
+In many scientific disciplines including genetics, neurology, and vaccine development researchers are often interested in understanding the relationship between an outcome and a large set of covariates.
+A first step to investigating such relationships is to screen covariates for an association with the outcome.
+This screening can be achieved using a variety of methods, from general methods such as those based on Bonferroni adjustment to techniques tailored to a single problem.
+Existing general methods that can be applied across a variety of problems frequently have lower power.
+Tailor-made procedures tend to attain higher power by building their procedures around problem-specific information that makes adaptation to new settings difficult.
+We propose a general framework to test for the existence of an association between an outcome and any number of covariates in which the estimator is adaptively selected to optimize an estimate of local power.
+We present theoretical asymptotic guarantees for our test under fixed and local alternatives.
+We then show numerically that tests created using our framework can perform nearly as well as tailor-made methods.
+Finally, we develop tests in two settings in which tailor-made methods are not available.
+\end{abstract}
+
+% utilizes information about the asymptotic distribution of the estimators, but does not place restrictions on the data generating mechanism or the parameter of interest
+% frequently a trade off is made between generalizability (ability to use the test for different parameters of interest and data generating mechanisms) and power (ability to detect an association when one exists).
+that can be carried out for most parameters of interest that.
 We compare our method with other modern methods in a simple simulated data setting.
-We then study the tests performance in a setting with a complex sampling scheme, and a setting with a complex parameter of interest.
-\end{abstract}
 
@@
 
-One of the central goals of science is to be able to predict some outcome, often with the help of other related information.
-This goal is often attained using the construction of mathematical and statistical models in which many covariates are used to predict the outcome of interest.
-Because the accuracy of the models is dependent on the presence of an association between the outcome of interest and some number of the covariates it is important to know if any associations exist before attempting to create a model.
-While this first step is always important, it has become more important as it becomes more common for large numbers of covariates to be collected, often without an explicit outcome of interest in mind.
-
-To test if any covariate is associated with the outcome, a standard approach is to test each covariates association with the outcome.
-It is desirable for the testing procedure to account for the potentially large number of hypotheses that are simultaneously being tested when using this approach.
-
+To broaden scientific understanding in a field it is typical to seek an understanding of the relationships between various observations.
+It is common for the set of potentially related observations to be quite large while the number of truly related observations is small.
+Thus an important first step is to find which variables are truly related to each other.
+%To discover these relationships, it is common to construct a mathematical or statistical model in which many covariates are used to predict the outcome of interest.
+Because the usefulnes of these models is dependent on the presence of an association between the outcome of interest and some number of the covariates, it is important to know if any associations exist before working to create a model.
+This initial screening step has become increasingly important as the research collect information on more and more potentially related observations.
+
+One method to check for the existence of such relationships or associations is to test the association of each covariate with the outcome.
+Because of the many tests this procedure could consider, it is desirable for the testing procedure to account for the potentially large number of hypotheses that are simultaneously being tested when using this approach.
 Work with \textcolor{red}{simultaneous hypothesis testing}
@@
 
-Newer procedures \citep{donoho_higher_2004} and \sh{add other papers here} attain improved power compared to Bonferroni-based methods, but often rely on asymptotics to obtain these results, and don't account for the irregularity of the estimator on which their test is based.
-Subsequent work \citep{mckeague_adaptive_2015, pan_powerful_2014, xu_adaptive_2016} addressed these concerns by accounting for the adaptive nature of the considered tests.
-While these tests obtain higher power while maintaining type one error control, they were constructed using assumptions about the data generating mechanism, and for only a single measure of association between the outcome of interest and each covariate.
-As a result, investigators may still choose to use bonferroni correction based tests if they are interested in a different measure of association or are unsure of how deviations from the assumed data generating mechanism could effect the properties of the testing procedure.
-
-In this article a testing procedure is proposed that can be used for a wide variety of data generating mechanisms and parameters of interest, but also achieves comparable power to tailor made procedures.
-Section \ref{sec:Working Examples} describes the data generating mechanisms that are considered to evaluate the performance of the test and the competing test made for the given data generating mechanism.
-Section \ref{sec:prop_test_proc} proposes the testing procedure.
+Newer procedures \citep{donoho_higher_2004} and \sh{add other papers here} using modern statistical theory to provide asymptotic guarantees for their methods and to account for the correlation between parameter estimates.
+However, these methods are made for specific parameters and data generating mechanisms and do not account for the irregularity of the estimator on which their test is based.
+This irregularity can cause poor performance in scenarios in which the probablility of rejecting the null is far away from the $\alpha$ level of the test and one.
+Subsequent work \citep{mckeague_adaptive_2015, pan_powerful_2014, xu_adaptive_2016} addressed these concerns by accounting for the flexible nature of these adaptive tests.
+However these methods were still created for a specific measure of association and data generating mechanisms in mind.
+Thus while much has been done to improve the performance of tests in certain settings investigators may still use bonferroni based methods because advanced methods do not exist for their particular situation  As a result, investigators may still choose to use bonferroni correction based tests if they are interested in a different measure of association or are unsure of how deviations from the assumed data generating mechanism could effect the properties of the testing procedure.
+
+In this article we propose a testing procedure that can be used for a wide variety of data generating mechanisms and parameters of interest.
+This test also achieves comparable power to tailor made procedures in some settings.
+Section \ref{sec:Working Examples} describes the data generating mechanisms and the corresponding parameters that are considered to evaluate the performance of the test and the competing test.
+Section \ref{sec:prop_test_proc} describes the testing procedure.
+Section \ref{sec:theorems} provides the theoretical guarantees of the described procedure.
 Section \ref{sec:sim_stdy} shows the performance of our testing procedure in the three considered simulation settings.
@@
 Section \ref{sec:discuss} summarizes the findings of this article and notes potential weaknesses and extensions of our procedure.
+
 %This is done using a two step procedure.
@@
 \label{sec:Working Examples}
-Let $\rvo_1, \dots, \rvo_n$ be independent identically distributed draws from some distribution $\disto$, and let $\boldsymbol{\rvo} = \{\rvo_1, \dots, \rvo_n\}$ .
-Let $\rvo_i = \left(Y_i, W_{1 i}, \dots, W_{d i}\right), i \in \{1, \dots n\}$ where $Y$ is the outcome of interest, and each $W$ is a covariate.
-Let $\psi_1 = \Psi_1(\disto), \dots, \psi_a = \Psi_a(\disto)$ be measures of association between $Y$ and some combination of the $W_j$'s.
+Throughout all examples let $\rvo_1, \dots, \rvo_n$ be independent identically distributed draws from some distribution $\disto$, and let $\boldsymbol{\rvo} = \{\rvo_1, \dots, \rvo_n\}$.
+Let $\rvo_i = \left(Y_i, W_{1 i}, \dots, W_{d i}\right), \ i \in \{1, \dots n\}$ where $Y$ is the outcome of interest, and each $W$ is a covariate.
+Let $\psi_1 = \Psi_1(\disto), \dots, \psi_a = \Psi_a(\disto)$ be measures of association between $Y$ and some combination of the $W_j$s.
 While the results found in this article are valid for any integer $a$, for the remainder of this article assume $a = d$, the number of covariates.
-Also, let $\psi_j$ correspond to a measure of association between $Y$ and $W_j$.
+Also in this article, let $\psi_j$ correspond to a measure of association between $Y$ and $W_j$.
 The null hypothesis for our test will be the strong null:
-
 \begin{align*}
@@
 \end{align*}
-
-Last, let $\mathscr{M}$ denote the set of all possible distributions, and let $\mathscr{M}_0  \subset \mathscr{M}$ be the subset of distributions in $\mathscr{M}$ satisfying $H_0$.
-
-We consider three different simulated data settings to study the test's performance.
+Finally, let $\mathscr{M}$ denote the set of all possible distributions, and let $\mathscr{M}_0  \subset \mathscr{M}$ be the subset of distributions in $\mathscr{M}$ satisfying $H_0$.
+We consider three different simulated data settings to study the performance of the test.
 
 \subsection{Correlation Parameter}
-We will compare our method to a Bonferroni correct marginal testing method and the method described in \citep{zhang_comment_2015}.
-The settings considered will be the same as the firs setting in \citep{mckeague_adaptive_2015}.
-The parameter of interest, $\psi_j(P)$ will be the correlation between the outcome of interest and the $j$'th covariate.
-
+In the first example, our method is compared to a Bonferroni correct marginal testing method and the parametric bootstrap analog of the adaptive resampling test described in \citep{zhang_comment_2015} that built on the adaptive resampling test proposed by \citep{mckeague_adaptive_2015}.
+This example uses the same settings as those used in the first example of \citep{mckeague_adaptive_2015}.
+The parameter of interest $\psi_j(P)$ is the correlation between the outcome of interest and the $j$'th covariate.
 The vector of covariates in this setting will be generated from a normal distribution with mean zero and a variance covariance of $\Sigma$ with $\Sigma_{ij}$ equal to $\rho$ when $i \neq j$ and equal to 1 when $i = j$.
 Three different models for the outcome of interest ($Y$) will be considered.
-For all considered settings, $\varepsilon \sim N(0, 1)$ and is independent of all $X$.
-In the first model $Y = \varepsilon$, in the second model $Y = X_1 / 4 + \varepsilon$, and in the third model $Y = \sum_{k = 1}^{10} \beta_k X_k + \varepsilon$ where $\beta_k = 0.15$ for $k = \{1, \dots, 5\}$, and $\beta_k = -0.1$ for $k = \{6 \dots 10\}$.
-Sample sizes of $100$ and $200$, dimensions of $10$, $50$, $100$, $150$, and $200$, and $\rho$ of  $0, 0.5$, and $0.8$ are considered.
-All combinations of model, sample size, dimension and $\rho$ are considered, and every test's performance is measured for all considered settings.
+For every setting $\varepsilon \sim N(0, 1)$ and is independent of all $W$.
+In the first setting $Y = \varepsilon$, in the second setting $Y = W_1 / 4 + \varepsilon$, and in the third setting $Y = \sum_{k = 1}^{10} \beta_k W_k + \varepsilon$ where $\beta_k = 0.15$ for $k = \{1, \dots, 5\}$, and $\beta_k = -0.1$ for $k = \{6 \dots 10\}$.
+Sample sizes of $100$ and $200$, dimensions of $10$, $50$, $100$, $150$, and $200$, and correlations $(\rho)$ of  $0, 0.5$, and $0.8$ are considered.
+All combinations of model, sample size, dimension and correlation are considered, and the performance of each test is measured for every settings.
 
 \subsection{Missing Data Example}
-In the second example, $Y$ is binary, $\Delta$ is a missingness indicator, and each $W_j$ is a covariate of interest.
-When $\Delta = 0$ we don't observe $Y$.
-The identifying assumption is $\Delta \indep Y | W$, and the parameter of interest is the risk ratio under a poission working model for the probability that $Y = 1$.
-
-\begin{align*}
-	\Psi_{j}\left(P^{\text{full}}\right) &= \frac{\text{Cov}\left(\log\left(Pr \left(Y = 1 |  W_j\right)\right), W_j\right)}{\text{Var}(W_j)}.\\
-\end{align*}
-
-Using the identifying assumption, the observed data parameter is:
-
-\begin{align*}
-	\tilde{\Psi}_{j}\left(P^{\text{obs}}\right)&= \frac{\text{Cov}\left(\log\left(E\left[Pr \left(\Delta  Y = 1 | \Delta = 1, W = W\right) |  W_j\right]\right), W_j\right)}{\text{Var}(W_j)}\\
-\end{align*}
-
+\label{sec:missing_data}
+In the second example $Y$ is binary variable and $\Delta$ is a missingness indicator.
+When $\Delta = 0$, $Y$ is not observed.
+The parameter of interest is the risk ratio under a poission working model for the probability that $Y = 1$.
+\begin{align*}
+	\Psi_{j}\left(P^{\text{full}}\right) &= \frac{\text{Cov}\left(\log\left(Pr \left(Y = 1 |  W_j\right)\right), W_j\right)}{\text{Var}(W_j)}.
+\end{align*}
+The identifying assumption is $\Delta \indep Y | W$, and when this assumption holds the corresponding identifiable parameter is:
+\begin{align*}
+	\tilde{\Psi}_{j}\left(P^{\text{obs}}\right)&= \frac{\text{Cov}\left(\log\left(E\left[Pr \left(\Delta  Y = 1 | \Delta = 1, W = W\right) |  W_j\right]\right), W_j\right)}{\text{Var}(W_j)}.
+\end{align*}
 The data are drawn from a binomial model:
-
 \begin{align*}
@@
 \end{align*}
-
-There will be three settings considered which determine  the values of the $\beta$'s in the data generating model:
-
-In all simulation settings the working model is used to take draws from $y$.
-In each setting, the vector $\boldsymbol{W}$ is draw from a multivariate normal with mean zero and covariance matrix $\Sigma_{DE2}$ where $\Sigma_{DE2, i, j} = 1$ for $i = j$ and $0.6$ for $i \neq j$.
+and in all settings, the probability of missingness is given by 
+\begin{align*}
+% probs <- expit(-0.25 + 1 * ws[, max(1, ncol(ws) - 1)] -
+% 1.5 * ws[, max(2, ncol(ws))])
+	\text{logit}(\pr(A = 1 | w)) = -0.25 + 1 w_{d - 1} - 1.5 w_d \text{ where d is the number of covariates.} 
+\end{align*}
+
+There will be three settings considered which determine  the values of the $\beta$s in the data generating model.
+While it is not necessary for the covariates to be normally distributed, in each setting the vector $\boldsymbol{W}$ is draw from a multivariate normal with mean zero and covariance matrix $\textcolor{blue}{\Sigma_{DE2}}$ where $\Sigma_{DE2, i, j} = 1$ for $i = j$ and $0.6$ for $i \neq j$.
 $A$ is drawn from a binomial distribution independent from $W$.
 For all three settings
-
-\begin{align*}
-	\text{logit}\left(Pr(Y = 1 | w, a)\right) = \sum_{i = 1}^{d} \beta_{i} w_i
-\end{align*}
-
-In the first setting $\beta_1 \dots \beta_d = 0$.
-In the second setting $\beta_1 = 3$ and $\beta_2, \dots \beta_d = 0$.
-In the last setting, $\beta_1 \dots \beta_5 = 1$, $\beta_6 \dots \beta_{10} = -1$ and $\beta_{11} \dots \beta_d = 0$.
-Data are generated from all three models with every possible combination of sample size ($n = 100$, or $200$), and dimension ($d = 10, 50, 100, 150$, or $200$).
-
-\subsection{Marginal Structural Model}
+\begin{align*}
+	\text{logit}\left[Pr(Y = 1 | w, a)\right] = \sum_{i = 1}^{d} \beta_{i} w_i
+\end{align*}
+In the first setting $\beta_1, \dots, \beta_d = 0$.
+In the second setting $\beta_1 = 3$ and $\beta_2, \dots,  \beta_d = 0$.
+In the last setting, $\beta_1, \dots, \beta_5 = 1$, $\beta_6, \dots, \beta_{10} = -1$ and $\beta_{11}, \dots, \beta_d = 0$.
+Data are generated using all three settings with every possible combination of sample size ($n = 5,000$, or $10,000$), and dimension ($d = 10, 50, 100, 150$, or $200$).
+
+\subsection{Marginal Structural Model Example}
+\label{sec:msm_data}
 The third data example is a marginal structural model in which we test if the average treatment effect of a binary treatment $A$ is modified by any covariates $W_j$.
 The marginal structural model for each $W_j$ is defined by the working model:
-
-\begin{align*}
-\text{logit}\left(Pr(Y^{(a)} = 1 | w)\right) = \beta_0 + \beta_1 a + \beta_2 w_j + \beta_3 w_j a
-\end{align*}
-
+\begin{align}
+\text{logit}\left[Pr(Y^{(a)} = 1 | w)\right] = \beta_0 + \beta_1 a + \beta_2 w_j + \beta_3 w_j a \label{eqn:DE2param}
+\end{align}
 in which our parameter of interest is:
-
-\begin{align*}
-(\beta_0^*, \beta_1^*, \beta_2^*, \beta_3^*) = \text{argmin}_{\beta_0, \beta_1, \beta_2, \beta_3}\int\left(\text{logit}\left(Pr(Y^{(a)} = 1 | w\right) - (\beta_0 + \beta_1 a + \beta_2w_j + \beta_3 w_j a) \right)^2 dP(w, a)
-\end{align*}
-
-The parameter of interest is $\beta_3^*$, but is worth noting that parameter is different from a usual logistic regression parameter because we are marginalizing over all $w_i$, not just $w_j$.
-
-In all simulation settings the working model is used to take draws from $y$.
-In each setting, the vector $\boldsymbol{W}$ is draw from a multivariate normal with mean zero and covariance matrix $\Sigma_{DE3}$ where $\Sigma_{DE3, i, j} = 1$ for $i = j$ and $0.6$ for $i \neq j$.
+\begin{align*}
+(\beta_0^*, \beta_1^*, \beta_2^*, \beta_3^*) = \text{argmin}_{\beta_0, \beta_1, \beta_2, \beta_3}\int\left\{\text{logit}\left[Pr\left(Y^{(a)} = 1 | w\right)\right] - (\beta_0 + \beta_1 a + \beta_2w_j + \beta_3 w_j a) \right\}^2 dP(w, a)
+\end{align*}
+The parameter of interest is $\beta_3^*$, but it is worth noting that this parameter is different from a usual logistic regression parameter because we are marginalizing over all other $w_i$.
+
+In all simulation settings the working model is used to take draws from $Y$.
+In each setting, the vector $\boldsymbol{W}$ is draw from a multivariate normal with mean zero and covariance matrix $\textcolor{blue}{\Sigma_{DE3}}$ where $\Sigma_{DE3, i, j} = 1$ for $i = j$ and $0.6$ for $i \neq j$.
 $A$ is drawn from a binomial distribution independent from $W$.
@@
 \begin{align*}
-	\text{logit}\left(Pr(Y = 1 | w, a)\right) = \beta_1 a + \sum_{i = 1}^{d} \beta_{i + 1} w_i + \sum_{j = 1}^d \gamma_{j} w_j a
-\end{align*}
-
-In every setting, $\beta_1 = 0.2$, $\beta_2, \dots \beta_{d/2 + 1} = 2/\sqrt{d}$, and $\beta_{d/2 + 1} \dots \beta_{d + 1} = 0$.
-In the first (null) setting, $\gamma_{1} \dots \gamma{d} = 0$.
-In the second setting, $\gamma_{1} = 3$ and $\gamma_{2} \dots \gamma_{d} = 0$.
-In the final setting $\gamma_{1} \dots \beta_{5} = 1, \gamma_{6} \dots \beta_{10} = -1$, and $\gamma_{11} \dots \gamma_{d} = 0$.
-Data are generated from all three models with every possible combination of sample size ($n = 100$, or $200$), and dimension ($d = 10, 50, 100, 150$, or $200$).
+	\text{logit}\left(Pr(Y = 1 | w, a)\right) = \alpha a + \sum_{i = 1}^{d} \beta_{i} w_i + \sum_{j = 1}^d \gamma_{j} w_j a
+\end{align*}
+
+In every setting, $\alpha = 0.2$, $\beta_1, \dots, \beta_{d/2} = 2/\sqrt{d}$, and $\beta_{d/2}, \dots, \beta_{d}  = 0$.
+In the first (null) setting, $\gamma_{1}, \dots, \gamma_{d} = 0$.
+In the second setting, $\gamma_{1} = 3$ and $\gamma_{2}, \dots, \gamma_{d} = 0$.
+In the final setting $\gamma_{1}, \dots, \gamma_{5} = 0.15$, $\gamma_{6}, \dots, \gamma_{10} = -0.15$, and $\gamma_{11}, \dots, \gamma_{d} = 0$.
+Data are generated using all three settings with every possible combination of sample size ($n = 1,000$, or $2,000$), and dimension ($d = 10, 30$, or $75$).
 
@@
 \label{sec:prop_test_proc}
-For some test statistic $\tst$, any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$.
-Letting $ \tst \xrightarrow{P_0} \rvv \sim \distv(\disto)$ for any $P_0 \in \mathscr{M}_0$, the region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
+
+For some test statistic $\tst$, any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by checking if $\tst$ falls within acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$.
+Letting $\tst \xrightarrow{P_0} \rvv \sim \distv(\disto)$ for any $P_0 \in \mathscr{M}_0$, the region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
 \begin{align}
-  Pr_{\distv}\{\rvv \not \in \Theta_0(P)\} = 1 - \alpha \text{ for every } P_0 \in \mathscr{M}_0.\label{eqn:alpha_rej}
+  Pr_{\distv}\{\rvv \not \in \Theta_0(P)\} = 1 - \alpha \text{ for every } P \in \mathscr{M}_0.\label{eqn:alpha_rej}
 \end{align}
@@
 To construct a test using the region defined above, let $\hat{\boldsymbol{\Psi}} : \mathbb{R}^d \to \mathbb{R}$ be an estimator of $\boldsymbol{\psi}$, and let $\Hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$.
-Suppose for now that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to a normal distribution $\distv(P)$ when $P$ is contained in the model space  $\mathcal{M}_0$.
+Letting $\tst \equiv \sqrt{n}\hat{\boldsymbol{\psi}}$, suppose for now that  $\tst$ converges in law to a normal distribution $\distv(P)$ when $P$ is contained in the model space  $\mathcal{M}_0$.
 The test can be defined by
@@
 \label{eqn:simp_test}
-	\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha(P_0),
+	\text{reject } H_0 \text{ if } \|\rnp\|_2 \geq r_\alpha(P_0),
 \end{align} 
 and the corresponding p-values are defined by $
-	\text{Pr}_\distv(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2)$.
+	\text{Pr}_\distv(\|\rvv\|_2 \geq \|\rnp\|_2)$.
 
@@
 
-So far, we have outlined a method of constructing a test of $H_0$, but it is easy to imagine other tests defined using different norms.
-The natural next question is which test will perform the best, and does the choice of norm make a difference.
-To explore this question, consider a simple example comparing the test described in equation \eqref{eqn:simp_test} with a test that is identical except it uses the $\ell_\infty$ norm (maximum absolute value) instead of the $\ell_2$ norm.
+So far, we have outlined a method to construct a test of $H_0$, but it is easy to imagine other tests defined using different norms.
+With so many potential tests to consider, it is natural to wonder if tests based on different norms have different power, and if so how can someone select the norm with optimal power.
+To explore the first question, consider a simple example comparing the test described in equation \eqref{eqn:simp_test} with a test that is identical except it uses the maximum absolute deviation or $\ell_\infty$ norm (maximum absolute value) in place the $\ell_2$ norm.
+Letting $\boldsymbol{x} = (x_1, \dots, x_d)$ then $\ell_\infty(\boldsymbol{x}) = \max\left\{|x_1|, \dots, |x_d|\right\}$.
 Figure \ref{fig:figure1}, panel (A) illustrates these two tests in $\mathbb{R}^2$.
-One hundred draws are taken from $Y$, a bivariate normal distribution with mean zero and identity covariance matrix.
+One hundred draws are taken from $\nrvs$, a surrogate for the estimated limiting distribution of $\tst$.
+The random variable $\nrvs$ is a bivariate normal distribution with mean zero and identity covariance matrix.
 All observations in panel (A) except the five with the largest $\ell_2$ norm are contained within the red circle.
 The blue square contains all observations in panel (A) except the five with the largest $\ell_\infty$ norm.
-The circle and square represent the acceptance regions of tests using empirical estimates of the $95^{\text{th}}$ percentile of $\ell_2(\rvt)$ and $\ell_\infty(\rvt)$ respectively corresponding to $r_\alpha(P)$ from \eqref{eqn:ra}.
-The same square and circle are redrawn in panels (B) and (C) to illustrate the test's performance under two alternatives.
+The circle and square represent the acceptance regions of tests using empirical estimates of the $95^{\text{th}}$ percentile of $\ell_2(\nrvs)$ and $\ell_\infty(\nrvs)$ respectively corresponding to $r_\alpha(P)$ from \eqref{eqn:ra}.
+The same square and circle are redrawn in panels (B) and (C) to illustrate the performance of the test under two alternatives.
 Observations that fall within the blue shaded region would result in a rejected null hypothesis if the $\ell_2$ norm was used to define the test, but not if the $\ell_\infty$ norm was used.
 The converse is true of the red shaded region.
-Panels B shows draws from an alternative in which $\psi_2 \ne 0$ and $\psi_1 = 0$ and the $\ell_\infty$ norm performs better (achieves higher power).
-Panel C shows draws from an alternative in which $\psi_1$ and $\psi_2 \neq 0$ and the $\ell_2$ norm performs better.
-
-While both acceptance regions are created to achieve asymptotic type $1$ error control, depending on the alternative one test will outperform the other.
+Panel B shows draws from an alternative in which $\psi_2 \ne 0$ and $\psi_1 = 0$, and panel C shows draws from an alternative in which $\psi_1$ and $\psi_2 \neq 0$.
+
+While both acceptance regions are created to achieve asymptotic type one error control, depending on the alternative one test will outperform the other.
 Panel $B$ shows an alternative in which only $\psi_2$ is non-zero.
@@
 However, the choice of norm can influence the power of the test.
-In many scenarios it will not be clear a priori which test will have maximal power for the true alternative.
-The procedure proposed in this section adaptively selects a norm and it will be shown that this procedure achieves greater power than a test with a fixed norm, while maintaining type 1 error control.
-
-The test defined in \eqref{eqn:simp_test} is a function of three objects; the chosen norm, $\sqrt{n}\hat{\boldsymbol{\psi}}$, and the limiting distribution of  $\hat{t} = \sqrt{n}\hat{\boldsymbol{\psi}}$.
+In many scenarios it will not be clear a priori which test will have maximal power because the power of each test depends on the unknown value of the true alternative.
+The procedure proposed in this section data adaptively selects a norm to attain some of the power improvements that can be attained from selecting the best norm without needing to specify the norm a priori.
+It will be shown via simulation that this procedure can achieve greater power than a test with a fixed norm.
+It will also be shown with  both theory and simulation that this adaptive procedure maintains type 1 error control for large sample sizes.
+
+% The test defined in \eqref{eqn:simp_test} is a function of three objects; the chosen norm, $\sqrt{n}\hat{\boldsymbol{\psi}}$, and the limiting distribution of  $\hat{t} = \sqrt{n}\hat{\boldsymbol{\psi}}$.
 Note that the limiting distribution of $\hat{t}$ under the null will always be a multivariate normal with mean zero with some covariance $\Sigma$.
@@
 
-In order to choose between tests (or norms) it will be important to measures the tests performance in a way that is consistent across norms.
-While all tests will reject as the test statistic becomes larger, if the measure of performance was the norm $\hat{t}$ then the optimal norm would always be the $\ell_1$ norm.
+To define norm data adaptive selection rules it will be important to measure the performance of each test.
+These measures will be referred to as performance metrics and will be denoted by $\Gamma$.
+While these metrics can be quite general, they should provide an ordering in which better performance results in a more extreme measure of performance.
+These metrics should provide reasonable comparisons across norms.
+For example if one were to use the $\ell_p$ of the test statistic as the performance metric, the first criteria would be satisfied because for most definitions of ``large'' as $x$ grows large, so does $\|x\|_p$.
+However, the second criateria is not satisfied because $\ell_1(x) \geq \ell_2(x) \geq \dots \geq \max(x)$, it does not satisfy the second criteria.
+
+In order to achieve both criteria mentioned previously, the performance metrics considered in this paper will be functions of both the test statistic $\tst$ and the limiting distribution of the test statistic $\rvt$ under the null.
+The limiting distributions will allow us to understand how extreme $\tst$ is relative to what we would see under the null which allows us to make comparisons across norms.
+
+As an asside, note that the limiting distribution of $\tst$ under the null will always be a multivariate normal with mean zero with some covariance $\Sigma$.
+Thus potential tests can be functions of the finite dimensional $\Sigma$ matrix rather than the infinite dimension distribution $Q(P)$.
+To maintain consistency throughout this paper performance metrics will have the added condition that they become smaller as performance improves.
+This condition is discussed more in section \ref{sec:test_cnsty}.
+If a candidate performance metric becomes large as $\tst$ grows large, the reciprocal of this performance metric can be used.
+Performance metrics can be thought of analogously to the p-value of a test in which a non-adaptive version of the test was used.
+
+% While all tests will reject as the test statistic becomes larger, if the measure of performance was the norm $\hat{t}$ then the optimal norm would always be the $\ell_1$ norm.
 To achive this goal, we will consider other mappings from $\mathbb{R}$ into $\mathbb{R}$ that are comparable across norms.
-Consider a general function $\Gammaf$, of a vector in $\mathbb{R}^d$ (corresponding to $\tst$).
-While $\Gammaf(x)$ should get larger as $x$ moves away from the null, $\Gammaf$ can be quite general.
-An example of a more complicated $\Gammaf$ is given below:
+% Consider a general function $\Gammaf$, of a vector in $\mathbb{R}^d$ (corresponding to $\tst$).
+There is a requirement that $\Gammaf(x)$ should get smaller as $x$ moves away from the null, $\Gammaf$ can be quite general.
+The first performance metric we consider is the acceptance rate of the test defined in  \eqref{eqn:simp_test} if $\psi = \tst$: 
 \begin{align}
-	\Gammaf(x) &= Pr_\distv(\|\rvt + x\| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr(\|\rvt\| < c) \geq 0.8 \} \text{ and } \rvt \sim N(0, \Sigma). \label{gamma:pow}
+	\Gamma(x, \Sigma) &= Pr_\distv(\|\rvt + x\| \leq c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr(\|\rvt\| < c) \geq 0.8 \} \text{ and } \rvt \sim N(0, \Sigma). \label{gamma:pow}
 \end{align}
-% To simplify this test, replace  $\sqrt{n}\hat{\boldsymbol{\psi}}$ with $ \tst \equiv \sqrt{n}\Sigma^{-1/2}\hat{\boldsymbol{\psi}}$.
-Because $\tst$ will always converge to a standard multivariate normal regardless of which $P \in \mathscr{M}_0$ is true \textcolor{blue}{(point to proof)}, for the test defined using $\tst$:
-
-% \begin{align}
-% \label{eqn:simp_test_simp}
-% 		\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha \text{ where } r_\alpha = \min\left\{r : Pr(\|\rvt\|_2 \leq r) \geq 1 - \alpha \right\} \text{ where } \rvt \sim N(\boldsymbol{0}, \Sigma).
-% \end{align}
-
-% has the property that $r_\alpha$ will not vary between null distributions. Using this simplification, the result of this test is determined by the norm chosen and the value of the test statistic.
-% \subsection{\textcolor{blue}{Creating a rejection region using a function}}
-
-%For the example of the $\ell_2$ norm, the p-value calculation was a function of the limiting distribution $Z$ and the test statistic $\sqrt{n}\hat{\boldsymbol{\psi}}$
-% Because the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under $H_0$ is always a mean zero multivariate normal, we will index our general functions $\Gamma$ by the $d$ by $d$ variance covariance matrix instead of the infinite dimensional distribution function.
-%   Under $H_0$, the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ will be a mean zero multivariate normal distribution. 
-% any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.
-Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.
-However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.
-% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(\|\rvv\| \geq \|x\| \right)$.
-For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.
-However, for other $\Gamma$, this may not be the case.
-Consider
-
-We can define the test using $\Gammaf$ as 
-\begin{align*}
-	\text{reject } H_0 \text{ if } \Gammaf(\tst) > c_{1 - \alpha} \text { where } c_{1 - \alpha} = \min_{c}\{c : \text{Pr}(\Gammaf(Y) \geq c) < \alpha\} \text{ where } Y \sim N(\boldsymbol{0}, \Sigma)
+
+We can define a test using $\Gamma$: 
+\begin{align*}
+	\text{reject } H_0 \text{ if } \Gamma(\tst, \Sigma) \leq c_{1 - \alpha} \text { where } c_{1 - \alpha} = \min_{c}\{c : \text{Pr}(\Gamma(\rvt, \Sigma) \geq c) < \alpha\} \text{ where } \rvt \sim N(\boldsymbol{0}, \Sigma)
 \end{align*}
@@
 
-Considering the $\Gammaf$ for which it is possible to compare across norms, we can now define a new, adaptive $\Gammaf^*$ which is the pointwise maximum of all of the considered $\Gammaf$'s.
-First define $\Gamma_{\Sigma, 1}(x), \dots, \Gamma_{\Sigma, p}(x)$ as collection of functions in which the functions only differ by the norm used in their definition.
+Considering the $\Gamma$ for which it is possible to compare across norms, we can now define a new, adaptive $\Gamma^*$ which is the pointwise maximum of all of the considered $\Gamma$s.
+First define $\Gamma_{1}(x, \Sigma), \dots, \Gamma_{p}(x, \Sigma)$ as collection of performance metrics which only differ by the norm used in their definition.
 Next, define
@@
 \begin{align*}
-	\Gammaf^*(x) = \max\left\{\Gamma_{\Sigma, 1}(x), \Gamma_{\Sigma, 2}(x), \dots, \Gamma_{\Sigma, p}(x)\right\}.
-\end{align*}
-\textcolor{blue}{This could be the min if smaller values indicate larger distances away from the norm (such as p-values).}
-
-While this function is more complicated than before, distribution of $\Gammaf^*(\rvt)$ can still be compared to $\Gammaf^*(\tst)$ to obtain a p-value.
-Also, while it may be difficult to obtain the exact distribution of $\Gammaf^*(\rvt)$, the distribution is a function of $\vmat$, so obtaining good approximations of $\Gammaf^*(\rvt)$ is possible by taking many draws from $\rvt$.
+	\Gamma^*(x, \Sigma) = \min\left\{\Gamma_{1}(x, \Sigma), \dots, \Gamma_{p}(x, \Sigma)\right\}.
+\end{align*}
+
+While this function is more complicated than before, distribution of $\Gamma^*(\rvt, \Sigma)$ can still be compared to $\Gamma^*(\tst, \Sigma)$ to obtain a p-value.
+Also, while it may be difficult to obtain the exact distribution of $\Gamma^*(\rvt, \Sigma)$, the distribution is a function of $\vmat$, so obtaining good approximations of $\Gamma^*(\rvt, \Sigma)$ is possible by taking many draws from $\rvt$.
 
@@
 \label{ssec:obtaining_null}
-The described procedure requires knowledge of the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ when $P \in \mathscr{M}_0$.
-To obtain an estimate of this limiting distribution, we require that each of the estimators $\hat{\boldsymbol{\psi}}_1, \dots, \hat{\boldsymbol{\psi}}_d$ of $\boldsymbol{\psi}_1, \dots, \boldsymbol{\psi}_d$ is asymptotically linear.
+The described procedure requires knowledge of the limiting distribution of $\rnp$ when $P \in \mathscr{M}_0$.
+To obtain an estimate of this limiting distribution, we require that each of the estimators $\rnp_1, \dots, \rnp_d$ of $\boldsymbol{\psi}_1, \dots, \boldsymbol{\psi}_d$ is asymptotically linear.
 That is for each $j \in \{1, \dots, d\}$:
@@
 Where the $D_j$ function will be referred to as an influence function.
-While this requirement may seem rigid, most standard measures of association are asymptotically linear, and there exists a rich and growing body of literature that describes asymptotically linear estimators and their corresponding functions \textcolor{blue}{Need citations here}.
+Most standard estimators of association are asymptotically linear and have known influence functions.There also exists a growing body of literature describing asymptotically linear estimators and their corresponding functions \textcolor{blue}{Need citations here}.
 
@@
 
-When there is a fixed number of covariates, the Cramer-Wold device can be used to show that the vector of parameter estimates is asymptotically normal with mean zero, and variance covariance matrix given by $\Sigma = E_{\disto_0}\left[D(\rvo) D(\rvo)^\top \right]$:
+When there is a fixed number of covariates, the Cramer-Wold device can be used to show that $\sqrt{n}( \hat{\boldsymbol{\psi}}  - \boldsymbol{\psi})$ estimates is asymptotically normal with mean zero, and variance covariance matrix given by $\Sigma = E_{\disto_0}\left[D(\rvo) D(\rvo)^\top \right]$:
 % \textcolor{blue}{Note from Alex: do you mean $D(\rvo) D(\rvo)^\top$?
 This is what you would want if $D(\rvo)$ were a column vector, which would be more standard (similar comment in other places where `$\top$' is used)}
-
-\begin{align*}
-    \sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right) \xrightarrow{d} \rvv \sim N\left(0, \Sigma\right)
-\end{align*}
-
-Under $H_0$, $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges to $Z$, and $\Sigma$ can be approximated with $\widehat{\Sigma} = \frac{1}{n}\sum_{i = 1}^n D(\boldsymbol{x}_i) D(\boldsymbol{x}_i)^\top$.
+\begin{align*}
+    \sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right) \xrightarrow{d} \rvt \sim N\left(0, \Sigma\right)
+\end{align*}
+
+Under $H_0$, $\rnp$ converges to $\rvt$, and $\Sigma$ can be consistently estimated using $\widehat{\Sigma} = \frac{1}{n}\sum_{i = 1}^n D(\boldsymbol{x}_i) D(\boldsymbol{x}_i)^\top$.
 In practice, a consistent estimator of $\vmat$, $\hat{\vmat}$ will be used in place of $\vmat$ for the calculation of $\tst$.
-Thus, the test statistic will be $\Gammafe(\tst)$ will be compared to $\Gammafe(\rvt)$.
+Thus, the test statistic will be $\Gamma(\tst, \hat{\Sigma})$ will be compared to $\Gamma(\hat{\rvt}, \hat{\Sigma})$ where $\hat{\rvt} \sim N\left(0, \hat{\Sigma}\right)$.
 
 \subsection{Using a permutation test for the test statistic}
-While the above approach works asymptotically, there can be issues for small sample sizes.
-To avoid inflated type one error, a permutation based test can be used.
-Here, $\hat{\distv}^\#$ is used to define $\Gammaf$, and the test will compare $\Gamma_{\hat{\distv}}(\sqrt{n} \hat{\boldsymbol{\psi}})$ to $\Gamma_{\hat{\distv}}(\rvv^\#)$.
-To determine $\hat{\distv}^\#$, the $Y$'s from the observed data are permuted before calculating $\widehat \Sigma$.
-Draws from $\rvv^\#$ are taken by permuting all of the $Y$'s of the observed data.
-\textcolor{blue}{There are a few more complications here that need to be figured out.}
+While the above approach works asymptotically, for small sample sizes there can be greater than $\alpha$ type one error.  To avoid this, a permutation based test can be used in certain settings.
+
+Letting $\Pi$ be the set of all $n!$ one-to-one functions mapping from $\{1, \dots, n\}$ to $\{1, \dots, n\}$, let  $\pi_1, \dots, \pi_B$ be drawn uniformly from $\Pi$ with replacement.
+To carry out the permutation test test, $B$ draws are taken from the null distribution where each the $j^{\text{th}}$ draw is the test statistic $\sqrt{n}\hat{\boldsymbol{\psi}}^{\#}_j$ for a permuted data set $(y_{\pi_j(1)}, x_{1, 1}, \dots, x_{1, d}), \dots, (y_{\pi_j(n)}, x_{n, 1}, \dots, x_{n, d})$.
+After taking these draws, a p-value can be calculated $B^{-1}\sum_{i = 1}^B I\{\sqrt{n}\hat{\boldsymbol{\psi}} \geq \sqrt{n}\hat{\boldsymbol{\psi}}^{\#}_i\}$ and the corresponding test rejects the null if this $p-$value is less than $\alpha$.
+
+This approach can only be applied in settings in which the null hypothesis corresponds to all used covariates being jointly independent of the outcome.
+For example if the parameter of interest is a conditional association measure as is the case in the second and third examples, this procedure will not work.
+
+\section{Theoretical Results}
+\label{sec:theorems}
+While we try to keep theoretical results as general as possible, in order to establish consistency and  non-trivial local ubiasedness of the testing procedure we place restrictions on the norms and performance metrics.
+
+\subsection*{Performance metric and norms considered}
+In the examples considered in this article two performance metrics are considered.
+The first is the estimated acceptance rate performance metric as described in equation \eqref{gamma:pow}.
+The other performance metric considered is the multiplicative distance $\tst$  performance metric defined by:
+
+\begin{align}
+	\Gamma(t, \Sigma) = \text{min}\left\{s : \text{Pr}(\|Z + st\|_p \geq c_\alpha) \geq 0.8 \right\} \label{eqn:mult_dist_gam}
+\end{align}
+
+Both performance metrics are considered to provide multiple examples of viable performance metrics and because each has its own advantages and disadvantages.
+The estimated acceptance rate performance metric has the advantage of being intuitively simple and relatively simple to calculate.
+However this metric also is bounded between zero and one which has the potential to cause issues when calculating the limiting distribution if most of the mass of $\Gamma(Y, \Sigma)$ is concentrated near 1.
+The multiplicative distance performance metric does not face this constraint, but is more difficult to understand intuitively.
+Additionally this metric is more computationally costly, and the $0.8$ used is somewhat arbitrary and it is not clear what effect changing this value would have on the power of tests based on this metric (we hope it has little to no effect).
+
+For both metrics, two sets of norms are considered for the adaptive test.  Letting $\boldsymbol{x} = \left(x_1, \dots, x_d\right)$ the $\ell_p$ norm is defined by
+
+\begin{align*}
+ \ell_p(\boldsymbol{x}) = \sqrt[p]{\sum_{i = 1}^d |x_i|^p }
+\end{align*}
+
+The second set of norms referred to as the sum of squares norm is a function mapping from $\mathbb{R}^d$ to $\mathbb{R}$ defined by 
+\begin{align*}
+	\|\boldsymbol{x}\|_k = \sum_{i = 1}^k x_{(d - i + 1)} 
+\end{align*}
+where $x_{(1)}, \dots, x_{(d)}$ are the order statistics of $x_1, \dots, x_d$.
+When adaptive versions of either performance metric are used in practice one must specify which norms to select over.
+In this work the possible indices ($p$'s) for the $\ell_p$ norm are $1, 2, 4, 6,$ and $\infty$ and the possible indices for the sum of squares norm are the six evenly spaced values between $1$ and $d$ (the dimension of $x$).
+If any of these values are not whole numbers they are rounded to the nearest whole number.
+
+Lemmas \ref{lemma:est_accept} and \ref{lemma:mult_dist_gam} show that the estimated acceptance rate and multiplicative distance performance metrics satisfy these restrictions respectively.
+
+\subsection{Consistency under fixed Alternatives}
+
+\label{sec:test_cnsty}
+
+Consider the following conditions on the performance metric $\Gamma : \mathbb{R}^d \otimes \mathbb{R}^{d \times d} \mapsto \mathbb{R}$:
+
+\begin{enumerate}
+	\item The performance metric $\Gamma$ is continuous and is non-negative
+	\item $\pr\left(\Gamma(Z, \Sigma) = 0\right) = 0$ where $Z \sim N(0, \Sigma)$
+	\item $E\left[\left|\Gamma^*_{\hat{\Sigma}}(\sqrt{n}\hat{\boldsymbol{\psi}})\right| \right] \rightarrow 0$ for all fixed $P \not \in \mathcal{M}_0$, all consistent estimators $\hat{\boldsymbol{\psi}}$ of $\boldsymbol{\psi}$ and all consistent estimators $\hat{\Sigma}$ of $\Sigma$.
+	\setcounter{conditions}{\value{enumi}}
+\end{enumerate}
+
+\begin{theorem}
+\label{thm:cnst}
+If $\hat{\boldsymbol{\psi}}$ is a consistent estimator of $\psi$, $\hat{\Sigma}$ is a consistent estimator of $\Sigma$, and $\Gamma$ satisfies conditions 1 - 3 then the test defined by
+\begin{align*}
+	\text{reject } H_0 \text{ if } \Gamma^*(\sqrt{n}\hat{\boldsymbol{\psi}}, \hat{\vmat}) \leq F^{-1}_{\Gamma^*(\hat{\rvt}, \hat{\vmat})}(\alpha)
+\end{align*}
+is consistent.  
+\end{theorem}
+
+\subsection*{Local Unbiasedness}
+Consider a sequence of local alternatives $P_n$ in which the value of $\Psi(P_n) = \psi_n = \underline{h}/\sqrt{n}$ shrinks towards zero as $n$ grows.
+We wish to show that our test is non-trivially locally unbiased, that is for large $n$:
+\begin{align*}
+	Pr_{\disto}\left(\gamestp \leq F^{-1}_{\gamestz}(\alpha)\right) > \alpha 
+\end{align*}
+To achieve this, we fist assume our estimator $\rnp$ is consistent and regular at $\boldsymbol{\psi}$.
+The estimator $\hat{\boldsymbol{\psi}}$ is regular if and only if for every sequence $\psi_n$ with $\sqrt{n} (\psi_n - \psi) \to \underline{h}$, the sequence $\sqrt{n}(\hat{\psi} - \psi_n) \xrightarrow{P_{\psi_n}} Z$, where $Z$ can be different for different $\psi$, but not for different $t$.
+Two additional conditions on $\Gamma$ are sufficient to have tests based on $\Gamma$ be locally unbiasedness.
+
+\begin{enumerate}
+	\setcounter{enumi}{\value{conditions}}
+	\item $\Gamma$ is unimodal for every $\Sigma$ (for every $k$, the set $\{x : \Gamma(x, \Sigma) \geq k\}$ is convex).
+	\item $\Gamma$ is centrally symmetric for every $\Sigma$, $(\Gamma(-x, \Sigma) = \Gamma(x, \Sigma))$.
+\end{enumerate}
+
+\begin{theorem}
+	\label{thm:unbiased_locl_alt}
+Let $P_{n}$ be a sequence of local alternatives under which the value of $\Psi(P_n)$ is $\underline{h}/\sqrt{n}$, and let $\nrvs \sim N\left(\boldsymbol{0}, \Sigma\right)$ and  $\hat{Y}_{\Sigma} \sim N\left(\boldsymbol{0}, \hat{\Sigma}\right)$.
+If $\Gamma$ satisfies conditions 1, 2, 4, and 5, the estimator $\hat{\Sigma}$ of $\Sigma$ is consistent, and the estimator $\hat{\psi}$ of $\psi$ is regular at $\boldsymbol{\psi}$.
+Then the test defined by
+\begin{align*}
+	\text{ reject } H_0 \text{ if } \gamestp \leq F^{-1}_{\gamestz}(\alpha)
+\end{align*}
+has power greater than $\alpha$ under $P_n$.
+\end{theorem}
 
@@
 Three different models for the outcome of interest ($Y$) will are considered.
-Letting $\varepsilon \sim N(0, 1)$ and be independent of $X$, in the first model $Y = \varepsilon$, in the second $Y = X_1 / 4$, and in the third $Y = \sum_{k = 1}^{10} \beta_k X_k + \varepsilon$ where $\beta_k = 0.15$ for $k = \{1, \dots, 5\}$, and $\beta_k = -0.1$ for $k = \{6 \dots 10\}$.
+Letting $\varepsilon \sim N(0, 1)$ and be independent of $W$, in the first model $Y = \varepsilon$, in the second $Y = W_1 / 4$, and in the third $Y = \sum_{k = 1}^{10} \beta_k W_k + \varepsilon$ where $\beta_k = 0.15$ for $k = \{1, \dots, 5\}$, and $\beta_k = -0.1$ for $k = \{6 \dots 10\}$.
 Sample sizes of $100$ and $200$, dimensions of $10$, $50$, $100$, $150$, and $200$ are considered.}
@@
 
-In the above figure, the rejection rates of six different tests are shown for a wide variety of settings.
-Data are generated from three different potential models.
-In the first model no covariates are directly associated with the outcome ($H_0$ holds), in the second model a single covariate is strongly directly associated with the outcome ($H_0$ does not hold), and in the third model ten covariates are directly associated with the outcome ($H_0$ does not hold).
-In all models the covariates are generated from a mean zero multivariate normal distribution $\Sigma$, where $\Sigma_{ij} = 0.8$ for $i \neq j$ and 1 for $i = j$.
-Each color of dots represents a different type of test.
-The red dots indicate a bonferroni adjusted marginal test for each covariates estimated correlation with the outcome.
-The light blue dots indicate performance of the test proposed by [Zhang and Laber].
+In figures (\ref{fig:uncor}, \ref{fig:somecor}, \ref{fig:lotscor}), the rejection rates of six different tests are shown for a wide variety of settings.
+Each test has the null hypothesis that $\psi_1, \dots, \psi_d = 0$ where $\psi_i = \Psi_i(P)$ is the correlation between the outcome $Y$, and the $j^\text{th}$ covariate $W_j$.
+A description of the data generating mechanism can be found in section \ref{sec:Working Examples}.
+Red dots indicate a bonferroni adjusted marginal test for the estimated correlation between each covariate and the outcome.
+Light blue dots indicate the performance of the test proposed by [Zhang and Laber].
 The other colors correspond to different variants of our test.
@@
 \subsection*{Two Phase Sampling Risk Ratio}
-Here, we would expect that the $\ell_2$ norm would perform poorly in the model 2 setting while performing well in the model 3 setting, and that the max norm would perform poorly in the model three setting while performing well in the model two setting.
+The for the second example was carried out after deriving the influence of the parameter given in equation \ref{eqn:DE2param}.
+Marginal expectations were estimated using either an elastic net \citep{simon_blockwise_2013,tibshirani_strong_2012,friedman_regularization_2010, tibshirani_strong_2012} or a superlearner \citep{polley_super_2010}.
+
+Figure \ref{fig:dat_examp_2} shows the rejection rates of four different tests across the settings described in section \ref{sec:data_app}.
+Each test has the null hypothesis that $\psi_1, \dots, \psi_d = 0$ where $\psi_i = \Psi_i(P)$ is the risk ratio that $Y = 1$ comparing two observations which differ by a unit in the covariate $W_j$.
+Data are generated using three  different settings.
+In the first setting no covariates are directly associated with the outcome ($H_0$ holds), in the second setting a single covariate has a strong, direct association with the outcome ($H_0$ does not hold), and in the third setting ten covariates are directly associated with the outcome ($H_0$ does not hold).
+Each color of dots represents a different version of our test.
+Red and light green dots indicate the performance of our test using only the $\ell_2$ or maximum absolute value norm respectively.
+Dark green dots indicate the performance of our test when it adaptively select one of the $\ell_p$ norms.
+Yellow dots indicate our tests performance when the test adaptively selects over various sum of squares norms.
+The dotted red line in each plot indicates the $0.05$ rejection rate that should be observed when $H_0$ holds.
+
+% Here, we would expect that the $\ell_2$ norm would perform poorly in the model 2 setting while performing well in the model 3 setting, and that the max norm would perform poorly in the model three setting while performing well in the model two setting.
 However, we see the opposite behavior.
 Additionally, we find that our adaptive test performs well consistently across all alternatives.
-
-\textcolor{blue}{I will eventually just chose one of these figures because performance will be very similar between the two measures.
-I just want to see how similar they are once I get a complete set of simulation results.}
-
 \begin{figure}[H]
 	\centering
-\includegraphics[width = 0.7 \linewidth]{magnitude.pdf}
+\includegraphics[width = \linewidth]{mag_w_unc_de2.pdf}
+\label{fig:dat_examp_2}
 	\caption{Rejection rates across three different data generating mechanisms.
-Here we are using the the multiplicative distance our test statistic is from obtaining 80\% power as our measure of performance.}
+Here we are using the multiplicative distance our test statistic is from obtaining 80\% power as our measure of performance.}
 	\label{fig:magnitude}
@@
 
+\subsection*{Marginal Structural Model}
+Testing for this example was carried out using code from the ltmle package \citep{lendle_ltmle_2017} to estimate the influence function of our parameter.
+Using this estimate of the influence function, a parametric bootstrap was used to estimate the limiting distribution of our test statistic.
+The multiplicative distance performance metric was used for these simulations.
+Data are generated using three  different settings.
+In the first setting no covariates modifies the treatment effect ($H_0$ holds), in the second setting a single covariate modifies the treatment effect ($H_0$ does not hold), and in the third setting ten covariates modify the treatment($H_0$ does not hold).
+Each color of dots represents a different version of our test.
+Red and light green dots indicate the performance of our test using only the $\ell_2$ or maximum absolute value norm respectively.
+Dark green dots indicate the performance of our test when it adaptively select one of the $\ell_p$ norms.
+Yellow dots indicate our tests performance when the test adaptively selects over various sum of squares norms.
+The dotted red line in each plot indicates the $0.05$ rejection rate that should be observed when $H_0$ holds.
+
 \begin{figure}[H]
 	\centering
-\includegraphics[width = 0.7 \linewidth]{power.pdf}
-	\caption{Rejection rates across three different data generating mechanisms. Here we are using estimated power as the measure of performance.}
-	\label{fig:magnitude}
+	\includegraphics[width = \linewidth]{mag_w_unc_de3.pdf}
+	\caption{Rejection rates across a range of settings when a marginal structural model was used to define the parameter of interest.}
+	\label{fig:de3}
 \end{figure}
+
+Because $H_0$ is true for the first setting, we expect the rejection rates in this setting to be $0.05$.
+Figure \ref{fig:de3} show results consistent with this being the case.
+For the other two settings $H_0$ does not hold so these plots compare the powers between the different testing procedures.
+While results are not definitive it appears that for the second setting in which a single covariate modifies the treatment effect it appears that the max norm has the best performance followed by the adaptive procedures and then the $\ell_2$ norm.
+In the third setting in which many covariates are associated with the outcome the adaptive norms appear to once again have middling performance now with the $\ell_2$ norm performing the best and the max norm performing the worst.
+It was expected that the non-adaptive tests would excel where they did and that the adaptive versions tend to perform well across multiple settings.
+It is unclear from these results if, for a given setting, at least one non-adaptive version of the test will outperform the adaptive version of the test.
+
+One setting in which the adaptive test performs poorly is in settings in which a single covariate is correlated with the outcome of interest and no covariates are correlated as seen for model 2 in figure \ref{fig:uncor}.
+This behavior could be due to the parameter estimates inability to be sparse even in settings when sparsity occurs.
+The many small errors in the parameter estimate across many covariates leads to a preference for the $\ell_2$ norm that obtains an overly optimistic estimate of power due to the accumulation of many small effects across all the covariates.
 
@@
 \label{sec:data_app}
-
-\sh{\begin{enumerate}
-	\item Data from Peter Gilbert
-\end{enumerate}
-}
-
-\subsection*{Marginal Structural Model}
+\sh{Data from Peter Gilbert}
 
@@
 \label{sec:discuss}
-
-In this paper, we have discussed the difficulties of creating multivariate test of no correlated coefficients.
-General methods are have wide applicability, but are often underpowered.
-More powerful methods are frequently difficult to understand, and will only work properly in narrow settings for a single parameter of interest.
-
-We described a test that addresses these issues, by achieving comparable performance to taylor made methods, while being applicable in a wide variety of settings.
-We have demonstrated the methods ability to compete with existing methods in section \ref{sec:sim_stdy}, and shown novel settings in which the method can also be performed.
-Data example 2 was an example of testing a relatively simple parameter (a risk ratio) in a setting with a non-standard sampling scheme.
-Data example 3 was an example of testing a more complex parameter (a parameter inside of a marginal structural model) for a straightforward sampling scheme.
-
-While our procedure does rely on asymptotic results to function properly for many parameters, in certain cases, a our test can be carried out using permutations of the data to obtain better finite sample properties.
-This is done by repeating our estimation procedure many times after randomly permuting the outcome variable.
+When developing anything there is frequently a trade off to between generalizability and performance.
+However the reduction in power of bonferroni-based methods compared to taylor made procedures is often larger than is needed.
+We have developed a generalizable testing procedure that still can outperform bonferroni based methods.
+We have demonstrated this in section \ref{sec:sim_stdy} and shown novel settings in which the method can also be performed.
+These settings show that our test can be applied to parameters in non-standard sampling schemes (see section \ref{sec:missing_data}) and complex parameters (see section \ref{sec:msm_data}).
+
+Our procedure does rely on asymptotic results to achieve correct type one error rates which can cause issues when the number of covariates of interest is larger than sample size.
+To address this issue, in certain cases a our test can be carried out using permutations of the data to obtain better finite sample properties.
+%\textcolor{blue}{This is done by repeating our estimation procedure many times after randomly permuting the outcome variable.
 The method is used in our first data example, and could be used for our third data example.
-However, in certain settings with more complicated sampling schemes, the permutation based test is more difficult to implement because many of the outcomes are not even observed.
-
-While we have outlined some of the ways in which our method can be used, there are many other ways in which it can be extended improved.
+In certain settings with more complicated sampling schemes, the permutation based test is more difficult to implement because many of the outcomes are not even observed.}
+
+While we have outlined some of the ways in which our method can be used, there are other possible applications and improvements.
 
@@
 However, this estimator runs into issues when $p > n$ and $\hat{\Sigma}^{-1/2}$ becomes impossible to estimate because of the rank deficiency of the variance estimator.
-While this problem still technically exist when indexing our $\Gamma$'s by $\hat{\Sigma}$, using a multiplier bootstrap to take draws from $N(0, \Sigma)$ avoids the computation issues of having a degenerate estimate of the limiting distributions variance matrix.
+While this problem still technically exist when indexing our $\Gamma$s by $\hat{\Sigma}$, using a multiplier bootstrap to take draws from $N(0, \hat{\Sigma})$ avoids the computation issues of having a degenerate estimate of the limiting distributions variance matrix.
+
+\textcolor{blue}{Mention choice of norms and choice of performance metric}
 
 While changing the test statistic as described above has major hurdles to overcome to be implemented in $p > n$ settings, there are other extensions or generalizations of our procedure that are possible without much change.
-While we considered one set of $\Gammaf$ funcitons in this article, any set of reasonable $\Gammaf$ functions could be used.
-These $\Gammaf$ functions could even be picked by machine learning methods used for classification.
+While we considered one set of $\Gamma$ funcitons in this article, any set of reasonable $\Gamma$ functions could be used.
+These $\Gamma$ functions could even be picked by machine learning methods used for classification.
 The classifier would provide a probability that any observation was generated from the null distribution.
-Doing this provides a more rich set of $\Gammaf$ over which to select, and has the potential to provide large increases in test performance.
+Doing this provides a more rich set of $\Gamma$ over which to select, and has the potential to provide large increases in test performance.
 One would expect that a classifier would perform better better when data are generated at an alternative versus at the null.
@@
 These probabilities could be estimated by taking many draws from a normal with mean $\sqrt{n}\hat{\boldsymbol{\psi}}$ and variance $\hat{\Sigma}$ and finding the optimal norm for each of these draws.
-This method while being more computationally costly, could potentially be shown to be optimal in the sense that it would maximize the average power of all tests based on the specified family of norms for each local alternative.
+This method while being more computationally costly, could potentially be shown theoretically to be optimal in the sense that it would maximize the average power of all tests based on the specified family of norms for each local alternative.
 
 While $\ell_p$ norms were used throughout this paper, one issue observed with our test is that it selects the $\ell_2$ norm more frequently than it should, likely because of the many small estimates for parameters that are not associated with the outcome.
-One could consider a slightly modified norm that sets to zero all component values of the vector that are less than some value (say $2 \times \text{var}(X)\sqrt{n}$).
+One could consider a slightly modified norm that sets to zero all component values of the vector that are less than some value.
 This would hopefully solve issues of small values close to zero causing incorrect selection of norms that perform well when there are many small effects.
 
-\textcolor{blue}{add notes about limitation of our method (need to fin influence function)}
-
-\textcolor{blue}{Multiple measures of association for each covariate.)}
+\textcolor{blue}{add notes about limitation of our method (need to find influence function).  Also discuss difficulty with convergence when using the parametric bootstrap.}
+
+In this article chose tests in which each parameter corresponded to a single covariate, and each covariate only had a single corresponding parameter.
+However it would also be possible to have tests where each parameter corresponded to a set of many covariates or each covariate or group of covariates had multiple measures of association.
 
@@
 \section{Appendix}
-
-\subsection{Test Consistency}
-\label{sec:test_cnsty}
-
-\begin{theorem}
-\label{thm:cnst}
-Assume the performance metric of choice is $\hat{r}_{\alpha, p}(a)$, and each the norms $g_a$ considered have the following properties: 
-\begin{align}
-& \text{for } x \in \mathbb{R}^d, \text{ and } s, l > 0, s \cdot \max({\boldsymbol{x}}) \leq g_a(\boldsymbol{x}) \leq l \cdot d \cdot \max({\boldsymbol{x}}) \label{eqn:nrm_bounds}\\
-& \text{for } s \leq 1, l \geq 1, g_a(s \cdot \boldsymbol{x}) \leq g_a(\boldsymbol{x}) \leq g_a(l \cdot \boldsymbol{x}) \label{eqn:linegrowth}
-\end{align}
-Then for all $P \not \in \mathscr{M}_0$ 
-\begin{align*}
-	Pr \left(\frac{1}{B}\sum_{k = 1}^B I\left\{\hat{T} \leq \hat{T}_k^{\#}\right\} < 0.05\right) \xrightarrow{p} 1 \text{ as } n \to \infty
-\end{align*}
-or Equivalently
-
-\begin{align*}
-Pr\left(\hat{T} \leq F^{-1}_{\hat{T}^\#}(0.05)\right) \xrightarrow{p} 1 \text{ as } n \to \infty
-\end{align*}
-\end{theorem}
+This appendix is primarily focused on proving the consistency and local power of our testing procedure.
+
+For multiple proofs it will be necessary to use the dominated convergence theorem, and find a dominating measure for $\phi(x, \mu, \Sigma)$ and $\phi(x, \mu_n, \Sigma_n)$ where $\phi$ is the pdf for a multivariate normal distribution.
+
+\begin{lemma}
+	\label{lemma:dom_measure}
+	The function $\phi : \mathbb{R}^d \otimes \mathbb{R}^d \otimes \mathbb{R}^{d \times d} \to \mathbb{R}$ defined by
+\begin{align*}
+	\phi : (x, \mu, \Sigma) \mapsto \text{det}(\Sigma)^{-1/2}(2\pi)^{-k/2}\text{exp}\left( - \frac{1}{2}(x- \mu)\Sigma^{-1}(x- \mu)\right)
+\end{align*}
+	is continuous and $\phi_{\Sigma, \mu} : x \mapsto \phi(x, \Sigma, \mu)$ and $\phi_{\mu_n, \Sigma_n} : x \mapsto \phi(x, \Sigma_n, \mu_n)$ are dominated by an integrable function.
+\end{lemma}
 
 \begin{proof}
-This proof will consist of three parts.
-We will first show that as $n \to \infty, \hat{T}_a^\#$ becomes bounded away from $0$ for any valid norm.
-Next we will show $\hat{T}_a$ converges to $0$ in probability for any valid norm.
-Last we will show the two previous findings imply theorem \ref{thm:cnst}.
-
-Let $P^\#_{\rvo}$ denote the distribution of the randomly permuted observations.
-\sh{Because $Pr(Y^{\#}_i \indep \boldsymbol{W}^\#_{i}) \to 0$, $\boldsymbol{\Psi}(P^\#_{\rvo}) = \boldsymbol{0}$.
-Additionally, $\sqrt{n}\left(\hat{\boldsymbol{\psi}}^\# -\boldsymbol{\psi}^\# \right) \xrightarrow{d} Z^\# \sim N\left(\boldsymbol{0}, \Sigma_{\text{perm}}\right)$}.
-Define $\hat{T}_a^\# = \min_s\{s : g_a(s \cdot \sqrt{n}\hat{\boldsymbol{\psi}}^\#) \geq C_{0.95, a}^\# \}$ and $C^\#_{0.95, a}$ is $F^{-1}_{Z^\#}(0.95)$.
-Since we know that $\psi^\# = \boldsymbol{0}$, it follows that $\sqrt{n}\hat{\boldsymbol{\psi}}^\# \overset{d}{\approx} Z^\#$.
-
-Now, consider:
-\begin{align*}
-	\pr\left(\hat{T}^\#_a  > \epsilon\right) &= \pr\left(g_a\left(\epsilon \cdot \sqrt{n}\hat{\boldsymbol{\psi}}^\#\right) \leq C_{0.95, a}\right)\\
-	& \geq \pr\left(\epsilon \cdot d \cdot  \max\left(\sqrt{n} \hat{\boldsymbol{\psi}}^\# \right)\leq C_{0.95, a}\right)\\
-	& = \pr\left( \max\left(\sqrt{n} \hat{\boldsymbol{\psi}}^\# \right)\leq C_{0.95, a}/(\epsilon \cdot d)\right)
-\end{align*}
-Because $\max\left(\left|\sqrt{n} \hat{\boldsymbol{\psi}}^\#\right|\right)$ converges to a well defined, positive distribution as a result of the continuous mapping theorem, for each constant $c < 1$, we know there exists an $\epsilon_c$ such that $\pr\left(\hat{T}^\#_a  > \epsilon_c\right) \geq c$.
-
-%From the definition of $C_{0.95, a}^\#$ it follows that $Pr(g_a(\sqrt{n}\hat{\boldsymbol{\psi}}^\#) \leq C^\#_{0.95, a}) \to 0.95$.
-For realizations in which $g_a(\sqrt{n}\hat{\boldsymbol{\psi}}^\#) \leq C^\#_{0.95, a}$ it must also be true that $\hat{t}^\# > 1$  from \eqref{eqn:linegrowth}.
-From the above logic it follows that $Pr(\hat{T}_a^\# > 1) \geq 0.95$ and thus $F^{-1}_{\hat{T}_a^\#}(0.05) \geq 1$ with a probability approaching 1.
-
-Now, shifting our focus to $\hat{T}_a$, under alternatives, $\boldsymbol{\psi} \neq \boldsymbol{0}$.
-Define $\psi_{\max} = \max(\psi_1, \dots, \psi_d)$.
-Using this knowledge, and \eqref{eqn:nrm_bounds}, note that
-\begin{align}
-\pr\left(\hat{T}_a < \epsilon\right) &= \pr\left(g_a\left(\epsilon \cdot \sqrt{n} \hat{\boldsymbol{\psi}}\right) \geq C_{0.95, a}\right) \nonumber\\
-&\geq \pr\left(\epsilon \cdot \sqrt{n}\max(\hat{\psi}_1, \dots, \hat{\psi}_d) \geq C_{0.95, a}\right) \nonumber \\
-&= \pr\left(\max(\hat{\psi}_1, \dots, \hat{\psi}_d) \geq C_{0.95, a}/\left(\epsilon \cdot \sqrt{n}\right)\right) \nonumber \\
-&\geq \pr\left(\max(\hat{\psi}_1, \dots, \hat{\psi}_d) \geq \psi_{\max}/2\right) \pr\left(\psi_{\max}/2\geq C_{0.95, a}/\left(\epsilon \cdot \sqrt{n}\right)\right) \label{eqn:prod_tlte} 
-\end{align}
-The first factor of the product in \eqref{eqn:prod_tlte} will converge to 1 as $n \to \infty$ from the consistency of $\hat{\boldsymbol{\psi}}$.
-The second quantity will be equal to 1 for sufficiently large $n$.
-Thus $\hat{T}_a \xrightarrow{p} 0$ under any alternative.
-
-It was shown that for each $a$ that $\hat{T}_a \xrightarrow{p} 0$.
-This means that our adaptive estimator $\hat{T} \xrightarrow{p} 0$ as well.
-Now, let $c = 0.05/k$ and $\epsilon_c$ be small enough that $\pr\left(\hat{T}^\#_a  > \epsilon_c\right) \geq 1 - (0.05/k)$.
-The permutation version of the adaptive estimator $\hat{T}^\#$ has the property that
-\begin{align*}
-	\pr\left(\hat{T}^\# < \epsilon_c\right) \leq \pr(\hat{T}^\#_1 < \epsilon_c) + \dots + \pr(\hat{T}^\#_k < \epsilon_c) \leq 0.05,
-\end{align*}
-and the theorem's conclusion follows.
+Since matrix inverses, matrix determinants, matrix multiplication, and the exponential function are all continuous, it follows that the multivariate normal distribution is also continuous with respect to $\Sigma, \mu$ and $x$.
+Because of this, we also know that for large enough $n$ that
+
+\begin{align*}
+\left|\frac{1}{2}(x_n - \mu_n)\Sigma_n^{-1}(x_n - \mu_n) - \frac{1}{2}(x - \mu)\Sigma^{-1}(x - \mu)\right| < \varepsilon
+\end{align*}
+
+for any $\varepsilon$ we choose.  When $\varepsilon = \text{log}(2)$ it is the case that 
+% $\max\left(0, 2 \text{log}\left((2 \pi)^{-k} \text{det}(\Sigma)^{1/2}\right)\right)$. 
+% We can also bound $\left|\phi(x_n, \mu_n, \Sigma_n) - \phi(x, \mu, \Sigma)\right|$ by 1 for large enough $n$.
+For $x, \mu$ such that $\frac{1}{2}(x - \mu)\Sigma^{-1}(x - \mu)/2 < \varepsilon$, we know $\phi(x, \mu, \Sigma) > 1$ therefore.
+% \begin{align*}
+% 	\phi(x, \mu_n, \Sigma_n) - \phi(x, \mu, \Sigma) &\leq \left|\phi(x, \mu_n, \Sigma_n) - \phi(x, \mu, \Sigma)\right| \leq 1 \leq \phi(x, \mu, \Sigma)\\
+% 	\text{therefore }\phi(x, \mu_n, \Sigma_n) &\leq 2\phi(x, \mu, \Sigma)
+% \end{align*}
+
+\begin{align*}
+	\frac{\psi(x, \mu_n, \Sigma_n)}{\psi(x, \mu, \Sigma)} &= \frac{\frac{\text{det}(\Sigma_n)^{-1/2}}{(2\pi)^{k/2}}\text{exp}\left( - \frac{1}{2}(x_n - \mu_n)\Sigma_n^{-1}(x_n - \mu_n)\right)}{\frac{\text{det}(\Sigma)^{-1/2}}{(2\pi)^{k/2}}\text{exp}\left( - \frac{1}{2}(x - \mu)\Sigma^{-1}(x - \mu)\right)}\\
+	&= \frac{\text{det}(\Sigma_n)^{-1/2}\text{exp}\left(- \frac{1}{2}\left((x_n - \mu_n)\Sigma_n^{-1}(x_n - \mu_n)- (x - \mu)\Sigma^{-1}(x - \mu)\right)\right)}{\text{det}(\Sigma)^{-1/2}} \\
+	&\leq \frac{\text{det}(\Sigma_n)^{-1/2}\text{exp}\left( \left| - \frac{1}{2}\left((x_n - \mu_n)\Sigma_n^{-1}(x_n - \mu_n) - (x - \mu)\Sigma^{-1}(x - \mu) \right|\right)\right)}{\text{det}(\Sigma)^{-1/2}} \\
+	&\leq \frac{\text{det}(\Sigma_n)^{-1/2}\text{exp}\left(\text{log}(2)\right)}{\text{det}(\Sigma)^{-1/2}} \\
+	&\leq \frac{\text{det}(\Sigma_n)^{-1/2} 2 }{\text{det}(\Sigma)^{-1/2}} 
+\end{align*}
+% For $\frac{1}{2} (x - \mu)\Sigma^{-1}(x - \mu) \geq \varepsilon$ we can do something similar.  First note that for $n$ large enough, 
+Next, note that 
+\begin{align*}
+	\text{det}(\Sigma_n)^{-1/2} - \text{det}(\Sigma)^{-1/2} \leq \left|  \text{det}(\Sigma_n)^{-1/2} - \text{det}(\Sigma)^{-1/2} \right| \leq \text{det}(\Sigma)^{-1/2} \Rightarrow \text{det}(\Sigma_n)^{-1/2} \leq 2\text{det}(\Sigma)^{-1/2}
+\end{align*}
+Therefore, we find that 
+\begin{align*}
+	\frac{\text{det}(\Sigma_n)^{-1/2} 2 }{\text{det}(\Sigma)^{-1/2}} &\leq \frac{\left[2\text{det}(\Sigma_n)\right]^{-1/2} 2 }{\text{det}(\Sigma)^{-1/2}} = 2\sqrt{2}
+\end{align*}
+
+Thus, for large enough $n$, we can bound $\phi(x, \mu_n, \Sigma_n)$ by $2\sqrt{2} \phi(x, \mu, \Sigma)$ which is integrable.
+
+% \begin{align*}
+% 	\left|\frac{1}{2}(x_n - \mu_n)\Sigma_n^{-1}(x_n - \mu_n) - \frac{1}{2}(x - \mu)\Sigma^{-1}(x - \mu)\right| < \varepsilon &\leq \frac{1}{2}(x - \mu)\Sigma^{-1}(x - \mu) / 2 \\
+% 	\frac{1}{2}(x_n - \mu_n)\Sigma_n^{-1}(x_n - \mu_n) & \geq \frac{1}{2}(x - \mu)\Sigma^{-1}(x - \mu)/2\\
+% 	\text{exp}\left( - \frac{1}{2}(x_n - \mu_n)\Sigma_n^{-1}(x_n - \mu_n)\right) &\leq \text{exp}\left( - \frac{1}{2}(x - \mu)\Sigma^{-1}/2(x - \mu)\right)\\
+% 	\frac{\text{det}(\Sigma_n)^{-1/2}}{(2\pi)^{k/2}}\text{exp}\left( - \frac{1}{2}(x_n - \mu_n)\Sigma_n^{-1}(x_n - \mu_n)\right) &\leq (2\pi)^{-k/2}2\text{det}(\Sigma)^{-1/2}\text{exp}\left( - \frac{1}{2}(x - \mu)\Sigma^{-1}/2(x - \mu)\right)\\
+% 	\phi\left(x_n, \mu_n, \Sigma_n\right) &\leq (2\pi)^{-k/2}2\text{det}(\Sigma)^{-1/2}\frac{\text{det}(2\Sigma)^{-1/2}}{\text{det}(2\Sigma)^{-1/2}}\text{exp}\left( - \frac{1}{2}(x - \mu)\Sigma^{-1}/2(x - \mu)\right)\\
+% 	&=\frac{\text{det}(2\Sigma)^{-1/2}}{(2\pi)^{k/2}}\frac{2\text{det}(\Sigma)^{-1/2}}{2^{-k/2}\text{det}(\Sigma)^{-1/2}}\text{exp}\left( - \frac{1}{2}(x - \mu)\Sigma^{-1}/2(x - \mu)\right)\\
+% 	&=\frac{\text{det}(2\Sigma)^{-1/2}}{(2\pi)^{k/2}}2^{1 + k/2}\text{exp}\left( - \frac{1}{2}(x - \mu)\Sigma^{-1}/2(x - \mu)\right)\\
+% 	&=2^{k/2 + 1}\phi(x, \mu, 2\Sigma)\\
+% e\end{align*}
+
+% Thus, we know that we can bound both $\phi(x, \mu, \Sigma)$ and $\phi(x_n, \mu_n, \Sigma_n)$ by the function:
+
+% \begin{align*}
+% 	\zeta(x, \mu, \Sigma) = 2\phi(x, \mu, \Sigma) + 2^{k/2 + 1} \phi(x, \mu, 2\Sigma)
+% \end{align*}
+
+% Which we know is integrable with respect to $x \in \mathbb{R}^d$ because it is a linear combination of two integrable functions.
 \end{proof}
 
-\sh{\subsection{Unbiasedness at local alternatives}
-Consider a local alternative in which the true value of $\psi$ is shrinking towards zero at a root $n$ rate: $\psi = \underline{h}/\sqrt{n}$.
-We assume that each potential norm is convex.
-This assumption can be relaxed to what was described by Eaton and Perlman (1991) (Concentration inequalitites for multivariate distributions: mv normal).
-Under this local alternative, we will have $\sqrt{n} \hat{\psi} \xrightarrow{d} N(\underline{h}, \Sigma)$.
-Show that the test will reject the null with a probability greater than $\alpha$ for an $\alpha$ level test}
-
-\begin{theorem}
-
-Under local alternatives described above, 
-\begin{align*}
-	Pr_{\disto}\left(\Gamma^*_{\hat{\vmat}}(\sqrt{n}\hat{\boldsymbol{\psi}}) \leq F^{-1}_{\Gamma^*_{\hat{\vmat}}(\hat{\rvv})}(\alpha)\right) > \alpha,
-\end{align*}
-
-Where $\hat{\rvv} \sim \hat{\distv}$ and $\rvv \sim \distv$.
-Here (unlike other parts of the paper) small values of $\Gamma$ provide evidence against the null.
-Values of $\Gamma$ can be thought of as similar to $p$-values.
-\end{theorem}
-
 \begin{lemma}
-	\label{lemma:cont_of_gam}
-	The function:
-	\begin{align*}
-		\Gamma_{\Sigma}(t) = Pr_\distv(\|\tilde\rvv + t\| > c_{0.8})  \text{ where }  c_{\vmat, 0.8} \equiv \min_{c}\{c : Pr_\distv(\|\tilde\rvv\| < c) \geq 0.8 \} \text{ and } \tilde\rvv \sim N(0, \Sigma)
-	\end{align*}
-	is continuous with respect to $\Sigma$ and $t$.  
+	\label{lemma:gamma_conv}
+	Let $\hat{Z} \sim N(0, \hat{\Sigma})$ and $Z \sim N(0, \Sigma)$.
+If $\hat{\Sigma}$ is a consistent estimator of $\Sigma$, $\Gamma : \mathbb{R}^{d} \otimes \mathbb{R}^{d^2}$ is continuous, and $Pr(\Gamma(Z, \Sigma) = t) = 0$ for each $t$.
+It follows that the distribution function of $\Gamma(\hat{Z}, \hat{\Sigma})$ denoted by $F_{\Gamma(\hat{Z}, \hat{\Sigma})}$ converges pointwise to the distribution function of $\Gamma(Z, \Sigma)$ denoted by $F_{\gamz}$ and the quantile function of $\gamestz$ denoted by $F^{-1}_{\gamestz}$ converges pointwise to the quantile function of $\gamz$ denoted $F^{-1}_{\gamz}$ where $F^{-1} : [0, 1] \to \mathbb{R}$ is defined By $F^{-1}(p) = \inf\{x : F(x) \geq p\}$
 \end{lemma}
 
-This lemma will follow because $\Gamma$ is the integral of a composition of bounded, continuous functions.
-
 \begin{proof}
-	The multivariate normal probability density function
-\begin{align*}
-	\phi(x, \mu, \Sigma) = \left(2\pi\right)^{-k} \text{det}\left({\Sigma}\right)^{- \frac{1}{2}} \exp\left(-\frac{1}{2} (x - \mu)^\top \Sigma^{-1}(x - \mu)i\right) 
-\end{align*}	
-is continuous with respect to both $\Sigma$ and $t$.
-
-Since the exponential function, determinate, matrix inverses, and linear operators are all differentiable, they are also all continuous.
-Because the multivariate normal pdf is the composition of continuous functions, it is also continuous.
-
-It follows that if $\mu_n \rightarrow \mu$, and $\Sigma_n \rightarrow \Sigma$, then for each $x$, $\phi(x, \mu_n, \Sigma_n) \rightarrow \phi(x, \mu, \Sigma)$.
-This result and the dominated convergence theorem imply the corresponding CDF's are also continuous \textcolor{blue}{($\phi(x, \hat{\mu}, \hat{\Sigma}) + \phi(x, \mu, \Sigma)$ can be used as the dominating measure): (dominating function shouldn't depend on $n$)}  To find a dominating measure, assume that $\vmat_n^{-1}$ is close enough to $\vmat^{-1}$ so the smallest eigenvalue is within $\varepsilon$ then bound the pdf using this fact and that $(x - \mu)^\top \Sigma^{-1}(x - \mu) = (x - \mu)^\top ADA^{-1}(x - \mu) \leq \|(x - \mu)\|^2 c$ where $c$ is the largest eigen value (can be done to provide oposite direction as well).
-
-\begin{align*}
-	\pf_{\hat{\Sigma}, \hat{\mu}}\left(t \right) = \int_{\|x\| < t} \phi(x, \hat{\mu}, \hat{\Sigma})dx \rightarrow \int_{\|x\| < t} \phi(x, \mu, \Sigma)dx = \Phi_{\Sigma, \mu}(t).
-\end{align*}
-
-\textcolor{blue}{Show (or find reference showing that) $\Phi_{\Sigma_n,0}^{-1}(0.8)\rightarrow \Phi_{\Sigma,0}^{-1}(0.8)$ when $\Sigma_n\rightarrow \Sigma$.
-E.g., implicit function theorem will do this}
-
-Because the normal cdf is continuous, we know the normal quantile function will be continuous as well.
-Potentially we can prove the existence of the inverse using the fact the CDF has a bounded derivative on all of $\mathbb{R}$.
-Let $\Sigma_n \rightarrow \Sigma$ and $h_n \rightarrow h$.
-Also, let $Q_n$ be a normal distribution with mean zero and variance-covaraince $\Sigma_n$.
-These findings imply the following:
-
-\begin{align*}
-	\left|\Gamma_{\Sigma_n}(h) - \Gamma_{\Sigma}(h)\right| &= \left|Pr_{\distv_n}(\|\tilde\rvv + h\| > \Phi^{-1}_{\Sigma_n, 0}(0.8)) - Pr_{\distv}(\|\tilde\rvv + h\| > \Phi^{-1}_{\Sigma, 0}(0.8))\right|\\
-	&= \left|\int_{\mathbb{R}^d} \phi(t, 0, \Sigma_n) I\{\|t+h\| > \Phi^{-1}_{\Sigma_n, 0}(0.8) \} - \phi(t, 0, \Sigma) I\{\|t+h\| > \Phi^{-1}_{\Sigma, 0}(0.8) \}dt \right| \\ 
-	&= \left|\int_{\mathbb{R}^d \setminus \left\{t : ||t|| =  \Phi^{-1}_{\Sigma, 0}(0.8) \right\}} \phi(t, h, \Sigma_n) I\{\|t\| > \Phi^{-1}_{\Sigma_n, 0}(0.8) \} - \phi(t, h, \Sigma) I\{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8) \}dt \right| \\
-	&\leq \int_{\mathbb{R}^d \setminus \left\{t : ||t|| =  \Phi^{-1}_{\Sigma, 0}(0.8) \right\}} |\phi(t, h, \Sigma_n) I\{\|t\| > \Phi^{-1}_{\Sigma_n, 0}(0.8) \} - \phi(t, h, \Sigma) I\{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8) \}|dt \\
-\end{align*}
-The above quantity converges to zero by the dominated convergence theorem.
-
-\begin{align*}
-	& = \int_{\|t\| > \Phi^{-1}_{\Sigma_n, 0}(0.8), \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, h, \Sigma_n) - \phi(t, h, \Sigma)|dt + \\
-	& \hspace{5em} \int_{\Phi^{-1}_{\Sigma, 0}(0.8) \geq \|t\| > \Phi^{-1}_{\Sigma_n, 0}(0.8)} |\phi(t, h, \Sigma_n)|dt + \int_{\Phi^{-1}_{\Sigma_n, 0}(0.8) \geq \|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} | \phi(t, h, \Sigma)|dt \\
-	& \leq \int_{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, h, \Sigma_n) - \phi(t, h, \Sigma)|dt + \\
-	& \hspace{5em} \int_{\Phi^{-1}_{\Sigma, 0}(0.8) \geq \|t\| > \Phi^{-1}_{\Sigma_n, 0}(0.8)} \phi(t, h, \Sigma_n)dt + \int_{\Phi^{-1}_{\Sigma_n, 0}(0.8) \geq \|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} \phi(t, h, \Sigma)dt \\
-	& = \int_{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, h, \Sigma_n) - \phi(t, h, \Sigma)|dt + \\
-	& \hspace{5em} \Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) + \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) \\
-	& = \int_{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, h, \Sigma_n) - \phi(t, h, \Sigma)|dt + \\
-	& \hspace{5em} \Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) - \left(\Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8))\right)+\\
-	& \hspace{5em} \left(\Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8))\right) +  \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) \\
-	& = \int_{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, h, \Sigma_n) - \phi(t, h, \Sigma)|dt + \\
-	& \hspace{5em} \left(\Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) \right) - \left(\Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) -  \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8))\right)+\\
-% Also, because $\Phi_{\Sigma, \mu}(t)$ has a bounded derivative, it is uniformly continuous.
-	& \hspace{5em} \left(\Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8))\right) +  \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) \\
-\end{align*}
-% \textcolor{blue}{LHS should be $|\Gamma_{\Sigma_n}(x_n) - \Gamma_{\Sigma}(x)|$}
-
-Taking the limit as $n \to \infty$ of the quantity above, we find that the first term is zero by dominated convergence theorem.
-The other four terms are also zero because of the uniform continuity of $\Phi_{\Sigma, x}$ and continuity of $\Phi^{-1}_{\Sigma, x}$
+	From Lemma \ref{lemma:dom_measure} we know that we there exists a dominating function for the probability density functions of $\hat{Z}$ and $Z$. Applying dominated convergence theorem shows that 
+	\begin{align*}
+		\text{Pr}\left(\Gamma(\hat{Z}, \hat{\Sigma}) \leq t \right) = \int I\{\Gamma(x, \hat{\Sigma}) \leq t\} \phi(x, \hat{\mu}, \hat{\Sigma}) dx \rightarrow \int I\{\Gamma(x, \Sigma) \leq t\} \phi(x, \mu, \Sigma) dx = \text{Pr}\left(\Gamma(Z, \Sigma)) \leq t \right).
+	\end{align*}
+The convergence of the distribution functions shown above and lemma 21.1 of \citep{van_der_vaart_asymptotic_2000} imply the pointwise convergence of the corresponding quantile functions.
 \end{proof}
 
-\begin{lemma}
-Under local alternatives, 
-	\begin{align*}
-		\Gamma^*_{\hat{\Sigma}}(\sqrt{n} \hat{\boldsymbol{\psi}}) \xrightarrow{d} \Gamma^*_{\Sigma}(Z + \underline{h}) 
-	\end{align*}
-\end{lemma}
-
+\subsection{Proof of Theorem \ref{thm:cnst} (Test Consistency)}
 \begin{proof}
-	It was shown in Lemma \ref{lemma:cont_of_gam} that for each norm $\|\cdot\|$, $\Gamma_{\Sigma}(x)$ is continuous with respect to $\Sigma$ and $x$.
-This finding, the continuity of the max function, and because a composition of continuous functions is also continuous it follows that
-
-	\begin{align*}
-		\Gamma^*_{\Sigma} \equiv \max\left\{\Gamma_{1, \Sigma}, \dots, \Gamma_{d, \Sigma}\right\}
-	\end{align*}
-	is also continuos with respect to $\Sigma$ and $x$.
-Under local alternatives, $\sqrt{n} \hat{\boldsymbol{\psi}} \xrightarrow{d} Z + \underline{h}$ and $\hat{\Sigma} \xrightarrow{p} \Sigma$.
-It follows from the continuous mapping theorem that $\Gamma^*_{\hat{\Sigma}}(\sqrt{n} \hat{\boldsymbol{\psi}}) \xrightarrow{d} \Gamma^*_{\Sigma}(Z + \underline{h}) $
+Let $Z \sim N\left(\boldsymbol{0}, \Sigma\right)$ and  $\hat{Z} \sim N\left(\boldsymbol{0}, \hat{\Sigma}\right)$.
+Lemma \ref{lemma:gamma_conv} and the assumptions of the theorem imply the pointwise convergence of the distribution function of $\gamestz$ denoted by $F_{\gamestz}$ to the distribution function of $\gamz$ denoted by $F_{\gamz}$ and the pointwise convergence of the quantile function of $F_{\gamestz}$ to the quantile function of $F_{\gamz}$.
+By the assumption of the theorem $F^{-1}_{\gamz}(\alpha) > 0$, so
+
+\begin{align*}
+	\text{Pr}_{P}\left(\gamestp \leq F^{-1}_{\gamestz}(\alpha)\right) &= 1 - \text{Pr}_{P}\left(\gamestp \geq F^{-1}_{\gamestz}(\alpha)\right)\\
+	& \geq 1 - \frac{E\left[|\gamestp|\right]}{F^{-1}_{\gamestz}(\alpha)} \xrightarrow{p} 1.
+\end{align*}
 \end{proof}
 
-It has now been establish that under local alternatives the distribution of our estimate converges to $\Gamma^*_{\Sigma}(Z + \underline{h})$.
-Denote the CDF of $\Gamma^*_{\Sigma}(Z + t)$ this distribution by $F_{\Sigma, t}$ and the corresponding quantile function of the distribution by $F^{-1}_{\Sigma, t}$.
-
-To prove unbiasedness at local alternatives, we show \textcolor{blue}{$>$?}
-\begin{align*}
-	F_{\Sigma, t}(F^{-1}_{\Sigma, 0}(1 - \alpha)) \geq F_{\Sigma, 0}(F^{-1}_{\Sigma, 0}(1 - \alpha)) = \alpha
-\end{align*}
-using results from the \citep{anderson_integral_1955} manuscript.
-% \textcolor{blue}{What is $\rvv^* \overset{d}{=} \rvv$ telling us?
-Don't we already know that the probabilities over both of these quantities are indexed by $Q$?
-Also, why use different notation at all?
-Why not just $\rvv^*$ for both?
-Here because $c_{0.8}$ is not random so this is distinction does not need to be made.}
-% In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\vmat(\sqrt{n}\hat{\boldsymbol{\psi}}, \|\cdot\|)$ to $\Gamma_\vmat(\rvv, \|\cdot\|).$
-
-A result of \citep{anderson_integral_1955} is that for two centrally symmetric, unimodal functions, $f_1(x)$ and  $f_2(x)$, the convolution,  
-\begin{align*}
-	g(\theta) = \int f_1(x) f_2(x - \theta)
+While $\Gamma(x, \Sigma)$ may not grow close to zero as $x$ becomes large, one can use transformations of the original $\Gamma$ to achieve this property.  
+% Note that this property is implicitly dependent on choice of norms.
+We show that the performance metrics used in this paper satisfy the satisfy conditions 1-3 in lemmas \ref{lemma:est_accept} and \ref{lemma:mult_dist_gam}.
+
+\subsection{Unbiasedness at local alternatives}
+To prove non-trivial local unbiasedness, we rely heavily on a result of \citep{eaton_multivariate_1991}.
+It states that for two centrally symmetric, unimodal functions, $f_1$ and $f_2$, the function $g : \mathbb{R}^d \mapsto \mathbb{R}$ defined by the convolution:
+	\begin{align*}
+		g(\underline{h}) = \int f_1(x) f_2(x - \underline{h})
 	\end{align*}
@@
 A function is unimodal if for every $k$, the set $\{x : f(x) \geq k\}$ is convex.
-A function $f$ on $\mathbb{R}^p$ is ray decreasing if for every $x$ in $\mathbb{R}^p$, the function $g(\beta) = f(\beta x), \beta \in \mathbb{R}$ is a decreasing function of $\beta$.
-
-For now, we will assume that.
-We assume that our tests will always be define our tests in such a way that we reject the null when $\Gamma^*_{\hat{\vmat}}(\sqrt{n} \hat{\boldsymbol{\psi}}) > c$ for some $c$.
-It is expected that $\Gamma^*_{\vmat}(x)$  increases as $x$ moves away from the origin.
-For the purposes of this proof it will be useful to define new functions
-
-\begin{align*}
-	\gi_{i, \Sigma} \equiv \left(\gi_{i, \Sigma}\right)^{-1} \text{ and } \gi_{\Sigma}^* = \min\left\{\gi_{1, \Sigma}, \dots, \gi_{d, \Sigma}\right\}
-\end{align*}
-
-that decrease as $x$ moves away from the origin.
+A function $f$ on $\mathbb{R}^p$ is ray decreasing if for every $x$ in $\mathbb{R}^p$, the function $g(\beta) = f(\beta x), \beta \in \mathbb{R}^+$ is a non-increasing function of $\beta$.
+Additional conditions are required to hold for $g(\beta)$ to be a strictly decreasing function of $\beta$.
+These conditions are shown to hold in lemma \ref{lemma:aditional_anderson_cond} for $\Gamma$ that satisfy conditions 1, 2, 4, and 5.
+
+Our testing procedure can be rewritten in using the above form, where $f_1(x)$ is $I\{\Gamma^*_{\vmat}(x) > F^{-1}_{\Gamma^*_{\vmat}(\rvv)}(\alpha)\}$, and $f_2$ is a multivariate pdf with mean $0$.
+The ray decreasing quality of $g$ can then be used to show that
+
+\begin{align*}
+	Pr_{\disto}\left(\Gamma(Z + \underline{h}, \Sigma) \leq F^{-1}_{\Gamma(\rvv, \Sigma)}(\alpha)\right) > Pr_{\disto}\left(\gamz \leq F^{-1}_{\gamz}(\alpha)\right) = \alpha
+\end{align*}
+
+Because the multivariate normal pdf is centrally symmetric and unimodal (see lemma \ref{lemma:mvtnorm_unimodality}), all that remains to be shown is that the function $(x, \Sigma) \mapsto I\{\Gamma(x, \Sigma) > F^{-1}_{\gamz}(\alpha)\}$ is unimodal and centrally symmetric.
+Lemma \ref{lemma:indct_cent_sym_unm} tells us that this indicator function is unimodal if $\Gamma$ is unimodal and centrally symmetric.
+
+In lemmas \ref{lemma:est_accept} and \ref{lemma:mult_dist_gam}, we show that the $\Gamma$ used in this article are unimodal and centrally symmetric.
+
+\subsection{Proof of Theorem \ref{thm:unbiased_locl_alt} (Non-Trivial Local Unbiasedness)}
+
+\begin{proof}
+Lemma \ref{lemma:gamma_conv} and the assumptions of the theorem imply the pointwise convergence of the distribution function of $\gamestz$ denoted by $F_{\gamestz}$ to the distribution function of $\gamz$ denoted by $F_{\gamz}$ and the pointwise convergence of the quantile function of $F_{\gamestz}$ to the quantile function of $F_{\gamz}$.
+Thus
+% Thus, letting $c_\alpha = F^{-1}_{\Gamma^*_{\vmat}(\rvv)}(\alpha)$ we find
+
+\begin{align*}
+	Pr_{\disto}\left(\gamestp \leq F^{-1}_{\gamestz}(\alpha)\right) \xrightarrow{p} Pr_{\disto}\left(\Gamma(Z + \underline{h}, \vmat) \leq F^{-1}_{\gamz}(\alpha)\right).
+\end{align*}
+
+Breaking down the quantity on the right, the only random part inside of the probability statement is $Z$.
+Define the function $g^* : \mathbb{R}^d \to \mathbb{R}$ by the quantity inside the probability statement on the right hand side of the the above display:
+
+\begin{align}
+	g(\underline{h}) = Pr_{\disto}\left(\Gamma(Z + \underline{h}, \Sigma) \leq F^{-1}_{\gamz}(\alpha)\right)  &= \int I\left\{\Gamma(x, \Sigma) \leq c_\alpha\right\} \phi(x - \underline{h}) dx \nonumber \\
+	&=  \int \left(1 - I\left\{\Gamma(x, \Sigma) \geq c_\alpha \right\}\right)\phi(x - \underline{h}) dx \nonumber\\
+	&= 1 - \int I\left\{\Gamma(x, \Sigma) \geq c_{\alpha}\right\} \phi(x - \underline{h}) dx. \label{eqn:decreasing_part}
+\end{align}
+Because $\Gamma$ is unimodal and centrally symmetric it follows from Lemma \ref{lemma:indct_cent_sym_unm} that $I\left\{\Gamma(x, \Sigma) \geq c_{\alpha}\right\}$ is also centrally symmetric and unimodal.
+Thus, the subtracted quantity in \eqref{eqn:decreasing_part} is ray decreasing with respect to $\underline{h}$ by \citep{anderson_integral_1955} and attains it maximum at $\underline{h} = 0$.
+To show that $g(\underline{h}a)$ is increasing for $a \in [0, 1]$ and $g(\underline{h}) > g(0)$ where \begin{align*}
+	g(0) = Pr_{\disto}\left(\gamz \leq F^{-1}_{\gamz}(\alpha)\right),
+\end{align*}
+The asymptotic probability of rejecting $H_0$ when $H_0$ holds.
+\end{proof}
+
+\subsection{Extension of results from $\Gamma$ to $\Gamma^*$}
+
+While theorems \ref{thm:cnst} and \ref{thm:unbiased_locl_alt} place conditions on our adaptive estimator $\Gamma^*$, it may be difficult to directly prove conditions 2-6 hold for $\Gamma^*$.
+Here we show that if conditions 2-6 hold for each $\Gamma_1, \dots, \Gamma_k$ and $\Gamma^*(x) = \max\{\Gamma_{1}(x), \dots, \Gamma_{k}(x)\}$, then conditions 2-6 also hold for $\Gamma^*$.
+
+\begin{lemma}
+	Let $\Gamma_{1}, \dots, \Gamma_{Sigma, k}$ be such that each $\Gamma_{i}$ is continuous with respect to $x$ and $\Sigma$ is non-negative, and  at least one $\Gamma_{j}$ has the property that $E\left[\Gamma_{j}(\sqrt{n}\hat{\boldsymbol{\psi}}, \hat{\Sigma})\right] \rightarrow 0$ for all fixed $P \not \in \mathcal{M}_0$.
+Then if $\Gamma(x) = \max\{\Gamma_{1}(x), \dots, \Gamma_{k}(x)\}$ satisfies conditions 2-4.
+\end{lemma}
+
+\begin{proof}
+	Because the max function is continuous and the composition of continuous functions is also continuous it follows that $\Gamma^*(x) = \max\{\Gamma_{1}(x), \dots, \Gamma_{k}(x)\}$ is also continuous.  
+	Because $\Gamma_{i}(Z) = 0$ for every $i \in \{1, \dots, k\}$, it follows that 
+	\begin{align*}
+		\text{Pr}(\Gamma^*(Z, \Sigma) = 0) = \text{Pr}\left(Z \in \bigcup_{i = 1}^k \left\{ \omega : \Gamma_{i}(\omega, \Sigma) = 0 \right\} \right) \leq \sum_{i = 1}^k \text{Pr}(\Gamma_{\Sigma, 1}(Z) = 0) = 0
+	\end{align*}
+\end{proof}
 
@@
 	\label{lemma:min_cent_sym_unm}
-	Let $\gi_1, \dots, \gi_d$ all be centrally symmetric, unimodal functions.  Then $\gi^* = \min\left\{\gi_1, \dots, \gi_d\right\}$ is also centrally symmetric and unimodal.
+	Let $\Gamma_{1}, \dots, \Gamma_{k}$ all be centrally symmetric, unimodal functions.  Then $\Gamma^* = \min\left\{\Gamma_{1}, \dots, \Gamma_{k}\right\}$ is also centrally symmetric and unimodal.
 \end{lemma}
 \begin{proof}
-Because each $\gi_i$ is a centrally symmetric and $\gi^*$ is a function of $x$ only through the $\gi_i$'s, $\gi^*$ is also centrally symmetric:
-	\begin{align*}
-	\gi^*(x) = \min\left\{\gi_1(x), \dots, \gi_d(x)\right\} = \min\left\{\gi_1(-x), \dots, \gi_d(-x)\right\} = \gi^*(-x)
-	\end{align*}
-The set $M^* \equiv \{x : \gi^*(x) \geq k\}$ contains all of the $x$ for which $\gi_i(x) \geq k$ for all $i \in \{1, \dots, d\}$.
-Thus $M^*$ is the intersection of all sets $M_i \equiv \{x : \gi_i(x) \geq k\}$.
-Each $M_i$ is convex because each $\gi_i$ is unimodal, and the intersection of a countable number of convex sets is convex.
-Thus $M^*$ is convex and $\gi^*$ is unimodal.
+Because each $\gi_i$ is a centrally symmetric and $\gi^*$ is a function of $x$ only through $\gi_i$ it follows that $\gi^*$ is also centrally symmetric:
+	\begin{align*}
+	\gi^*(x) = \min\left\{\gi_1(x), \dots, \gi_k(x)\right\} = \min\left\{\gi_1(-x), \dots, \gi_k(-x)\right\} = \gi^*(-x)
+	\end{align*}
+The set $M^* \equiv \{x : \Gamma^*(x) \geq k\}$ contains all of the $x$ for which $\Gamma \geq k$ for all $i \in \{1, \dots, d\}$.
+Thus $M^*$ is the intersection of all sets $M_i \equiv \{x : \Gamma_{i}(x) \geq k\}$.
+Each $M_i$ is convex because each $\Gamma_{i}$ is unimodal, and the intersection of a countable number of convex sets is convex.
+Thus $M^*$ is convex and $\Gamma_{\Sigma}^*$ is unimodal.
 	% \begin{align*}
@@
 	% \end{align*}
+\end{proof}
+
+\subsection*{Performance Metric Specific proofs}
+In this section, we show that both performance metrics we consider satisfy conditions 2-6.
+This requires setting conditions on the norms that index the performance metrics.
+The requirements we place on the norms are that
+\begin{itemize}
+	\item each norm obeys the triangle inequality: $\|x\|_p + \|y\|_p \geq \|x + y\|_p$ for every $x$ and $y$ in $\mathbb{R}^d$
+	\item For each $\omega \in \mathbb{R}$, the set $\left\{x : \|x\| < \omega\right\}$ is convex.
+	\item each norm has a gradient which is finite at $\psi$ for all possible values of $\psi$.
+\end{itemize}
+
+The second requirement mentioned above will allow us to bound the variance of the normed vector of parameter estimators as described in the following lemma.
+This fact will be used to prove both condition 4 ($E\left[\gamestp \right] \rightarrow 0$ for all fixed $P \not \in \mathcal{M}_0$.) for both performance metrics.
+
+\begin{lemma}
+	Let $\hat{Z} \sim N(0, \hat{\Sigma})$ with $\hat{\Sigma} \xrightarrow{p} \Sigma$ be independent of $\hat{\boldsymbol{\psi}}$ for every $n$, and $\tst \xrightarrow{p} N(0, \Sigma)$.
+If $||\cdot||_p$ has a finite derivative at $\boldsymbol{\psi}$ then
+
+	\begin{align*}
+		\text{var}\left(\left\|\hat{Z} + \sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right) \right\|_p\right) \leq M
+	\end{align*}
+	for some $M$.
+\end{lemma}
+
+\begin{proof}
+	Because of the independence of the two random variables, and the convergence in distribution of $\sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right)$, we know that
+	\begin{align*}
+		\hat{Z} + \sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right) =  \sqrt{n}\left(\hat{\boldsymbol{\psi}} + \frac{\hat{Z}}{\sqrt{n}} - \boldsymbol{\psi}\right) \xrightarrow{d} Z^* \sim N(0, \sqrt{2} \Sigma)
+	\end{align*}
+	Thus, the delta method tells us that
+	\begin{align*}
+		\|\hat{Z} + \sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right)\|_p \xrightarrow{d} \|Z^*\|_p \sim N\left(0, \nabla\|\boldsymbol{\psi}\|_p^\top \sqrt{2}\Sigma \nabla\|\boldsymbol{\psi}\|_p \right)
+	\end{align*}
+	Because the gradient of $\|\cdot\|_p$ is bounded at $ \boldsymbol{\psi}$, the variance of $\|Z^*\|_p$ will be bounded as well.
+\end{proof}
+
+\subsubsection{Estimated Acceptance Rate}
+
+\begin{lemma}
+	\label{lemma:est_accept}
+	The function $\Gamma : \mathbb{R}^d \otimes \mathbb{R}^{d \times d} \to \mathbb{R}$ defined by 
+	\begin{align*}
+		\Gamma(t, \Sigma) = Pr_\distv(\|\tilde\rvv + t\| < c_{0.8})  \text{ where }  c_{\vmat, 0.8} \equiv \min_{c}\{c : Pr_\distv(\|\tilde\rvv\| < c) \geq 0.8 \} \text{ and } \tilde\rvv \sim N(0, \Sigma)
+	\end{align*}
+	satisfies conditions 1 - 5.
+\end{lemma}
+
+\begin{proof}
+
+\textbf{Continuity:}
+Because $\Gamma$ is the integral of a function (namely the multivariate normal probability density function) that is continuous with respect to both $\Sigma$ and $x$ (see Lemma \ref{lemma:dom_measure}), it follows that $\Gamma$ is also continuous.
+
+\textbf{$\pr\left(\gamz = t\right) = 0$ for each $t$:}
+Because $Z$ and $\tilde{Z}$ are both normally distributed the probability mass functions of both random variables are positive over the entirety of $\mathbb{R}^d$.
+Considering the set of values $\left\{\omega : \|\omega\| = t\right\}$, the probability any normal random variable falls within this region is some positive value no matter what the mean of the random variable is.
+Therefore, $\pr\left(\gamz = 0\right) = 0$.
+
+\textbf{Convergence of $\Gamma_{\hat{\Sigma}}(\sqrt{n}\hat{\boldsymbol{\psi}})$ to zero under fixed alternatives:}
+\begin{align*}
+	E[|\gamestp|] &= E\left[ |\text{Pr}(\|\hat{Z} + \tst \|\leq c_\alpha) |\right]\\
+	&= E\left[E\left(I\left\{\|\hat{Z} + \tst\|_p \leq c_\alpha\right\} \right)\right]\\
+	&= E\left[I\left\{\|\hat{Z} + \sqrt{n}\hat{\boldsymbol{\psi}} \|_p \leq c_\alpha\right\} \right]  = \text{Pr}_{P}\left(\|\hat{Z} + \tst\|_p \leq c_\alpha\right) \\
+	& = \text{Pr}_{P}\left(\|\hat{Z} + \sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right) + \sqrt{n} \boldsymbol{\psi}\|_p \leq c_\alpha\right) \\
+	& \leq \text{Pr}_{P}\left(\|\sqrt{n} \boldsymbol{\psi}\|_p - \|\hat{Z} + \sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right)\|_p  \leq c_\alpha\right) \\
+	& = \text{Pr}_{P}\left(\|\sqrt{n} \boldsymbol{\psi}\|_p -  c_\alpha \leq \|\hat{Z} + \sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right)\|_p\right) \\
+	& \leq \frac{\text{var}\left(\|\hat{Z} + \sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right)\|_p \right)}{\|\sqrt{n} \boldsymbol{\psi}\|_p -  c_\alpha}\\
+\end{align*}
+Since the numerator converges to a finite value, and the denominator grows without bound, we know the fraction as a whole will converge to zero.
+
+\textbf{Central Symmetry:}
+Because the multivariate normal distribution is centrally symmetric, so is $\Gamma(t, \Sigma)$:
+
+\begin{align*}
+	\Gamma(\mu, \Sigma) = \int I\left\{\|x\|_p < c\right\} \phi_{\Sigma}(x - \mu)dx &= \int I\left\{\|x + \mu\|_p < c\right\} \phi_{\Sigma}(x))dx \\
+	&= \int I\left\{\|x + \mu\|_p < c\right\} \phi_{\Sigma}(-x))dx\\
+	&= \int I\left\{\|x\|_p < c\right\} \phi_{\Sigma}(-x - \mu))dx\\
+	&= \int I\left\{\|x\|_p < c\right\} \phi_{\Sigma}(x + \mu))dx\\
+	&= \Gamma(-\mu, \Sigma)
+\end{align*}
+
+\textbf{Unimodality: }
+First note that
+
+\begin{align*}
+	\Gamma(\mu, \Sigma) & = \int I\left\{\|x\|_p < c\right\} \phi_{\Sigma}(x - \mu)dx = \int I\left\{\|x + \mu\|_p < c\right\} \phi_{\Sigma}(x)dx = P(Z \in A_\mu) \equiv P_Z(A_\mu)
+\end{align*}
+
+Where $Z \sim N(0, \Sigma)$ and $A_\mu = \{t : \|t + \mu\| < c\}$
+
+Next consider $\mu_1, \mu_2$ such that $\Gamma(\mu_1, \Sigma) \geq k$, and $\Gamma(\mu_2, \Sigma) \geq k$.
+Because the multivariate normal pdf is log concave (Theorem 4.2.1 of \citep{tong_multivariate_2012}), we can apply theorem 1 of \citep{rinott_convexity_1976} to obtain the result that:
+\begin{align*}
+	k = k^{t}k^{1 - t} \leq \Gamma(\mu_1, \Sigma)^t \Gamma(\mu_2, \Sigma)^{1 - t} =  P_Z(A_{\mu_1})^tP_Z(A_{\mu_2})^{1 - t} \leq P_Z(tA_{\mu_1} + (1 - t) A_{\mu_2}).
+\end{align*}
+Lemma \ref{lemma:set_convexity} shows that $tA_{\mu_1} + (1 - t) A_{\mu_2} = A_{t\mu_1 + (1 - t) \mu_2}$ so it follows that
+\begin{align*}
+	P_Z(tA_{\mu_1} + (1 - t) A_{\mu_2}) = P_Z(A_{t\mu_1 + (1 - t) \mu_2}) = \Gamma_{\Sigma}(t\mu_1 + (1 - t) \mu_2)
+\end{align*}
+
+\end{proof}
+
+\textbf{Multiplicative distance performance metric}
+\textcolor{red}{Still need to show continuity and condition 3 hold for this performance metric}
+
+Consider the other measure of performance we have used:
+
+\begin{lemma}
+	\label{lemma:mult_dist_gam}
+	The function $\Gamma : \mathbb{R}^d \otimes \mathbb{R}^{d^2} \mapsto (0, \infty)$ defined by
+	\begin{align*}
+		\Gamma(t, \Sigma) = \text{min}\left\{s : \text{Pr}(\|Z + st\|_p \geq c_\alpha) \geq 0.8 \right\}
+	\end{align*}
+	satisfies conditions 1-5.
+\end{lemma}
+
+\begin{proof}
+\textbf{Continuity}
+
+\textbf{$\gamz$ has measure zero at zero.}
+	Because $c_{\alpha}$ is defined in such a way that $\text{Pr}(\|Z\|_p \geq c_\alpha) \leq 0.2 < 0.8$, and because $0 \times t = 0$ for any real-valued $t$, the probability that $\Gamma^*(Z, \Sigma) = 0$ is 0.
+
+\textbf{$E\left[|\gamestp|\right]$ converges to zero for fixed alternatives:}
+
+Consider the sequence of $s_n^* = n^{- 1/4}$
+
+\begin{align*}
+ \text{Pr}(\|\hat{Z} + s_n^{*}\tst\|_p \geq c_\alpha) &= \text{Pr}\left(\left\|\hat{Z} + n^{-1/4}\left[\sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi} + \boldsymbol{\psi}\right)\right]\right\|_p \geq c_\alpha\right)\\
+ &= \text{Pr}\left(\left\|\hat{Z} + n^{-1/4}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right) + n^{1/4}\boldsymbol{\psi}\right\|_p \geq c_\alpha\right)\\
+ &\geq \text{Pr}\left( \|n^{1/4}\boldsymbol{\psi}\|_p - \left\|\hat{Z} + n^{1/4}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right) \right\|_p \geq c_\alpha\right)\\
+ & = 1 - \text{Pr}\left( \|n^{1/4}\boldsymbol{\psi}\|_p - c_\alpha \leq \left\|\hat{Z} + n^{1/4}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right) \right\|_p \right)\\
+ & \geq 1 - \frac{\text{var}\left(\left\|\hat{Z} + n^{1/4}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right) \right\|_p\right)}{\|n^{1/4}\boldsymbol{\psi}\|_p - c_\alpha} 
+\end{align*}
+Since the denominator of the second term grows without bound, we know the above quantity will tend to 1.
+Because  $\gamestp$ takes the smallest $s$ such that $\text{Pr}(\|\hat{Z} + s\tst\|_p \geq c_\alpha) \geq 0.8$, and the chosen sequence satisfies $\text{Pr}(\|\hat{Z} + s_n^*\tst\|_p \geq c_\alpha) \rightarrow 1$ it follows that $\gamestp$ must be least as small as $s_n^*$ for large $n$.
+Thus for large $n$ it follows that $E\left[|\Gamma(\tst, \Sigma) | \right] \leq E\left[s_n^*\right]\rightarrow 0$
+
+\textbf{Central Symmetry}
+	Lemma \ref{lemma:est_accept} showed that the function $f(y) =  \text{Pr}(\|Z + y\|_p \geq c)$ is centrally symmetric and unimodal for any $c$.
+
+	Therefore, $\Gamma$ is also centrally symmetric:
+	\begin{align*}
+		\Gamma(-x, \Sigma) = \text{min}\left\{s : \text{Pr}(\|Z + -sx\|_p \geq c_\alpha) \geq 0.8 \right\} = \text{min}\left\{s : \text{Pr}(\|Z + sx\|_p \geq c_\alpha) \geq 0.8 \right\} = \Gamma(x, \Sigma)
+	\end{align*}
+
+	\textbf{Unimodality: }
+	To show unimodality, consider $\mu_1$ and $\mu_2$ such that $\Gamma(\mu_1, \Sigma)$ and $\Gamma(\mu_2, \Sigma) \geq k$.
+Let $s = \text{max}(s_1, s_2)$.
+Theorem \ref{thm:unbiased_locl_alt} and lemma \ref{lemma:est_accept} tell us that $\text{Pr}(\|Z + sx\|_p \geq c_\alpha)$ is increasing in $s$, so if $\Gamma(\mu, \Sigma) \geq k$ then $\text{Pr}(\|Z + k\mu\|_p \geq c_\alpha) \geq 0.8$.
+This means
+	\begin{align*}
+		&\text{Pr}(\|Z + k\mu_1\|_p \geq c_\alpha) \leq 0.8 \text{ and } \text{Pr}(\|Z + k\mu_2\|_p \geq c_\alpha) \leq 0.8\\
+		\text{ or equivalently }& \text{Pr}(\|Z + k\mu_1\|_p < c_\alpha) > 0.2 \text{ and } \text{Pr}(\|Z + k\mu_2\|_p < c_\alpha) > 0.2
+	\end{align*}
+	it follows from lemma \ref{lemma:est_accept} that 
+	\begin{align*}
+		&\text{Pr}(\|Z + k (t\mu_1 + (1 - t)\mu_2)\|_p < c_\alpha) > 0.2\\
+	\text{ or quivalently }	&\text{Pr}(\|Z + k (t\mu_1 + (1 - t)\mu_2)\|_p \geq c_\alpha) \leq 0.8
+	\end{align*}
+	Thus $\Gamma(t\mu_1 + (1 - t)\mu_2, \Sigma) \geq k$ as well.
+\end{proof}
+
+\subsection{Short, but important lemmas}
+
+\begin{lemma}
+	\label{lemma:mvtnorm_unimodality}
+	The multivariate normal probability density function is unimodal for all $\Sigma$.  
+\end{lemma}
+
+\begin{proof}
+	Suppose that both $\phi(\mu_1)$ and $\phi(\mu_2) \geq k$.  Because the multivariate normal probability density function is log concave \citep{tong_multivariate_2012}, it follows that 
+\begin{align*}
+	\log\left(\phi(t \mu_1 + (1 - t) \mu_2)\right) & \geq t\log\left(\phi(\mu_1)\right) + (1 - t) \log\left((\phi(\mu_2)\right)
+\end{align*}
+Also, since $e^x$ is a strictly increasing function, this would imply:
+\begin{align*}
+	\exp\left(\log\left(\phi(t \mu_1 + (1 - t) \mu_2)\right)\right) & \geq \exp \left(t\log\left(\phi(\mu_1)\right) + (1 - t) \log\left(\phi(\mu_2)\right) \right)\\
+	\phi(t \mu_1 + (1 - t) \mu_2) &\geq \phi(\mu_1)^{t} \phi(\mu_2)^{1-t}\geq k^{t}k^{1 - t} = k
+\end{align*}
 \end{proof}
@@
 
-Because each $\gi_{\Sigma, i}$ is unimodal and centrally symmetric, lemma \ref{lemma:min_cent_sym_unm} implies $\gi^*_{\Sigma, i}$ is also unimodal and centrally symmetric.
-It follows from lemma \ref{lemma:indct_cent_sym_unm} and the previous finding that $I\left\{\gi^*_Q(x) \geq c_{0.95}\right\}$ is centrally symmetric and unimodal.
-
-\begin{align*}
-	\int I\left\{\Gamma^*_Q(x) > c_{0.95}\right\} \phi(x - \mu) dx &= \int I\left\{\gi^*_Q(x) < c_{0.95}^{-1}\right\} \phi(x - \mu) dx\\
-	& = \int \left(1 - I\left\{\gi^*_Q(x) \geq c^{-1}_{0.95}\right\}\right)\phi(x - \mu) dx
-	\\
-	&= 1 - \int I\left\{\gi^*_Q(x) \geq c^{-1}_{0.95}\right\} \phi(x - \mu) dx
-\end{align*}
-Since the subtracted quantity is decreasing by \citep{anderson_integral_1955}, the quantity as a whole will be increasing.  Thus local power is obtained.
-
-While each set of performance measures will require a proof that they are centrally symmetric and unimodal, we will show that the estimate power performance measure is centrally symmetric and unimodal.
-Consider the power function.
-
-\begin{align*}
-	\Gammaf(\mu) & = \int I\left\{\|x\|_p > c\right\} \phi_{\Sigma}(x - \mu)
-\end{align*}
-
-Consider two values $\mu_1$, $\mu_2$ such that $ \Gammaf(\mu_1), \Gammaf(\mu_2) \geq k$.  Now, consider $\Gammaf\left(t\mu_1 + (1 - t)\mu_2\right)$
-
-\begin{align*}
-	\Gammaf\left(t\mu_1 + (1 - t)\mu_2\right) & = \int I\left\{\|x\|_p > c\right\} \phi_{\Sigma}(x - t\mu_1 + (1 - t)\mu_2)dx \\
-	& =  \int I\left\{\|x\|_p > c\right\} \phi_{\Sigma}(t(x - \mu_1) + (1 - t)(x - \mu_2))dx\\
-	& \geq  \int I\left\{\|x\|_p > c\right\} \left[t\phi_{\Sigma}(x - \mu_1)) + (1 - t)\phi_{\Sigma}(x - \mu_2)\right]dx \\
-	& = t \int I\left\{\|x\|_p > c\right\} \phi_{\Sigma}(x - \mu_1))dx + (1 - t) \int I\left\{\|x\|_p > c\right\} \phi_{\Sigma}(x - \mu_2)dx \\
-	& = t \Gammaf(\mu_1) + (1 - t) \Gammaf(\mu_2) \geq k	
-\end{align*}
-The inequality on the third line comes from the fact that multivariate normal pdf is concave.
-
-\sh{Proof Outline: \\
-\begin{itemize}
-	\item Under local alternatives, $\sqrt{n}\hat{\boldsymbol{\psi}} \xrightarrow{d} N(\boldsymbol{c}, \Sigma)$
-	\item With a large enough sample size, and enough MC draws, we have that for each norm: 
-    \item \textcolor{blue}{Think of Gamma as a funciton indexed by $\Sigma$ to allow it to be similar.
-Also make some assumptions about how smooth $\gi$ is with respect to this parameters.
-For any given value of the input ($t$) think about }
-	\item \textcolor{blue}{Right now we have given up on proving things for the permutation test, but we may try to do it again at some point.} The permutation test statistic will converge in distribution to a standard normal.
-This paper should help: \citep{omelka_testing_2012}
-	\item For each norm selected, \citep{gupta_inequalitites_1972} states that the power will be non-decreasing as long as the rejection region is convex (This should be true most of our rejection regions), and the probability density is decreasing away from the mean (which is true of a normal distribution).
-	\item Show that for $n$ large, the norm is selected to give the best power.  Thus since each norm obtains local power, the adaptive test will also obtain local power for $n$ large.
-\end{itemize}} 
-\begin{align*}
-	\mathcal{L}\left(\Gamma_{\hat{\vmat}}\left(\sqrt{n} \hat{\boldsymbol{\Psi}}(\boldsymbol{X})\right), \Gamma_{\vmat}\left(\sqrt{n} \hat{\boldsymbol{\Psi}}(\boldsymbol{X})\right)\right) \rightarrow 0
-\end{align*}
+\begin{lemma}
+	\label{lemma:set_convexity}
+	If the set $A$ is convex, and if $A_\mu = \{a + \mu : a \in A\}$, then the set $t A_{\mu_1} + (1 - t) A_{\mu_2} = \{b : b = ta_{\mu_1} + (1 - t)a_{\mu_2}, a_{\mu_1} \in A_{\mu_1}, a_{\mu_2} \in A_{\mu_2}\}$ is equivalent to $A_{t\mu_1 + (1 - t) \mu_2}$
+\end{lemma}
+\begin{proof}
+	Let $x \in t A_{\mu_1} + (1 - t) A_{\mu_2}$.  Therefore
+	\begin{align*}
+		x &= a_{\mu_1}t + a_{\mu_2}(1 - t) \text{ where } a_{\mu_1} \in A_{\mu_1}, a_{\mu_2} \in A_{\mu_2}\\
+		 &= (a_1 + \mu_1) t + (a_2 + \mu_2)(1 - t) \text{ where } a_1, a_2 \in A\\
+		 &= a_1 t + a_2 (1 - t) + \mu_1 t + \mu_2 (1 - t) \text{ where } a_1, a_2 \in A\\
+	\end{align*}
+	Because of the convexity of $A$ it follows that $a_1 t + a_2 (1 - t)$ and $x \in A_{\mu_1 t + \mu_2 (1 - t)}$.
+To show inclusion in the reverse direction, let $y \in A_{\mu_1 t + \mu_2 (1 - t)}$.
+Then:
+	\begin{align*}
+		y &= a + \mu_1 t + \mu_2 (1 - t) \text{ where } a \in A\\
+		 &= (a + \mu_1) t + (a + \mu_2) (1 - t) \text{ where } a \in A
+	\end{align*}
+	so $y \in t A_{\mu_1} + (1 - t) A_{\mu_2}$.
+\end{proof}
+
+\subsection*{Additional conditions for Anderson Theorem}
+In order to show a strict inequality
+
+\begin{align*}
+\int I\left\{\Gamma(x, \Sigma) \geq c_{\alpha}\right\} \phi(x - \underline{h}) dx = \int I\left\{\Gamma(x + \underline{h}, \Sigma) \geq c_{\alpha}\right\} \phi(x ) dx  < \int I\left\{\Gamma(x, \Sigma) \geq c_{\alpha}\right\} \phi(x) dx \label{eqn:decreasing_part}
+\end{align*}
+
+it must be shown that for at least one $u$, $K_u = \left\{ x : \phi(x) \geq u\right\}$ and $H_h = \left\{x : \Gamma(x + \underline{h}, \Sigma) \geq c_\alpha\right\}$ that the volume of $\left\{K_u \cap H_h \right\}$ is less than $\left\{K_u \cap H_0 \right\}$.
+
+\begin{lemma}
+	The above condition holds for all $\Gamma$ satisfying conditions 1 - 5. \label{lemma:aditional_anderson_cond}
+\end{lemma}
+
+\begin{proof}
+	Because the set $H_0$ is closed and bounded, let $x_0 \in \text{argmin}\left\{\phi(x) : x \in H_0\right\}$. 
+	Now, consider the equivalent point inside of $H_h$ which is the point $x_0 + \underline{h}$.  Comparing these two values, compare:
+	\begin{align*}
+		x_0^{\top}\Sigma^{-1}x_0 \text{ v.s.
+} (x_0 + \underline{h})^{\top}\Sigma^{-1}(x_0 + \underline{h}) = x_0^\top\Sigma^{-1}x_0 + 2 \underline{h}^{\top}\Sigma^{-1}x_0 + \underline{h}^{\top}\Sigma\underline{h}
+	\end{align*}
+	If the value of $2 \underline{h}^{\top}\Sigma^{-1}x_0$ is negative, instead consider $-x_0$.
+Because $\phi$ is centrally symmetric we now that $-x_0 \in \text{argmin}\left\{\phi(x) : x \in H_0\right\}$ as well.
+	Thus it is the case that $\phi(x_0) > \phi(x_0 + \underline{h}_0)$.
+Also, because $\phi$ is continuous, it is also true that for some $\delta$ all $x \in B(x_0 + \underline{h}, \delta) = \left\{y : |y - x_0 + \underline{h}| < \delta \right\}$ that $\phi(x) < \phi(x_0)$.
+
+	Because $H_0$ has a positive volume, we know that there exists a set of points $\left\{\omega_1, \dots, \omega_{d + 1}\right\}$ inside of $H_0$ which form a convex hull with positive volume (otherwise $H_0$ would have a volume of zero).
+Adding an additional point a convex hull can only increase its volume, so the convex hull $H^*$ of the points $\left\{x_0 + \underline{h}, \omega_1, \dots, \omega_{d + 1}\right\}$ will also be a subset of $H_0$ and have a positive volume.
+Let $L = B(x_0 + \underline{h}, \delta) \cap H^*$.
+Because $B(x_0 + \underline{h}, \delta)$ is an open set, and both sets contain $x_0 + \underline{h}$, the set $L$ will have a positive volume.
+
+	Because of how $L$ is defined, we know that the volumen of $\left\{K_{\phi(x_0)} \cap H_h \right\}$ is less the volume of $H_h$ minus the volume of $L$.
+Because the volume of $H_h$ is the same as the volume of $H_0$, it follows that the volume of $\left\{K_{\phi(x_0)} \cap H_h \right\}$ is less than $\left\{K_{\phi(x_0)} \cap H_0 \right\}$ which is equal to the volume of $H_0$
+\end{proof}
 
@@
 Simulating the test-statistic generating procedure under the null using a permutation guarantees family-wise error control.
-\bibliography{paper_bib}
+\bibliography{paper_bib.bib}
 
@@
 % Even coming up with optimal properties for tests becomes difficult since it must make assumptions about the true data-generating mechanism.
+
+\begin{align}
+& \text{for } x \in \mathbb{R}^d, \text{ and } s, l > 0, s \cdot \max({\boldsymbol{x}}) \leq g_a(\boldsymbol{x}) \leq l \cdot d \cdot \max({\boldsymbol{x}}) \label{eqn:nrm_bounds}\\
+& \text{for } s \leq 1, l \geq 1, g_a(s \cdot \boldsymbol{x}) \leq g_a(\boldsymbol{x}) \leq g_a(l \cdot \boldsymbol{x}) \label{eqn:linegrowth}
+\end{align}
+Then for all $P \not \in \mathscr{M}_0$ 
+\begin{align*}
+	Pr \left(\frac{1}{B}\sum_{k = 1}^B I\left\{\hat{T} \leq \hat{T}_k^{\#}\right\} < 0.05\right) \xrightarrow{p} 1 \text{ as } n \to \infty
+\end{align*}
+or Equivalently
+
+\begin{align*}
+Pr\left(\hat{T} \leq F^{-1}_{\hat{T}^\#}(0.05)\right) \xrightarrow{p} 1 \text{ as } n \to \infty
+\end{align*}
+
+\begin{proof}
+This proof will consist of three parts.
+We will first show that as $n \to \infty, \hat{T}_a^\#$ becomes bounded away from $0$ for any valid norm.
+Next we will show $\hat{T}_a$ converges to $0$ in probability for any valid norm.
+Last we will show the two previous findings imply theorem \ref{thm:cnst}.
+
+Let $P^\#_{\rvo}$ denote the distribution of the randomly permuted observations.
+\sh{Because $Pr(Y^{\#}_i \indep \boldsymbol{W}^\#_{i}) \to 0$, $\boldsymbol{\Psi}(P^\#_{\rvo}) = \boldsymbol{0}$.
+Additionally, $\sqrt{n}\left(\hat{\boldsymbol{\psi}}^\# -\boldsymbol{\psi}^\# \right) \xrightarrow{d} Z^\# \sim N\left(\boldsymbol{0}, \Sigma_{\text{perm}}\right)$}.
+Define $\hat{T}_a^\# = \min_s\{s : g_a(s \cdot \sqrt{n}\hat{\boldsymbol{\psi}}^\#) \geq C_{0.95, a}^\# \}$ and $C^\#_{0.95, a}$ is $F^{-1}_{Z^\#}(0.95)$.
+Since we know that $\psi^\# = \boldsymbol{0}$, it follows that $\sqrt{n}\hat{\boldsymbol{\psi}}^\# \overset{d}{\approx} Z^\#$.
+
+Now, consider:
+\begin{align*}
+	\pr\left(\hat{T}^\#_a  > \epsilon\right) &= \pr\left(g_a\left(\epsilon \cdot \sqrt{n}\hat{\boldsymbol{\psi}}^\#\right) \leq C_{0.95, a}\right)\\
+	& \geq \pr\left(\epsilon \cdot d \cdot  \max\left(\sqrt{n} \hat{\boldsymbol{\psi}}^\# \right)\leq C_{0.95, a}\right)\\
+	& = \pr\left( \max\left(\sqrt{n} \hat{\boldsymbol{\psi}}^\# \right)\leq C_{0.95, a}/(\epsilon \cdot d)\right)
+\end{align*}
+Because $\max\left(\left|\sqrt{n} \hat{\boldsymbol{\psi}}^\#\right|\right)$ converges to a well defined, positive distribution as a result of the continuous mapping theorem, for each constant $c < 1$, we know there exists an $\epsilon_c$ such that $\pr\left(\hat{T}^\#_a  > \epsilon_c\right) \geq c$.
+
+%From the definition of $C_{0.95, a}^\#$ it follows that $Pr(g_a(\sqrt{n}\hat{\boldsymbol{\psi}}^\#) \leq C^\#_{0.95, a}) \to 0.95$.
+For realizations in which $g_a(\sqrt{n}\hat{\boldsymbol{\psi}}^\#) \leq C^\#_{0.95, a}$ it must also be true that $\hat{t}^\# > 1$  from \eqref{eqn:linegrowth}.
+From the above logic it follows that $Pr(\hat{T}_a^\# > 1) \geq 0.95$ and thus $F^{-1}_{\hat{T}_a^\#}(0.05) \geq 1$ with a probability approaching 1.
+
+Now, shifting our focus to $\hat{T}_a$, under alternatives, $\boldsymbol{\psi} \neq \boldsymbol{0}$.
+Define $\psi_{\max} = \max(\psi_1, \dots, \psi_d)$.
+Using this knowledge, and \eqref{eqn:nrm_bounds}, note that
+\begin{align}
+\pr\left(\hat{T}_a < \epsilon\right) &= \pr\left(g_a\left(\epsilon \cdot \sqrt{n} \hat{\boldsymbol{\psi}}\right) \geq C_{0.95, a}\right) \nonumber\\
+&\geq \pr\left(\epsilon \cdot \sqrt{n}\max(\hat{\psi}_1, \dots, \hat{\psi}_d) \geq C_{0.95, a}\right) \nonumber \\
+&= \pr\left(\max(\hat{\psi}_1, \dots, \hat{\psi}_d) \geq C_{0.95, a}/\left(\epsilon \cdot \sqrt{n}\right)\right) \nonumber \\
+&\geq \pr\left(\max(\hat{\psi}_1, \dots, \hat{\psi}_d) \geq \psi_{\max}/2\right) \pr\left(\psi_{\max}/2\geq C_{0.95, a}/\left(\epsilon \cdot \sqrt{n}\right)\right) \label{eqn:prod_tlte} 
+\end{align}
+The first factor of the product in \eqref{eqn:prod_tlte} will converge to 1 as $n \to \infty$ from the consistency of $\hat{\boldsymbol{\psi}}$.
+The second quantity will be equal to 1 for sufficiently large $n$.
+Thus $\hat{T}_a \xrightarrow{p} 0$ under any alternative.
+
+It was shown that for each $a$ that $\hat{T}_a \xrightarrow{p} 0$.
+This means that our adaptive estimator $\hat{T} \xrightarrow{p} 0$ as well.
+Now, let $c = 0.05/k$ and $\epsilon_c$ be small enough that $\pr\left(\hat{T}^\#_a  > \epsilon_c\right) \geq 1 - (0.05/k)$.
+The permutation version of the adaptive estimator $\hat{T}^\#$ has the property that
+\begin{align*}
+	\pr\left(\hat{T}^\# < \epsilon_c\right) \leq \pr(\hat{T}^\#_1 < \epsilon_c) + \dots + \pr(\hat{T}^\#_k < \epsilon_c) \leq 0.05,
+\end{align*}
+and the conclusion of the theorem follows.
+\end{proof}
+
+\begin{align*}
+	& = \int_{\|t\| > \Phi^{-1}_{\Sigma_n, 0}(0.8), \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, h, \Sigma_n) - \phi(t, h, \Sigma)|dt + \\
+	& \hspace{5em} \int_{\Phi^{-1}_{\Sigma, 0}(0.8) \geq \|t\| > \Phi^{-1}_{\Sigma_n, 0}(0.8)} |\phi(t, h, \Sigma_n)|dt + \int_{\Phi^{-1}_{\Sigma_n, 0}(0.8) \geq \|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} | \phi(t, h, \Sigma)|dt \\
+	& \leq \int_{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, h, \Sigma_n) - \phi(t, h, \Sigma)|dt + \\
+	& \hspace{5em} \int_{\Phi^{-1}_{\Sigma, 0}(0.8) \geq \|t\| > \Phi^{-1}_{\Sigma_n, 0}(0.8)} \phi(t, h, \Sigma_n)dt + \int_{\Phi^{-1}_{\Sigma_n, 0}(0.8) \geq \|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} \phi(t, h, \Sigma)dt \\
+	& = \int_{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, h, \Sigma_n) - \phi(t, h, \Sigma)|dt + \\
+	& \hspace{5em} \Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) + \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) \\
+	& = \int_{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, h, \Sigma_n) - \phi(t, h, \Sigma)|dt + \\
+	& \hspace{5em} \Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) - \left(\Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8))\right)+\\
+	& \hspace{5em} \left(\Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8))\right) +  \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) \\
+	& = \int_{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, h, \Sigma_n) - \phi(t, h, \Sigma)|dt + \\
+	& \hspace{5em} \left(\Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) \right) - \left(\Phi_{\Sigma_n, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) -  \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8))\right)+\\
+% Also, because $\Phi_{\Sigma, \mu}(t)$ has a bounded derivative, it is uniformly continuous.
+	& \hspace{5em} \left(\Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8))\right) +  \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, h}(\Phi^{-1}_{\Sigma_n, 0}(0.8)) \\
+\end{align*}
+% \textcolor{blue}{LHS should be $|\Gamma_{\Sigma_n}(x_n) - \Gamma_{\Sigma}(x)|$}
+
+Taking the limit as $n \to \infty$ of the quantity above, we find that the first term is zero by dominated convergence theorem.
+The other four terms are also zero because of the uniform continuity of $\Phi_{\Sigma, x}$ and continuity of $\Phi^{-1}_{\Sigma, x}$
+
+The multivariate normal probability density function
+\begin{align*}
+	\phi(x, \mu, \Sigma) = \left(2\pi\right)^{-k} \text{det}\left({\Sigma}\right)^{- \frac{1}{2}} \exp\left(-\frac{1}{2} (x - \mu)^\top \Sigma^{-1}(x - \mu)\right) 
+\end{align*}
+
+is continuous with respect to both $\Sigma$ and $t$.
+
+Since the exponential function, determinate, matrix inverses, and linear operators are all differentiable, they are also all continuous.
+Because the multivariate normal pdf is the composition of continuous functions, it is also continuous.
+
+It follows that if $\mu_n \rightarrow \mu$, and $\Sigma_n \rightarrow \Sigma$, then for each $x$, $\phi(x, \mu_n, \Sigma_n) \rightarrow \phi(x, \mu, \Sigma)$.
+This result and the dominated convergence theorem imply the corresponding CDFs are also continuous.
+Note that  for $n > N_\varepsilon$ large enough, $\Sigma_n^{-1}$ will have eigen values all of which are within $\varepsilon$ of the eigen values of $\Sigma^{-1}$.
+Take $\varepsilon$  to be equal to half of the absolute value of the smallest eigenvalue of $\Sigma^{-1}$.
+Take smallest $n$ that satisfies this condition to be $N_{\varepsilon, 1}$.
+For $n \geq N_{\varepsilon, 1}$, we can bound the quantity:
+\begin{align*}
+(x - \mu)^\top \Sigma_n^{-1}(x - \mu) = (x - \mu)^\top ADA^{-1}(x - \mu) \geq \|(x - \mu)\|^2 c_{n, (1)} \geq \|(x - \mu)\|^2 \left(c_{(1)} - \varepsilon\right),
+\end{align*}
+where $c_{n, (1)}$ is the smallest eigenvalue of $\Sigma_n$
+and $c_{(1)}$ is the smallest eigenvalue of $\Sigma$
+Because the determinate is a continuous function all of the elements of $\Sigma$, we know that for $n$ large enough that $|\text{det}(\Sigma_n)^{-1/2} - \text{det}\left(\Sigma\right)^{-1/2} | < \varepsilon$.
+Take the smallest $n$ for which this inequality holds to be $N_{\varepsilon, 2}$.
+Because of the continuity of euclidean distance, we know that for $n$ large enough $\|\mu_n - \mu\|_2 \leq \varepsilon = 1/2$, and therefore,
+
+\begin{align*}
+	\left\| \|x - \mu_n\|_2 - \|x - \mu\|_2 \right\|_2  \leq \| x - \mu_n - (x - \mu)\|_2 = \|\mu - \mu_n\|_2 \leq \varepsilon
+\end{align*}
+
+For all $x$ such that $\|x - \mu\| \leq 1$, a lower bound of $0$ will be used.  For $\|x - \mu\| \geq 1$, we know that :
+
+\begin{align*}
+	\frac{1}{2} \| x - \mu \|_2 &> | \|x - \mu\|_2 - \|x - \mu_n\|_2 | \geq \|x - \mu\|_2 - \|x - \mu_n\|_2\\
+	\| x - \mu_n \|_2 &> \frac{1}{2} \|x - \mu\|_2
+\end{align*}
+
+For $n \geq \text{max}(N_{\varepsilon, 1}, N_{\varepsilon, 2})$, the pdf of $\phi(x, \mu_n, \Sigma_n)$ will be bounded above by
+
+\begin{align*}
+	\phi(x, \mu_n, \Sigma_n) &= \left(2\pi\right)^{-k} \text{det}\left({\Sigma_n}\right)^{- \frac{1}{2}} \exp\left(-\frac{1}{2} (x - \mu_n)^\top \Sigma_n^{-1}(x - \mu_n)\right)\\
+	& \leq \left(2\pi\right)^{-k} \left(\text{det}\left({\Sigma}\right)^{- \frac{1}{2}} + \varepsilon\right) \exp\left(-\frac{1}{2} (x - \mu_n)^\top \Sigma_n^{-1}(x - \mu_n)\right)\\
+	& \leq \left(2\pi\right)^{-k} \left(\text{det}\left({\Sigma}\right)^{- \frac{1}{2}} + \varepsilon\right) \exp\left(-\frac{1}{2} \|(x - \mu_n)\|_2^2 \left(c_{(1)} - \varepsilon\right)\right)\\
+\end{align*}
+	The quantity inside of the exponential will always be less than $0$.
+However, when $\|(x - \mu)\|_2 \geq 1$  this quantity will also be less than $ - \frac{1}{2} \|\frac{1}{2}(x - \mu)\|_2^2 \left(c_{(1)} - \varepsilon\right)$.
+\begin{align*}
+	& \leq \left(2\pi\right)^{-k} \left(\text{det}\left({\Sigma}\right)^{- \frac{1}{2}} + \varepsilon\right)\left[ \exp\left(-\frac{1}{2} \left\|\frac{1}{2}(x - \mu)\right\|^2 \left(c_{(1)} - \varepsilon\right)\right) + I\{\|x - \mu\|_2 \leq 1\}\right]\\
+	& = \left(\text{det}\left({\Sigma}\right)^{- \frac{1}{2}} + \varepsilon\right) \left[ \phi(x, \mu,\left(4 \left[c_{(1)} - \varepsilon\right]\right)^{-1} I_d) + I\{\|x - \mu\|_2 \leq 1\}\right] \\
+\end{align*}
+
+Let the function $\zeta(x, \mu, \Sigma)$ be defined by the last line of the above display.
+We can thus bound both measures by \textcolor{blue}{($\phi(x, \mu_n, \Sigma_n) + \phi(x, \mu, \Sigma) \leq \zeta(x, \mu, \Sigma) + \phi(x, \mu, \Sigma)$ can be used as the dominating measure):}
+
+\sh{Proof Outline: \\
+\begin{itemize}
+	\item Under local alternatives, $\sqrt{n}\hat{\boldsymbol{\psi}} \xrightarrow{d} N(\boldsymbol{c}, \Sigma)$
+	\item With a large enough sample size, and enough MC draws, we have that for each norm: 
+    \item \textcolor{blue}{Think of Gamma as a funciton indexed by $\Sigma$ to allow it to be similar.
+Also make some assumptions about how smooth $\gi$ is with respect to this parameters.
+For any given value of the input ($t$) think about }
+	\item \textcolor{blue}{Right now we have given up on proving things for the permutation test, but we may try to do it again at some point.} The permutation test statistic will converge in distribution to a standard normal.
+This paper should help: \citep{omelka_testing_2012}
+	\item For each norm selected, \citep{gupta_inequalitites_1972} states that the power will be non-decreasing as long as the rejection region is convex (This should be true most of our rejection regions), and the probability density is decreasing away from the mean (which is true of a normal distribution).
+	\item Show that for $n$ large, the norm is selected to give the best power.  Thus since each norm obtains local power, the adaptive test will also obtain local power for $n$ large.
+\end{itemize}}
+
+\begin{lemma}
+Under local alternatives, 
+	\begin{align*}
+		\Gamma^*_{\hat{\Sigma}}(\sqrt{n} \hat{\boldsymbol{\psi}}) \xrightarrow{d} \Gamma^*_{\Sigma}(Z + \underline{h}) 
+	\end{align*}
+\end{lemma}
+
+\begin{proof}
+	It was shown in Lemma \ref{lemma:cont_of_gam} that for each norm $\|\cdot\|$, $\Gamma_{\Sigma}(x)$ is continuous with respect to $\Sigma$ and $x$.
+This finding, the continuity of the max function, and because a composition of continuous functions is also continuous it follows that
+
+	\begin{align*}
+		\Gamma^*_{\Sigma} \equiv \max\left\{\Gamma_{1, \Sigma}, \dots, \Gamma_{d, \Sigma}\right\}
+	\end{align*}
+	is also continuos with respect to $\Sigma$ and $x$.
+Under local alternatives, $\sqrt{n} \hat{\boldsymbol{\psi}} \xrightarrow{d} Z + \underline{h}$ and $\hat{\Sigma} \xrightarrow{p} \Sigma$.
+It follows from the continuous mapping theorem that $\Gamma^*_{\hat{\Sigma}}(\sqrt{n} \hat{\boldsymbol{\psi}}) \xrightarrow{d} \Gamma^*_{\Sigma}(Z + \underline{h}) $
+\end{proof}
+
+\begin{align*}
+	\left|\Gamma_{\Sigma_n}(h) - \Gamma_{\Sigma}(h)\right| &= \left|Pr_{\distv_n}(\|\tilde\rvv + h\| > \Phi^{-1}_{\Sigma_n, 0}(0.8)) - Pr_{\distv}(\|\tilde\rvv + h\| > \Phi^{-1}_{\Sigma, 0}(0.8))\right|\\
+	&= \left|\int_{\mathbb{R}^d} \phi(t, 0, \Sigma_n) I\{\|t+h\| > \Phi^{-1}_{\Sigma_n, 0}(0.8) \} - \phi(t, 0, \Sigma) I\{\|t+h\| > \Phi^{-1}_{\Sigma, 0}(0.8) \}dt \right| \\ 
+	&= \left|\int_{\mathbb{R}^d \setminus \left\{t : ||t|| =  \Phi^{-1}_{\Sigma, 0}(0.8) \right\}} \phi(t, h, \Sigma_n) I\{\|t\| > \Phi^{-1}_{\Sigma_n, 0}(0.8) \} - \phi(t, h, \Sigma) I\{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8) \}dt \right| \\
+	&\leq \int_{\mathbb{R}^d \setminus \left\{t : ||t|| =  \Phi^{-1}_{\Sigma, 0}(0.8) \right\}} |\phi(t, h, \Sigma_n) I\{\|t\| > \Phi^{-1}_{\Sigma_n, 0}(0.8) \} - \phi(t, h, \Sigma) I\{\|t\| > \Phi^{-1}_{\Sigma, 0}(0.8) \}|dt \\
+\end{align*}
+
+The above quantity converges to zero by the dominated convergence theorem.
+
+It has now been establish that under local alternatives the distribution of our estimate converges to $\Gamma^*_{\Sigma}(Z + \underline{h})$.
+Denote the CDF of $\Gamma^*_{\Sigma}(Z + t)$ by $F_{\Sigma, t}$ and the corresponding quantile function of the distribution by $F^{-1}_{\Sigma, t}$.
+To prove unbiasedness at local alternatives, we show \textcolor{blue}{$>$?}
+\begin{align*}
+	F_{\Sigma, t}(F^{-1}_{\Sigma, 0}(1 - \alpha)) > F_{\Sigma, 0}(F^{-1}_{\Sigma, 0}(1 - \alpha)) = \alpha
+\end{align*}
+using results from the \citep{anderson_integral_1955} manuscript.
+% \textcolor{blue}{What is $\rvv^* \overset{d}{=} \rvv$ telling us?
+Don't we already know that the probabilities over both of these quantities are indexed by $Q$?
+Also, why use different notation at all?
+Why not just $\rvv^*$ for both?
+Here because $c_{0.8}$ is not random so this is distinction does not need to be made.}
+% In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\vmat(\sqrt{n}\hat{\boldsymbol{\psi}}, \|\cdot\|)$ to $\Gamma_\vmat(\rvv, \|\cdot\|).$
+
+For now, we will assume that.
+We assume that our tests will always be define our tests in such a way that we reject the null when $\Gamma^*_{\hat{\vmat}}(\sqrt{n} \hat{\boldsymbol{\psi}}) > c$ for some $c$.
+It is expected that $\Gamma^*_{\vmat}(x)$  increases as $x$ moves away from the origin.
+For the purposes of this proof it will be useful to define new functions
+
+\begin{align*}
+	\gi_{i, \Sigma} \equiv \left(\gi_{i, \Sigma}\right)^{-1} \text{ and } \gi_{\Sigma}^* = \min\left\{\gi_{1, \Sigma}, \dots, \gi_{d, \Sigma}\right\}
+\end{align*}
+
+that decrease as $x$ moves away from the origin.
+
+Because each $\gi_{\Sigma, i}$ is unimodal and centrally symmetric, lemma \ref{lemma:min_cent_sym_unm} implies $\gi^*_{\Sigma, i}$ is also unimodal and centrally symmetric.
+It follows from lemma \ref{lemma:indct_cent_sym_unm} and the previous finding that $I\left\{\gi^*_Q(x) \geq c_{0.95}\right\}$ is centrally symmetric and unimodal.
+
+where
+
+\begin{align*}
+	(1 - t)A_{\mu_1} + t A_{\mu_2}	&= \{a : a = t a_1 + (1 - t) a_2; a_1 \in A_{\mu_1}, a_2 \in A_{\mu_2}\}\\
+	& = \{a : a = t a_1 + (1 - t) a_2; \|a_1 + \mu_1\| \leq c, \|a_2 + \mu_2\| \leq c\}\\
+	& = \{a : a = t a_1 + (1 - t) a_2; \|a_1 + \mu_1\|t \leq ct; \|a_2 + \mu_2\|(1 - t) \leq c(1 - t)\}\\
+	& = \{a : a = t a_1 + (1 - t) a_2, \|a_1t + \mu_1t\| \leq ct, \|a_2 (1 - t) + \mu_2(1 - t) \| \leq c(1 - t)\}\\
+	& = \{a : a = b_1 + b_2; \|b_1 + \mu_1t\| \leq ct, \|b_2 + \mu_2(1 - t) \| \leq c(1 - t)\}\\
+	& \subseteq \{a : a = b_1 + b_2; \|b_1 + \mu_1t\| + \|b_2 + \mu_2(1 - t) \| \leq  ct + c(1 - t)\}\\
+	& \subseteq \{a : a = b_1 + b_2; \|b_1 + \mu_1t + b_2 + \mu_2(1 - t) \| \leq  c\}\\
+	& = \{a : a = b_1 + b_2; \|b_1 + b_2 + \mu_1t + \mu_2(1 - t) \| \leq  c\}\\
+	& = \{a : a = c; \|c  + \mu_1t + \mu_2(1 - t) \| \leq  c\}\\
+	& =  A_{\mu_1 t + \mu_2 (1 - t)}
+\end{align*}
+
+\begin{lemma}
+	\label{lemma:sym_and_unimodality}
+	The function:
+	\begin{align*}
+		\Gamma_{\Sigma}(t) = Pr_\distv(\|\tilde\rvv + t\| < c_{0.8})  \text{ where }  c_{\vmat, 0.8} \equiv \min_{c}\{c : Pr_\distv(\|\tilde\rvv\| < c) \geq 0.8 \} \text{ and } \tilde\rvv \sim N(0, \Sigma)
+	\end{align*}
+	is centrally symmetric and unimodal.    
+\end{lemma}
+
+\begin{proof}
+
+To show unimodality, first note that
+
+\end{proof}
+
+\begin{lemma}
+	\label{lemma:cons_mult_d}
+	The performance metric: 
+	\begin{align*}
+		\Gamma^*(t, \hat{\Sigma}) = \text{min}\left\{s : \text{Pr}(\|\hat{Z} + st\|_p \geq c_\alpha) \geq 0.8 \right\}
+	\end{align*}
+has the property that $\Gamma^*(\sqrt{n}\hat{\boldsymbol{\psi}}, \hat{\Sigma})\xrightarrow{p} 0$ for all fixed $P \not \in \mathcal{M}_0$	
+\end{lemma}
+
+\begin{lemma}
+	\label{lemma:sym_and_unimodality_mult_pow}
+	The function:
+	\begin{align*}
+		\Gamma^*(x, \Sigma) = \text{min}\left\{s : \text{Pr}(\|Z + sx\|_p \geq c_\alpha) \geq 0.8 \right\}
+	\end{align*}
+	is centrally symmetric and unimodal.    
+\end{lemma}
+
+% To simplify this test, replace  $\sqrt{n}\hat{\boldsymbol{\psi}}$ with $ \tst \equiv \sqrt{n}\Sigma^{-1/2}\hat{\boldsymbol{\psi}}$.
+Because $\tst$ will always converge to a standard multivariate normal regardless of which $P \in \mathscr{M}_0$ is true \textcolor{blue}{(point to proof)}, for the test defined using $\tst$:
+
+% \begin{align}
+% \label{eqn:simp_test_simp}
+% 		\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha \text{ where } r_\alpha = \min\left\{r : Pr(\|\rvt\|_2 \leq r) \geq 1 - \alpha \right\} \text{ where } \rvt \sim N(\boldsymbol{0}, \Sigma).
+% \end{align}
+
+% has the property that $r_\alpha$ will not vary between null distributions. Using this simplification, the result of this test is determined by the norm chosen and the value of the test statistic.
+% \subsection{\textcolor{blue}{Creating a rejection region using a function}}
+
+%For the example of the $\ell_2$ norm, the p-value calculation was a function of the limiting distribution $Z$ and the test statistic $\sqrt{n}\hat{\boldsymbol{\psi}}$
+% Because the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under $H_0$ is always a mean zero multivariate normal, we will index our general functions $\Gamma$ by the $d$ by $d$ variance covariance matrix instead of the infinite dimensional distribution function.
+%   Under $H_0$, the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ will be a mean zero multivariate normal distribution. 
+% any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.
+Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.
+However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.
+% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(\|\rvv\| \geq \|x\| \right)$.
+For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.
+However, for other $\Gamma$, this may not be the case.
+Consider

### 2020-05-14 figure_code/paper_scripts.R

@@ -84,10 +84,12 @@ where_are_you <- function(points, max_cut, l2_cut){
   return(col_ind)
 }
 
-make_three_plot <- function(seed){
+make_three_plot <- function(seed, p_cor = 0){
   set.seed(seed)
   par(mar = c(5, 2.5, 0, 0.5))
-  my_data <- MASS::mvrnorm(n = 100, mu = rep(0, 2), Sigma = diag(2))
+  s_mat <- diag(2)
+  s_mat[1, 2] <- s_mat[2, 1] <- p_cor
+  my_data <- MASS::mvrnorm(n = 100, mu = rep(0, 2), Sigma = s_mat)
   par(mfrow = c(1, 3))
   p_xlim <- range(my_data[, 1]) * 1.2
   p_ylim <- range(my_data[, 2]) * 1.2
@@ -138,7 +140,7 @@ make_three_plot <- function(seed){
   mtext("(B)", side = 3, line = -1, adj = 0.1, cex = 1.6, padj = 1)
   lines(max_line[, 1], max_line[, 2], col = cols[1], lwd = 4)
   lines(l_2_line[, 1], l_2_line[, 2], col = cols[5], lwd = 4)
-  my_data_2 <- MASS::mvrnorm(n = 100, mu = c(max_cutoff * 1.2, 0), Sigma = diag(2))
+  my_data_2 <- MASS::mvrnorm(n = 100, mu = c(max_cutoff * 1.2, 0), Sigma = s_mat)
 
   points(my_data_2[, 1], my_data_2[, 2], pch = 16,
          col = where_are_you(my_data_2, max_cut = max_cutoff,
@@ -151,7 +153,7 @@ make_three_plot <- function(seed){
   mtext("(C)", side = 3, line = -1, adj = 0.1, cex = 1.6, padj = 1)
   lines(max_line[, 1], max_line[, 2], col = cols[1], lwd = 4)
   lines(l_2_line[, 1], l_2_line[, 2], col = cols[5], lwd = 4)
-  my_data_3 <- MASS::mvrnorm(n = 100, mu = 1.2 * rep(l_2_cutoff/sqrt(2), 2), Sigma = diag(2))
+  my_data_3 <- MASS::mvrnorm(n = 100, mu = 1.2 * rep(l_2_cutoff/sqrt(2), 2), Sigma = s_mat)
   
   points(my_data_3[, 1], my_data_3[, 2], pch = 16,
          col = where_are_you(my_data_3, max_cut = max_cutoff,
[…]

### 2020-05-14 article_draft.tex
Changes from Alex

@@
 \usepackage[table]{xcolor}
-\usepackage{amsmath,amsthm,amsfonts,dsfont,mathtools,float,setspace, booktabs, algorithm,tcolorbox,xparse,colortbl,longtable,array,multirow,wrapfig,float,pdflscape,tabu, setspace, threeparttable,threeparttablex,makecell,natbib, pdfpages, url}
+\usepackage{amsmath,amsthm,amsfonts,dsfont,mathtools,float,setspace, booktabs, algorithm,tcolorbox,xparse,colortbl,longtable,array,multirow,wrapfig,float,pdflscape,tabu, setspace, threeparttable,threeparttablex,makecell, pdfpages, url}
+\usepackage{natbib}
 \usepackage{lineno}[displaymath, mathlines]
@@
 
-To broaden scientific understanding in a field it is typical to seek an understanding of the relationships between various observations.
+To broaden scientific understanding in many fields, including XX, it is typical to seek an understanding of the relationships between various observations.
 It is common for the set of potentially related observations to be quite large while the number of truly related observations is small.
-Thus an important first step is to find which variables are truly related to each other.
+Thus, an important first step is to find which variables are truly related to each other.
 %To discover these relationships, it is common to construct a mathematical or statistical model in which many covariates are used to predict the outcome of interest.
 Because the usefulnes of these models is dependent on the presence of an association between the outcome of interest and some number of the covariates, it is important to know if any associations exist before working to create a model.
-This initial screening step has become increasingly important as the research collect information on more and more potentially related observations.
+This initial screening step has become increasingly important as researchers collect information on more and more potentially related observations.
 
@@
 Because of the many tests this procedure could consider, it is desirable for the testing procedure to account for the potentially large number of hypotheses that are simultaneously being tested when using this approach.
-Work with \textcolor{red}{simultaneous hypothesis testing}
+Work on \textcolor{red}{simultaneous hypothesis testing}
 began with Tukey in 1953 \citep{miller_simultaneous_1981}.
-Previous work by Bonferroni was used by \citep{dunn_estimation_1959,dunn_multiple_1961} to come up with some of the first multiple hypothesis testing procedures.
-Further improvements were proposed by \citep{hochberg_sharper_1988,holm_simple_1979,s._holland_improved_1988}.
+Previous work by Bonferroni was used by \cite{dunn_estimation_1959,dunn_multiple_1961} to come up with some of the first multiple hypothesis testing procedures.
+Further improvements to these methods were proposed by various authors \citep{hochberg_sharper_1988,holm_simple_1979,s._holland_improved_1988}.
 Bonferroni-based correction procedures are easy to apply to already existing tests, while guaranteeing family-wise error control.
-However because these tests ignore the joint distribution of the test statistics, they suffer from low power, especially in cases where the probability of rejecting each hypothesis is highly correlated.
-
-Newer procedures \citep{donoho_higher_2004} and \sh{add other papers here} using modern statistical theory to provide asymptotic guarantees for their methods and to account for the correlation between parameter estimates.
-However, these methods are made for specific parameters and data generating mechanisms and do not account for the irregularity of the estimator on which their test is based.
-This irregularity can cause poor performance in scenarios in which the probablility of rejecting the null is far away from the $\alpha$ level of the test and one.
-Subsequent work \citep{mckeague_adaptive_2015, pan_powerful_2014, xu_adaptive_2016} addressed these concerns by accounting for the flexible nature of these adaptive tests.
-However these methods were still created for a specific measure of association and data generating mechanisms in mind.
-Thus while much has been done to improve the performance of tests in certain settings investigators may still use bonferroni based methods because advanced methods do not exist for their particular situation  As a result, investigators may still choose to use bonferroni correction based tests if they are interested in a different measure of association or are unsure of how deviations from the assumed data generating mechanism could effect the properties of the testing procedure.
+However because these tests ignore the joint distribution of the test statistics, they suffer from low power, especially in cases where the rejections of the various hypotheses are highly correlated.
+
+Newer procedures using modern statistical theory provide asymptotic guarantees for their methods and account for the correlation between parameter estimates\citep[e.g.,][]{donoho_higher_2004}.
+However, these methods are tailored to specific parameters and data generating mechanisms and do not account for the irregularity of the estimator upon which their test is based.
+This irregularity can cause poor performance in settings in which the null is false, but the probability of rejecting the null is far away from both the $\alpha$ level of the test and one.
+Subsequent work addressed these concerns by accounting for the flexible nature of these adaptive tests \citep{mckeague_adaptive_2015, pan_powerful_2014, xu_adaptive_2016}.
+However each of these methods was still created for a specific measure of association and class of data generating mechanisms.
+Thus while much has been done to improve the performance of tests in certain settings, investigators may still use Bonferroni based methods because advanced methods do not exist for their particular situation  As a result, investigators may still choose to use Bonferroni correction based tests if they are interested in a different measure of association or are unsure of how deviations from the assumed data generating mechanism could impact the properties of the testing procedure.
 
 In this article we propose a testing procedure that can be used for a wide variety of data generating mechanisms and parameters of interest.
-This test also achieves comparable power to tailor made procedures in some settings.
-Section \ref{sec:Working Examples} describes the data generating mechanisms and the corresponding parameters that are considered to evaluate the performance of the test and the competing test.
-Section \ref{sec:prop_test_proc} describes the testing procedure.
-Section \ref{sec:theorems} provides the theoretical guarantees of the described procedure.
-Section \ref{sec:sim_stdy} shows the performance of our testing procedure in the three considered simulation settings.
-Section \ref{sec:data_app} shows the application of our method to real world data.
-Section \ref{sec:discuss} summarizes the findings of this article and notes potential weaknesses and extensions of our procedure.
+This test also achieves comparable power to tailor made procedures in several settings \textcolor{red}{Mention the fact that the settings used were the ones people used to show off their own methods  (also end sentence with fact that our procedure is adaptive)}.
+Section \ref{sec:Working Examples} describes a variety of examples in which our method applies.
+Section \ref{sec:prop_test_proc} introduces the testing procedure.
+Section \ref{sec:theorems} provides the theoretical guarantees of the procedure.
+Section \ref{sec:sim_stdy} demonstrates the performance of our testing procedure in the three simulation settings.
+Section \ref{sec:discuss} describes potential weaknesses of our procedure and extensions to overcome them.
 
@@
 \label{sec:Working Examples}
-Throughout all examples let $\rvo_1, \dots, \rvo_n$ be independent identically distributed draws from some distribution $\disto$, and let $\boldsymbol{\rvo} = \{\rvo_1, \dots, \rvo_n\}$.
-Let $\rvo_i = \left(Y_i, W_{1 i}, \dots, W_{d i}\right), \ i \in \{1, \dots n\}$ where $Y$ is the outcome of interest, and each $W$ is a covariate.
-Let $\psi_1 = \Psi_1(\disto), \dots, \psi_a = \Psi_a(\disto)$ be measures of association between $Y$ and some combination of the $W_j$s.
-While the results found in this article are valid for any integer $a$, for the remainder of this article assume $a = d$, the number of covariates.
+In all examples, we let $\rvo_1, \dots, \rvo_n$ be independent identically distributed draws from some distribution $\disto$ and define $\boldsymbol{\rvo} = \{\rvo_1, \dots, \rvo_n\}$.
+Let $\rvo_i = \left(Y_i, W_{1 i}, \dots, W_{d i}\right)$ for $i \in \{1, \dots n\}$, where $Y$ is the outcome of interest and each $W$ is a covariate.
+Let $\psi_1 = \Psi_1(\disto), \dots, \psi_a = \Psi_a(\disto)$ be measures of association between $Y$ and some combination of the covariates.
+While the results in this article are valid for any integer $a$, for the remainder of this article we assume $a = d$, the number of covariates.
 Also in this article, let $\psi_j$ correspond to a measure of association between $Y$ and $W_j$.
-The null hypothesis for our test will be the strong null:
+We will aim to test the strong null versus the complementary alternative:
 \begin{align*}
@@
 \end{align*}
-Finally, let $\mathscr{M}$ denote the set of all possible distributions, and let $\mathscr{M}_0  \subset \mathscr{M}$ be the subset of distributions in $\mathscr{M}$ satisfying $H_0$.
+Finally, let $\mathscr{M}$ denote the set of all possible distributions that could have generated the data, and let $\mathscr{M}_0  \subset \mathscr{M}$ be the subset of distributions in $\mathscr{M}$ satisfying $H_0$.
+We note that $\mathscr{M}$ may be nonparametric, or may be restricted based on subject matter knowledge.
 We consider three different simulated data settings to study the performance of the test.
@@
 \label{sec:missing_data}
-In the second example $Y$ is binary variable and $\Delta$ is a missingness indicator.
+In the second example $Y$ is a binary variable and $\Delta$ is a missingness indicator.
 When $\Delta = 0$, $Y$ is not observed.
-The parameter of interest is the risk ratio under a poission working model for the probability that $Y = 1$.
+The parameter of interest is the risk ratio under a Poisson working model for the probability that $Y = 1$:
 \begin{align*}
@@
 \end{align*}
-The identifying assumption is $\Delta \indep Y | W$, and when this assumption holds the corresponding identifiable parameter is:
+The identifying assumption is $\Delta \indep Y | W$, and when this assumption holds the corresponding identifiable parameter is
 \begin{align*}
@@
 \end{align*}
-The data are drawn from a binomial model:
-\begin{align*}
-    \log(Pr(Y = 1 | W)) = \beta_0 + W^\top \beta.
+The data are drawn from a binomial logistic model:
+\begin{align*}
+\text{logit}(Pr(Y = 1 | W)) = \beta_0 + W^\top \beta.
 \end{align*}
@@
 
-There will be three settings considered which determine  the values of the $\beta$s in the data generating model.
-While it is not necessary for the covariates to be normally distributed, in each setting the vector $\boldsymbol{W}$ is draw from a multivariate normal with mean zero and covariance matrix $\textcolor{blue}{\Sigma_{DE2}}$ where $\Sigma_{DE2, i, j} = 1$ for $i = j$ and $0.6$ for $i \neq j$.
+There will be three settings considered which determine  the $\beta$ values of the data generating model.
+While it is not necessary for the covariates to be normally distributed, in each setting the vector $\boldsymbol{W}$ is draw from a multivariate normal with mean zero and covariance matrix $\textcolor{blue}{\Sigma_{DE2}}$ where $\Sigma_{DE2, i, j} = 1$ for $i = j$ and \textcolor{red}{(Check this $0.6$)} for $i \neq j$.
 $A$ is drawn from a binomial distribution independent from $W$.
@@
 \begin{align*}
-	\text{logit}\left[Pr(Y = 1 | w, a)\right] = \sum_{i = 1}^{d} \beta_{i} w_i
+	\text{logit}\left[Pr(Y = 1 | w, a)\right] = \sum_{i = 1}^{d} \beta_{i} w_i.
 \end{align*}
@@
 In the last setting, $\beta_1, \dots, \beta_5 = 1$, $\beta_6, \dots, \beta_{10} = -1$ and $\beta_{11}, \dots, \beta_d = 0$.
-Data are generated using all three settings with every possible combination of sample size ($n = 5,000$, or $10,000$), and dimension ($d = 10, 50, 100, 150$, or $200$).
+Data are generated using all three settings with every possible combination of sample size ($n = 5000$, or $10000$), and dimension ($d = 10, 50, 100, 150$, or $200$).
 
@@
 \end{align}
-in which our parameter of interest is:
-\begin{align*}
-(\beta_0^*, \beta_1^*, \beta_2^*, \beta_3^*) = \text{argmin}_{\beta_0, \beta_1, \beta_2, \beta_3}\int\left\{\text{logit}\left[Pr\left(Y^{(a)} = 1 | w\right)\right] - (\beta_0 + \beta_1 a + \beta_2w_j + \beta_3 w_j a) \right\}^2 dP(w, a)
+in which our parameter of interest is the following projection of $P$ onto this working model:
+\begin{align*}
+(\beta_0^*, \beta_1^*, \beta_2^*, \beta_3^*) = \text{argmin}_{\beta_0, \beta_1, \beta_2, \beta_3}\int\left\{\text{logit}\left[Pr\left(Y^{(a)} = 1 | w\right)\right] - (\beta_0 + \beta_1 a + \beta_2w_j + \beta_3 w_j a) \right\}^2 dP(w, a).
 \end{align*}
@@
 In the final setting $\gamma_{1}, \dots, \gamma_{5} = 0.15$, $\gamma_{6}, \dots, \gamma_{10} = -0.15$, and $\gamma_{11}, \dots, \gamma_{d} = 0$.
-Data are generated using all three settings with every possible combination of sample size ($n = 1,000$, or $2,000$), and dimension ($d = 10, 30$, or $75$).
+Data are generated using all three settings with every possible combination of sample size ($n = 1000$, or $2000$), and dimension ($d = 10, 30$, or $75$).
 
@@
 For some test statistic $\tst$, any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by checking if $\tst$ falls within acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$.
-Letting $\tst \xrightarrow{P_0} \rvv \sim \distv(\disto)$ for any $P_0 \in \mathscr{M}_0$, the region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
+Letting $\tst \xrightarrow{P} \rvv \sim \distv(\disto)$ whenever $P \in \mathscr{M}_0$, the region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
 \begin{align}
-  Pr_{\distv}\{\rvv \not \in \Theta_0(P)\} = 1 - \alpha \text{ for every } P \in \mathscr{M}_0.\label{eqn:alpha_rej}
+  Pr_{\distv(P)}\{\rvv \not \in \Theta_0(P)\} = 1 - \alpha \text{ for every } P \in \mathscr{M}_0.\label{eqn:alpha_rej}
 \end{align}
+Hereafter, when it will not cause confusion, $\distv(P)$ will be written as $\distv$.
 While there are many regions satisfying \eqref{eqn:alpha_rej},  we focus for now on a particular class of regions defined using $\ell_p$ norms which will naturally lead to a straightforward testing procedure.
-For simplicity, first consider regions defined using an $\ell_2$ norm:
+For simplicity, we start by considering regions defined using an $\ell_2$ norm:
 \begin{align}
@@
 \label{eqn:simp_test}
-	\text{reject } H_0 \text{ if } \|\rnp\|_2 \geq r_\alpha(P_0),
+	\text{reject } H_0 \text{ if } \|\rnp\|_2 \geq r_\alpha(P),
 \end{align} 
@@
 
-Considering the $\Gamma$ for which it is possible to compare across norms, we can now define a new, adaptive $\Gamma^*$ which is the pointwise maximum of all of the considered $\Gamma$s.
-First define $\Gamma_{1}(x, \Sigma), \dots, \Gamma_{p}(x, \Sigma)$ as collection of performance metrics which only differ by the norm used in their definition.
-Next, define
 % by defining a $\Gamma$ to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.
@@
 
-\section{Data Application}
-\label{sec:data_app}
-\sh{Data from Peter Gilbert}
+% \section{Data Application}
+% \label{sec:data_app}
+% \sh{Data from Peter Gilbert}
 
@@
 \label{sec:discuss}
-When developing anything there is frequently a trade off to between generalizability and performance.
-However the reduction in power of bonferroni-based methods compared to taylor made procedures is often larger than is needed.
-We have developed a generalizable testing procedure that still can outperform bonferroni based methods.
+%When developing anything there is frequently a trade off to between generalizability and performance.
+However the reduction in power of Bonferroni-based methods compared to taylor made procedures is often larger than is needed.
+We have developed a generalizable testing procedure that still can outperform Bonferroni based methods.
 We have demonstrated this in section \ref{sec:sim_stdy} and shown novel settings in which the method can also be performed.
@@
 
-Our procedure does rely on asymptotic results to achieve correct type one error rates which can cause issues when the number of covariates of interest is larger than sample size.
-To address this issue, in certain cases a our test can be carried out using permutations of the data to obtain better finite sample properties.
+The general hypothesis testing procedure that we have described relies on asymptotic results to achieve correct type one error rates.
+This can cause issues when the number of covariates of interest is larger than the sample size.
+To address this issue, in certain cases our test can be carried out using permutations of the data to obtain better finite sample properties.
+
 %\textcolor{blue}{This is done by repeating our estimation procedure many times after randomly permuting the outcome variable.
@@
 
-While we have outlined some of the ways in which our method can be used, there are other possible applications and improvements.
+% While we have outlined some of the ways in which our method can be used, there are other possible applications and improvements.
 
@@
 However, this estimator runs into issues when $p > n$ and $\hat{\Sigma}^{-1/2}$ becomes impossible to estimate because of the rank deficiency of the variance estimator.
-While this problem still technically exist when indexing our $\Gamma$s by $\hat{\Sigma}$, using a multiplier bootstrap to take draws from $N(0, \hat{\Sigma})$ avoids the computation issues of having a degenerate estimate of the limiting distributions variance matrix.
+While this problem still technically exists when indexing our $\Gamma$s by $\hat{\Sigma}$, using a multiplier bootstrap to take draws from $N(0, \hat{\Sigma})$ avoids the computation issues of having a degenerate estimate of the limiting distributions variance matrix.
 
@@
 
-While changing the test statistic as described above has major hurdles to overcome to be implemented in $p > n$ settings, there are other extensions or generalizations of our procedure that are possible without much change.
-While we considered one set of $\Gamma$ funcitons in this article, any set of reasonable $\Gamma$ functions could be used.
-These $\Gamma$ functions could even be picked by machine learning methods used for classification.
+%While changing the test statistic as described above has major hurdles to overcome to be implemented in $p > n$ settings, there are other extensions or generalizations of our procedure that are possible without much change.
+While we considered one set of $\Gamma$ functions in this article, any set of reasonable $\Gamma$ functions could be used.
+%These functions could even be picked by machine learning methods used for classification.
 The classifier would provide a probability that any observation was generated from the null distribution.
@@
 These probabilities could be estimated by taking many draws from a normal with mean $\sqrt{n}\hat{\boldsymbol{\psi}}$ and variance $\hat{\Sigma}$ and finding the optimal norm for each of these draws.
-This method while being more computationally costly, could potentially be shown theoretically to be optimal in the sense that it would maximize the average power of all tests based on the specified family of norms for each local alternative.
-
-While $\ell_p$ norms were used throughout this paper, one issue observed with our test is that it selects the $\ell_2$ norm more frequently than it should, likely because of the many small estimates for parameters that are not associated with the outcome.
+%This method while being more computationally costly, could potentially be shown theoretically to be optimal in the sense that it would maximize the average power of all tests based on the specified family of norms for each local alternative.
+
+% While $\ell_p$ norms were used throughout this paper, one issue observed with our test is that it selects the $\ell_2$ norm more frequently than it should, likely because of the many small estimates for parameters that are not associated with the outcome.
 One could consider a slightly modified norm that sets to zero all component values of the vector that are less than some value.
@@
 
-\textcolor{blue}{add notes about limitation of our method (need to find influence function).  Also discuss difficulty with convergence when using the parametric bootstrap.}
-
-In this article chose tests in which each parameter corresponded to a single covariate, and each covariate only had a single corresponding parameter.
+\textcolor{blue}{add notes about limitation of our method (need to find influence function).
+Add notes of computeraization.
+Also discuss difficulty with convergence when using the parametric bootstrap.}
+
+% In this article chose tests in which each parameter corresponded to a single covariate, and each covariate only had a single corresponding parameter.
 However it would also be possible to have tests where each parameter corresponded to a set of many covariates or each covariate or group of covariates had multiple measures of association.
@@
 	\end{align*}
-	is also continuos with respect to $\Sigma$ and $x$.
+	is also continuous with respect to $\Sigma$ and $x$.
 Under local alternatives, $\sqrt{n} \hat{\boldsymbol{\psi}} \xrightarrow{d} Z + \underline{h}$ and $\hat{\Sigma} \xrightarrow{p} \Sigma$.
